### 2016-11-07 manuscript_3.tex
current manuscript import

\documentclass[11pt]{article}                     
\usepackage{graphicx}
\usepackage[section]{placeins}
\usepackage{color}
\usepackage{lineno}
\linenumbers
%
% \usepackage{mathptmx}      % use Times fonts if available on your TeX system
%
% insert here the call for the packages your document requires
%\usepackage{latexsym}
% etc.
%
% please place your own definitions here and don't use \def but
% \newcommand{}{}
%
% Insert the name of "your journal" with
% \journalname{myjournal}
%
\begin{document}

\title{A game-theory modeling approach to utility
  and strength of interactions dynamics in biomedical research social networks}
%\title{Two games modeling approach to collaboration dynamics in biomedical
%research social networks}

%\thanks{Grants or other notes
%about the article that should go on the front page should be
%placed here. General acknowledgments should be placed at the end of the article.}

%\subtitle{Do you have a subtitle?\\ If so, write it here}

%\titlerunning{Fitness \& trust in biomedical research networks}

%\titlerunning{Short form of title}        % if too long for running head

\author{J. Mario Siqueiros-Garc\'ia         \and      Rodrigo Garc\'ia-Herrera \and         Enrique Hern\'andez-Lemus \and
        Sergio A. Alcal\'a-Corona  %etc.
}

%\authorrunning{Short form of author list} % if too long for running head

%% \institute{J. Mario Siqueiros-Garc\'ia \at
%%   IIMAS-UNAM. Circuito Escolar 3000, Cd Universitaria, Coyoacán, Ciudad de México, D.F. \\
%%               Tel.: +123-45-678910\\
%%               Fax: +123-45-678910\\
%%               \email{jmario.siqueiros@iimas.unam.mx}           %  \\
%% %             \emph{Present address:} of F. Author  %  if needed
%%               \and
%%               Rodrigo Garc\'ia-Herrera,\\ Enrique Hern\'andez-Lemus, \\ Sergio A. Alcal\'a-Corona \at
%%               National Institute of Genomic Medicine\\
%%               Perif\'erico Sur 4809, Arenal Tepepan, Tlalpan, 14610, \\
%%               Ciudad de M\'exico, D.F., M\'exico  
%%            %% S. Author \at
%%            %%    second address
%% }

\date{\today}
% The correct dates will be entered by the editor

\maketitle

\begin{abstract}

What would happen if researchers in a community were given the same amount of
resources and then set free to interact among each other? How would these
resources be distributed in the population after many interactions? The final
result may be determined by the researchers'social and political power, an by
her or his prestige. Nevertheless, all these attributes depend, to a 
certain degree, on the research collaboration social network in which scientists
are embedded. Here we develop a model based on the Prisoner's Dilemma
implemented on a collaboration network. With this model we explore the
distribution of resources and the dynamics of the strengthening or weakening of collaboration
connections among partners, as scientists cooperate or
defect in order to gain access to others resources. The network is based on data
about projects that were awarded with a grant. In this sense, we assume that
resources are funds, equipment and time. Fitness, as we define it here
represents how much access does a researcher has over the resources of its collegues.  
We tested our simulation on the real biomedical research network and compared
the results with an Erd\"{o}s-Reny\'i, a Watts-Strogatz small-world
and Barab\'asi-Albert topologies. Different topologies display different fitness
and connections strength distributions. Moreover, the distribution of fitness
and connections strength in the researchers network is similar to that of Barab\'asi-Albert 
and Watts-Strogatz topologies, respectively. We believe that fitness
distribution in the researchers network suggests that there are socio-cultural
mechanisms governing the network that produces asymmetric distribution to
resources. Nevertheless, the high distribution of strong connections might reflect some sort of
subordination among researchers by which they are morally obliged to cooperate
by the same socio-cultural mechanisms. The range around the threshold that
regulates the decision to cooperate or defect according to the agent's
historical balance between utility and strength of collaborative relationships and carring
capacity of the system is small, suggesting that there is a region in which a
phase transition takes place from a population of cooperators to a population of
defectors. Simulations like this may help to develop science policies to promote
fair distribution of resources.

\end{abstract}

\section{Introduction}
\label{intro}

\textbf{Notes:}

\begin{itemize}

%% \item In this paper there are two games played simultaneously: One for
%% maximazing individual utility; the second for maximazing the connection
%% strength. We are interested in how they affect eachother in the context of a
%% network of collaboration.

\item We change utility for fitness. Utility seems a better concept in order to
  reflect players' preferences.

%% \item In the context of our paper, utility represents
%%   the preference for having access to the resources of others. Maximazing
%%   utility means that the player is increasing its access to the resources of
%%   other players.  Utility function is just the sum of the payoffs of playing
%%   with its neighbors. As for the payoff matrix, the best strategy for a player
%%   is to defect. Any other option will not be an optimal payoff. The opossing
%%   force is in the other game. The game for maximazing the strength of the
%%   connection among players. In this case defecting or cooperating? is the best
%%   strategy as it pays the most when coordinating regardeless they both cooperate
%%   or defect, this is because when both cooperate the interaction gets a positive
%%   payoff, when both defect, the interaction doesn't get affected; but if they
%%   anti-coordinate, then the interaction looses. In this sense, this might be a
%%   game were there are multiple (i.e., 2 points or strategies) equilibria. It
%%   seems that there is no single dominant strategy.}\\

\item Choosing a strategy depends on the balance $\eta'$ equation --look at page
  9. This
  equation states that the probability of an agent to cooperate increases as: a)
  its utility increases --as it moves away from 0, or; b) The strength of the
  connection with its peers increases --as it moves away from 0, or; c) both
  increases.

  $\eta_i = \frac{\langle f_i \rangle + \langle w_{ij} \rangle _j}{2}$\\

\item{En la pagina 9 decimos que ``In order for the agent to choose to cooperate
  or defect, a degree of willingness to cooperate is assigned to each agent.'' No estoy
  seguro que ``degree of willingness to cooperate'' sea la mejor manera de
  decirlo, mi duda está en la palabra ``degree'', por lo que cambi\'e la
  oraci\'on a: The probability for an agent to cooperate or defect depends on a
number that referes to a historical balance between average utility and the average strength of
the connections with its neigbors. }

\end{itemize}

Collaboration has become a corner stone in biomedical research today.
In contrast to physics which has a long history and experience in collaborative
projects, biology has only recently become an evermore collaborative
discipline\cite{Vermeulen2013}. Biology has an interesting record in such
matters because scientific collaboration means something different to
different branches of biology: molecular biology has traditionally been a
research activity of small laboratories\cite{KnorrCetina1999,Strasser2006},
whereas in natural history there has been data and samples exchange since the
$XVII^{th}$ century\cite{Muller2012,Strasser2012}.\\

Despite the differences in culture and practices, the Human Genome
Project made collaboration a central feature of biology. Nowadays it
is widely acknowledged that collaboration takes many forms, from
biological samples and biobanking to international groups in charge of
helping the bio-research communities to harmonize and share their
data. Collaboration in science may take many forms, nevertheless, sharing
resources such as equipment, funds, and time are critical; also, building
trust among scientists is fundamental. What is more important, resources are
mobilized in order to create strategic alliances.\\

The analysis of cooperation in scientific research has been the subject of a
number of studies
\cite{Vermeulen2013,Newman2001,Newman2004,Elango2012,HernandezLemus2013,Strasser2006,Strasser2012}. This
is not surprising since cooperation and competition are quite important in
today's academic success. How do collaboration happens within a competitive
academic environment and what kind of payoff is present in these settings were
questions considered recently by Wardil and Hauert \cite{Wardil2015} in the
context of cooperation in multi-authored publications. Also, the role of game
theory over complex scientific information and collaboration networks has
attracted attention, mainly focusing on how long-term strategies may shape
different scenarios for Nash equilibria \cite{hanauske2012}. Prisoner's Dilemma
has been used in the study of impact factor and collaboration
\cite{Hara_etal_2002,Lieberman_etal_2005}. \\

In spite of all these research efforts, cooperation in the context of scientific
collaboration is still loosely defined and the long time dynamics of academic
cooperation (and its consequences) are yet to be fully elucidated. Furthermore,
to our current knowledge, we are not aware of the use of game theory and
the complex network analysis for understanding how the topology of scientific collaboration networks
affects access to resources among individuals present in the network \footnote{For
  an account of scientific collaboration and definitions, please refer to
  \cite{Sonnenwald2007}.}. In this context our work aims to contribute to
further our current understanding on the matte, specially when agents have to
maximize their acces to resources while they need to take care of their collaboration links.\\

  %% nevertheless
  %% and to a certain degree, the idea behind the model is ethnographically
  %% inspired\footnote{For a mixed methodology approach to scientific
  %%   collaboration refer to Hara et al., 2002 \cite{Hara_etal_2002}.}. In
  %% previous work we observed that members of biomedical research groups interact
  %% strongly with each other but interactions between groups are only
  %% superficial. Our ethnographic work also allowed us to see how difficult is for
  %% Principal Investigators to collaborate with peer groups that are considered
  %% somehow equal in terms of different criteria such a productivity or power. On
  %% the other hand, collaboration may be easier with groups that are far beyond in
  %% some of these terms. This seems to be so because when dealing with a smaller
  %% group, the stronger one can establish conditions of collaboration; when the
  %% group is weaker, there might be a lot to win. For example, this latter
  %% situation can be seen when local groups collaborate with research groups form
  %% overseas, specially from the US.}\\

%% {\color{red}The question behind our model rests on three premises: Scientist
%%   have self-interests and may act seeking their own interests; Scientific
%%   collaboration needs researchers to cooperate and build relationships that can
%%   last; Scientific collaboration networks have a particular topology. Under such
%%   context, if the same amount of resources were given to every researcher at the
%%   same point in time, how would the access to resources be distributed, in the
%%   long run, in a population of interacting researchers that seek to improve
%%   their profits but at the same time have to invest in building trustworthy
%%   relationships with their colleagues?}
%%\\

  %% Seen from a different point of view, how would trust be
  %% distributed in a population of researchers that are mainly interested in
  %% improving their profits, even when acting selfishly always could have a
  %% negative impact on that primary objective?}\\

 {\color{red}In this article we explore the network effect on the distribution
   of players having access to certain amount of resources from other players in the
   network and the distribution of the strength of connections among
   them. Particularly, we implemented two games played simultaneously: 
   one for maximazing individual utility based on the iterated Prisoner's
   dilemma; the other, a coordination game for maximazing the connection strength between
   players. We are interested in how they affect each other in 
   the context of a network of scientific collaboration under the idea that while
   researchers are interested in maximazing their utilities, they also know that
   it is important to invest in building collaborative relationships. These two
   behaviors are explored in a biomedical research community of M\'exico.}\\

{\color{red}In the context of our paper, utility represents
  the preference for having access to the resources of others. Maximazing
  utility means that the player is increasing its access to the resources of
  other players.  Utility function is the sum of the payoffs of playing
  with its neighbors. The opossing force is in the other game. The game for
  maximazing the strength of the connection among players. In this case
  coordinating is the best strategy as it pays the most when
  coordinating regardeless they both cooperate or defect, this is because when
  both cooperate the interaction gets a positive payoff, when both defect, the
  interaction doesn't get affected; but if they anti-coordinate, then the
  interaction looses. Finally, cooperation is a central feature in science
  doing. For our biomedical network, cooperation can be metaphorically thought
  as sharing resources such as time, students, equipment, even money. Defection
  to a cooperator may also have some examples, such as ghost authorship or
  prestige authorship, or even a part of a working strategy in which a some
  members of a team do the work at certain moment, and then the other part of
  the team will do its part in some other moment in the future --some sort of
  reciprocity. }\\

The manuscript is structured in five sections. The following describes
\textit{FOSISS}, the main program for grants destined for biomedical applied
research in M\'exico. This description is important because that is the source
of our database for creating the researchers collaboration network. Next we
describe our model, and then, in the following section we introduce the
different network topologies on which we explored the model. In the fourth
section we present  our results and discuss them briefly. In the fifth section
we draw some final remarks and conclusions.

%Our main objective is to achieve a better understanding of the role of network
%topology on scientific collaborative social dynamics. The dynamics of the
%system are explored following the distribution of utility -as a proxy for
%resources- and trust as agents on the network play the Prisoner's Dilemma while
%constrained by trust with their neighbors.\\

%% In order to explore these questions we implemented a game theory simulation on a
%% real social network of biomedical researchers from M\'exico. Game theoretical
%% approaches to cooperation have – of course– been studied for decades. Taking
%% into account the nature of social interaction among players by means of an
%% underlying social network is also an explored topic. Some 10 years ago, Lo and
%% colleagues \cite{Lo2004} formulated a minority game model to connected
%% population within a network and studied the role of connectivity on such
%% games. Later on, Buesser and Tomassini \cite{Buesser2012} studied the dynamics
%% of cooperation for players located on a spatially embedded network in order to
%% categorize the effect that different interaction structures may have in
%% maintaining cooperation (or defection) domains.\\

%% The impact that network topology may have in the robustness of cooperation was
%% investigated in numerical experiments and simulations \cite{Ichinose2013}
%% revealing that clusters of cooperating agents become robust by increasing the
%% number of links to cooperators, with the possible implication that a large
%% number of individuals is required to maintain global cooperation patterns.\\

%% Regarding possible strategies to improve cooperation patterns, several mechanisms such as inequity aversion
%% \cite{Ahmed2014}, social imitation and strategic choice \cite{Vilone2014} have been explored. Inequity aversion is the
%% condition in which individuals care about payoff equality in the outcomes. A kind of moral memory in past outcomes
%% implies that inequity aversion promotes cooperation \cite{Ahmed2014}. Social imitation contrasts with strategic choices
%% in such a way that social influence models may impact on background rationality in decision making. This balance may be
%% behind moody conditional cooperation within a social environment \cite{Vilone2014}.\\

%% The analysis of cooperation in scientific research has been also the subject of a number of studies. This is not
%% surprising since cooperation and competitionare quite important in today’s academic success. How do collaboration 
%% happens within a competitive academic environment and what kind of payoff
%% is present in these settings were questions considered recently by Wardil and
%% Hauert \cite{Wardil2015} in the context of cooperation in multi-authored
%% publications. Also, the role of game theory over complex scientific information 
%% and collaboration networks has attracted attention, mainly focusing on how
%% long-term strategies may shape different scenarios for Nash equilibria \cite{hanauske2012}. \\

%% In spite of all these research efforts, cooperation in the context of scientific
%% collaboration is still loosely defined and the long time dynamics of academic
%% cooperation (and its consequences) are yet to be fully elucidated. Furhtermore,
%% to our current knowledge, we are not aware of any work on how the topology of
%% scientific collaboration networks affects the differences of access among
%% individuals to resources present on the network \footnote{For
%%   an account of scientific collaboration and definitions, please refer to
%%   \cite{Sonnenwald2007}.}. In this context our work aims to contribute to
%% further our current understanding on the matter.\\

%% As has been pointed by others, social research on scientific
%% collaboration is mostly about physics and space research\cite{Vermeulen2013}.
%% Collaboration in biology has been studied to a lesser degree
%% \cite{Newman2001,Newman2004,Elango2012,HernandezLemus2013,Strasser2006,Strasser2012}. The
%% use of game theory, and specifically the Prsioner's Dilemma to understand social
%% dynamics in scientific collaboration can be found at 
%% \cite{Hara_etal_2002,Lieberman_etal_2005}.\\

%% The manuscript is structured in five sections. The following describes \textit{FOSISS}, the main program for grants
%% destined for biomedical applied research in M\'exico. This description is important because that is the source of our
%% database for creating the researchers collaboration network. Next we describe our model, and then, in the following
%% section we introduce the different network topologies on which we explored the model. In the fourth section we present
%% our results and discuss them briefly. In the fifth section we draw some final remarks and conclusions.

\section{Biomedical research: CONACyT and FOSISS}
\label{sec:1}

CONACyT (National Council of Science and Technology) is the Mexican government
entity in charge of promoting the development of science and 
technology. It is also in charge of creating the country's scientific
policies.  Among CONACyT's functions are to develop science and technology
policies according to national needs and demands, to advise the different
instances of government on scientific and technological topics, to promote the
creation of research networks among the scientific community, to grant
scholarships for masters and doctoral studies, and to manage different trusts 
intended to fund individuals and groups for scientific and
technological research.\\

In the year 2002 CONACyT, along with other government agencies and
entities, created sectoral funds which are trusts for scientific and
technological research.The objective of such funds is to cover and equally
promote the research capacities of different areas such as energy, agriculture,
or technological innovation by means of the generation of human resources
and helping research groups to consolidate. It is expected that the
knowledge generated under the sponsorship of these funds
will be the product of applied research that attends national public
needs, and promotes economic growth.\\

\emph{FOSISS} or Sectoral Fund for Health and Social Security Research
(\emph{Fondo Sectorial en Investigaci\'on en Salud y Seguridad Social}) is among
such funds. FOSISS is constituted by CONACyT, SSA, IMSS and ISSSTE,\footnote{SSA
  is the acronym for Secretariat of Health \emph{Secretar\'ia de Salud}; IMSS is
  the acronym for Social Security Mexican Institute (\emph{Instituto Mexicano
    del Seguro Social}); ISSSTE stands for Institute for Social Security and
  Services for State Workers (\emph{Instituto de Seguridad y Servicios Sociales
    de los Trabajadores del Estado})} being all of them the major public health
providers and research institutions in the country. Every year CONACyT opens a
call for funds limited to a set of health research areas previously defined by a
group of experts. Such areas range from public health issues to chronic and
degenerative diseases.\\

Eligibility is open to the public and private health research sectors,
nevertheless, most applicants are public universities and research
institutions. Up to the year of 2013, there were 91 institutions funded that
comprised 4988 researchers.\\

From these data some important considerations should be made clear. The
population represented in the data include principal investigators (PIs),
associate researchers, postdoctoral associates, under and postgraduate
students. Unfortunately, this information is not specified in the
database. Still, this is something we acknowledge and it's important because
researchers in our network are under different circumstances and we know
that this diversity has a real impact on the structure and eventually on the
dynamics of the network, as well as on the results of our model.\\

Our database includes different information about the projects. It includes the
name of the project, the year it was approved for funding, and the research area
to which it was assigned. It also specifies the names of PIs or the person who
was responsible of a project, the names of those who have been collaborators,
some PIs have also been collaborators of a different project. The institutional
affiliation of all participants can be found too. This is important because
knowing the affiliation of the researcher we also know the principal institution
behind every project.\\

Though, cleaning and analysis work of the database is still ongoing, some
relevant facts about the biomedical research can be said. Over the period of 12
years, 32 general research areas have been defined, the three most funded
research areas are \emph{chronic and degenerative diseases}, \emph{malignant
  neoplasms}, and \emph{infectious and parasitic diseases}. The least funded
area is \emph{Ethics and medicine}. But the areas with more researchers is
\emph{malignant neoplasms}. Other areas of relevance for M\'exico are
\emph{diseases related to poverty} and \emph{Health and vulnerable groups}. \\

From the institutions that have participated in a protocol funded by FOSISS,
less than one fifth has been responsible for a project and more than 95\% of
them are Mexican, public institutions. There is also an important presence of
foreign institutions as collaborators, most of them from the United States,
though institutions from the UK, France, Spain, Netherlands, Colombia and Cuba
are also in the database.\\

Besides the characteristics of the population there are some other boundary
conditions that play an important role on the network topology and dynamics,
that motivated the development of our model. Biomedical research in M\'exico
constitutes a vibrant community and collaboration is part of everyday
work. Nevertheless, M\'exico does not have public biobanks for research purposes
(which are specially relevant for research in genomics, for example), there is
no regulation on the access to biological samples such as tissue, cells, DNA,
RNA, etc.\footnote{Regulation exists regarding researcher-subject relations
  based on legal and ethical grounds. Also, all projects need to be approved by
  the Ethics Committee and IRB.} Something similar happens with data. There have
been some attempts to create open data repositories for biomedical research, but
they have not been established yet. Regulation on these subjects is still
missing. Finally, technology (e.g., PCR, sequencing and expression profiling
technology) is in the domain of the institutions with the highest research
profiles and sometimes PIs see technology as a personal good.\\

From our brief ethnographic work to date, we have been able to see that
biological samples, data and technology can become instruments for negotiating
collaboration. For example, among people involved in research projects, there
are researchers that do not have direct access to samples, simply because their
institution does not offer clinical services. Many of them are non medical
doctors but chemists, biologists, physicists, and mathematicians. There is
another group of researchers that are placed on hospitals who are able to do
research and have access to biological samples from their own patients. It seems
that this group is the most privileged one, and the least pressured to establish
collaboration at whatever cost. Finally, there is one more group formed by those
who work as clinicians at small hospitals with no research infrastructure
whatsoever. This group may have an interest in research and the way for them to
become part of a project and be listed as authors in scientific papers is by
giving researchers who do not have access to biological samples access to
patients.\\

Due to these differences in the access to resources, researchers in
general are compelled to build strategic alliances through which samples, data,
technology and authorship, among others, become part of a constant flow through
the network. Social and political capital, as well as concentrations of
resources become fundamental tools for establishing fruitful collaborations.

\section{Methodology}
\label{sec:2}
%% In this work we developed a model in order to have a better understanding of the
%% distribution of utility and trust in real networks of biomedical research
%% collaboration under certain social constraints  or topological properties.\\

Our model is based on the iterated version of the Prisoner's Dilemma (PD) and a
coordination game instantiated on
networks. Implementing games on networks is not new and it's an active area of
research aimed to understand the evolution of cooperation in networks populated
by selfish agents \cite{Szabo2007,Nowak1992,Nowak2006,Santos2005,Santos2006}. In many network models
on which some of game theory games are simulated, agents' decision to cooperate
or defect depend on a specific strategy, such as the well known
\textit{tit-for-tat} \cite{Axelrod2006,Nowak2011}. In some other cases, agents
can modify the weight of the interactions with their neighbors
\cite{Santos2006}. From a different perspective others have explored the effect
of different topologies on the emergence of cooperation
\cite{Santos2005,Hauert2004}. {\color{red}In our case, agents' decision to cooperate or
defect is an outcome that depends on the agent's balance between
utilities and the current strength of its collaboration relationships. Such
balance reflects the overall success or failure of its strategies}. We
study the behavior of the system under different topologies, including a
real-world network.\\

In our model, agents are embedded in a network with varying number of
neighbors. Following the traditional PD game, the strategy chosen by an agent
and the strategy chosen by its neighbors will produce a pay-off. Pay-off follows
the traditional PD rule: $T > R > P > S$. $T$ is for temptation to defect. It is the highest
pay-off and it takes place when the player defects and the other cooperates. $R$
is for reward for when both players cooperate. $P$ is the punishment for when
both players defect. And $S$ is for suckers pay-off, the worst outcome that
takes place when the player cooperates but its neighbor defects. Utility is a
property of agents in which pay-off is accumulated.\\

{\bf PD utility pay-off matrix}\\

\begin{tabular}{| l | l | l |}
\hline
          & \bf{Cooperate} & \bf{Defect} \\ \hline
\bf{Cooperate} &  $R,R$      &  $S,T$   \\ \hline
\bf{Defect}    &  $T,S$      &  $P,P$   \\ \hline

\end{tabular}\\ \\

The strength of the connection, represented by $w$, is a property of the link between two agents and
gets updated according to an $A_{ij}$ matrix of a coordination game. In the $w$ matrix, the highest value
goes to an edge when both agents cooperate, getting an $R$ for reward, if one of
them defects, the connection gets weaker getting $P$ for the collaborative
connection being punished. If both agents defect, the value $w$ doesn't change,
which means that agents didn't interact or that the interaction gets nullified
$N$. In this game, the best action for any agent is to coordinate with its
neighbor, either beacuse it wins or it doesn't loose. \\

{\bf $w$ pay-off matrix}\\

\begin{tabular}{| l | l | l |}
\hline
          & \bf{Cooperate} & \bf{Defect} \\ \hline
\bf{Cooperate} &  $R$      &  $P$   \\ \hline
\bf{Defect}    &  $P$      &  $N$   \\ \hline

\end{tabular}\\ \\

After each game, the agent adds-up utility ($u$), which is the sum of the
pay-offs following the PD matrix. A pair of neighbors will add-up to the strength of
their connection ($w_{ji}$) as they coordinate or anti-coordinate, being $w$
also cumulative. We measure global utility and connection strength for the whole
network. Global utility $U$ is the sum of all individual utilities and global
strength of connections or $W$ is the sum of every pair of agents' links
$w$. Metaphorically, the strength of connection can 
be thought as some sort of ``trust''.\\

{\color{red} It should be noticed that the same actions or behaviors work for
  both $u$ and $w$. There are two reasons for this decision in the design of the
model. The most general one is that we believe that in the real world,
actions such as cooperating and defecting affect the strength of the connection
among people. The second one is that we think that selfishly maximizing resources and
strenghting relationships as \emph{opposing forces} acting on the same set of
behaviors. The actions of an agent imply a trade-off in which defecting may
increase its utility at the expense of its collaborative relationships. If
collaborators have nurished their relationship, it might be strong enough to
endure occasional defection. Cooperating may build up relationships but it can be
expensive for the player.}

\subsection{Network initialization and agent state update}

All networks are initialized equally. The number of nodes for every network is 4122, the same as in the FOSISS network.
To every agent the same utility is given and to every edge the same trust weight is assigned. In the case of FOSISS
network, trust is given by the number of collaborations among researchers, utility remains the same for all nodes as in
the other networks.\\

The probability for an agent to cooperate or defect depends on a
number ($\eta$) that referes to a historical balance between average utility and
the average strength of the connections with its neigbors.   {\color{red} This is so
  because we assume that whatever the result in utility or strength of
  connection, as long as one of them increases, the player will be confident in
  the strategy followed so far}.\\

$\eta$ is calculated as:\\

$\eta_i = \frac{\langle f_i \rangle + \langle w_{ij} \rangle _j}{2}$\\

{\color{red} For the agent to decide to whether cooperate or not, $\eta$ is
  compared to a global threshold $\nu$. If the agents' $\eta$ $>$ $\nu$,
  then the agent will cooperate, otherwise will act suspiciously and it will
  defect. $\nu$ is a global parameter that establishes a threshold that an
  agents' $\eta$ must cross in order to decide to cooperate. In such a way,
  $\eta$ can limit the size of the population of cooperators. Due
  to what the system and the game can offer to agents in terms of utilities and the strength
  of collaboration relationships, $\eta$ represents the carrying capacity of the
  system for the population of cooperators}.

Our simulation was tested on an Erd\"{o}s-Reny\'i, a
Watts-Strogatz small-world and Barab\'asi-Albert topologies, as well
as on the real biomedical research collaboration network. The
simulation was run in a synchronous manner, in which all agents update their
behavior simultaneously. \\

We ran two different experiments. In the first we simulated different values of
carrying capacity $\nu$. With this experiment we were able to see how number of
cooperators, utility, strength of connections among agents and the ratio of
shifting state population would change in the range of the carrying
capacity. For this experiment the states of the agents were the same at
initialization, for all values of the carrying capacity. Since the model is
deterministic, it will return the same result if ran under the same
conditions.\\

The second experiment consisted in running the simulation under the same degree of carrying capacity $\nu$ but randomizing the initial states of the agents. This would show if the system converges to a global state. For every network, the simulation was run 100 times and results were averaged.

\section{Implementation of the model in different topologies}

We built three classical topologies for networks besides the FOSISS network, their parameters are shown in the following table.\\

\begin{tabular}{| l |  l | l |l|l|}
\hline
\bf{Topology}       & $m$              & $\langle k \rangle$          & $\langle C \rangle$      & $\langle l \rangle$ \\ \hline
Erd\"{o}s-R\'enyi  &  $25591$      &  $12.4$        &  $0.003$ & $3.6$  \\ \hline
Watts-Strogatz    &  $206100$   &  $100$         &  $0.7$      & $3.4$  \\ \hline
Barb\'asi-Albert    &  $183465$   &  $89$           &  $0.06$    & $2.13$ \\ \hline
FOSISS                    &  $23391$     &   11.39     &  $0.87$    &  $5.49$ \\ \hline
\end{tabular}\\

\subsection{Erd\"{o}s-Reny\'i}

Erd\"{o}s-Reny\'i networks \cite{Erdos1959} (random networks) are constructed by randomly selecting a pair of $N$ possible nodes and attaching them with an edge, given a probability $p$, as long as there is no edge between them. The result is a Poisson distribution for connectivity of nodes $P(k)$, where each node has a degree quite close to the average $\langle k \rangle$. Also for this type of network, average clustering coefficient  $\langle C \rangle$ is small, actually it is equal to $p$ (the probability of connecting two nodes) and the average shortest path length $\langle l \rangle = \frac{lnN}{ln\langle k \rangle}$.

\subsection{Small-World}

Watts-Strogatz networks \cite{Watts1998} (small-world networks) are in a regime between a fully regular grid (lattice) and a random network (Erd\"{o}s-R\'enyi). In order to build them, a node is chosen from a lattice (a ring) and the edge that connects it to nearest neighbor in a clockwise sense. With probability $p$, this edge is reconnected to a node chosen uniformly at random over the entire ring, with duplicate edges forbidden; otherwise the edge is left in place. This process is repeated by moving clockwise around the ring, considering each node in turn until one lap is completed. Next, the edges connect nodes to their second-nearest neighbors clockwise. And as before, randomly rewire each of these edges with probability $p$, and continue this process, circulating around the ring and proceeding outward to more distant neighbors after each lap, until, each edge in the original lattice has been considered once. The main characteristic of these networks is that the average shortest path length is small and grows as $log(N)$ ($\langle l \rangle \sim log(N)$). Also, the average clustering coefficient $\langle C \rangle$ remains large in terms of $p$. For $p < 0.1$, $\langle C \rangle \sim 1$.

\subsection{Barb\'asi-Albert}

Barb\'asi-Albert networks \cite{Barabasi1999} (scale-free networks) are generated by adding new nodes to a network. Each new node is added connecting it to an existing node with a probability proportional to the degree $k$ (connectivity) of each node (\textit{preferential attachment}). The result is a a power law distribution for connectivity of nodes $P(k)$ where few nodes have many connections and the most have very few connections. Furthermore these networks are also small world networks, showing a quite small $\langle l \rangle$.

\subsection{FOSISS: Biomedical research community network}

The biomedical research network on which we are running our model was generated 
with data from collaborative projects. Our data was obtained from CONACyT and includes information for twelve years of \textit{FOSISS} grants. Data included names of Principal Investigators, collaborators, research topics, etc. The network we are using here has researchers as nodes and edges represent the connection of two scientists when they participate in the same project. Edges are also weighted according to the number of projects shared by any pair of scientists.\\

\section{Results}
\label{sec:3}

In this section we present the main results of the study, namely the topological
structure of the underlying network models, the dynamics of the games under
different parameters and network topologies and the distribution of utility and
of the strength of interaction resulting of playing the games in all the
different scenarios considered, including the real FOSISS network.\\

FOSISS network summed-up a total of 145 components or subnetworks, but we ran
the model on the giant component made-up of 4122 researchers, and 23391 edges.
The giant component was analyzed using \textit{Cytoscape} \textbf{Figure
  1}. Results show that it is a well integrated network, with a clustering
coefficient $\langle C \rangle = 0.870$, an average shortest path length of
$\langle l \rangle = 5.493$  and a density of $p = 0.003$. Such properties
recall a small-world topology \cite{Watts1998}, and a great deal of
self-organization when compared to a random network with the same density and
number of nodes. Network centralization is $0.023$, since there are no visible
researchers that play as hubs in the network. Nevertheless the network
heterogeneity is $0.873$, which means that the network is highly
hierarchical. When the degree distribution is analyzed, degree decreases as a
power-law with an exponent of $1.7$, similar to other social networks described
as scale-free topology networks \cite{Barabasi1999}. Finally, the average number
of neighbors of each node is $11.39$ \cite{Shannon2003}.\\

\begin{figure} [h!]
\centering
\includegraphics[scale=0.5]{Fosiss_GC_final.png}
\caption{Bioemdical research collaboration network (FOSISS) giant component.}\label{Fosiss_GC}
\end{figure}

\FloatBarrier

Other results to report are those of the dynamics of different
variables as the carrying capacity $\nu$ changes. The  most salient
result is that for $\nu$ between $0.19$ and $0.24$, there is an
apparent phase transition in all different topologies and for all the
different variables. Nevertheless, it is worth noticing that the shape
of the phase transition is different according to the topology of the
network at stake. When $\nu$ is between $0.0$ and $0.2$, that is, when there is
no space or a very short one for suspiciousness, all agents cooperate, when
\textit{carrying capacity} is above $0.25$, all agents defect. \textit{Utility},
\textit{strength of interactions}, and \textit{changing state population}
replicate that same behavior for the same limits. \\

In \textbf{Figure 2}, we present how the number of cooperators in the population
change as $\nu$ changes. In the Erd\"{o}s-Reny\'i, network, between $0$ and
$0.18$ approximately, all agents converge to a cooperative behavior, from $18$
to $20$, convergence to cooperative state takes longer but eventually all agents
are cooperating. Close to $\nu \approx 0.21$ there is a sharp fall to a point in
which around half the population is cooperating and the rest is
defecting. Reaching $\nu \approx 0.25$ there is another sharp fall of
cooperators and all agents turn into a defecting state.\\

In the case of the Watts-Strogatz, small-world network, the whole population
remains cooperating for ranges between $0$ and $0.2$ but as it gets closer to
$0.2$, more time is needed for the population to become full of cooperators. In
$\nu \approx 0.2$ the cooperators will represent only half of the population and
such number of them will be constant up to $\nu \approx 0.25$ forming a short
plateau. From $\nu \approx 0.25$ to $\nu \approx 0.6$ cooperators will be
present at the beginning of the simulation but will go diminishing as time passes
by. In the case of the Barab\'asi-Albert network, crossing the threshold of $\nu
\approx 0.2$, there is a sharp decrease in the number of cooperators, but stays
constant over time. Such behavior is present for a very short range of $\nu$, and
before $\nu \approx 0.24$, cooperators disappear for the rest of values of
$\nu$. Finally, FOSISS network behaves similar to the other networks in that
there is a fall in the number of cooperators close  $\nu \approx 0.2$. Different
to the other networks, FOSISS network lacks the sharp reduction of
cooperators, instead this population declines smoothly and progressively;
specially, when it reaches a $\nu \approx 0.25$ cooperators go 
decreasing in a less dramatic manner all the way to $\nu \approx 0.5$. It is
also worth of mention that from $\nu = 0$ to $\nu \approx 0.5$ the number of
cooperators converge to a certain amount and stays constant for the rest of the
simulation.

\begin{figure} [h!]
\centering
\begin{tabular}{cc}

\includegraphics[scale=0.28]{erdos_dc_nus_1.png} & \includegraphics[scale=0.28]{watts_dc_nus_1.png} \\
\includegraphics[scale=0.28]{barabasi_dc_nus_1.png} & \includegraphics[scale=0.28]{fosiss_dc_nus_1.png}
\end{tabular}
\caption{Proportion of cooperators as a function of carrying capacity and time.}\label{CD}
\end{figure}

\FloatBarrier

Utility and strength of interactions dynamics under different $\nu$ emulate the
phase transition found before. In \textbf{Figures 3 and 4}, it can be observed
that there is a drop in utility and strength of interactions according to the
drop in the number of cooperators. Erd\"{o}s-Reny\'i and Barab\'asi-Albert
networks are quite similar in the way these variables fall in two steps, the
first one at $\nu \approx 0.2$ and the next one at $\nu \approx 0.23$. The fall
is sharper still in the Barab\'asi-Albert topology. Utility and strength of
interactions phase transition in Watts-Strogatz network is significantly more
staggered compared to the former networks. In the case of utility, there is a
region in the limits of $\nu \approx 0.25$ and $\nu \approx 0.3$, before utility
goes to $0$, in which it remains low but stable over time. In general, strength
of interactions follows the same pattern as utility but in the same $\nu \approx
0.25$ and $\nu \approx 0.3$, strength of interactions grows to a value that is
higher than the one given by default but soon starts to decrease as the
simulation runs. For FOSISS network, utility and strength of interactions fall
is quite steep but smooth, without sharp cuts. Between $\nu \approx 0.23$ and
$\nu \approx 0.28$, utility and strength of interactions start at their lowest,
but there is a slight increase in both of them.

\begin{figure} [h!]
\centering
\begin{tabular}{cc}

\includegraphics[scale=0.28]{erdos_fitness_nus_1.png} & \includegraphics[scale=0.28]{watts_fitness_nus_1.png} \\
\includegraphics[scale=0.28]{barabasi_fitness_nus_1.png} & \includegraphics[scale=0.28]{fosiss_fitness_nus_1.png}
\end{tabular}
\caption{Utility $U$ dynamics as a function of carrying capacity $\nu$ and time.}\label{fitness}
\end{figure}

\FloatBarrier

\begin{figure} [h!]
\centering
\begin{tabular}{cc}

\includegraphics[scale=0.28]{erdos_trust_nus_1.png} & \includegraphics[scale=0.28]{watts_trust_nus_1.png} \\
\includegraphics[scale=0.28]{barabasi_trust_nus_1.png} & \includegraphics[scale=0.28]{fosiss_trust_nus_1.png}
\end{tabular}
\caption{Strength of interactions $w$ dynamics as a function of carrying capacity $\nu$ and time.}\label{trust}
\end{figure}

\FloatBarrier

We also measured the number of agents shifting states --between cooperating and
defecting- under different $\nu$ values. We found that for all networks there is
a critical point around  $\nu \approx 0.2$ in which all agents are shifting
states. For Erd\"{o}s-Reny\'i and Barab\'asi-Albert networks, for this region,
agents never settle to a single state. Contrary to the former cases, the number
of shifting agents decreases considerably for the Watts-Strogatz and FOSISS
networks, and find an equilibrium state. Once the the limits of this region are
crossed as $\nu$ increases, the number of agents shifting states falls to $0$
and all nodes become defectors.

\begin{figure} [h!]
\centering
\begin{tabular}{cc}

\includegraphics[scale=0.28]{erdos_state_nus.png} & \includegraphics[scale=0.28]{watts_state_nus.png} \\
\includegraphics[scale=0.28]{barabasi_state_nus.png} & \includegraphics[scale=0.28]{fosiss_state_nus.png}
\end{tabular}
\caption{Shifting population between cooperators and defectors as a function of
  carrying capacity $\nu$ and time.}\label{state} 
\end{figure}

\FloatBarrier

Central to our argument is the differences in utility and strength of
interactions distribution at the end of the simulation, for every topology. We
found that utility distribution for the \textit{FOSISS} network, resembles quite
accurately to the distribution of utility in the Barab\'asi-Albert
network.\\

The distribution of utility on each topology is induced by the degree
distribution. This is so, since a given agent (node) will interact with its
neighbors to either cooperate or defect, in such a way that connectivity
influences the number of events played and thus the likelihood of increasing its
corresponding utility. For instance, utility distribution in the random,
Erd\"{o}s-R\'enyi network displays a normal-like curve. The algorithm that
generates this kind of topology, assigns to every node the same probability of
connecting with any other node, which produces a \textit{poissonian} degree
distribution \cite{Erdos1959}. Since the Watts-Strogatz degree distribution is
described by a function that is midways between a random distribution and a
scale-free network \cite{Barrat2000} one may expect also  an intermediate
behavior of the utility distribution, assumption that seems to be fulfilled by
the distribution in Figure 6B.

The resemblance of the degree-distribution and utility distribution also holds
for the Bar\'abasi-Albert network. As mentioned in the methods section, the
degree distribution of a Bar\'abasi-Albert topology follows a power-law that
describes the fact that there are a small number of nodes with large $k$ and most
nodes have a small $k$ \cite{Barabasi1999}. As it is shown in the following
figure, most utility is concentrated in a few number of agents, while most
agents have a small amount of it. This is consistent with other research in
which concentration of resources, fame or citations in science decreases as a
power-law \cite{Simon1955,Price1965,Merton1968}. FOSISS network utility
distribution is also skewed to the left, similar to that of the
Barab\'asi-Albert network. \\

\begin{figure} [h!]
\centering
\begin{tabular}{cc}

\includegraphics[scale=0.28]{erdos_fitness.png} & 
\includegraphics[scale=0.28]{watts_fitness.png} \\
\includegraphics[scale=0.28]{barabasi_fitness.png} & 
\includegraphics[scale=0.28]{fosiss_fitness.png}
\end{tabular}
\caption{Utility distribution on different topologies. A. Random,
  Erd\"{o}s-R\'enyi network displays a normal-like
  distribution. B. Watts-Strogatz network utility distribution is highly skewed
  to the right. C. Barab\'asi-Albert network. Utility is distributed highly
  skewed to the left. D. FOSISS, biomedical researchers collaboration network
  distribution of utility resembles to Barab\'asi-Albert
  network.}\label{histo_fitness} 
\end{figure}

\FloatBarrier

Regarding strength of interactions distribution, the Erd\"{o}s-R\'enyi random
network displays a normal distribution of strength of interactions, as
expected. Again strength of interactions values are highly influenced by the
corresponding degree distribution (Figure 7A). However, in the Watts-Strogatz
network topology (Figure 7B), the strength of interactions distribution is a
highly asymmetric bimodal, with a really-low frequency mode of low strength of
interactions and a highly probability mode for high strength of interactions. A
possible explanation for this phenomenon is that under network topologies
maximizing inter-node communication (by minimizing the average distance between
nodes) such as the Watts-Strogatz, strength of interactions is favored both
among the cooperators (constituting the majority of players) and the
defectors. \\

The Barab\'asi-Albert network (7C) presents also a symmetric unimodal
distribution with values higher (on average) than those of the Erd\"{o}s-R\'enyi
random network, this may be the effect of increased communication due to more
efficient network navigability. Interestingly, the network corresponding to the
real FOSISS collaborations (7D) is an asymmetric unimodal distribution in which
moderate to high values of strength of interactions are more likely. We can
hypothesize that this effect is also due to the communication properties of the
network.

\begin{figure} [h!]
\centering
\begin{tabular}{cc}

\includegraphics[scale=0.28]{erdos_trust.png} & 
\includegraphics[scale=0.28]{watts_trust.png} \\
\includegraphics[scale=0.28]{barabasi_trust.png} & 
\includegraphics[scale=0.28]{fosiss_trust.png}
\end{tabular}
\caption{Strength of interactions distribution on different topologies. A. Random, Erd\"{o}s-R\'enyi network displays a normal-like
  distribution. B. Watts-Strogatz network strength of interactions distribution is bimodal and highly skewed to the right. C.
  Barab\'asi-Albert network strength of interactions distribution is also a normal-like curve. D. FOSISS, biomedical researchers
  collaboration network distribution of strength of interactions is skewed to
  the right.}\label{histo_trust}  
\end{figure}

\FloatBarrier

An interesting feature of highly communicated networks (characterized by high values of clustering coefficient) is the
fact that certainty among players seem to be enhanced, that is, in such networks the rate of change of strategy is
significantly lower (and smoother) than in poorly connected networks. This is another instance in which easier
communication (i.e. lower average minimum path lengths) lead to better performance of the whole collaborative research
system.\\

\section{Discussion and Conclusions}
\label{sec:3}

{\color{red}In this work we have analyzed the influence of parameters given by the underlying social structure of a science
collaborative network on collective strength of interactions and utility dynamical behavior, based on a class of iterated
PD and coordination games. Such parameters include mainly local and global connectivity like the degree centrality and
average clustering coefficient, as well as communication patterns.}\\

{\color{red}Under the assumptions given by the model, we were able to notice
  that, in general, communication within the social
collaborative networks has a positive correlation with average strength of interactions between the individuals partaking in the games and
also with the global collective utility (given by the sum of the individual payoffs). The better the
communication among players, the higher the strength of interactions and the utility leading to an optimized functioning of the whole
\emph{scientific collaboration system}. This is an important result that may be useful for scientific policy planning
and may set a foundation for the optimal use of social networks in scientific collaboration as a means to improve the
relationships among collaborating peers and thus ultimately the performance of research systems. It is out of question
the fact that we need more qualitative work in order to validate these results from a sociological and anthropological
perspective.\\ %Furthermore, such validation is necessary because, as we said at
             %the beginning of this work, \emph{strength of interactions} can
             %have many different meanings and implementations in the real
             %world. The same we can say about \emph{utility} and most of all,
             %about the very idea of the game we explored here since ``playing
             %the game'' must have so, many different meanings among resarchers
             %and their communities.}\\

{\color{red}In order to close this article, we would like to comment on three issues we consider important. The first one is about
confronting our results with our available data of the biomedical research community. Second, we believe is important
saying something about the role of computational simulations in the social sciences. One last point would be about our
future work.}\\

{\color{red}The two main results of our model are the smoothness in the phase transition-like behavior for different parameters and the distribution of utility and strength of interactions in the FOSISS network compared to other networks and their topologies. We are certain that the particular structure of FOSISS network is playing a central role in the results and because of that we would like to discuss it a little bit further.}\\

{\color{red}FOSISS network is higly hierarchical according to its heterogeneity of $0.873$. Because of it, one would
  expect to find the presence of important hubs \cite{Wu-etal2008}, that is, some few researchers that control the whole
  network as it has been reported in some other places \cite{yousefi-etal2008}. Surprisingly, FOSISS network
  centralization is very low $0.023$, that is, there are no researchers that centralize the majority of connections. Our
  guess is that the network is composed of many small communities or groups with a central researcher or Principal
  Investigator (PI). If this is FOSISS network scenario, it means that those groups have a very hierarchic structure as well.}\\

{\color{red}Under such structure, when the clustering coefficient is considered, it can be said that groups are also well connected
but that inter-groups connections are sparse. In other words, individual groups are strongly connected but the network
as a whole is supported by a small number of links. This idea is partially by
another study about scientific collaborations based on co-authorships in one of
the research centers that is part 
of the FOSISS network \cite{HernandezLemus2013}. In the cited reference an apparently well integrated community was
found (high clustering coefficient and a very short characteristic path length). Such integration was no more than
superficial, since it depended on the presence of external collaborators from other research institutions (most of them from overseas) that when removed,
the network broke into small subgraphs that worked independently. Remarkably those subgraphs corresponded to the real
groups of that research center.  What is more, several groups had a hierarchical structure as 
the one we suspect is common in FOSISS subgraphs. The results showed that collaboration was poor between groups but strong
among the members of each group, and that collaboration among groups doesn't emerge bottom-up, instead it seems to be promoted from the
top, from the administrative authorities.}\\

{\color{red}We believe that the the situation just refered is also true for the whole biomedical research community in M\'exico. The
amount of PIs who have also been collaborators in other projects is about one fifth of the total number of participants.
This is a number big enough to connect the whole network in one giant component. Yet, due to the topological
characteristics of FOSISS network, it appears to be the case in which researchers can be the leaders in one project and
collaborators of different project of \emph{its own research group}. CONACyT's funding policies makes impossible for a
researcher to get a grant from a fund if that researcher has an ongoing project with a grant from that same fund. That
is, a researcher can ask for a grant from FOSISS if and only if at the moment
doesn't have a grant from FOSISS already. This
policy has lead researchers from the same group to compete for grants from the same fund in order to rise their
budgets. As consequence of this behavior, group interactions get reinforced while is not necessarily true for integroups
connections.}\\

{\color{red}As is common among scientific communities in biomedical research, PIs play a central role in the network. Strong PIs and
well connected groups seem to be somehow responsible for the high levels of strength of interactions and the centralization of utility in
our simulation. As for what seems to be phase transitions, in the case of FOSISS networks, these are smoother than
those in the other networks with different topologies, even for those with a small-world topology. We think that this
behavior is also the result of the hierarchical structure already mentioned. If this is true, strength of interactions is first loss in the
edges that link diffrent goups and then in the edges that connect members of the groups. Connections between groups would not
be as dense as those inside the groups, which means that there would not be enough information of the behavior of one group regarding
its neighbors to constrain them as it seems to happen with individual researchers inside their communities. Nevertheless,
if values of the carrying capacity $\nu$ keep increasing and becomes more
difficult to strength of interactions, then strength of interactions begins to diminish inside groups.}\\

{\color{red}Another issue that we would like to mention about FOSISS network topology is that it is not a robust collaboration network.
At the level of groups, these might be well connected and consolidated but at the level of the network, this could be
no more than an aggregate of individual groups. A robust network would be resistant to changes in the connections
between groups but in the case of FOSISS, it seems that the network would brake down into
small research groups by cutting some edges, as it happened in our co-authorship
collaboration network \cite{HernandezLemus2013}. The lack of robustness might be 
indicative of the fact that resources stay inside the groups, that is, they do not circulate through or articulate different communities. For
example, one may think of certain expensive technologies for genomic research that could be bought once and shared
among research groups, nevertheless, this is something that doesn't seem to happen very often. There are some other
consequences, such as low communication among groups, atomization of practices and know-hows, redundancy in equipment,
difficulties for implementing community-wide infrastructures such as biobanks, etc.}\\

%% {\color{red}Regarding simulations and social science. We believe that social scientists may learn many lessons from
%%   computational modeling. Tipically, the use of computational modeling as part of the social sciences
%%   has been justified by arguing that such methods allow to understand the connection between the level of the individual
%%   and the level of the group, they make possible to explore different outcomes by tuning different parameters and to
%%   perform --virtual-- experiementation, as well as studying different propensities as Stephen Lansing calls them
%%   \cite{Epstein1996,Lansing2002}. All these are important arguments but we would also like to say something else about 
%%   them. When presenting computational modeling to non-computational social scientists (specially anthropologists) one gets
%%   confronted with several critiques from which, the most common are that computational modeling tends to ignore cultural
%%   differences (should be noticed that cultural differences is not the same as social differences), and that it is hard to grasp the cultural
%%   meaning or significance of the dynamics expressed in the simulation. Because of this kind of observations we are
%%   particularly interested in not forgiving from our work the ethnographical, culturally loaded content of social life,
%%   while recognizing the value of computational simulations.}\\

%% {\color{red}We believe that computational simulations are methodologically valuable for two reasons. The first one is that
%% simulations can play an important role in social research as heuristics. If, as we have been doing in this project, fieldwork
%% observations influence and inspire the development of a computational simulation, parameters must be an abstraction of
%% those observations or at least of part of them. In this sense, the outcomes of simulations are a guide towards new
%% questions and future fieldwork explorations at the time that it constrains and helps to prioritize what is to be
%% observed. For example, from out results it seems mandatory to interview different research groups in order to disclose
%% internal group dynamics and how and which are the terms for collaboration between groups. The second reason emerges from
%% the first, we think that simulations are excellent hypothesis generators for the social sciences. Due to the
%% imposibility of ``observing'' the social dynamics on real-time, just because we can only observe locally while one is
%% doing fieldwork, there are left a few options to see how local dynamics may produce emergent patterns. Simulations may
%% be of great help to elaborate guesses about the mechanisms for the behaviors observed at the local scale, as well as for
%% the global. For example, we could guess that the hierarchical structure without hubs imposes strong limits to the flow
%% of resources and information or that we can expect certain cultural intepretation regarding collaboration due to the
%% position of researchers in the network. Such hypothesis can be computationally tested too.}\\

{\color{red}On these grounds, part of our future work is based on some of the results presented here. We would like to
identify researchers in our simulations and corroborate their situation in the model and in the real world. We are
also interested in going back to the field and interview those groups with an interesting behavior found in our
simulations, probably we would follow a similar strategy as the one developed in \cite{Haraetal2003}. Finding
communities beyond the level of the groups is an important task. We think that there are many possibilities that emerge
from the integration of different methodologies. Moreover, studying social processes in science is particularly
attractive due to the amounts of data already available that can be easily collected. This is a privilege because
simulations can be designed on real world data, something that only very recently has become possible
\cite{Barabasi2011}.\\

No doubt, social sciences are getting more ``computational''. This can be seen everywhere, but curiously enough,
disciplines like physicis and computer science are the ones who are moving towards the social sciences and not so much
the other way around. It might be the case that the pioneering disciplines in the computational social sciences will set
the agenda, an agenda that will apparently be mostly based on exploiting big data and on hypothesis-free approaches. We
believe that the social science have important questions that should be added to that agenda and those questions may not
be answered only by big data techniques but they may require creating models and simulations in the style of the best
hypothesis-driven research.}

%Text with citations \cite{RefB} and \cite{RefJ}.
%\subsection{Subsection title}
%\label{sec:2}
%as required. Don't forget to give each section
%and subsection a unique label (see Sect.~\ref{sec:1}).
%\paragraph{Paragraph headings} Use paragraph headings as needed.
%\begin{equation}
%a^2+b^2=c^2
%\end{equation}

% For one-column wide figures use
%\begin{figure}
% Use the relevant command to insert your figure file.
% For example, with the graphicx package use
%  \includegraphics{example.eps}
% figure caption is below the figure
%\caption{Please write your figure caption here}
%\label{fig:1}       % Give a unique label
%\end{figure}
%
% For two-column wide figures use
%\begin{figure*}
% Use the relevant command to insert your figure file.
% For example, with the graphicx package use
%  \includegraphics[width=0.75\textwidth]{example.eps}
% figure caption is below the figure
%\caption{Please write your figure caption here}
%\label{fig:2}       % Give a unique label
%\end{figure*}
%
% hello, friend
%
% For tables use
%\begin{table}
% table caption is above the table
%\section{%\caption{Please write your table caption here}}
%\label{tab:1}       % Give a unique label
% For LaTeX tables use
%\begin{tabular}{lll}
%\hline\noalign{\smallskip}
%first & second & third  \\
%\noalign{\smallskip}\hline\noalign{\smallskip}
%number & number & number \\
%number & number & number \\
%\noalign{\smallskip}\hline
%\end{tabular}
%\end{table}

\section{acknowledgements}
The authors gratefully acknowledge support by grants: CB-222220-R/2013 and
CB-179431/2012 (Consejo Nacional de Ciencia y Tecnolog\'ia). We would also like
to acknowledge CONACyT for letting us access their database. Finally, we
acknowledge the help of Francisco Allende for his work cleaning researchers
databases.

%If you'd like to thank anyone, place your comments here
%and remove the percent signs.

% BibTeX users please use one of
%\bibliographystyle{spbasic}      % basic style, author-year citations
%\bibliographystyle{spmpsci}      % mathematics and physical sciences
%\bibliographystyle{spphys}       % APS-like style for physics
%\bibliography{}   % name your BibTeX data base

% Non-BibTeX users please use

\begin{thebibliography}{100}

\bibitem{Vermeulen2013} Vermeulen, Nikki; Parker, John N \& Penders,
  Bart, Understanding life together: A brief history of collaboration
  in biology, \textit{Endeavour}, 37(3): 162-171 (2013)

\bibitem{KnorrCetina1999} Knorr-Cetina, Karol; \textit{Epistemic
  cultures: how the sciences make knowledge}, MIT Press, Cambridge, MA
  (1999)

\bibitem{Strasser2006} Strasser, B.J. Collecting and Experimenting:
  The Moral Economies of Biological Research, 1960s-1980s.
  \textit{Preprint no. 310.} Berlin: Max Planck Institute for the
  History of Science, (2006)

\bibitem{Muller2012} M\"{u}ller-Wille, S. \& Charmantier. I.  Natural
  history and information overload: The case of Linnaeus.
  \textit{Studies in History and Philosophy of Biological and
    Biomedical Sciences.} 43:4-15, (2012)

\bibitem{Strasser2012} Strasser, BJ. Data-driven sciences: From
  wonder cabinets to electronic databases. \textit{Studies in History
    and Philosophy of Biological and Biomedical Sciences} 43:85-87,
  (2012)

\bibitem{Sonnenwald2007} Sonnenwald, DH. Scientific Collaborations. \textit{Annual Review of Information Science and
  Technology}, 41.

\bibitem{Newman2001} Newman, MEJ. Clustering and preferential
  attachment in growing networks. \textit{Physical Review E},
  64:025102-1/025102-4, (2001)

\bibitem{Newman2004} Newman, MEJ. Coauthorship networks and patterns
  of scientific collaboration. \textit{PNAS}, 101, no. suppl 1,
  5200-5205 (2004)

\bibitem{Elango2012} Elango, B. \& Rajendran, J. Authorship Trends and
  Collaboration Pattern in the Marine Sciences Literature: A
  Scientometric Study. \textit{International Journal of Information
    Dissemination and Technology}, 2(3), 166-169, (2012)

\bibitem{HernandezLemus2013} Hern\'andez-Lemus, Enrique \&
  Siqueiros-Garc\'ia JM, Information theoretical methods for complex
  network structure reconstruction. \textit{Complex Adaptive Systems
    Modeling}. 1: 8, doi:10.1186/2194-3206-1-8 (2013).

\bibitem{Gilbert1997} Gilbert, N. A Simulation of the Structure of
  Academic Science. \textit{Sociological Research Online}, 2(2) 3,
  http://www.socresonline.org.uk/2/2/3.html

\bibitem{Edmonds2011} Edmonds, B., Gilbert, N., Ahrweiler, P., \&
  Scharnhorst, A. Simulating the Social Processes of Science.
  \textit{Journal of Artificial Societies and Social Simulation},
  14(4) 14,  http://www.jasss.soc.surrey.ac.uk/14/4/14.html

\bibitem{Hara_etal_2002} Hara, N. Solomon, P. Kim SL. Sonnenwald DH. An Emerging View of Scientific Collaboration:
  Scientists’ Perspectives on Collaboration and Factors that Impact Collaboration. \textit{Journal of the American
    Society for Information Science and Technology}, 54(10):952–965, (2003)

\bibitem{Lieberman_etal_2005} Lieberman, E. Hauert, C. \& Nowak,
  MA. Evolutionary Dynamics on Graphs. Nature, 433, doi:0.1038/nature03204 (2005).

\bibitem{Lo2004} Lo, T.S., Chan, H.Y., Hui, P.M., Johnson, N.F.,
  Theory of networked minority games based on strategy pattern
  dynamics, \textit{Physical Review E} 70, 056012 (2004)

\bibitem{Buesser2012} Buesser, P. and Tomassini, M., Evolution of
  cooperation on spatially embedded networks, \textit{Physical Review E} 86,
  066107 (2012)

\bibitem{Ichinose2013} Ichinose, G., Tenguishi, Y., and Tanizawa, T.,
  Robustness of cooperation on scale-free networks under continuous
  topological change, \textit{Physical Review E} 88, 052808 (2013)

\bibitem{Ahmed2014} Ahmed, A., Karlapalem, K., Inequity aversion and
  the evolution of cooperation, \textit{Physical Review E} 89, 022802, (2014)

\bibitem{Vilone2014} Vilone, D., Ramasco, J.J., S\'anchez, A., San
  Miguel, M., Social imitation versus strategic choice, or consensus
  versus cooperation, in the networked Prisoner’s Dilemma,
  \textit{Physical Review E} 90, 022810, (2014)

\bibitem{Wardil2015} Wardil, L., Hauert, C., Cooperation and coauthorship in
  scientific publishing, Physical Review E 91, 012825, (2015)

 \bibitem{hanauske2012} Hanauske, M., Evolutionary Game Theory and Complex Networks of Scientific Information, in A. Scharnhorst et al. (eds.), \textit{Models of Science Dynamics, Understanding Complex Systems Series}, Springer Berlin Heidelberg, (2012)

\bibitem{Szabo2007} Szab\'o, Gy\"{o}rgy \& F\'ath, G\'abor,
  Evolutionary games on graphs. \textit{Physics Reports}, 446: 97-216
  (2007)

\bibitem{Nowak1992} Nowak, Martin A. \& May, Robert M, Evolutionary
  Games and Spatial Chaos. \textit{Nature}, 359: 826-829, (1992)

\bibitem{Nowak2006} Oshtuki, Hisashi, Hauert, Christoph, Lieberman, Erez \& Nowak, Martin A, A simple rule for the evolution of cooperation on social graphs. \textit{Nature}, 441: 502-505 (2006)

\bibitem{Axelrod2006} Axelrod, Robert, \textit{Evolution of cooperation: Revised edition}, Basic Books, Cambridge, MA (2006)

\bibitem{Nowak2011} Nowak, Martin A. \& Highfield, Roger,
  \textit{Supercooperators. Altruism, Evolution, and Why We Need Each
    Other to Succeed}. Free Press, New York, NY  (2011)

\bibitem{Santos2006} Santos, Francisco C., Pacheco, Jorge M., Lenaerts, Tom, Cooperation prevails when individuals adjust their social ties. \textit{PLoS Computational Biology}. 2(10): 1284-1291 (2006)

\bibitem{Santos2005} Santos, F.C. \& Pacheco, J.M., Scale-Free
  Networks Provide a Unifying Framework for the Emergence of
  Cooperation. \textit{PRL}, 95: 098104-1 to 098104-4, (2005)

\bibitem{Hauert2004} Hauert, Christoph \& Doebeli, Michael, Spatial
  structure often inhibits the evolution of cooperation in the
  snowdrift game. \textit{Nature}, 428: 643-646,  (2004)

\bibitem{Erdos1959} Erd\"{o}s, P. \& Reny\'i, A. On Random Graphs. \textit{Publ. Math}, 6:290 (1959).

\bibitem{Watts1998} Watts, Duncan J. \& Strogatz, Steven H, Collective dynamics
  of 'small-world' networks. \textit{Nature}, 393: 440-442 (1998)

  \bibitem{Barrat2000} Barrat, A.; Weigt, M., On the properties of small-world network models, \textit{European Physical Journal B} 13 (3): 547–560, (2000)

\bibitem{Barabasi1999} Barab\'asi, Albert-L\'aszl\'o. \& Albert, R\'eka, Emergence of Scaling in Random Networks. \textit{Science}, 286: 509-512 (1999)

\bibitem{Shannon2003} Shannon P, Markiel A, Ozier O, Baliga NS, Wang JT, Ramage D, Amin N, Schwikowski B, Ideker T. Cytoscape: a software environment for integrated models of biomolecular interaction networks. \textit{Genome Research}, 13(11):2498-504, (2003)

\bibitem{Wu-etal2008}Jun Wu, Yue-Jin Tan, Hong-Zhong Deng, Da-Zhi Zhu. A new measure of heterogeneity of complex networks based on degree sequence.  Eds. Ali Minai, Dan Braha, Yaneer Bar-Yam  \emph{Unifying Themes in Complex Systems. Proceedings of the Sixth International Conference on Complex Systems}, Springer Berlin Heidelberg, 66-73, (2008)

\bibitem{yousefi-etal2008} Yousefi-Nooraie R, Akbari-Kamrani M, Hanneman RA, Etemadi A. Association between co-authorship network and scientific productivity and impact indicators in academic medical research centers: A case study in Iran. \textit{Health Research Policy and Systems} 6:9 (2008) doi:10.1186/1478-4505-6-9.

%%Discusion references

\bibitem{Simon1955} Simon, HA. On a class of skew distribution functions. \textit{Biometrika}, 42 (3-4): 425-440, (1955)

\bibitem{Price1965} Price, Derek JS. Networks of Scientific Papers. \textit{Science}, 149(3683): 510-515, (1965)

\bibitem{Merton1968} Merton, Robert K, The Matthew Effect in Science, \textit{Science}, 159(3810): 56-63 (1968)

\bibitem{Epstein1996} Epstein JM \& Axtell R. \textit{Growing artificial societies. Social science from the bottom up}. The
  Brookings Institution Press and The MIT Press, Washington, DC. (1996)

\bibitem{Lansing2002} Lansing JS. ``Artificial Societies'' and the Social
  Sciences. \textit{Artificial Life}, 8:279-292, (2002)

\bibitem{Haraetal2003} Hara N, Solomon P, Kim SL, Sonnenwald DH. An emerging
  view of scientific collaboration: Scientists' perspectives on collaboration
  and factors that impact collaboration. Journal of the American Society for
  Information Science and Technology, 54(10):952–965, 2003

\bibitem{Barabasi2011} Barab\'asi, AL. The network takeover. \textit{Nature}, 8:14–16, (2012)

\bibitem{Conteetal2012} Conte R, Gilbert N, Bonelli G, Cioffi-Revilla C,
  Deffuant G, Kertesz J, Loreto V, Moat S, Nadal J.-P,  Sanchez A, Nowak A,
  Flache  A, San Miguel M, Helbing D. Manifesto of computational social
  science. \textit{The European Physical Journal, Special Topics} 214(1):325–346, (2012)

  %
% and use \bibitem to create references. Consult the Instructions
% for authors for reference list style.
%
%\bibitem{RefJ}
% Format for Journal Reference
%Author, Article title, Journal, Volume, page numbers (year)
% Format for books
%\bibitem{RefB}
%Author, Book title, page numbers. Publisher, place (year)
% etc
\end{thebibliography}

\end{document}
% end of file template.tex

### 2016-11-07 manuscript_3.tex
reviewed from the beginning thru Methodology
Mostly corrected verb tenses and removed lots of chaff.

@@
 
-What would happen if researchers in a community were given the same amount of
-resources and then set free to interact among each other? How would these
-resources be distributed in the population after many interactions? The final
-result may be determined by the researchers'social and political power, an by
-her or his prestige. Nevertheless, all these attributes depend, to a 
-certain degree, on the research collaboration social network in which scientists
-are embedded. Here we develop a model based on the Prisoner's Dilemma
-implemented on a collaboration network. With this model we explore the
-distribution of resources and the dynamics of the strengthening or weakening of collaboration
-connections among partners, as scientists cooperate or
-defect in order to gain access to others resources. The network is based on data
-about projects that were awarded with a grant. In this sense, we assume that
-resources are funds, equipment and time. Fitness, as we define it here
-represents how much access does a researcher has over the resources of its collegues.  
-We tested our simulation on the real biomedical research network and compared
-the results with an Erd\"{o}s-Reny\'i, a Watts-Strogatz small-world
-and Barab\'asi-Albert topologies. Different topologies display different fitness
-and connections strength distributions. Moreover, the distribution of fitness
-and connections strength in the researchers network is similar to that of Barab\'asi-Albert 
-and Watts-Strogatz topologies, respectively. We believe that fitness
-distribution in the researchers network suggests that there are socio-cultural
-mechanisms governing the network that produces asymmetric distribution to
-resources. Nevertheless, the high distribution of strong connections might reflect some sort of
-subordination among researchers by which they are morally obliged to cooperate
-by the same socio-cultural mechanisms. The range around the threshold that
-regulates the decision to cooperate or defect according to the agent's
-historical balance between utility and strength of collaborative relationships and carring
-capacity of the system is small, suggesting that there is a region in which a
-phase transition takes place from a population of cooperators to a population of
-defectors. Simulations like this may help to develop science policies to promote
-fair distribution of resources.
+  What would happen if researchers in a community were given the same
+  amount of resources and then set free to interact among each other?
+  How would these resources be distributed in the population after
+  many interactions? The final result may be determined by the
+  researchers' social and political power, an by their
+  prestige. Nevertheless, all these attributes depend, to a certain
+  degree, on the research collaboration social network in which
+  scientists are embedded. Here we develop a model based on the
+  Prisoner's Dilemma implemented on a collaboration network. With this
+  model we explore the distribution of resources and the dynamics of
+  the strengthening or weakening of collaboration connections among
+  partners, as scientists cooperate or defect in order to gain access
+  to others' resources. The network is based on data about projects
+  that were awarded with a grant. In this sense, we assume that
+  resources are funds, equipment and time. We define Fitness as how
+  much access a researcher has to the resources of his collegues.  We
+  tested our simulation on the real biomedical research network and
+  compared the results with an Erd\"{o}s-Reny\'i, a Watts-Strogatz
+  small-world and Barab\'asi-Albert topologies. Different topologies
+  display different fitness and connections strength
+  distributions. Moreover, the distribution of fitness and connections
+  strength in the researchers network is similar to that of
+  Barab\'asi-Albert and Watts-Strogatz topologies, respectively. We
+  believe that fitness distribution in the researchers network
+  suggests that there are socio-cultural mechanisms governing the
+  network that produce an asymmetric distribution of resources. The
+  high distribution of strong connections might reflect some sort of
+  subordination among researchers by which they are morally obliged to
+  cooperate by the same socio-cultural mechanisms. The range around
+  the threshold that regulates the decision to cooperate or defect
+  according to the agent's historical balance between utility and
+  strength of collaborative relationships and carrying capacity of the
+  system is small, suggesting that there is a region in which a phase
+  transition takes place from a population of cooperators to a
+  population of defectors. Simulations like this may help to develop
+  science policies to promote fair distribution of resources.
 
@@
 
-Collaboration has become a corner stone in biomedical research today.
-In contrast to physics which has a long history and experience in collaborative
-projects, biology has only recently become an evermore collaborative
-discipline\cite{Vermeulen2013}. Biology has an interesting record in such
-matters because scientific collaboration means something different to
-different branches of biology: molecular biology has traditionally been a
-research activity of small laboratories\cite{KnorrCetina1999,Strasser2006},
-whereas in natural history there has been data and samples exchange since the
-$XVII^{th}$ century\cite{Muller2012,Strasser2012}.\\
-
-Despite the differences in culture and practices, the Human Genome
-Project made collaboration a central feature of biology. Nowadays it
-is widely acknowledged that collaboration takes many forms, from
-biological samples and biobanking to international groups in charge of
-helping the bio-research communities to harmonize and share their
-data. Collaboration in science may take many forms, nevertheless, sharing
-resources such as equipment, funds, and time are critical; also, building
-trust among scientists is fundamental. What is more important, resources are
-mobilized in order to create strategic alliances.\\
+Collaboration has become a cornerstone in biomedical research today.
+In contrast to physics which has a long history and experience in
+collaborative projects, biology is only recently becoming an evermore
+collaborative discipline\cite{Vermeulen2013}. Biology has an
+interesting record in such matters because scientific collaboration
+means something different to different branches of biology: molecular
+biology has traditionally been a research activity of small
+laboratories\cite{KnorrCetina1999,Strasser2006}, whereas in natural
+history there has been data and samples exchange since the $XVII^{th}$
+century\cite{Muller2012,Strasser2012}. Despite the differences in
+culture and practices, the Human Genome Project made collaboration a
+central feature of biology.\\
+
+Nowadays it is widely acknowledged that collaboration takes many
+forms, from sharing of biological samples and biobanking to
+international groups in charge of helping research communities to
+harmonize and share their data. Sharing resources such as equipment,
+funds, and time is critical; building trust among scientists is
+fundamental. Also, resources are mobilized in order to create strategic alliances.\\
 
@@
 is not surprising since cooperation and competition are quite important in
-today's academic success. How do collaboration happens within a competitive
+today's academic success. How does collaboration happen within a competitive
 academic environment and what kind of payoff is present in these settings were
@@
 
-In spite of all these research efforts, cooperation in the context of scientific
-collaboration is still loosely defined and the long time dynamics of academic
-cooperation (and its consequences) are yet to be fully elucidated. Furthermore,
-to our current knowledge, we are not aware of the use of game theory and
-the complex network analysis for understanding how the topology of scientific collaboration networks
-affects access to resources among individuals present in the network \footnote{For
-  an account of scientific collaboration and definitions, please refer to
-  \cite{Sonnenwald2007}.}. In this context our work aims to contribute to
-further our current understanding on the matte, specially when agents have to
-maximize their acces to resources while they need to take care of their collaboration links.\\
+Even with all these research efforts, cooperation in the context of
+scientific collaboration is still loosely defined and the long term
+dynamics of academic cooperation (and its consequences) are yet to be
+fully elucidated. Furthermore, to our current knowledge, there has
+been no use of game theory and complex network analysis for
+understanding how the topology of scientific collaboration networks
+affects access to resources among individuals present in the network
+\footnote{For an account of scientific collaboration and definitions,
+  please refer to \cite{Sonnenwald2007}.}. Our work aims to contribute
+to our current understanding on the matter, specially when agents have
+to maximize their access to resources while taking care of their collaboration links.\\
 
@@
    one for maximazing individual utility based on the iterated Prisoner's
-   dilemma; the other, a coordination game for maximazing the connection strength between
+   Dilemma; the other, a coordination game for maximazing the connection strength between
    players. We are interested in how they affect each other in 
@@
   utility means that the player is increasing its access to the resources of
-  other players.  Utility function is the sum of the payoffs of playing
-  with its neighbors. The opossing force is in the other game. The game for
-  maximazing the strength of the connection among players. In this case
-  coordinating is the best strategy as it pays the most when
-  coordinating regardeless they both cooperate or defect, this is because when
+  other players. The value of the Utility function for a player is the sum of the payoffs of playing
+  with his neighbors. The opossing force comes from the other concurrent game: players
+  trying to maximize the strength of their connections to other players. In the coordinating game
+  the best strategy is to adopt the same strategy as the other player, as it pays the most
+  regardless of cooperation or defection in the utility game. When
   both cooperate the interaction gets a positive payoff, when both defect, the
   interaction doesn't get affected; but if they anti-coordinate, then the
-  interaction looses. Finally, cooperation is a central feature in science
-  doing. For our biomedical network, cooperation can be metaphorically thought
-  as sharing resources such as time, students, equipment, even money. Defection
-  to a cooperator may also have some examples, such as ghost authorship or
-  prestige authorship, or even a part of a working strategy in which a some
-  members of a team do the work at certain moment, and then the other part of
-  the team will do its part in some other moment in the future --some sort of
-  reciprocity. }\\
-
-The manuscript is structured in five sections. The following describes
-\textit{FOSISS}, the main program for grants destined for biomedical applied
-research in M\'exico. This description is important because that is the source
-of our database for creating the researchers collaboration network. Next we
-describe our model, and then, in the following section we introduce the
-different network topologies on which we explored the model. In the fourth
-section we present  our results and discuss them briefly. In the fifth section
+  interaction looses. Finally, cooperation is a central feature of scientific work.
+  For our biomedical network, cooperation can be thought of
+  as sharing resources such as time, students, equipment, even money. Examples of defection
+  to a cooperator are ghost authorship or
+  prestige authorship.
+
+  % este ejemplo de defection no es nada claro:
+  %
+  % Another example may be a working strategy in which some
+  % members of a team do the work at certain moment, and then another part 
+  % does its part in some other moment in the future --some sort of
+  % reciprocity.
+
+}\\
+
+The manuscript is structured in five sections. First we describe
+\textit{FOSISS}, the main program for grants destined to biomedical applied
+research in M\'exico. This is the source of the
+database from which we created the researchers collaboration network. Next we
+describe our model
+and the different network topologies on which we explored it.
+We then present our results and discuss them briefly. In the last section
 we draw some final remarks and conclusions.
@@
 entity in charge of promoting the development of science and 
-technology. It is also in charge of creating the country's scientific
-policies.  Among CONACyT's functions are to develop science and technology
+technology.
+Among CONACyT's functions are to develop science and technology
 policies according to national needs and demands, to advise the different
@@
 In the year 2002 CONACyT, along with other government agencies and
-entities, created sectoral funds which are trusts for scientific and
-technological research.The objective of such funds is to cover and equally
-promote the research capacities of different areas such as energy, agriculture,
-or technological innovation by means of the generation of human resources
-and helping research groups to consolidate. It is expected that the
+entities, created sectoral funds
+to cover and equally
+promote research capacities of different areas such as energy, agriculture
+and health. Technological innovation is fostered by the generation of human resources
+and by helping research groups to consolidate. It is expected that the
 knowledge generated under the sponsorship of these funds
@@
 \emph{FOSISS} or Sectoral Fund for Health and Social Security Research
-(\emph{Fondo Sectorial en Investigaci\'on en Salud y Seguridad Social}) is among
+(\emph{Fondo Sectorial en Investigaci\'on en Salud y Seguridad Social}) is one of
 such funds. FOSISS is constituted by CONACyT, SSA, IMSS and ISSSTE,\footnote{SSA
@@
 
-Eligibility is open to the public and private health research sectors,
-nevertheless, most applicants are public universities and research
-institutions. Up to the year of 2013, there were 91 institutions funded that
+Eligibility is open to public and private health research sectors,
+however most applicants are public universities and research
+institutions. From 2002 through 2013, there were 91 institutions funded that
 comprised 4988 researchers.\\
@@
 population represented in the data include principal investigators (PIs),
-associate researchers, postdoctoral associates, under and postgraduate
-students. Unfortunately, this information is not specified in the
+associate researchers, postdoctoral associates, postgraduate and undergraduate
+students.
+% wut? which information is not specified? which is pi and which is undergrad is not specified?
+Unfortunately, this information is not specified in the
 database. Still, this is something we acknowledge and it's important because
@@
 
-Our database includes different information about the projects. It includes the
-name of the project, the year it was approved for funding, and the research area
-to which it was assigned. It also specifies the names of PIs or the person who
-was responsible of a project, the names of those who have been collaborators,
-some PIs have also been collaborators of a different project. The institutional
-affiliation of all participants can be found too. This is important because
-knowing the affiliation of the researcher we also know the principal institution
+Our database includes the
+name of the project, the year it was approved for funding and the research area
+to which it was assigned. It specifies the names of PIs or the people 
+responsible for the project and the names of collaborators.
+Researchers can be PIs in one project and collaborators on a different project. The institutional
+affiliation of all participants is included. Through this affiliation
+we know the principal institution
 behind every project.\\
 
-Though, cleaning and analysis work of the database is still ongoing, some
+Even though curation and analysis work of the database is still ongoing, some
 relevant facts about the biomedical research can be said. Over the period of 12
@@
   neoplasms}, and \emph{infectious and parasitic diseases}. The least funded
-area is \emph{Ethics and medicine}. But the areas with more researchers is
+area is \emph{Ethics and medicine}. The area with the most researchers is
 \emph{malignant neoplasms}. Other areas of relevance for M\'exico are
@@
 From the institutions that have participated in a protocol funded by FOSISS,
-less than one fifth has been responsible for a project and more than 95\% of
+less than one fifth have been responsible for a project and more than 95\% of
 them are Mexican, public institutions. There is also an important presence of
@@
 constitutes a vibrant community and collaboration is part of everyday
-work. Nevertheless, M\'exico does not have public biobanks for research purposes
+work. However, M\'exico does not have public biobanks for research purposes
 (which are specially relevant for research in genomics, for example), there is
@@
 
-From our brief ethnographic work to date, we have been able to see that
+From our ethnographic work to date, we have been able to see that
 biological samples, data and technology can become instruments for negotiating
@@
 general are compelled to build strategic alliances through which samples, data,
-technology and authorship, among others, become part of a constant flow through
+technology and authorship, among other assets, become part of a constant flow through
 the network. Social and political capital, as well as concentrations of
@@
 of different topologies on the emergence of cooperation
-\cite{Santos2005,Hauert2004}. {\color{red}In our case, agents' decision to cooperate or
-defect is an outcome that depends on the agent's balance between
+\cite{Santos2005,Hauert2004}. {\color{red}In our case, an agent's decision to cooperate or
+defect is an outcome that depends on a balance between
 utilities and the current strength of its collaboration relationships. Such
@@
 
-{\color{red} It should be noticed that the same actions or behaviors work for
+{\color{red} It should be noted that the same actions or behaviors work for
   both $u$ and $w$. There are two reasons for this decision in the design of the
@@
 among people. The second one is that we think that selfishly maximizing resources and
-strenghting relationships as \emph{opposing forces} acting on the same set of
+strenghting relationships are \emph{opposing forces} acting on the same set of
 behaviors. The actions of an agent imply a trade-off in which defecting may
 increase its utility at the expense of its collaborative relationships. If
-collaborators have nurished their relationship, it might be strong enough to
+collaborators have nourished their relationships, they might be strong enough to
 endure occasional defection. Cooperating may build up relationships but it can be

### 2016-11-08 manuscript_3.tex
more review, mostly verb tenses and such

@@
 All networks are initialized equally. The number of nodes for every network is 4122, the same as in the FOSISS network.
-To every agent the same utility is given and to every edge the same trust weight is assigned. In the case of FOSISS
-network, trust is given by the number of collaborations among researchers, utility remains the same for all nodes as in
+The same utility is given to every agent and all edges are asigned the same weight. In the case of the FOSISS
+network, edge weight is given by the number of collaborations among researchers, utility remains the same for all nodes as in
 the other networks.\\
@@
 
-{\color{red} For the agent to decide to whether cooperate or not, $\eta$ is
+{\color{red} For the agent to decide whether to cooperate or not, $\eta$ is
   compared to a global threshold $\nu$. If the agents' $\eta$ $>$ $\nu$,
-  then the agent will cooperate, otherwise will act suspiciously and it will
+  then the agent will cooperate, otherwise he will be suspicious and will
   defect. $\nu$ is a global parameter that establishes a threshold that an
-  agents' $\eta$ must cross in order to decide to cooperate. In such a way,
+  agents' $\eta$ must cross in order to decide to cooperate. In this way,
   $\eta$ can limit the size of the population of cooperators. Due
@@
 We ran two different experiments. In the first we simulated different values of
-carrying capacity $\nu$. With this experiment we were able to see how number of
+carrying capacity $\nu$. With this experiment we were able to see how the number of
 cooperators, utility, strength of connections among agents and the ratio of
@@
 initialization, for all values of the carrying capacity. Since the model is
-deterministic, it will return the same result if ran under the same
+deterministic, it will return the same result if run under the same
 conditions.\\
@@
 The second experiment consisted in running the simulation under the same degree of carrying capacity $\nu$ but randomizing the initial states of the agents.
-This would show if the system converges to a global state.
+This would show that the system converges to a global state.
 For every network, the simulation was run 100 times and results were averaged.
@@
 Next, the edges connect nodes to their second-nearest neighbors clockwise.
-And as before, randomly rewire each of these edges with probability $p$, and continue this process, circulating around the ring and proceeding outward to more distant neighbors after each lap, until, each edge in the original lattice has been considered once.
+And as before, each of these edges is randomly rewired with probability $p$, and continue this process, circulating around the ring and proceeding outward to more distant neighbors after each lap, until, each edge in the original lattice has been considered once.
 The main characteristic of these networks is that the average shortest path length is small and grows as $log(N)$ ($\langle l \rangle \sim log(N)$).
@@
 Data included names of Principal Investigators, collaborators, research topics, etc.
-The network we are using here has researchers as nodes and edges represent the connection of two scientists when they participate in the same project.
+The network we are using here has researchers as nodes and edges represent the connection of two scientists when they colaborate in the same project.
 Edges are also weighted according to the number of projects shared by any pair of scientists.\\
@@
 plateau. From $\nu \approx 0.25$ to $\nu \approx 0.6$ cooperators will be
-present at the beginning of the simulation but will go diminishing as time passes
-by. In the case of the Barab\'asi-Albert network, crossing the threshold of $\nu
+present at the beginning of the simulation but will go diminishing as time goes on.
+In the case of the Barab\'asi-Albert network, crossing the threshold of $\nu
 \approx 0.2$, there is a sharp decrease in the number of cooperators, but stays
@@
 decreasing in a less dramatic manner all the way to $\nu \approx 0.5$. It is
-also worth of mention that from $\nu = 0$ to $\nu \approx 0.5$ the number of
+also noteworthy that from $\nu = 0$ to $\nu \approx 0.5$ the number of
 cooperators converge to a certain amount and stays constant for the rest of the
@@
 scale-free network \cite{Barrat2000} one may expect also  an intermediate
-behavior of the utility distribution, assumption that seems to be fulfilled by
+behavior of the utility distribution. This assumption seems to be fulfilled by
 the distribution in Figure 6B.
@@
 real FOSISS collaborations (7D) is an asymmetric unimodal distribution in which
-moderate to high values of strength of interactions are more likely. We can
+moderate to high values of strength of interactions are more likely. We 
 hypothesize that this effect is also due to the communication properties of the
@@
 An interesting feature of highly communicated networks (characterized by high values of clustering coefficient) is the
-fact that certainty among players seem to be enhanced, that is, in such networks the rate of change of strategy is
+fact that certainty among players seems to be enhanced, that is, in such networks the rate of change of strategy is
 significantly lower (and smoother) than in poorly connected networks. This is another instance in which easier
@@
 and may set a foundation for the optimal use of social networks in scientific collaboration as a means to improve the
-relationships among collaborating peers and thus ultimately the performance of research systems. It is out of question
-the fact that we need more qualitative work in order to validate these results from a sociological and anthropological
+relationships among collaborating peers and thus ultimately the performance of research systems. 
+We obviously need more qualitative work in order to validate these results from a sociological and anthropological
 perspective.\\ %Furthermore, such validation is necessary because, as we said at
@@
 
-{\color{red}In order to close this article, we would like to comment on three issues we consider important. The first one is about
-confronting our results with our available data of the biomedical research community. Second, we believe is important
-saying something about the role of computational simulations in the social sciences. One last point would be about our
+{\color{red}To close this article, we would like to comment on three issues we consider important. The first one is about
+confronting our results with data available to us from the biomedical research community. Second, some remarks we believe are important
+about the role of computational simulations in the social sciences. Finally we would like to comment on our
 future work.}\\
@@
 {\color{red}FOSISS network is higly hierarchical according to its heterogeneity of $0.873$. Because of it, one would
-  expect to find the presence of important hubs \cite{Wu-etal2008}, that is, some few researchers that control the whole
-  network as it has been reported in some other places \cite{yousefi-etal2008}. Surprisingly, FOSISS network
-  centralization is very low $0.023$, that is, there are no researchers that centralize the majority of connections. Our
+  expect to find the presence of important hubs \cite{Wu-etal2008}, that is, a few researchers control the whole
+  network, as has been reported in some other places \cite{yousefi-etal2008}. Surprisingly, FOSISS network
+  centralization is very low $0.023$, i.e. there are no researchers that centralize the majority of connections. Our
   guess is that the network is composed of many small communities or groups with a central researcher or Principal
-  Investigator (PI). If this is FOSISS network scenario, it means that those groups have a very hierarchic structure as well.}\\
+  Investigator (PI). If this is the case in the FOSISS network, it means that those groups have a very hierarchic structure as well.}\\
 
 {\color{red}Under such structure, when the clustering coefficient is considered, it can be said that groups are also well connected
-but that inter-groups connections are sparse. In other words, individual groups are strongly connected but the network
-as a whole is supported by a small number of links. This idea is partially by
+but that inter-group connections are sparse. In other words, individual groups are strongly connected but the network
+as a whole is supported by a small number of links. We came by this idea partially from
 another study about scientific collaborations based on co-authorships in one of
@@
 of the FOSISS network \cite{HernandezLemus2013}. In the cited reference an apparently well integrated community was
-found (high clustering coefficient and a very short characteristic path length). Such integration was no more than
-superficial, since it depended on the presence of external collaborators from other research institutions (most of them from overseas) that when removed,
-the network broke into small subgraphs that worked independently. Remarkably those subgraphs corresponded to the real
+found (high clustering coefficient and a very short characteristic path length). Such integration was mostly
+superficial, since it depended on the presence of external collaborators from other research institutions (most of them from overseas). 
+Removing these external collaborators broke down the network into small subgraphs that worked independently. Remarkably those subgraphs corresponded to the real
 groups of that research center.  What is more, several groups had a hierarchical structure as 
@@
 This is a number big enough to connect the whole network in one giant component. Yet, due to the topological
-characteristics of FOSISS network, it appears to be the case in which researchers can be the leaders in one project and
-collaborators of different project of \emph{its own research group}. CONACyT's funding policies makes impossible for a
+characteristics of the FOSISS network, it appears to be the case that researchers can be the leaders in one project and
+collaborators of different project of \emph{its own research group}. CONACyT's funding policies makes it impossible for a
 researcher to get a grant from a fund if that researcher has an ongoing project with a grant from that same fund. That
-is, a researcher can ask for a grant from FOSISS if and only if at the moment
+is, a researcher can ask for a grant from FOSISS if and only if at the moment he
 doesn't have a grant from FOSISS already. This
-policy has lead researchers from the same group to compete for grants from the same fund in order to rise their
-budgets. As consequence of this behavior, group interactions get reinforced while is not necessarily true for integroups
-connections.}\\
+policy has lead researchers from the same group to ask for grants from the same fund in order to rise their
+budgets. A consequence of this behavior is that group interactions get reinforced, but integroup connections not necessarily so.}\\
 
@@
 those in the other networks with different topologies, even for those with a small-world topology. We think that this
-behavior is also the result of the hierarchical structure already mentioned. If this is true, strength of interactions is first loss in the
+behavior is also the result of the hierarchical structure already mentioned. If this is true, strength of interactions is first lost in the
 edges that link diffrent goups and then in the edges that connect members of the groups. Connections between groups would not
@@
 its neighbors to constrain them as it seems to happen with individual researchers inside their communities. Nevertheless,
-if values of the carrying capacity $\nu$ keep increasing and becomes more
-difficult to strength of interactions, then strength of interactions begins to diminish inside groups.}\\
+if values of the carrying capacity $\nu$ keep increasing and it becomes more
+difficult to strengthen interactions, then strength of interactions begins to diminish inside groups.}\\
 
@@
 example, one may think of certain expensive technologies for genomic research that could be bought once and shared
-among research groups, nevertheless, this is something that doesn't seem to happen very often. There are some other
-consequences, such as low communication among groups, atomization of practices and know-hows, redundancy in equipment,
+among research groups, however, this doesn't seem to happen very often. There are some other
+consequences, such as low communication among groups, atomization of practices and know-hows, redundancy in equipment tenancy,
 difficulties for implementing community-wide infrastructures such as biobanks, etc.}\\
@@
 identify researchers in our simulations and corroborate their situation in the model and in the real world. We are
-also interested in going back to the field and interview those groups with an interesting behavior found in our
+also interested in going back to the field and interviewing those groups with an interesting behavior found in our
 simulations, probably we would follow a similar strategy as the one developed in \cite{Haraetal2003}. Finding
@@
 the other way around. It might be the case that the pioneering disciplines in the computational social sciences will set
-the agenda, an agenda that will apparently be mostly based on exploiting big data and on hypothesis-free approaches. We
-believe that the social science have important questions that should be added to that agenda and those questions may not
+the agenda, an agenda that will apparently be mostly based on taking advantage of big data and on hypothesis-free approaches. We
+believe that the social sciences have important questions that should be added to that agenda and those questions may not
 be answered only by big data techniques but they may require creating models and simulations in the style of the best
@@
 to acknowledge CONACyT for letting us access their database. Finally, we
-acknowledge the help of Francisco Allende for his work cleaning researchers
-databases.
+acknowledge the help of Francisco Allende for his work curating 
+databases of researchers.
 

### 2016-11-09 manuscript_3.tex
include images in path

@@
 
-}\\
+}
 
@@
 \centering
-\includegraphics[scale=0.5]{Fosiss_GC_final.png}
+\includegraphics[scale=0.5]{images/Fosiss_GC_final.png}
 \caption{Bioemdical research collaboration network (FOSISS) giant component.}\label{Fosiss_GC}
@@
 \begin{tabular}{cc}
-
-\includegraphics[scale=0.28]{erdos_dc_nus_1.png} & \includegraphics[scale=0.28]{watts_dc_nus_1.png} \\
-\includegraphics[scale=0.28]{barabasi_dc_nus_1.png} & \includegraphics[scale=0.28]{fosiss_dc_nus_1.png}
+  \includegraphics[scale=0.28]{images/erdos_dc_nus_1.png} & \includegraphics[scale=0.28]{images/watts_dc_nus_1.png}
+  \\
+  \includegraphics[scale=0.28]{images/barabasi_dc_nus_1.png} & \includegraphics[scale=0.28]{images/fosiss_dc_nus_1.png}
 \end{tabular}
@@
 
-\includegraphics[scale=0.28]{erdos_fitness_nus_1.png} & \includegraphics[scale=0.28]{watts_fitness_nus_1.png} \\
-\includegraphics[scale=0.28]{barabasi_fitness_nus_1.png} & \includegraphics[scale=0.28]{fosiss_fitness_nus_1.png}
+\includegraphics[scale=0.28]{images/erdos_fitness_nus_1.png} & \includegraphics[scale=0.28]{watts_fitness_nus_1.png} \\
+\includegraphics[scale=0.28]{images/barabasi_fitness_nus_1.png} & \includegraphics[scale=0.28]{fosiss_fitness_nus_1.png}
 \end{tabular}
@@
 
-\includegraphics[scale=0.28]{erdos_trust_nus_1.png} & \includegraphics[scale=0.28]{watts_trust_nus_1.png} \\
-\includegraphics[scale=0.28]{barabasi_trust_nus_1.png} & \includegraphics[scale=0.28]{fosiss_trust_nus_1.png}
+\includegraphics[scale=0.28]{images/erdos_trust_nus_1.png} & \includegraphics[scale=0.28]{watts_trust_nus_1.png} \\
+\includegraphics[scale=0.28]{images/barabasi_trust_nus_1.png} & \includegraphics[scale=0.28]{fosiss_trust_nus_1.png}
 \end{tabular}
@@
 
-\includegraphics[scale=0.28]{erdos_state_nus.png} & \includegraphics[scale=0.28]{watts_state_nus.png} \\
-\includegraphics[scale=0.28]{barabasi_state_nus.png} & \includegraphics[scale=0.28]{fosiss_state_nus.png}
+\includegraphics[scale=0.28]{images/erdos_state_nus.png} & \includegraphics[scale=0.28]{watts_state_nus.png} \\
+\includegraphics[scale=0.28]{images/barabasi_state_nus.png} & \includegraphics[scale=0.28]{fosiss_state_nus.png}
 \end{tabular}
@@
 
-\includegraphics[scale=0.28]{erdos_fitness.png} & 
-\includegraphics[scale=0.28]{watts_fitness.png} \\
-\includegraphics[scale=0.28]{barabasi_fitness.png} & 
-\includegraphics[scale=0.28]{fosiss_fitness.png}
+\includegraphics[scale=0.28]{images/erdos_fitness.png} & 
+\includegraphics[scale=0.28]{images/watts_fitness.png} \\
+\includegraphics[scale=0.28]{images/barabasi_fitness.png} & 
+\includegraphics[scale=0.28]{images/fosiss_fitness.png}
 \end{tabular}
@@
 
-\includegraphics[scale=0.28]{erdos_trust.png} & 
-\includegraphics[scale=0.28]{watts_trust.png} \\
-\includegraphics[scale=0.28]{barabasi_trust.png} & 
-\includegraphics[scale=0.28]{fosiss_trust.png}
+\includegraphics[scale=0.28]{images/erdos_trust.png} & 
+\includegraphics[scale=0.28]{images/watts_trust.png} \\
+\includegraphics[scale=0.28]{images/barabasi_trust.png} & 
+\includegraphics[scale=0.28]{images/fosiss_trust.png}
 \end{tabular}
@@
 % For example, with the graphicx package use
-%  \includegraphics{example.eps}
+%  \includegraphics{images/example.eps}
 % figure caption is below the figure

### 2016-11-15 manuscript_3.tex
Comentarios de Enrique added

@@
 \title{A game-theory modeling approach to utility
-  and strength of interactions dynamics in biomedical research social networks}
+  and attachment dynamics in biomedical research social networks}
 %\title{Two games modeling approach to collaboration dynamics in biomedical
@@
   the strengthening or weakening of collaboration connections among
-  partners, as scientists cooperate or defect in order to gain access
-  to others' resources. The network is based on data about projects
+  partners that we call attachment, as scientists cooperate or defect in order
+  to gain access to others' resources. The network is based on data about projects
   that were awarded with a grant. In this sense, we assume that
-  resources are funds, equipment and time. We define Fitness as how
+  resources are funds, equipment and time. We define Utility as how
   much access a researcher has to the resources of his collegues.  We
@@
   small-world and Barab\'asi-Albert topologies. Different topologies
-  display different fitness and connections strength
-  distributions. Moreover, the distribution of fitness and connections
-  strength in the researchers network is similar to that of
+  display different utility and attachment
+  distributions. Moreover, the distribution of utility and attachment in the
+  researchers network is similar to that of 
   Barab\'asi-Albert and Watts-Strogatz topologies, respectively. We
-  believe that fitness distribution in the researchers network
+  believe that utility distribution in the researchers network
   suggests that there are socio-cultural mechanisms governing the
@@
 
-\textbf{Notes:}
-
-\begin{itemize}
+%\textbf{Notes:}
+
+%\begin{itemize}
 
@@
 
-\item We change utility for fitness. Utility seems a better concept in order to
-  reflect players' preferences.
+%\item We change utility for fitness. Utility seems a better concept in order to
+  %reflect players' preferences.
 
@@
 
-\item Choosing a strategy depends on the balance $\eta'$ equation --look at page
-  9. This
-  equation states that the probability of an agent to cooperate increases as: a)
-  its utility increases --as it moves away from 0, or; b) The strength of the
-  connection with its peers increases --as it moves away from 0, or; c) both
-  increases.
-
-  $\eta_i = \frac{\langle f_i \rangle + \langle w_{ij} \rangle _j}{2}$\\
-
-\item{En la pagina 9 decimos que ``In order for the agent to choose to cooperate
-  or defect, a degree of willingness to cooperate is assigned to each agent.'' No estoy
-  seguro que ``degree of willingness to cooperate'' sea la mejor manera de
-  decirlo, mi duda está en la palabra ``degree'', por lo que cambi\'e la
-  oraci\'on a: The probability for an agent to cooperate or defect depends on a
-number that referes to a historical balance between average utility and the average strength of
-the connections with its neigbors. }
-
-\end{itemize}
+%\item Choosing a strategy depends on the balance $\eta'$ equation --look at page
+ %%  9. This
+%   equation states that the probability of an agent to cooperate increases as: a)
+%   its utility increases --as it moves away from 0, or; b) The strength of the
+%   connection with its peers increases --as it moves away from 0, or; c) both
+%   increases.
+
+%   $\eta_i = \frac{\langle f_i \rangle + \langle w_{ij} \rangle _j}{2}$\\
+
+% \item{En la pagina 9 decimos que ``In order for the agent to choose to cooperate
+%   or defect, a degree of willingness to cooperate is assigned to each agent.'' No estoy
+%   seguro que ``degree of willingness to cooperate'' sea la mejor manera de
+%   decirlo, mi duda está en la palabra ``degree'', por lo que cambi\'e la
+%   oraci\'on a: The probability for an agent to cooperate or defect depends on a
+% number that referes to a historical balance between average utility and the average strength of
+% the connections with its neigbors. }
+
+% \end{itemize}
 
@@
 network. Global utility $U$ is the sum of all individual utilities and global
-strength of connections or $W$ is the sum of every pair of agents' links
-$w$. Metaphorically, the strength of connection can 
-be thought as some sort of ``trust''.\\
+attachment or $W$ is the sum of every pair of agents' links
+$w$. Metaphorically, the attachment can be thought as some sort of ``trust''.\\
 
@@
 model. The most general one is that we believe that in the real world,
-actions such as cooperating and defecting affect the strength of the connection
+actions such as cooperating and defecting affect the attachment
 among people. The second one is that we think that selfishly maximizing resources and
@@
 number ($\eta$) that referes to a historical balance between average utility and
-the average strength of the connections with its neigbors.   {\color{red} This is so
-  because we assume that whatever the result in utility or strength of
-  connection, as long as one of them increases, the player will be confident in
-  the strategy followed so far}.\\
+the average attachment with its neigbors.   {\color{red} This is so
+  because we assume that whatever the result in utility or attachment, as long
+  as one of them increases, the player will be confident in the strategy
+  followed so far}.\\
 
@@
 carrying capacity $\nu$. With this experiment we were able to see how the number of
-cooperators, utility, strength of connections among agents and the ratio of
+cooperators, utility, attachment among agents and the ratio of
 shifting state population would change in the range of the carrying
@@
 different parameters and network topologies and the distribution of utility and
-of the strength of interaction resulting of playing the games in all the
-different scenarios considered, including the real FOSISS network.\\
+attachment resulting of playing the games in all the different scenarios
+considered, including the real FOSISS network.\\
 
@@
 \textit{carrying capacity} is above $0.25$, all agents defect. \textit{Utility},
-\textit{strength of interactions}, and \textit{changing state population}
+\textit{attachment}, and \textit{changing state population}
 replicate that same behavior for the same limits. \\
@@
 
-Utility and strength of interactions dynamics under different $\nu$ emulate the
+Utility and attachment dynamics under different $\nu$ emulate the
 phase transition found before. In \textbf{Figures 3 and 4}, it can be observed
-that there is a drop in utility and strength of interactions according to the
+that there is a drop in utility and attachment according to the
 drop in the number of cooperators. Erd\"{o}s-Reny\'i and Barab\'asi-Albert
@@
 first one at $\nu \approx 0.2$ and the next one at $\nu \approx 0.23$. The fall
-is sharper still in the Barab\'asi-Albert topology. Utility and strength of
-interactions phase transition in Watts-Strogatz network is significantly more
+is sharper still in the Barab\'asi-Albert topology. Utility and attachment phase
+transition in Watts-Strogatz network is significantly more 
 staggered compared to the former networks. In the case of utility, there is a
 region in the limits of $\nu \approx 0.25$ and $\nu \approx 0.3$, before utility
-goes to $0$, in which it remains low but stable over time. In general, strength
-of interactions follows the same pattern as utility but in the same $\nu \approx
-0.25$ and $\nu \approx 0.3$, strength of interactions grows to a value that is
+goes to $0$, in which it remains low but stable over time. In general,
+attachment follows the same pattern as utility but in the same $\nu \approx 
+0.25$ and $\nu \approx 0.3$, attachment grows to a value that is
 higher than the one given by default but soon starts to decrease as the
-simulation runs. For FOSISS network, utility and strength of interactions fall
+simulation runs. For FOSISS network, utility and attachment fall
 is quite steep but smooth, without sharp cuts. Between $\nu \approx 0.23$ and
-$\nu \approx 0.28$, utility and strength of interactions start at their lowest,
+$\nu \approx 0.28$, utility and attachment start at their lowest,
 but there is a slight increase in both of them.
@@
 \end{tabular}
-\caption{Strength of interactions $w$ dynamics as a function of carrying capacity $\nu$ and time.}\label{trust}
+\caption{Attachment $w$ dynamics as a function of carrying capacity $\nu$ and time.}\label{trust}
 \end{figure}
@@
 
-Central to our argument is the differences in utility and strength of
-interactions distribution at the end of the simulation, for every topology. We
+Central to our argument is the differences in utility and attachment
+distribution at the end of the simulation, for every topology. We 
 found that utility distribution for the \textit{FOSISS} network, resembles quite
@@
 Regarding strength of interactions distribution, the Erd\"{o}s-R\'enyi random
-network displays a normal distribution of strength of interactions, as
-expected. Again strength of interactions values are highly influenced by the
+network displays a normal distribution of attachment, as
+expected. Again attachment values are highly influenced by the
 corresponding degree distribution (Figure 7A). However, in the Watts-Strogatz
-network topology (Figure 7B), the strength of interactions distribution is a
+network topology (Figure 7B), the attachment distribution is a
 highly asymmetric bimodal, with a really-low frequency mode of low strength of
-interactions and a highly probability mode for high strength of interactions. A
+interactions and a highly probability mode for high attachment. A
 possible explanation for this phenomenon is that under network topologies
 maximizing inter-node communication (by minimizing the average distance between
-nodes) such as the Watts-Strogatz, strength of interactions is favored both
+nodes) such as the Watts-Strogatz, attachment is favored both
 among the cooperators (constituting the majority of players) and the
@@
 real FOSISS collaborations (7D) is an asymmetric unimodal distribution in which
-moderate to high values of strength of interactions are more likely. We 
+moderate to high values of attachment are more likely. We 
 hypothesize that this effect is also due to the communication properties of the
@@
 \end{tabular}
-\caption{Strength of interactions distribution on different topologies. A. Random, Erd\"{o}s-R\'enyi network displays a normal-like
-  distribution. B. Watts-Strogatz network strength of interactions distribution is bimodal and highly skewed to the right. C.
-  Barab\'asi-Albert network strength of interactions distribution is also a normal-like curve. D. FOSISS, biomedical researchers
-  collaboration network distribution of strength of interactions is skewed to
+\caption{attachment distribution on different topologies. A. Random, Erd\"{o}s-R\'enyi network displays a normal-like
+  distribution. B. Watts-Strogatz network attachment distribution is bimodal and highly skewed to the right. C.
+  Barab\'asi-Albert network attachment distribution is also a normal-like curve. D. FOSISS, biomedical researchers
+  collaboration network distribution of attachment is skewed to
   the right.}\label{histo_trust}  
@@
 {\color{red}In this work we have analyzed the influence of parameters given by the underlying social structure of a science
-collaborative network on collective strength of interactions and utility dynamical behavior, based on a class of iterated
+collaborative network on collective attachment and utility dynamical behavior, based on a class of iterated
 PD and coordination games. Such parameters include mainly local and global connectivity like the degree centrality and
@@
   that, in general, communication within the social
-collaborative networks has a positive correlation with average strength of interactions between the individuals partaking in the games and
+collaborative networks has a positive correlation with average attachment between the individuals partaking in the games and
 also with the global collective utility (given by the sum of the individual payoffs). The better the
-communication among players, the higher the strength of interactions and the utility leading to an optimized functioning of the whole
+communication among players, the higher the attachment and the utility leading to an optimized functioning of the whole
 \emph{scientific collaboration system}. This is an important result that may be useful for scientific policy planning
@@
 perspective.\\ %Furthermore, such validation is necessary because, as we said at
-             %the beginning of this work, \emph{strength of interactions} can
+             %the beginning of this work, \emph{attachment} can
              %have many different meanings and implementations in the real
@@
 
-{\color{red}The two main results of our model are the smoothness in the phase transition-like behavior for different parameters and the distribution of utility and strength of interactions in the FOSISS network compared to other networks and their topologies.
+{\color{red}The two main results of our model are the smoothness in the phase transition-like behavior for different parameters and the distribution of utility and attachment in the FOSISS network compared to other networks and their topologies.
 We are certain that the particular structure of FOSISS network is playing a central role in the results and because of that we would like to discuss it a little bit further.}\\
@@
 {\color{red}As is common among scientific communities in biomedical research, PIs play a central role in the network. Strong PIs and
-well connected groups seem to be somehow responsible for the high levels of strength of interactions and the centralization of utility in
+well connected groups seem to be somehow responsible for the high levels of attachment and the centralization of utility in
 our simulation. As for what seems to be phase transitions, in the case of FOSISS networks, these are smoother than
 those in the other networks with different topologies, even for those with a small-world topology. We think that this
-behavior is also the result of the hierarchical structure already mentioned. If this is true, strength of interactions is first lost in the
+behavior is also the result of the hierarchical structure already mentioned. If this is true, attachment is first lost in the
 edges that link diffrent goups and then in the edges that connect members of the groups. Connections between groups would not
@@
 if values of the carrying capacity $\nu$ keep increasing and it becomes more
-difficult to strengthen interactions, then strength of interactions begins to diminish inside groups.}\\
+difficult to strengthen interactions, then attachment begins to diminish inside groups.}\\
 

### 2016-11-15 manuscript_3.tex
update paths to images

@@
 
-\includegraphics[scale=0.28]{images/erdos_fitness_nus_1.png} & \includegraphics[scale=0.28]{watts_fitness_nus_1.png} \\
-\includegraphics[scale=0.28]{images/barabasi_fitness_nus_1.png} & \includegraphics[scale=0.28]{fosiss_fitness_nus_1.png}
+\includegraphics[scale=0.28]{images/erdos_fitness_nus_1.png} & \includegraphics[scale=0.28]{images/watts_fitness_nus_1.png} \\
+\includegraphics[scale=0.28]{images/barabasi_fitness_nus_1.png} & \includegraphics[scale=0.28]{images/fosiss_fitness_nus_1.png}
 \end{tabular}
@@
 
-\includegraphics[scale=0.28]{images/erdos_trust_nus_1.png} & \includegraphics[scale=0.28]{watts_trust_nus_1.png} \\
-\includegraphics[scale=0.28]{images/barabasi_trust_nus_1.png} & \includegraphics[scale=0.28]{fosiss_trust_nus_1.png}
+\includegraphics[scale=0.28]{images/erdos_trust_nus_1.png} & \includegraphics[scale=0.28]{images/watts_trust_nus_1.png} \\
+\includegraphics[scale=0.28]{images/barabasi_trust_nus_1.png} & \includegraphics[scale=0.28]{images/fosiss_trust_nus_1.png}
 \end{tabular}
@@
 
-\includegraphics[scale=0.28]{images/erdos_state_nus.png} & \includegraphics[scale=0.28]{watts_state_nus.png} \\
-\includegraphics[scale=0.28]{images/barabasi_state_nus.png} & \includegraphics[scale=0.28]{fosiss_state_nus.png}
+\includegraphics[scale=0.28]{images/erdos_state_nus.png} & \includegraphics[scale=0.28]{images/watts_state_nus.png} \\
+\includegraphics[scale=0.28]{images/barabasi_state_nus.png} & \includegraphics[scale=0.28]{images/fosiss_state_nus.png}
 \end{tabular}

### 2016-11-19 manuscript_3.tex
interaction strength needs less interpretation
attachment and trust are terms for different phenomena

--- 2016-11-09 manuscript_3.tex
@@
   model we explore the distribution of resources and the dynamics of
-  the strengthening or weakening of collaboration connections among
+  the strengthening or weakening of collaboration interactions among
   partners, as scientists cooperate or defect in order to gain access
-  to others' resources. The network is based on data about projects
+  to resources shared by others. The network is based on data about projects
   that were awarded with a grant. In this sense, we assume that
@@
 
-\textbf{Notes:}
-
-\begin{itemize}
-
-%% \item In this paper there are two games played simultaneously: One for
-%% maximazing individual utility; the second for maximazing the connection
-%% strength. We are interested in how they affect eachother in the context of a
-%% network of collaboration.
-
-\item We change utility for fitness. Utility seems a better concept in order to
-  reflect players' preferences.
-
-%% \item In the context of our paper, utility represents
-%%   the preference for having access to the resources of others. Maximazing
-%%   utility means that the player is increasing its access to the resources of
-%%   other players.  Utility function is just the sum of the payoffs of playing
-%%   with its neighbors. As for the payoff matrix, the best strategy for a player
-%%   is to defect. Any other option will not be an optimal payoff. The opossing
-%%   force is in the other game. The game for maximazing the strength of the
-%%   connection among players. In this case defecting or cooperating? is the best
-%%   strategy as it pays the most when coordinating regardeless they both cooperate
-%%   or defect, this is because when both cooperate the interaction gets a positive
-%%   payoff, when both defect, the interaction doesn't get affected; but if they
-%%   anti-coordinate, then the interaction looses. In this sense, this might be a
-%%   game were there are multiple (i.e., 2 points or strategies) equilibria. It
-%%   seems that there is no single dominant strategy.}\\
-
-\item Choosing a strategy depends on the balance $\eta'$ equation --look at page
-  9. This
-  equation states that the probability of an agent to cooperate increases as: a)
-  its utility increases --as it moves away from 0, or; b) The strength of the
-  connection with its peers increases --as it moves away from 0, or; c) both
-  increases.
-
-  $\eta_i = \frac{\langle f_i \rangle + \langle w_{ij} \rangle _j}{2}$\\
-
-\item{En la pagina 9 decimos que ``In order for the agent to choose to cooperate
-  or defect, a degree of willingness to cooperate is assigned to each agent.'' No estoy
-  seguro que ``degree of willingness to cooperate'' sea la mejor manera de
-  decirlo, mi duda está en la palabra ``degree'', por lo que cambi\'e la
-  oraci\'on a: The probability for an agent to cooperate or defect depends on a
-number that referes to a historical balance between average utility and the average strength of
-the connections with its neigbors. }
-
-\end{itemize}
+%% \textbf{Notes:}
+
+%% \begin{itemize}
+
+%% %% \item In this paper there are two games played simultaneously: One for
+%% %% maximazing individual utility; the second for maximazing the connection
+%% %% strength. We are interested in how they affect eachother in the context of a
+%% %% network of collaboration.
+
+%% \item We change utility for fitness. Utility seems a better concept in order to
+%%   reflect players' preferences.
+
+%% %% \item In the context of our paper, utility represents
+%% %%   the preference for having access to the resources of others. Maximazing
+%% %%   utility means that the player is increasing its access to the resources of
+%% %%   other players.  Utility function is just the sum of the payoffs of playing
+%% %%   with its neighbors. As for the payoff matrix, the best strategy for a player
+%% %%   is to defect. Any other option will not be an optimal payoff. The opossing
+%% %%   force is in the other game. The game for maximazing the strength of the
+%% %%   connection among players. In this case defecting or cooperating? is the best
+%% %%   strategy as it pays the most when coordinating regardeless they both cooperate
+%% %%   or defect, this is because when both cooperate the interaction gets a positive
+%% %%   payoff, when both defect, the interaction doesn't get affected; but if they
+%% %%   anti-coordinate, then the interaction looses. In this sense, this might be a
+%% %%   game were there are multiple (i.e., 2 points or strategies) equilibria. It
+%% %%   seems that there is no single dominant strategy.}\\
+
+%% \item Choosing a strategy depends on the balance $\eta'$ equation --look at page
+%%   9. This
+%%   equation states that the probability of an agent to cooperate increases as: a)
+%%   its utility increases --as it moves away from 0, or; b) The strength of the
+%%   connection with its peers increases --as it moves away from 0, or; c) both
+%%   increases.
+
+%%   $\eta_i = \frac{\langle f_i \rangle + \langle w_{ij} \rangle _j}{2}$\\
+
+%% \item{En la pagina 9 decimos que ``In order for the agent to choose to cooperate
+%%   or defect, a degree of willingness to cooperate is assigned to each agent.'' No estoy
+%%   seguro que ``degree of willingness to cooperate'' sea la mejor manera de
+%%   decirlo, mi duda está en la palabra ``degree'', por lo que cambi\'e la
+%%   oraci\'on a: The probability for an agent to cooperate or defect depends on a
+%% number that referes to a historical balance between average utility and the average strength of
+%% the connections with its neigbors. }
+
+%% \end{itemize}
 
@@
  {\color{red}In this article we explore the network effect on the distribution
-   of players having access to certain amount of resources from other players in the
-   network and the distribution of the strength of connections among
+   of players having access to certain amount of resources shared by other players in the
+   network and the distribution of the strength of interactions among
    them. Particularly, we implemented two games played simultaneously: 
@@
 {\color{red}In the context of our paper, utility represents
-  the preference for having access to the resources of others. Maximazing
-  utility means that the player is increasing its access to the resources of
-  other players. The value of the Utility function for a player is the sum of the payoffs of playing
-  with his neighbors. The opossing force comes from the other concurrent game: players
-  trying to maximize the strength of their connections to other players. In the coordinating game
+  access to resources shared by others.
+  The value of the Utility function for a player is the sum of the payoffs of playing
+  with its neighbors. The opossing force comes from the other concurrent game: players
+  trying to maximize the strength of their interactions with other players. In the coordinating game
   the best strategy is to adopt the same strategy as the other player, as it pays the most
@@
 
-  % este ejemplo de defection no es nada claro:
+  % TODO: este ejemplo de defection no es nada claro:
   %
@@
 and the different network topologies on which we explored it.
-We then present our results and discuss them briefly. In the last section
+We then present our results and discuss them. In the last section
 we draw some final remarks and conclusions.
@@
   Services for State Workers (\emph{Instituto de Seguridad y Servicios Sociales
-    de los Trabajadores del Estado})} being all of them the major public health
+    de los Trabajadores del Estado})} all of them being the major public health
 providers and research institutions in the country. Every year CONACyT opens a
@@
 
-Eligibility is open to public and private health research sectors,
-however most applicants are public universities and research
-institutions. From 2002 through 2013, there were 91 institutions funded that
+Most applicants are public universities and research institutions, but
+eligibility is open to public and private health research sectors.
+From 2002 through 2013, there were 91 institutions funded that
 comprised 4988 researchers.\\
 
-From these data some important considerations should be made clear. The
-population represented in the data include principal investigators (PIs),
-associate researchers, postdoctoral associates, postgraduate and undergraduate
-students.
-% wut? which information is not specified? which is pi and which is undergrad is not specified?
-Unfortunately, this information is not specified in the
-database. Still, this is something we acknowledge and it's important because
-researchers in our network are under different circumstances and we know
+From these data some important considerations should be made
+clear. Scientists in the database take on the roles of principal
+investigators (PIs), associate researchers, postdoctoral associates,
+postgraduate and undergraduate students.
+Unfortunately, information on these roles is not specified in the database.
+We acknowledge the importance of this deficiency because
+researchers in our network act under different circumstances and we know
 that this diversity has a real impact on the structure and eventually on the
@@
 affiliation of all participants is included. Through this affiliation
-we know the principal institution
+we determine the principal institution
 behind every project.\\
 
-Even though curation and analysis work of the database is still ongoing, some
+Even though curation and analysis work of this database is still going on, some
 relevant facts about the biomedical research can be said. Over the period of 12
@@
 they have not been established yet. Regulation on these subjects is still
-missing. Finally, technology (e.g., PCR, sequencing and expression profiling
-technology) is in the domain of the institutions with the highest research
-profiles and sometimes PIs see technology as a personal good.\\
+missing. Finally, technologically advanced equipment such as high throughput sequencers
+are kept by institutions with the highest research
+profiles and sometimes PIs manage them in a self serving way.\\
 
@@
 are researchers that do not have direct access to samples, simply because their
-institution does not offer clinical services. Many of them are non medical
+parent institution does not offer clinical services. Many of them are non medical
 doctors but chemists, biologists, physicists, and mathematicians. There is
-another group of researchers that are placed on hospitals who are able to do
+another group of researchers that are placed on hospitals which is able to do
 research and have access to biological samples from their own patients. It seems
-that this group is the most privileged one, and the least pressured to establish
+that this group is the most privileged one, and the one with the least pressure to establish
 collaboration at whatever cost. Finally, there is one more group formed by those
@@
 of different topologies on the emergence of cooperation
-\cite{Santos2005,Hauert2004}. {\color{red}In our case, an agent's decision to cooperate or
-defect is an outcome that depends on a balance between
+\cite{Santos2005,Hauert2004}. {\color{red}In our model, an agent's decision to cooperate or
+defect depends on a balance between
 utilities and the current strength of its collaboration relationships. Such
@@
 
-The strength of the connection, represented by $w$, is a property of the link between two agents and
+The strength of the interaction, represented by $w$, is a property of the link between two agents and
 gets updated according to an $A_{ij}$ matrix of a coordination game. In the $w$ matrix, the highest value
@@
 $N$. In this game, the best action for any agent is to coordinate with its
-neighbor, either beacuse it wins or it doesn't loose. \\
+neighbor, either beacuse it wins or because it doesn't loose. \\
 
@@
 pay-offs following the PD matrix. A pair of neighbors will add-up to the strength of
-their connection ($w_{ji}$) as they coordinate or anti-coordinate, being $w$
+their interaction ($w_{ji}$) as they coordinate or anti-coordinate, being $w$
 also cumulative. We measure global utility and connection strength for the whole
@@
 strength of connections or $W$ is the sum of every pair of agents' links
-$w$. Metaphorically, the strength of connection can 
+$w$. The strength of interaction can 
 be thought as some sort of ``trust''.\\
@@
 model. The most general one is that we believe that in the real world,
-actions such as cooperating and defecting affect the strength of the connection
-among people. The second one is that we think that selfishly maximizing resources and
-strenghting relationships are \emph{opposing forces} acting on the same set of
+actions such as cooperating and defecting affect the strength of the interaction
+among people. The second one is that we think that selfishly maximizing access to resources and
+strengthening relationships are \emph{opposing forces} acting on the same set of
 behaviors. The actions of an agent imply a trade-off in which defecting may
@@
 
-We ran two different experiments. In the first we simulated different values of
-carrying capacity $\nu$. With this experiment we were able to see how the number of
-cooperators, utility, strength of connections among agents and the ratio of
-shifting state population would change in the range of the carrying
-capacity. For this experiment the states of the agents were the same at
-initialization, for all values of the carrying capacity. Since the model is
-deterministic, it will return the same result if run under the same
-conditions.\\
-
-The second experiment consisted in running the simulation under the same degree of carrying capacity $\nu$ but randomizing the initial states of the agents.
-This would show that the system converges to a global state.
-For every network, the simulation was run 100 times and results were averaged.
+We ran two different experiments. In the first we simulated different
+values of carrying capacity $\nu$. With this experiment we were able
+to see how the number of cooperators, utility, strength of connections
+among agents and the ratio of shifting state population would change
+in the range of the carrying capacity. The states of the agents were
+the same at initialization, for all values of the carrying
+capacity. Since the model is deterministic, it will return the same
+result if run under the same conditions.\\
+
+The second experiment consisted in running the simulation under the
+same degree of carrying capacity $\nu$ but randomizing the initial
+states of the agents. This would show that the system converges to a
+global state. For every network, the simulation was run 100 times and
+results were averaged.
 
@@
 Next, the edges connect nodes to their second-nearest neighbors clockwise.
-And as before, each of these edges is randomly rewired with probability $p$, and continue this process, circulating around the ring and proceeding outward to more distant neighbors after each lap, until, each edge in the original lattice has been considered once.
+As before, each of these edges is randomly rewired with probability $p$.
+This process continues, circulating around the ring and proceeding outward to more distant neighbors after each lap, until each edge in the original lattice has been considered once.
 The main characteristic of these networks is that the average shortest path length is small and grows as $log(N)$ ($\langle l \rangle \sim log(N)$).
@@
 Data included names of Principal Investigators, collaborators, research topics, etc.
-The network we are using here has researchers as nodes and edges represent the connection of two scientists when they colaborate in the same project.
+The network we are using here has researchers as nodes and edges represent the connection of two scientists when they colaborate on the same project.
 Edges are also weighted according to the number of projects shared by any pair of scientists.\\
@@
 apparent phase transition in all different topologies and for all the
-different variables. Nevertheless, it is worth noticing that the shape
+different variables. It is worth noting that the shape
 of the phase transition is different according to the topology of the
-network at stake. When $\nu$ is between $0.0$ and $0.2$, that is, when there is
+network under study. When $\nu$ is between $0.0$ and $0.2$, that is, when there is
 no space or a very short one for suspiciousness, all agents cooperate, when
@@
 
-In the case of the Watts-Strogatz, small-world network, the whole population
-remains cooperating for ranges between $0$ and $0.2$ but as it gets closer to
-$0.2$, more time is needed for the population to become full of cooperators. In
-$\nu \approx 0.2$ the cooperators will represent only half of the population and
-such number of them will be constant up to $\nu \approx 0.25$ forming a short
-plateau. From $\nu \approx 0.25$ to $\nu \approx 0.6$ cooperators will be
-present at the beginning of the simulation but will go diminishing as time goes on.
-In the case of the Barab\'asi-Albert network, crossing the threshold of $\nu
-\approx 0.2$, there is a sharp decrease in the number of cooperators, but stays
-constant over time. Such behavior is present for a very short range of $\nu$, and
-before $\nu \approx 0.24$, cooperators disappear for the rest of values of
-$\nu$. Finally, FOSISS network behaves similar to the other networks in that
-there is a fall in the number of cooperators close  $\nu \approx 0.2$. Different
-to the other networks, FOSISS network lacks the sharp reduction of
-cooperators, instead this population declines smoothly and progressively;
-specially, when it reaches a $\nu \approx 0.25$ cooperators go 
-decreasing in a less dramatic manner all the way to $\nu \approx 0.5$. It is
-also noteworthy that from $\nu = 0$ to $\nu \approx 0.5$ the number of
-cooperators converge to a certain amount and stays constant for the rest of the
-simulation.
+In the case of the Watts-Strogatz, small-world network, the whole
+population remains cooperating for ranges between $0$ and $0.2$ but as
+it gets closer to $0.2$, more time is needed for the population to
+become full of cooperators. In $\nu \approx 0.2$ the cooperators will
+represent only half of the population and such number of them will be
+constant up to $\nu \approx 0.25$ forming a short plateau. From $\nu
+\approx 0.25$ to $\nu \approx 0.6$ cooperators will be present at the
+beginning of the simulation but will diminish as time goes on.  In the
+case of the Barab\'asi-Albert network, crossing the threshold of $\nu
+\approx 0.2$, there is a sharp decrease in the number of cooperators,
+but stays constant over time. Such behavior is present for a very
+short range of $\nu$, and before $\nu \approx 0.24$, cooperators
+disappear for the rest of values of $\nu$. Finally, FOSISS network
+behaves similarly to the other networks in that there is a fall in the
+number of cooperators close to $\nu \approx 0.2$. In contrast with the
+other networks, the FOSISS network lacks the sharp reduction of
+cooperators, instead this population declines smoothly and
+progressively; specially, when it reaches a $\nu \approx 0.25$
+cooperators decrease in a less dramatic manner all the way to
+$\nu \approx 0.5$. It is also noteworthy that from $\nu = 0$ to $\nu
+\approx 0.5$ the number of cooperators converge to a certain degree
+and stays constant for the rest of the simulation.
 
@@
 \end{tabular}
-\caption{Proportion of cooperators as a function of carrying capacity and time.}\label{CD}
+\caption{Ratio of cooperators as a function of carrying capacity and time. Topologies are: A. Random, Erd\"{o}s-R\'enyi. B. Watts-Strogatz. C. Barab\'asi-Albert. D. FOSISS.
+}\label{CD}
 \end{figure}
@@
 
-Utility and strength of interactions dynamics under different $\nu$ emulate the
-phase transition found before. In \textbf{Figures 3 and 4}, it can be observed
+Utility and strength of interactions dynamics under different $\nu$ are similar to the
+phase transition found before. \textbf{Figures 3 and 4} show
 that there is a drop in utility and strength of interactions according to the
@@
 higher than the one given by default but soon starts to decrease as the
-simulation runs. For FOSISS network, utility and strength of interactions fall
-is quite steep but smooth, without sharp cuts. Between $\nu \approx 0.23$ and
+simulation runs. For the FOSISS network, utility and interaction strength fall
+quite steeply but smoothly, without sharp cuts. Between $\nu \approx 0.23$ and
 $\nu \approx 0.28$, utility and strength of interactions start at their lowest,
@@
 
-\includegraphics[scale=0.28]{images/erdos_fitness_nus_1.png} & \includegraphics[scale=0.28]{watts_fitness_nus_1.png} \\
-\includegraphics[scale=0.28]{images/barabasi_fitness_nus_1.png} & \includegraphics[scale=0.28]{fosiss_fitness_nus_1.png}
+\includegraphics[scale=0.28]{images/erdos_fitness_nus_1.png} & \includegraphics[scale=0.28]{images/watts_fitness_nus_1.png} \\
+\includegraphics[scale=0.28]{images/barabasi_fitness_nus_1.png} & \includegraphics[scale=0.28]{images/fosiss_fitness_nus_1.png}
 \end{tabular}
-\caption{Utility $U$ dynamics as a function of carrying capacity $\nu$ and time.}\label{fitness}
+\caption{Utility $U$ dynamics as a function of carrying capacity $\nu$ and time. Topologies are: A. Random, Erd\"{o}s-R\'enyi. B. Watts-Strogatz. C. Barab\'asi-Albert. D. FOSISS.}\label{fitness}
 \end{figure}
@@
 
-\includegraphics[scale=0.28]{images/erdos_trust_nus_1.png} & \includegraphics[scale=0.28]{watts_trust_nus_1.png} \\
-\includegraphics[scale=0.28]{images/barabasi_trust_nus_1.png} & \includegraphics[scale=0.28]{fosiss_trust_nus_1.png}
+\includegraphics[scale=0.28]{images/erdos_trust_nus_1.png} & \includegraphics[scale=0.28]{images/watts_trust_nus_1.png} \\
+\includegraphics[scale=0.28]{images/barabasi_trust_nus_1.png} & \includegraphics[scale=0.28]{images/fosiss_trust_nus_1.png}
 \end{tabular}
-\caption{Strength of interactions $w$ dynamics as a function of carrying capacity $\nu$ and time.}\label{trust}
+\caption{Strength of interactions $w$ dynamics as a function of carrying capacity $\nu$ and time.
+Topologies are: A.
+Random, Erd\"{o}s-R\'enyi.
+B.
+Watts-Strogatz.
+C.
+Barab\'asi-Albert.
+D.
+FOSISS.}\label{trust}
 \end{figure}
@@
 
-\includegraphics[scale=0.28]{images/erdos_state_nus.png} & \includegraphics[scale=0.28]{watts_state_nus.png} \\
-\includegraphics[scale=0.28]{images/barabasi_state_nus.png} & \includegraphics[scale=0.28]{fosiss_state_nus.png}
+\includegraphics[scale=0.28]{images/erdos_state_nus.png} & \includegraphics[scale=0.28]{images/watts_state_nus.png} \\
+\includegraphics[scale=0.28]{images/barabasi_state_nus.png} & \includegraphics[scale=0.28]{images/fosiss_state_nus.png}
 \end{tabular}
 \caption{Shifting population between cooperators and defectors as a function of
-  carrying capacity $\nu$ and time.}\label{state} 
+  carrying capacity $\nu$ and time. Topologies are: A. Random, Erd\"{o}s-R\'enyi. B. Watts-Strogatz. C. Barab\'asi-Albert. D. FOSISS.}\label{state} 
 \end{figure}
@@
 
-An interesting feature of highly communicated networks (characterized by high values of clustering coefficient) is the
-fact that certainty among players seems to be enhanced, that is, in such networks the rate of change of strategy is
-significantly lower (and smoother) than in poorly connected networks. This is another instance in which easier
-communication (i.e. lower average minimum path lengths) lead to better performance of the whole collaborative research
-system.\\
+An interesting feature of highly communicated networks (characterized
+by high values of clustering coefficient) is the fact that certainty
+among players seems to be enhanced, that is, in such networks the rate
+of change of strategy is significantly lower (and smoother) than in
+poorly connected networks. This is another instance in which easier
+communication (i.e. lower average minimum path lengths) leads to better
+performance of the whole collaborative research system.\\
 
@@
 
-{\color{red}In this work we have analyzed the influence of parameters given by the underlying social structure of a science
-collaborative network on collective strength of interactions and utility dynamical behavior, based on a class of iterated
-PD and coordination games. Such parameters include mainly local and global connectivity like the degree centrality and
-average clustering coefficient, as well as communication patterns.}\\
-
-{\color{red}Under the assumptions given by the model, we were able to notice
-  that, in general, communication within the social
-collaborative networks has a positive correlation with average strength of interactions between the individuals partaking in the games and
-also with the global collective utility (given by the sum of the individual payoffs). The better the
-communication among players, the higher the strength of interactions and the utility leading to an optimized functioning of the whole
-\emph{scientific collaboration system}. This is an important result that may be useful for scientific policy planning
-and may set a foundation for the optimal use of social networks in scientific collaboration as a means to improve the
-relationships among collaborating peers and thus ultimately the performance of research systems. 
-We obviously need more qualitative work in order to validate these results from a sociological and anthropological
-perspective.\\ %Furthermore, such validation is necessary because, as we said at
-             %the beginning of this work, \emph{strength of interactions} can
-             %have many different meanings and implementations in the real
-             %world. The same we can say about \emph{utility} and most of all,
-             %about the very idea of the game we explored here since ``playing
-             %the game'' must have so, many different meanings among resarchers
-             %and their communities.}\\
-
-{\color{red}To close this article, we would like to comment on three issues we consider important. The first one is about
-confronting our results with data available to us from the biomedical research community. Second, some remarks we believe are important
-about the role of computational simulations in the social sciences. Finally we would like to comment on our
-future work.}\\
-
-{\color{red}The two main results of our model are the smoothness in the phase transition-like behavior for different parameters and the distribution of utility and strength of interactions in the FOSISS network compared to other networks and their topologies.
-We are certain that the particular structure of FOSISS network is playing a central role in the results and because of that we would like to discuss it a little bit further.}\\
-
-{\color{red}FOSISS network is higly hierarchical according to its heterogeneity of $0.873$. Because of it, one would
-  expect to find the presence of important hubs \cite{Wu-etal2008}, that is, a few researchers control the whole
-  network, as has been reported in some other places \cite{yousefi-etal2008}. Surprisingly, FOSISS network
-  centralization is very low $0.023$, i.e. there are no researchers that centralize the majority of connections. Our
-  guess is that the network is composed of many small communities or groups with a central researcher or Principal
-  Investigator (PI). If this is the case in the FOSISS network, it means that those groups have a very hierarchic structure as well.}\\
-
-{\color{red}Under such structure, when the clustering coefficient is considered, it can be said that groups are also well connected
-but that inter-group connections are sparse. In other words, individual groups are strongly connected but the network
-as a whole is supported by a small number of links. We came by this idea partially from
-another study about scientific collaborations based on co-authorships in one of
-the research centers that is part 
-of the FOSISS network \cite{HernandezLemus2013}. In the cited reference an apparently well integrated community was
-found (high clustering coefficient and a very short characteristic path length). Such integration was mostly
-superficial, since it depended on the presence of external collaborators from other research institutions (most of them from overseas). 
-Removing these external collaborators broke down the network into small subgraphs that worked independently. Remarkably those subgraphs corresponded to the real
-groups of that research center.  What is more, several groups had a hierarchical structure as 
-the one we suspect is common in FOSISS subgraphs. The results showed that collaboration was poor between groups but strong
-among the members of each group, and that collaboration among groups doesn't emerge bottom-up, instead it seems to be promoted from the
-top, from the administrative authorities.}\\
-
-{\color{red}We believe that the the situation just refered is also true for the whole biomedical research community in M\'exico. The
-amount of PIs who have also been collaborators in other projects is about one fifth of the total number of participants.
-This is a number big enough to connect the whole network in one giant component. Yet, due to the topological
-characteristics of the FOSISS network, it appears to be the case that researchers can be the leaders in one project and
-collaborators of different project of \emph{its own research group}. CONACyT's funding policies makes it impossible for a
-researcher to get a grant from a fund if that researcher has an ongoing project with a grant from that same fund. That
-is, a researcher can ask for a grant from FOSISS if and only if at the moment he
-doesn't have a grant from FOSISS already. This
-policy has lead researchers from the same group to ask for grants from the same fund in order to rise their
-budgets. A consequence of this behavior is that group interactions get reinforced, but integroup connections not necessarily so.}\\
-
-{\color{red}As is common among scientific communities in biomedical research, PIs play a central role in the network. Strong PIs and
-well connected groups seem to be somehow responsible for the high levels of strength of interactions and the centralization of utility in
-our simulation. As for what seems to be phase transitions, in the case of FOSISS networks, these are smoother than
-those in the other networks with different topologies, even for those with a small-world topology. We think that this
-behavior is also the result of the hierarchical structure already mentioned. If this is true, strength of interactions is first lost in the
-edges that link diffrent goups and then in the edges that connect members of the groups. Connections between groups would not
-be as dense as those inside the groups, which means that there would not be enough information of the behavior of one group regarding
-its neighbors to constrain them as it seems to happen with individual researchers inside their communities. Nevertheless,
-if values of the carrying capacity $\nu$ keep increasing and it becomes more
-difficult to strengthen interactions, then strength of interactions begins to diminish inside groups.}\\
-
-{\color{red}Another issue that we would like to mention about FOSISS network topology is that it is not a robust collaboration network.
-At the level of groups, these might be well connected and consolidated but at the level of the network, this could be
-no more than an aggregate of individual groups. A robust network would be resistant to changes in the connections
-between groups but in the case of FOSISS, it seems that the network would brake down into
-small research groups by cutting some edges, as it happened in our co-authorship
-collaboration network \cite{HernandezLemus2013}. The lack of robustness might be 
-indicative of the fact that resources stay inside the groups, that is, they do not circulate through or articulate different communities. For
-example, one may think of certain expensive technologies for genomic research that could be bought once and shared
-among research groups, however, this doesn't seem to happen very often. There are some other
-consequences, such as low communication among groups, atomization of practices and know-hows, redundancy in equipment tenancy,
-difficulties for implementing community-wide infrastructures such as biobanks, etc.}\\
+{\color{red}In this work we have analyzed the influence of parameters
+  given by the underlying social structure of a science collaborative
+  network on collective strength of interactions and utility dynamical
+  behavior, based on a class of iterated PD and coordination
+  games. Such parameters include mainly local and global connectivity
+  like the degree centrality and average clustering coefficient, as
+  well as communication patterns.}\\
+
+{\color{red}Under the assumptions given by the model, we were able to
+  notice that, in general, communication within the social
+  collaborative networks has a positive correlation with average
+  strength of interactions between the individuals partaking in the
+  games and also with the global collective utility (given by the sum
+  of the individual payoffs). The better the communication among
+  players, the higher the strength of interactions and the utility
+  leading to an optimized functioning of the whole \emph{scientific
+    collaboration system}. This is an important result that may be
+  useful for scientific policy planning and may set a foundation for
+  the optimal use of social networks in scientific collaboration as a
+  means to improve the relationships among collaborating peers and
+  ultimately the performance of research systems.  We obviously need
+  more qualitative work in order to validate these results from a
+  sociological and anthropological perspective.\\
+
+%Furthermore, such validation is necessary because, as we said at
+%the beginning of this work, \emph{strength of
+%interactions} can have many different meanings and
+%implementations in the real world. The same we can say
+%about \emph{utility} and most of all, about the idea of the game we
+%explored here since ``playing the
+%game'' must have so, many different meanings among
+%resarchers and their communities.}\\
+
+{\color{red}To close this article, we would like to comment on three
+  issues we consider important. The first one is about confronting our
+  results with data available to us from the biomedical research
+  community. Second, some remarks we believe are important about the
+  role of computational simulations in the social sciences. Finally we
+  would like to comment on our future work.}\\
+
+{\color{red}The two main results of our model are the smoothness in
+  the phase transition-like behavior for different parameters and the
+  distribution of utility and strength of interactions in the FOSISS
+  network compared to other networks and their topologies. We are
+  certain that the particular structure of FOSISS network is playing a
+  central role in the results and because of that we would like to
+  discuss it a little bit further.}\\
+
+{\color{red}FOSISS network is higly hierarchical according to its
+  heterogeneity of $0.873$. Because of it, one would expect to find
+  the presence of important hubs \cite{Wu-etal2008}, that is, a few
+  researchers control the whole network, as has been reported in some
+  other places \cite{yousefi-etal2008}. Surprisingly, FOSISS network
+  centralization is very low $0.023$, i.e. there are no researchers
+  that centralize the majority of connections. Our guess is that the
+  network is composed of many small communities or groups with a
+  central researcher or Principal Investigator (PI). If this is the
+  case in the FOSISS network, it means that those groups have a very
+  hierarchic structure as well.}\\
+
+{\color{red}Under such structure, when the clustering coefficient is
+  considered, it can be said that groups are also well connected but
+  that inter-group connections are sparse. In other words, individual
+  groups are strongly connected within but the network as a whole is
+  supported by a small number of links. We came by this idea partially
+  from another study about scientific collaborations based on
+  co-authorships in one of the research centers that is part of the
+  FOSISS network \cite{HernandezLemus2013}. In the cited reference an
+  apparently well integrated community was found (high clustering
+  coefficient and a very short characteristic path length). Such
+  integration was mostly superficial, since it depended on the
+  presence of external collaborators from other research institutions
+  (most of them from overseas).  Removing these external collaborators
+  broke down the network into small subgraphs that worked
+  independently. Remarkably those subgraphs corresponded to the real
+  groups of that research center.  What is more, several groups had a
+  hierarchical structure as the one we suspect is common in FOSISS
+  subgraphs. The results showed that collaboration was poor between
+  groups but strong among the members of each group, and that
+  collaboration among groups doesn't emerge bottom-up, instead it
+  seems to be promoted from the top, from the administrative
+  authorities.}\\
+
+{\color{red}We believe that the the situation just refered is also
+  true for the whole biomedical research community in M\'exico. The
+  amount of PIs who have also been collaborators in other projects is
+  about one fifth of the total number of participants.  This is a
+  number big enough to connect the whole network in one giant
+  component. Yet, due to the topological characteristics of the FOSISS
+  network, it appears to be the case that researchers can be the
+  leaders in one project and collaborators of different project of
+  \emph{its own research group}. CONACyT's funding policies makes it
+  impossible for a researcher to get a grant from a fund if that
+  researcher has an ongoing project with a grant from that same
+  fund. That is, a researcher can ask for a grant from FOSISS if and
+  only if at the moment he doesn't already have one
+  This policy has lead researchers from the same group to ask
+  for grants from the same fund in order to rise their budgets. A
+  consequence of this behavior is that group interactions get
+  reinforced, but integroup connections not necessarily so.}\\
+
+{\color{red}As is common among scientific communities in biomedical
+  research, PIs play a central role in the network. Strong PIs and
+  well connected groups seem to be somehow responsible for the high
+  levels of strength of interactions and the centralization of utility
+  in our simulation. As for what seems to be phase transitions, in the
+  case of FOSISS networks, these are smoother than those in the other
+  networks with different topologies, even for those with a
+  small-world topology. We think that this behavior is also the result
+  of the hierarchical structure already mentioned. If this is true,
+  strength of interactions is first lost in the edges that link
+  diffrent goups and then in the edges that connect members of the
+  groups. Connections between groups would not be as dense as those
+  inside the groups, which means that there would not be enough
+  information of the behavior of one group regarding its neighbors to
+  constrain them as it seems to happen with individual researchers
+  inside their communities. Nevertheless, if values of the carrying
+  capacity $\nu$ keep increasing and it becomes more difficult to
+  strengthen interactions, then strength of interactions begins to
+  diminish inside groups.}\\
+
+{\color{red}Another issue that we would like to mention about FOSISS
+  network topology is that it is not a robust collaboration network.
+  At the level of groups, these might be well connected and
+  consolidated but at the level of the network, this could be no more
+  than an aggregate of individual groups. A robust network would be
+  resistant to changes in the connections between groups but in the
+  case of FOSISS, it seems that the network would brake down into
+  small research groups by cutting some edges, as it happened in our
+  co-authorship collaboration network \cite{HernandezLemus2013}. The
+  lack of robustness might be indicative of the fact that resources
+  stay inside the groups, that is, they do not circulate through or
+  articulate different communities. For example, one may think of
+  certain expensive technologies for genomic research that could be
+  bought once and shared among research groups, however, this doesn't
+  seem to happen very often. There are some other consequences, such
+  as low communication among groups, atomization of practices and
+  know-hows, redundancy in equipment tenancy, difficulties for
+  implementing community-wide infrastructures such as biobanks,
+  etc.}\\
 
@@
 
-{\color{red}On these grounds, part of our future work is based on some of the results presented here. We would like to
-identify researchers in our simulations and corroborate their situation in the model and in the real world. We are
-also interested in going back to the field and interviewing those groups with an interesting behavior found in our
-simulations, probably we would follow a similar strategy as the one developed in \cite{Haraetal2003}. Finding
-communities beyond the level of the groups is an important task. We think that there are many possibilities that emerge
-from the integration of different methodologies. Moreover, studying social processes in science is particularly
-attractive due to the amounts of data already available that can be easily collected. This is a privilege because
-simulations can be designed on real world data, something that only very recently has become possible
-\cite{Barabasi2011}.\\
-
-No doubt, social sciences are getting more ``computational''. This can be seen everywhere, but curiously enough,
-disciplines like physicis and computer science are the ones who are moving towards the social sciences and not so much
-the other way around. It might be the case that the pioneering disciplines in the computational social sciences will set
-the agenda, an agenda that will apparently be mostly based on taking advantage of big data and on hypothesis-free approaches. We
-believe that the social sciences have important questions that should be added to that agenda and those questions may not
-be answered only by big data techniques but they may require creating models and simulations in the style of the best
-hypothesis-driven research.}
+{\color{red}On these grounds, part of our future work is based on
+  the results presented here. We would like to identify researchers
+  in our simulations and corroborate their situation in the model and
+  in the real world. We are also interested in going back to the field
+  and interviewing those groups with an interesting behavior found in
+  our simulations, probably we would follow a similar strategy as the
+  one developed in \cite{Haraetal2003}. Finding communities beyond the
+  level of the groups is an important task. We think that there are
+  many possibilities that emerge from the integration of different
+  methodologies. Moreover, studying social processes in science is
+  particularly attractive due to the amounts of data already available
+  that can be easily collected. This is a privilege because
+  simulations can be designed on real world data, something that only
+  very recently has become possible \cite{Barabasi2011}.\\
+
+No doubt, social sciences are becoming more ``computational''. This can
+be seen everywhere, but curiously enough, disciplines like physicis
+and computer science are moving towards the social
+sciences and not so much the other way around. It might be the case
+that the pioneering disciplines in the computational social sciences
+will set the agenda, an agenda that will apparently be mostly based on
+taking advantage of big data and on hypothesis-free approaches. We
+believe that the social sciences have important questions that should
+be added to that agenda and those questions may not be answered only
+by big data techniques but they may require creating models and
+simulations in the style of the best hypothesis-driven research.}
 
@@
 
-\section{acknowledgements}
+\section{Acknowledgements}
 The authors gratefully acknowledge support by grants: CB-222220-R/2013 and

### 2016-11-23 manuscript_3.tex
caught typo!
New abstract and removed red color from paragraphs.

@@
 
-  What would happen if researchers in a community were given the same
-  amount of resources and then set free to interact among each other?
-  How would these resources be distributed in the population after
-  many interactions? The final result may be determined by the
-  researchers' social and political power, an by their
-  prestige. Nevertheless, all these attributes depend, to a certain
-  degree, on the research collaboration social network in which
-  scientists are embedded. Here we develop a model based on the
-  Prisoner's Dilemma implemented on a collaboration network. With this
-  model we explore the distribution of resources and the dynamics of
-  the strengthening or weakening of collaboration interactions among
-  partners, as scientists cooperate or defect in order to gain access
-  to resources shared by others. The network is based on data about projects
-  that were awarded with a grant. In this sense, we assume that
-  resources are funds, equipment and time. We define Fitness as how
-  much access a researcher has to the resources of his collegues.  We
-  tested our simulation on the real biomedical research network and
+Collaboration has become a cornerstone in biomedical research today.
+In contrast to physics which has a long history and experience in
+collaborative projects, biology is only recently becoming an evermore
+collaborative discipline.
+In this article we explore the effect of a collaboraion network on the distribution
+of players having access to certain amount of resources from other players in the
+network and the distribution of the strength of connections among
+them. Particularly, we implemented two games played simultaneously:
+one for maximazing individual utility based on the iterated Prisoner's
+Dilemma; the other, a coordination game for maximazing the connection strength between
+players. We are interested in how they affect each other in 
+the context of a network of scientific collaboration under the idea that while
+researchers are interested in maximazing their utilities, they also know that
+it is important to invest in building collaborative relationships.
+We tested our simulation on a biomedical research community network of M\'exico. and
 compared the results with an Erd\"{o}s-Reny\'i, a Watts-Strogatz
 small-world and Barab\'asi-Albert topologies. Different topologies
-  display different fitness and connections strength
-  distributions. Moreover, the distribution of fitness and connections
-  strength in the researchers network is similar to that of
+display different utility and attachment
+distributions. Moreover, the distribution of utility and attachment in the
+researchers network is similar to that of 
 Barab\'asi-Albert and Watts-Strogatz topologies, respectively. We
-  believe that fitness distribution in the researchers network
+believe that utility distribution in the researchers network
 suggests that there are socio-cultural mechanisms governing the
@@
 
- {\color{red}In this article we explore the network effect on the distribution
+ In this article we explore the network effect on the distribution
    of players having access to certain amount of resources shared by other players in the
@@
    it is important to invest in building collaborative relationships. These two
-   behaviors are explored in a biomedical research community of M\'exico.}\\
-
-{\color{red}In the context of our paper, utility represents
+   behaviors are explored in a biomedical research community of M\'exico.\\
+
+In the context of our paper, utility represents
   access to resources shared by others.
@@
   to a cooperator are ghost authorship or
-  prestige authorship.
-
-  % TODO: este ejemplo de defection no es nada claro:
-  %
-  % Another example may be a working strategy in which some
-  % members of a team do the work at certain moment, and then another part 
-  % does its part in some other moment in the future --some sort of
-  % reciprocity.
-
-}
+  prestige authorship.\\
 
@@
 of different topologies on the emergence of cooperation
-\cite{Santos2005,Hauert2004}. {\color{red}In our model, an agent's decision to cooperate or
+\cite{Santos2005,Hauert2004}. In our model, an agent's decision to cooperate or
 defect depends on a balance between
 utilities and the current strength of its collaboration relationships. Such
-balance reflects the overall success or failure of its strategies}. We
+balance reflects the overall success or failure of its strategies. We
 study the behavior of the system under different topologies, including a
@@
 
-{\color{red} It should be noted that the same actions or behaviors work for
+It should be noted that the same actions or behaviors work for
   both $u$ and $w$. There are two reasons for this decision in the design of the
@@
 endure occasional defection. Cooperating may build up relationships but it can be
-expensive for the player.}
+expensive for the player.
 
@@
 number ($\eta$) that referes to a historical balance between average utility and
-the average strength of the connections with its neigbors.   {\color{red} This is so
+the average strength of the connections with its neigbors. This is so
   because we assume that whatever the result in utility or strength of
   connection, as long as one of them increases, the player will be confident in
-  the strategy followed so far}.\\
+  the strategy followed so far.\\
 
@@
 
-{\color{red} For the agent to decide whether to cooperate or not, $\eta$ is
+ For the agent to decide whether to cooperate or not, $\eta$ is
   compared to a global threshold $\nu$. If the agents' $\eta$ $>$ $\nu$,
@@
   of collaboration relationships, $\eta$ represents the carrying capacity of the
-  system for the population of cooperators}.
+  system for the population of cooperators.\\
 
@@
 
-{\color{red}In this work we have analyzed the influence of parameters
+In this work we have analyzed the influence of parameters
   given by the underlying social structure of a science collaborative
@@
   like the degree centrality and average clustering coefficient, as
-  well as communication patterns.}\\
-
-{\color{red}Under the assumptions given by the model, we were able to
+  well as communication patterns.\\
+
+  Under the assumptions given by the model, we were able to
   notice that, in general, communication within the social
@@
 %game'' must have so, many different meanings among
-%resarchers and their communities.}\\
-
-{\color{red}To close this article, we would like to comment on three
+%resarchers and their communities.\\
+
+ To close this article, we would like to comment on three
   issues we consider important. The first one is about confronting our
@@
   role of computational simulations in the social sciences. Finally we
-  would like to comment on our future work.}\\
-
-{\color{red}The two main results of our model are the smoothness in
+  would like to comment on our future work.\\
+
+  The two main results of our model are the smoothness in
   the phase transition-like behavior for different parameters and the
@@
   central role in the results and because of that we would like to
-  discuss it a little bit further.}\\
-
-{\color{red}FOSISS network is higly hierarchical according to its
+  discuss it a little bit further.\\
+
+  FOSISS network is higly hierarchical according to its
   heterogeneity of $0.873$. Because of it, one would expect to find
@@
   case in the FOSISS network, it means that those groups have a very
-  hierarchic structure as well.}\\
-
-{\color{red}Under such structure, when the clustering coefficient is
+  hierarchic structure as well.\\
+
+  Under such structure, when the clustering coefficient is
   considered, it can be said that groups are also well connected but
@@
   seems to be promoted from the top, from the administrative
-  authorities.}\\
-
-{\color{red}We believe that the the situation just refered is also
+  authorities.\\
+
+  We believe that the the situation just refered is also
   true for the whole biomedical research community in M\'exico. The
@@
   consequence of this behavior is that group interactions get
-  reinforced, but integroup connections not necessarily so.}\\
-
-{\color{red}As is common among scientific communities in biomedical
+  reinforced, but integroup connections not necessarily so.\\
+
+ As is common among scientific communities in biomedical
   research, PIs play a central role in the network. Strong PIs and
@@
   strengthen interactions, then strength of interactions begins to
-  diminish inside groups.}\\
-
-{\color{red}Another issue that we would like to mention about FOSISS
+  diminish inside groups.\\
+
+  Another issue that we would like to mention about FOSISS
   network topology is that it is not a robust collaboration network.
@@
   implementing community-wide infrastructures such as biobanks,
-  etc.}\\
+  etc. \\
 
@@
 
-{\color{red}On these grounds, part of our future work is based on
+On these grounds, part of our future work is based on
   the results presented here. We would like to identify researchers
@@
 by big data techniques but they may require creating models and
-simulations in the style of the best hypothesis-driven research.}
+simulations in the style of the best hypothesis-driven research.
 

### 2016-11-27 manuscript_3.tex
caught some "attachments"

@@
 collaborative projects, biology is only recently becoming an evermore
-collaborative discipline.
-In this article we explore the effect of a collaboraion network on the distribution
-of players having access to certain amount of resources from other players in the
-network and the distribution of the strength of connections among
-them. Particularly, we implemented two games played simultaneously:
-one for maximazing individual utility based on the iterated Prisoner's
-Dilemma; the other, a coordination game for maximazing the connection strength between
-players. We are interested in how they affect each other in 
-the context of a network of scientific collaboration under the idea that while
-researchers are interested in maximazing their utilities, they also know that
-it is important to invest in building collaborative relationships.
-We tested our simulation on a biomedical research community network of M\'exico. and
-compared the results with an Erd\"{o}s-Reny\'i, a Watts-Strogatz
-small-world and Barab\'asi-Albert topologies. Different topologies
-display different utility and attachment
-distributions. Moreover, the distribution of utility and attachment in the
-researchers network is similar to that of 
-Barab\'asi-Albert and Watts-Strogatz topologies, respectively. We
-believe that utility distribution in the researchers network
-suggests that there are socio-cultural mechanisms governing the
-network that produce an asymmetric distribution of resources. The
-high distribution of strong connections might reflect some sort of
+collaborative discipline.  In this article we explore the effect of
+collaboraion on the distribution of players' access to resources from
+other players in the network and the distribution of the strength of
+interactions among them. Particularly, we implemented two games played
+simultaneously: one for maximazing individual utility based on the
+iterated Prisoner's Dilemma; the other, a coordination game for
+maximazing the connection strength between players. We are interested
+in how they affect each other in the context of a network of
+scientific collaboration under the idea that while researchers are
+interested in maximazing their individual utilities, they also know
+that it is important to invest in building collaborative
+relationships.  We tested our simulation on a biomedical research
+community network of M\'exico and compared the results with an
+Erd\"{o}s-Reny\'i, a Watts-Strogatz small-world and Barab\'asi-Albert
+topologies. Different topologies display different utility and
+interaction strength distributions. Moreover, the distribution of
+utility and interaction strength in the researchers network is similar
+to that of Barab\'asi-Albert and Watts-Strogatz topologies,
+respectively. We believe that utility distribution in the researchers
+network suggests that there are socio-cultural mechanisms governing
+the network that produce an asymmetric distribution of resources. The
+high distribution of strong interactions might reflect some sort of
 subordination among researchers by which they are morally obliged to
-cooperate by the same socio-cultural mechanisms. The range around
-the threshold that regulates the decision to cooperate or defect
-according to the agent's historical balance between utility and
-strength of collaborative relationships and carrying capacity of the
-system is small, suggesting that there is a region in which a phase
-transition takes place from a population of cooperators to a
-population of defectors. Simulations like this may help to develop
-science policies to promote fair distribution of resources.
+cooperate by the same socio-cultural mechanisms. The range around the
+threshold that regulates the decision to cooperate or defect according
+to the agent's historical balance between utility and strength of
+collaborative relationships and carrying capacity of the system is
+small, suggesting that there is a region in which a phase transition
+takes place from a population of cooperators to a population of
+defectors. Simulations like this may help to develop science policies
+to promote fair distribution of resources.
 

### 2016-11-27 manuscript_3.tex
ran ispell, caught many a typo

@@
 collaborative discipline.  In this article we explore the effect of
-collaboraion on the distribution of players' access to resources from
+collaboration on the distribution of players' access to resources from
 other players in the network and the distribution of the strength of
 interactions among them. Particularly, we implemented two games played
-simultaneously: one for maximazing individual utility based on the
+simultaneously: one for maximizing individual utility based on the
 iterated Prisoner's Dilemma; the other, a coordination game for
-maximazing the connection strength between players. We are interested
+maximizing the connection strength between players. We are interested
 in how they affect each other in the context of a network of
 scientific collaboration under the idea that while researchers are
-interested in maximazing their individual utilities, they also know
+interested in maximizing their individual utilities, they also know
 that it is important to invest in building collaborative
@@
    them. Particularly, we implemented two games played simultaneously: 
-   one for maximazing individual utility based on the iterated Prisoner's
-   Dilemma; the other, a coordination game for maximazing the connection strength between
+   one for maximizing individual utility based on the iterated Prisoner's
+   Dilemma; the other, a coordination game for maximizing the connection strength between
    players. We are interested in how they affect each other in 
    the context of a network of scientific collaboration under the idea that while
-   researchers are interested in maximazing their utilities, they also know that
+   researchers are interested in maximizing their utilities, they also know that
    it is important to invest in building collaborative relationships. These two
@@
   The value of the Utility function for a player is the sum of the payoffs of playing
-  with its neighbors. The opossing force comes from the other concurrent game: players
+  with its neighbors. The opposing force comes from the other concurrent game: players
   trying to maximize the strength of their interactions with other players. In the coordinating game
@@
 $N$. In this game, the best action for any agent is to coordinate with its
-neighbor, either beacuse it wins or because it doesn't loose. \\
+neighbor, either because it wins or because it doesn't loose. \\
 
@@
 All networks are initialized equally. The number of nodes for every network is 4122, the same as in the FOSISS network.
-The same utility is given to every agent and all edges are asigned the same weight. In the case of the FOSISS
+The same utility is given to every agent and all edges are assigned the same weight. In the case of the FOSISS
 network, edge weight is given by the number of collaborations among researchers, utility remains the same for all nodes as in
@@
 The probability for an agent to cooperate or defect depends on a
-number ($\eta$) that referes to a historical balance between average utility and
-the average strength of the connections with its neigbors. This is so
+number ($\eta$) that represents a historical balance between average utility and
+the average strength of the connections with its neighbors. This is so
   because we assume that whatever the result in utility or strength of
@@
 Data included names of Principal Investigators, collaborators, research topics, etc.
-The network we are using here has researchers as nodes and edges represent the connection of two scientists when they colaborate on the same project.
+The network we are using here has researchers as nodes and edges represent the connection of two scientists when they collaborate on the same project.
 Edges are also weighted according to the number of projects shared by any pair of scientists.\\
@@
 \includegraphics[scale=0.5]{images/Fosiss_GC_final.png}
-\caption{Bioemdical research collaboration network (FOSISS) giant component.}\label{Fosiss_GC}
+\caption{Biomedical research collaboration network (FOSISS) giant component.}\label{Fosiss_GC}
 \end{figure}
@@
 
-  FOSISS network is higly hierarchical according to its
+  FOSISS network is highly hierarchical according to its
   heterogeneity of $0.873$. Because of it, one would expect to find
@@
   consequence of this behavior is that group interactions get
-  reinforced, but integroup connections not necessarily so.\\
+  reinforced, but intergroup connections not necessarily so.\\
 
@@
   strength of interactions is first lost in the edges that link
-  diffrent goups and then in the edges that connect members of the
+  different groups and then in the edges that connect members of the
   groups. Connections between groups would not be as dense as those
@@
 No doubt, social sciences are becoming more ``computational''. This can
-be seen everywhere, but curiously enough, disciplines like physicis
+be seen everywhere, but curiously enough, disciplines like physics
 and computer science are moving towards the social
@@
 
-\section{Acknowledgements}
+\section{Acknowledgments}
 The authors gratefully acknowledge support by grants: CB-222220-R/2013 and

### 2016-11-29 gt_trust_network/histogram_from_average.py
include auxiliary scripts for plotting and such

@@ -1,0 +1,33 @@
+import argparse
+import csv
+import numpy as np
+
+parser = argparse.ArgumentParser(description='generate bins from histogram file')
+parser.add_argument('--csv', type=argparse.FileType('r'))
+args = parser.parse_args()
+
+
+reader = csv.reader(args.csv)
+
+h = []
+for row in reader:
+    h.append([float(j) for j in row])
+
+#from pprint import pprint
+#pprint(h)
+    
+# minbin = min(h[0])
+# maxbin = max(h[-1])
+
+
+# interval = (maxbin - minbin) / 100
+
+# bins = np.arange(minbin, maxbin, interval)
+
+counts, bins = np.histogram(h[-1], bins=100)
+
+
+for a in h:
+    c = [j for j in a]
+    counts, b= np.histogram(c, bins=100)
+    print ",".join([str(j) for j in counts])

### 2016-11-29 gt_trust_network/plot_dynamics.py

@@ -1,0 +1,24 @@
+import matplotlib
+matplotlib.use('svg')
+import matplotlib.pyplot as plt
+import pylab as pl
+import argparse
+
+parser = argparse.ArgumentParser(description='Plot dynamics file')
+parser.add_argument('--file', type=argparse.FileType('r'))
+parser.add_argument('--plot', type=argparse.FileType('w'))
+parser.add_argument('--label', default='label')
+args = parser.parse_args()
+
+values = [float(l.strip()) for l in args.file.readlines()]
+
+fig = plt.figure(figsize=(23.5, 13.0))
+ax1 = fig.add_subplot(111)
+
+ax1.plot(range(0,len(values)), values, 'b-')
+
+ax1.set_xlabel('Time')
+ax1.set_ylabel(args.label)
+    
+plt.savefig(args.plot, dpi=300)
+

### 2017-01-10 manuscript_3.tex

@@
   leaders in one project and collaborators of different project of
-  \emph{its own research group}. CONACyT's funding policies makes it
+  \emph{its own research group}. CONACyT's funding policies make it
   impossible for a researcher to get a grant from a fund if that
@@
   fund. That is, a researcher can ask for a grant from FOSISS if and
-  only if at the moment he doesn't already have one
+  only if at the moment he doesn't already have one.
   This policy has lead researchers from the same group to ask

### 2017-01-10 bmc_template/casm.tex
bmc stuff

--- 2016-11-27 manuscript_3.tex
@@
-\documentclass[11pt]{article}                     
-\usepackage{graphicx}
-\usepackage[section]{placeins}
-\usepackage{color}
-\usepackage{lineno}
-\linenumbers
-%
-% \usepackage{mathptmx}      % use Times fonts if available on your TeX system
-%
-% insert here the call for the packages your document requires
-%\usepackage{latexsym}
-% etc.
-%
-% please place your own definitions here and don't use \def but
-% \newcommand{}{}
-%
-% Insert the name of "your journal" with
-% \journalname{myjournal}
-%
+%% BioMed_Central_Tex_Template_v1.06
+%%                                      %
+%  bmc_article.tex            ver: 1.06 %
+%                                       %
+
+%%IMPORTANT: do not delete the first line of this template
+%%It must be present to enable the BMC Submission system to
+%%recognise this template!!
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%                                     %%
+%%  LaTeX template for BioMed Central  %%
+%%     journal article submissions     %%
+%%                                     %%
+%%          <8 June 2012>              %%
+%%                                     %%
+%%                                     %%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%                                                                 %%
+%% For instructions on how to fill out this Tex template           %%
+%% document please refer to Readme.html and the instructions for   %%
+%% authors page on the biomed central website                      %%
+%% http://www.biomedcentral.com/info/authors/                      %%
+%%                                                                 %%
+%% Please do not use \input{...} to include other tex files.       %%
+%% Submit your LaTeX manuscript as one .tex document.              %%
+%%                                                                 %%
+%% All additional figures and files should be attached             %%
+%% separately and not embedded in the \TeX\ document itself.       %%
+%%                                                                 %%
+%% BioMed Central currently use the MikTex distribution of         %%
+%% TeX for Windows) of TeX and LaTeX.  This is available from      %%
+%% http://www.miktex.org                                           %%
+%%                                                                 %%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%% additional documentclass options:
+%  [doublespacing]
+%  [linenumbers]   - put the line numbers on margins
+
+%%% loading packages, author definitions
+
+%\documentclass[twocolumn]{bmcart}% uncomment this for twocolumn layout and comment line below
+\documentclass{bmcart}
+
+%%% Load packages
+%\usepackage{amsthm,amsmath}
+%\RequirePackage{natbib}
+%\RequirePackage[authoryear]{natbib}% uncomment this for author-year bibliography
+%\RequirePackage{hyperref}
+\usepackage[utf8]{inputenc} %unicode support
+%\usepackage[applemac]{inputenc} %applemac support if unicode package fails
+%\usepackage[latin1]{inputenc} %UNIX support if unicode package fails
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%                                             %%
+%%  If you wish to display your graphics for   %%
+%%  your own use using includegraphic or       %%
+%%  includegraphics, then comment out the      %%
+%%  following two lines of code.               %%
+%%  NB: These line *must* be included when     %%
+%%  submitting to BMC.                         %%
+%%  All figure files must be submitted as      %%
+%%  separate graphics through the BMC          %%
+%%  submission process, not included in the    %%
+%%  submitted article.                         %%
+%%                                             %%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\def\includegraphic{}
+\def\includegraphics{}
+
+%%% Put your definitions there:
+\startlocaldefs
+\endlocaldefs
+
+%%% Begin ...
 \begin{document}
 
-\title{A game-theory modeling approach to utility
-  and strength of interactions dynamics in biomedical research social networks}
-%\title{Two games modeling approach to collaboration dynamics in biomedical
-%research social networks}
-
-%\thanks{Grants or other notes
-%about the article that should go on the front page should be
-%placed here. General acknowledgments should be placed at the end of the article.}
-
-%\subtitle{Do you have a subtitle?\\ If so, write it here}
-
-%\titlerunning{Fitness \& trust in biomedical research networks}
-
-%\titlerunning{Short form of title}        % if too long for running head
-
-\author{J. Mario Siqueiros-Garc\'ia         \and      Rodrigo Garc\'ia-Herrera \and         Enrique Hern\'andez-Lemus \and
-        Sergio A. Alcal\'a-Corona  %etc.
+%%% Start of article front matter
+\begin{frontmatter}
+
+\begin{fmbox}
+\dochead{Research}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%                                          %%
+%% Enter the title of your article here     %%
+%%                                          %%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\title{A game-theory modeling approach to utility and strength of interactions dynamics in biomedical research social networks}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%                                          %%
+%% Enter the authors here                   %%
+%%                                          %%
+%% Specify information, if available,       %%
+%% in the form:                             %%
+%%   <key>={<id1>,<id2>}                    %%
+%%   <key>=                                 %%
+%% Comment or delete the keys which are     %%
+%% not used. Repeat \author command as much %%
+%% as required.                             %%
+%%                                          %%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\author[
+   addressref={aff1,aff2},                   % id's of addresses, e.g. {aff1,aff2}
+   corref={aff1},                       % id of corresponding address, if any
+   noteref={n1},                        % id's of article notes, if any
+   email={jmario.siqueiros@iimas.unam.mx}   % email address
+]{\inits{JMSG}\fnm{J. Mario} \snm{Siqueiros-Garc\'ia}}
+\author[
+   addressref={aff2},
+   email={rgarcia@ie.unam.mx}
+]{\inits{RGH}\fnm{Rodrigo} \snm{Garc\'ia-Herrera}}
+\author[
+   addressref={aff3},
+   email={ehernandez@inmegen.mx}
+]{\inits{EHL}\fnm{Enrique} \snm{Hern\'andez-Lemus}}
+\author[
+   addressref={aff3},
+   email={sergio.alcala@ciencias.unam.mx}
+]{\inits{SAC}\fnm{Sergio} \snm{Alcal\'a-Corona}}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%                                          %%
+%% Enter the authors' addresses here        %%
+%%                                          %%
+%% Repeat \address commands as much as      %%
+%% required.                                %%
+%%                                          %%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\address[id=aff1]{%                           % unique id
+  \orgname{IIMAS, Universidad Nacional Aut\'onoma de M\'exico}, % university, etc
+  \street{Circuito Escolar 3000, Cd. Universitaria},                     %
+  \postcode{04510}                                % post or zip code
+  \city{Mexico City},                              % city
+  \cny{Mexico}                                    % country
 }
-
-%\authorrunning{Short form of author list} % if too long for running head
-
-%% \institute{J. Mario Siqueiros-Garc\'ia \at
-%%   IIMAS-UNAM. Circuito Escolar 3000, Cd Universitaria, Coyoacán, Ciudad de México, D.F. \\
-%%               Tel.: +123-45-678910\\
-%%               Fax: +123-45-678910\\
-%%               \email{jmario.siqueiros@iimas.unam.mx}           %  \\
-%% %             \emph{Present address:} of F. Author  %  if needed
-%%               \and
-%%               Rodrigo Garc\'ia-Herrera,\\ Enrique Hern\'andez-Lemus, \\ Sergio A. Alcal\'a-Corona \at
-%%               National Institute of Genomic Medicine\\
-%%               Perif\'erico Sur 4809, Arenal Tepepan, Tlalpan, 14610, \\
-%%               Ciudad de M\'exico, D.F., M\'exico  
-%%            %% S. Author \at
-%%            %%    second address
-%% }
-
-\date{\today}
-% The correct dates will be entered by the editor
-
-\maketitle
-
-\begin{abstract}
-
+\address[id=aff2]{%
+  \orgname{LANCIS-IE, Universidad Nacional Aut\'onoma de M\'exico},
+  \street{Ciudad Universitaria},
+  \postcode{04510}
+  \city{Mexico City},
+  \cny{Mexico}
+}
+\address[id=aff3]{%
+  \orgname{Instituto Nacional de Medicina Gen\'omica},
+  \street{Periferico Sur 4809},
+  \postcode{14610}
+  \city{Mexico City},
+  \cny{Mexico}
+}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%                                          %%
+%% Enter short notes here                   %%
+%%                                          %%
+%% Short notes will be after addresses      %%
+%% on first page.                           %%
+%%                                          %%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\begin{artnotes}
+%\note{Sample of title note}     % note to the article
+\note[id=n1]{Equal contributor} % note, connected to author
+\end{artnotes}
+
+\end{fmbox}% comment this for two column layout
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%                                          %%
+%% The Abstract begins here                 %%
+%%                                          %%
+%% Please refer to the Instructions for     %%
+%% authors on http://www.biomedcentral.com  %%
+%% and include the section headings         %%
+%% accordingly for your article type.       %%
+%%                                          %%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\begin{abstractbox}
+
+\begin{abstract} % abstract
+%\parttitle{First part title} %if any
 Collaboration has become a cornerstone in biomedical research today.
@@
 collaborative projects, biology is only recently becoming an evermore
-collaborative discipline.  In this article we explore the effect of
-collaboraion on the distribution of players' access to resources from
-other players in the network and the distribution of the strength of
-interactions among them. Particularly, we implemented two games played
-simultaneously: one for maximazing individual utility based on the
-iterated Prisoner's Dilemma; the other, a coordination game for
-maximazing the connection strength between players. We are interested
-in how they affect each other in the context of a network of
-scientific collaboration under the idea that while researchers are
-interested in maximazing their individual utilities, they also know
-that it is important to invest in building collaborative
-relationships.  We tested our simulation on a biomedical research
-community network of M\'exico and compared the results with an
-Erd\"{o}s-Reny\'i, a Watts-Strogatz small-world and Barab\'asi-Albert
-topologies. Different topologies display different utility and
-interaction strength distributions. Moreover, the distribution of
-utility and interaction strength in the researchers network is similar
-to that of Barab\'asi-Albert and Watts-Strogatz topologies,
-respectively. We believe that utility distribution in the researchers
-network suggests that there are socio-cultural mechanisms governing
-the network that produce an asymmetric distribution of resources. The
-high distribution of strong interactions might reflect some sort of
+collaborative discipline.
+In this article we explore the effect of a collaboraion network on the distribution
+of players having access to certain amount of resources from other players in the
+network and the distribution of the strength of connections among
+them. Particularly, we implemented two games played simultaneously:
+one for maximazing individual utility based on the iterated Prisoner's
+Dilemma; the other, a coordination game for maximazing the connection strength between
+players. We are interested in how they affect each other in 
+the context of a network of scientific collaboration under the idea that while
+researchers are interested in maximazing their utilities, they also know that
+it is important to invest in building collaborative relationships.
+We tested our simulation on a biomedical research community network of M\'exico. and
+compared the results with an Erd\"{o}s-Reny\'i, a Watts-Strogatz
+small-world and Barab\'asi-Albert topologies. Different topologies
+display different utility and attachment
+distributions. Moreover, the distribution of utility and attachment in the
+researchers network is similar to that of 
+Barab\'asi-Albert and Watts-Strogatz topologies, respectively. We
+believe that utility distribution in the researchers network
+suggests that there are socio-cultural mechanisms governing the
+network that produce an asymmetric distribution of resources. The
+high distribution of strong connections might reflect some sort of
 subordination among researchers by which they are morally obliged to
-cooperate by the same socio-cultural mechanisms. The range around the
-threshold that regulates the decision to cooperate or defect according
-to the agent's historical balance between utility and strength of
-collaborative relationships and carrying capacity of the system is
-small, suggesting that there is a region in which a phase transition
-takes place from a population of cooperators to a population of
-defectors. Simulations like this may help to develop science policies
-to promote fair distribution of resources.
-
+cooperate by the same socio-cultural mechanisms. The range around
+the threshold that regulates the decision to cooperate or defect
+according to the agent's historical balance between utility and
+strength of collaborative relationships and carrying capacity of the
+system is small, suggesting that there is a region in which a phase
+transition takes place from a population of cooperators to a
+population of defectors. Simulations like this may help to develop
+science policies to promote fair distribution of resources.
+
+%\parttitle{Second part title} %if any
+Text for this section.
 \end{abstract}
 
-\section{Introduction}
-\label{intro}
-
-%% \textbf{Notes:}
-
-%% \begin{itemize}
-
-%% %% \item In this paper there are two games played simultaneously: One for
-%% %% maximazing individual utility; the second for maximazing the connection
-%% %% strength. We are interested in how they affect eachother in the context of a
-%% %% network of collaboration.
-
-%% \item We change utility for fitness. Utility seems a better concept in order to
-%%   reflect players' preferences.
-
-%% %% \item In the context of our paper, utility represents
-%% %%   the preference for having access to the resources of others. Maximazing
-%% %%   utility means that the player is increasing its access to the resources of
-%% %%   other players.  Utility function is just the sum of the payoffs of playing
-%% %%   with its neighbors. As for the payoff matrix, the best strategy for a player
-%% %%   is to defect. Any other option will not be an optimal payoff. The opossing
-%% %%   force is in the other game. The game for maximazing the strength of the
-%% %%   connection among players. In this case defecting or cooperating? is the best
-%% %%   strategy as it pays the most when coordinating regardeless they both cooperate
-%% %%   or defect, this is because when both cooperate the interaction gets a positive
-%% %%   payoff, when both defect, the interaction doesn't get affected; but if they
-%% %%   anti-coordinate, then the interaction looses. In this sense, this might be a
-%% %%   game were there are multiple (i.e., 2 points or strategies) equilibria. It
-%% %%   seems that there is no single dominant strategy.}\\
-
-%% \item Choosing a strategy depends on the balance $\eta'$ equation --look at page
-%%   9. This
-%%   equation states that the probability of an agent to cooperate increases as: a)
-%%   its utility increases --as it moves away from 0, or; b) The strength of the
-%%   connection with its peers increases --as it moves away from 0, or; c) both
-%%   increases.
-
-%%   $\eta_i = \frac{\langle f_i \rangle + \langle w_{ij} \rangle _j}{2}$\\
-
-%% \item{En la pagina 9 decimos que ``In order for the agent to choose to cooperate
-%%   or defect, a degree of willingness to cooperate is assigned to each agent.'' No estoy
-%%   seguro que ``degree of willingness to cooperate'' sea la mejor manera de
-%%   decirlo, mi duda está en la palabra ``degree'', por lo que cambi\'e la
-%%   oraci\'on a: The probability for an agent to cooperate or defect depends on a
-%% number that referes to a historical balance between average utility and the average strength of
-%% the connections with its neigbors. }
-
-%% \end{itemize}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%                                          %%
+%% The keywords begin here                  %%
+%%                                          %%
+%% Put each keyword in separate \kwd{}.     %%
+%%                                          %%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\begin{keyword}
+\kwd{Collaboration networks}
+\kwd{Social Networks Analysis}
+\kwd{Biomedicine}
+\kwd{Game theory}
+\end{keyword}
+
+% MSC classifications codes, if any
+%\begin{keyword}[class=AMS]
+%\kwd[Primary ]{}
+%\kwd{}
+%\kwd[; secondary ]{}
+%\end{keyword}
+
+\end{abstractbox}
+%
+%\end{fmbox}% uncomment this for twcolumn layout
+
+\end{frontmatter}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%                                          %%
+%% The Main Body begins here                %%
+%%                                          %%
+%% Please refer to the instructions for     %%
+%% authors on:                              %%
+%% http://www.biomedcentral.com/info/authors%%
+%% and include the section headings         %%
+%% accordingly for your article type.       %%
+%%                                          %%
+%% See the Results and Discussion section   %%
+%% for details on how to create sub-sections%%
+%%                                          %%
+%% use \cite{...} to cite references        %%
+%%  \cite{koon} and                         %%
+%%  \cite{oreg,khar,zvai,xjon,schn,pond}    %%
+%%  \nocite{smith,marg,hunn,advi,koha,mouse}%%
+%%                                          %%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%%%%%%%%%%%%%%%%%%%%%%%% start of article main body
+% <put your article body there>
+
+%%%%%%%%%%%%%%%%
+%% Background %%
+%%
+
+\section*{Introduction}
 
@@
 to maximize their access to resources while taking care of their collaboration links.\\
-
-  %% nevertheless
-  %% and to a certain degree, the idea behind the model is ethnographically
-  %% inspired\footnote{For a mixed methodology approach to scientific
-  %%   collaboration refer to Hara et al., 2002 \cite{Hara_etal_2002}.}. In
-  %% previous work we observed that members of biomedical research groups interact
-  %% strongly with each other but interactions between groups are only
-  %% superficial. Our ethnographic work also allowed us to see how difficult is for
-  %% Principal Investigators to collaborate with peer groups that are considered
-  %% somehow equal in terms of different criteria such a productivity or power. On
-  %% the other hand, collaboration may be easier with groups that are far beyond in
-  %% some of these terms. This seems to be so because when dealing with a smaller
-  %% group, the stronger one can establish conditions of collaboration; when the
-  %% group is weaker, there might be a lot to win. For example, this latter
-  %% situation can be seen when local groups collaborate with research groups form
-  %% overseas, specially from the US.}\\
-
-%% {\color{red}The question behind our model rests on three premises: Scientist
-%%   have self-interests and may act seeking their own interests; Scientific
-%%   collaboration needs researchers to cooperate and build relationships that can
-%%   last; Scientific collaboration networks have a particular topology. Under such
-%%   context, if the same amount of resources were given to every researcher at the
-%%   same point in time, how would the access to resources be distributed, in the
-%%   long run, in a population of interacting researchers that seek to improve
-%%   their profits but at the same time have to invest in building trustworthy
-%%   relationships with their colleagues?}
-%%\\
-
-  %% Seen from a different point of view, how would trust be
-  %% distributed in a population of researchers that are mainly interested in
-  %% improving their profits, even when acting selfishly always could have a
-  %% negative impact on that primary objective?}\\
 
@@
 
-%Our main objective is to achieve a better understanding of the role of network
-%topology on scientific collaborative social dynamics. The dynamics of the
-%system are explored following the distribution of utility -as a proxy for
-%resources- and trust as agents on the network play the Prisoner's Dilemma while
-%constrained by trust with their neighbors.\\
-
-%% In order to explore these questions we implemented a game theory simulation on a
-%% real social network of biomedical researchers from M\'exico. Game theoretical
-%% approaches to cooperation have – of course– been studied for decades. Taking
-%% into account the nature of social interaction among players by means of an
-%% underlying social network is also an explored topic. Some 10 years ago, Lo and
-%% colleagues \cite{Lo2004} formulated a minority game model to connected
-%% population within a network and studied the role of connectivity on such
-%% games. Later on, Buesser and Tomassini \cite{Buesser2012} studied the dynamics
-%% of cooperation for players located on a spatially embedded network in order to
-%% categorize the effect that different interaction structures may have in
-%% maintaining cooperation (or defection) domains.\\
-
-%% The impact that network topology may have in the robustness of cooperation was
-%% investigated in numerical experiments and simulations \cite{Ichinose2013}
-%% revealing that clusters of cooperating agents become robust by increasing the
-%% number of links to cooperators, with the possible implication that a large
-%% number of individuals is required to maintain global cooperation patterns.\\
-
-%% Regarding possible strategies to improve cooperation patterns, several mechanisms such as inequity aversion
-%% \cite{Ahmed2014}, social imitation and strategic choice \cite{Vilone2014} have been explored. Inequity aversion is the
-%% condition in which individuals care about payoff equality in the outcomes. A kind of moral memory in past outcomes
-%% implies that inequity aversion promotes cooperation \cite{Ahmed2014}. Social imitation contrasts with strategic choices
-%% in such a way that social influence models may impact on background rationality in decision making. This balance may be
-%% behind moody conditional cooperation within a social environment \cite{Vilone2014}.\\
-
-%% The analysis of cooperation in scientific research has been also the subject of a number of studies. This is not
-%% surprising since cooperation and competitionare quite important in today’s academic success. How do collaboration 
-%% happens within a competitive academic environment and what kind of payoff
-%% is present in these settings were questions considered recently by Wardil and
-%% Hauert \cite{Wardil2015} in the context of cooperation in multi-authored
-%% publications. Also, the role of game theory over complex scientific information 
-%% and collaboration networks has attracted attention, mainly focusing on how
-%% long-term strategies may shape different scenarios for Nash equilibria \cite{hanauske2012}. \\
-
-%% In spite of all these research efforts, cooperation in the context of scientific
-%% collaboration is still loosely defined and the long time dynamics of academic
-%% cooperation (and its consequences) are yet to be fully elucidated. Furhtermore,
-%% to our current knowledge, we are not aware of any work on how the topology of
-%% scientific collaboration networks affects the differences of access among
-%% individuals to resources present on the network \footnote{For
-%%   an account of scientific collaboration and definitions, please refer to
-%%   \cite{Sonnenwald2007}.}. In this context our work aims to contribute to
-%% further our current understanding on the matter.\\
-
-%% As has been pointed by others, social research on scientific
-%% collaboration is mostly about physics and space research\cite{Vermeulen2013}.
-%% Collaboration in biology has been studied to a lesser degree
-%% \cite{Newman2001,Newman2004,Elango2012,HernandezLemus2013,Strasser2006,Strasser2012}. The
-%% use of game theory, and specifically the Prsioner's Dilemma to understand social
-%% dynamics in scientific collaboration can be found at 
-%% \cite{Hara_etal_2002,Lieberman_etal_2005}.\\
-
-%% The manuscript is structured in five sections. The following describes \textit{FOSISS}, the main program for grants
-%% destined for biomedical applied research in M\'exico. This description is important because that is the source of our
-%% database for creating the researchers collaboration network. Next we describe our model, and then, in the following
-%% section we introduce the different network topologies on which we explored the model. In the fourth section we present
-%% our results and discuss them briefly. In the fifth section we draw some final remarks and conclusions.
-
-\section{Biomedical research: CONACyT and FOSISS}
-\label{sec:1}
+\section*{Biomedical research: CONACyT and FOSISS}
 
@@
 
-\section{Methodology}
-\label{sec:2}
+\section*{Methodology}
+
 %% In this work we developed a model in order to have a better understanding of the
@@
 
-\subsection{Network initialization and agent state update}
+\subsection*{Network initialization and agent state update}
 
@@
 
-\section{Implementation of the model in different topologies}
+\section*{Implementation of the model in different topologies}
 
@@
 
-\subsection{Erd\"{o}s-Reny\'i}
+\subsection*{Erd\"{o}s-Reny\'i}
 
@@
 
-\subsection{Small-World}
+\subsection*{Small-World}
 
@@
 
-\subsection{Barb\'asi-Albert}
+\subsection*{Barb\'asi-Albert}
 
@@
 
-\subsection{FOSISS: Biomedical research community network}
+\subsection*{FOSISS: Biomedical research community network}
 
@@
 
-\section{Results}
-\label{sec:3}
-
-In this section we present the main results of the study, namely the topological
-structure of the underlying network models, the dynamics of the games under
-different parameters and network topologies and the distribution of utility and
-of the strength of interaction resulting of playing the games in all the
-different scenarios considered, including the real FOSISS network.\\
-
-FOSISS network summed-up a total of 145 components or subnetworks, but we ran
-the model on the giant component made-up of 4122 researchers, and 23391 edges.
-The giant component was analyzed using \textit{Cytoscape} \textbf{Figure
-  1}. Results show that it is a well integrated network, with a clustering
-coefficient $\langle C \rangle = 0.870$, an average shortest path length of
-$\langle l \rangle = 5.493$  and a density of $p = 0.003$. Such properties
-recall a small-world topology \cite{Watts1998}, and a great deal of
-self-organization when compared to a random network with the same density and
-number of nodes. Network centralization is $0.023$, since there are no visible
-researchers that play as hubs in the network. Nevertheless the network
-heterogeneity is $0.873$, which means that the network is highly
-hierarchical. When the degree distribution is analyzed, degree decreases as a
-power-law with an exponent of $1.7$, similar to other social networks described
-as scale-free topology networks \cite{Barabasi1999}. Finally, the average number
-of neighbors of each node is $11.39$ \cite{Shannon2003}.\\
-
-\begin{figure} [h!]
-\centering
-\includegraphics[scale=0.5]{images/Fosiss_GC_final.png}
-\caption{Bioemdical research collaboration network (FOSISS) giant component.}\label{Fosiss_GC}
+\section*{Content}
+Text and results for this section, as per the individual journal's instructions for authors. %\cite{koon,oreg,khar,zvai,xjon,schn,pond,smith,marg,hunn,advi,koha,mouse}
+
+\section*{Section title}
+Text for this section \ldots
+\subsection*{Sub-heading for section}
+Text for this sub-heading \ldots
+\subsubsection*{Sub-sub heading for section}
+Text for this sub-sub-heading \ldots
+\paragraph*{Sub-sub-sub heading for section}
+Text for this sub-sub-sub-heading \ldots
+In this section we examine the growth rate of the mean of $Z_0$, $Z_1$ and $Z_2$. In
+addition, we examine a common modeling assumption and note the
+importance of considering the tails of the extinction time $T_x$ in
+studies of escape dynamics.
+We will first consider the expected resistant population at $vT_x$ for
+some $v>0$, (and temporarily assume $\alpha=0$)
+%
+\[
+ E \bigl[Z_1(vT_x) \bigr]= E
+\biggl[\mu T_x\int_0^{v\wedge
+1}Z_0(uT_x)
+\exp \bigl(\lambda_1T_x(v-u) \bigr)\,du \biggr].
+\]
+%
+If we assume that sensitive cells follow a deterministic decay
+$Z_0(t)=xe^{\lambda_0 t}$ and approximate their extinction time as
+$T_x\approx-\frac{1}{\lambda_0}\log x$, then we can heuristically
+estimate the expected value as
+%
+\begin{eqnarray}\label{eqexpmuts}
+E\bigl[Z_1(vT_x)\bigr] &=& \frac{\mu}{r}\log x
+\int_0^{v\wedge1}x^{1-u}x^{({\lambda_1}/{r})(v-u)}\,du
+\nonumber\\
+&=& \frac{\mu}{r}x^{1-{\lambda_1}/{\lambda_0}v}\log x\int_0^{v\wedge
+1}x^{-u(1+{\lambda_1}/{r})}\,du
+\nonumber\\
+&=& \frac{\mu}{\lambda_1-\lambda_0}x^{1+{\lambda_1}/{r}v} \biggl(1-\exp \biggl[-(v\wedge1) \biggl(1+
+\frac{\lambda_1}{r}\biggr)\log x \biggr] \biggr).
+\end{eqnarray}
+%
+Thus we observe that this expected value is finite for all $v>0$ (also see \cite{koon,khar,zvai,xjon,marg}).
+%\nocite{oreg,schn,pond,smith,marg,hunn,advi,koha,mouse}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%                                          %%
+%% Backmatter begins here                   %%
+%%                                          %%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\begin{backmatter}
+
+\section*{Competing interests}
+  The authors declare that they have no competing interests.
+
+\section*{Author's contributions}
+    Text for this section \ldots
+
+\section*{Acknowledgements}
+  Text for this section \ldots
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%                  The Bibliography                       %%
+%%                                                         %%
+%%  Bmc_mathpys.bst  will be used to                       %%
+%%  create a .BBL file for submission.                     %%
+%%  After submission of the .TEX file,                     %%
+%%  you will be prompted to submit your .BBL file.         %%
+%%                                                         %%
+%%                                                         %%
+%%  Note that the displayed Bibliography will not          %%
+%%  necessarily be rendered by Latex exactly as specified  %%
+%%  in the online Instructions for Authors.                %%
+%%                                                         %%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+% if your bibliography is in bibtex format, use those commands:
+\bibliographystyle{bmc-mathphys} % Style BST file (bmc-mathphys, vancouver, spbasic).
+\bibliography{bmc_article}      % Bibliography file (usually '*.bib' )
+% for author-year bibliography (bmc-mathphys or spbasic)
+% a) write to bib file (bmc-mathphys only)
+% @settings{label, options="nameyear"}
+% b) uncomment next line
+%\nocite{label}
+
+% or include bibliography directly:
+% \begin{thebibliography}
+% \bibitem{b1}
+% \end{thebibliography}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%                               %%
+%% Figures                       %%
+%%                               %%
+%% NB: this is for captions and  %%
+%% Titles. All graphics must be  %%
+%% submitted separately and NOT  %%
+%% included in the Tex document  %%
+%%                               %%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%
+%% Do not use \listoffigures as most will included as separate files
+
+\section*{Figures}
+  \begin{figure}[h!]
+  \caption{\csentence{Sample figure title.}
+      A short description of the figure content
+      should go here.}
       \end{figure}
 
-\FloatBarrier
-
-Other results to report are those of the dynamics of different
-variables as the carrying capacity $\nu$ changes. The  most salient
-result is that for $\nu$ between $0.19$ and $0.24$, there is an
-apparent phase transition in all different topologies and for all the
-different variables. It is worth noting that the shape
-of the phase transition is different according to the topology of the
-network under study. When $\nu$ is between $0.0$ and $0.2$, that is, when there is
-no space or a very short one for suspiciousness, all agents cooperate, when
-\textit{carrying capacity} is above $0.25$, all agents defect. \textit{Utility},
-\textit{strength of interactions}, and \textit{changing state population}
-replicate that same behavior for the same limits. \\
-
-In \textbf{Figure 2}, we present how the number of cooperators in the population
-change as $\nu$ changes. In the Erd\"{o}s-Reny\'i, network, between $0$ and
-$0.18$ approximately, all agents converge to a cooperative behavior, from $18$
-to $20$, convergence to cooperative state takes longer but eventually all agents
-are cooperating. Close to $\nu \approx 0.21$ there is a sharp fall to a point in
-which around half the population is cooperating and the rest is
-defecting. Reaching $\nu \approx 0.25$ there is another sharp fall of
-cooperators and all agents turn into a defecting state.\\
-
-In the case of the Watts-Strogatz, small-world network, the whole
-population remains cooperating for ranges between $0$ and $0.2$ but as
-it gets closer to $0.2$, more time is needed for the population to
-become full of cooperators. In $\nu \approx 0.2$ the cooperators will
-represent only half of the population and such number of them will be
-constant up to $\nu \approx 0.25$ forming a short plateau. From $\nu
-\approx 0.25$ to $\nu \approx 0.6$ cooperators will be present at the
-beginning of the simulation but will diminish as time goes on.  In the
-case of the Barab\'asi-Albert network, crossing the threshold of $\nu
-\approx 0.2$, there is a sharp decrease in the number of cooperators,
-but stays constant over time. Such behavior is present for a very
-short range of $\nu$, and before $\nu \approx 0.24$, cooperators
-disappear for the rest of values of $\nu$. Finally, FOSISS network
-behaves similarly to the other networks in that there is a fall in the
-number of cooperators close to $\nu \approx 0.2$. In contrast with the
-other networks, the FOSISS network lacks the sharp reduction of
-cooperators, instead this population declines smoothly and
-progressively; specially, when it reaches a $\nu \approx 0.25$
-cooperators decrease in a less dramatic manner all the way to
-$\nu \approx 0.5$. It is also noteworthy that from $\nu = 0$ to $\nu
-\approx 0.5$ the number of cooperators converge to a certain degree
-and stays constant for the rest of the simulation.
-
-\begin{figure} [h!]
-\centering
-\begin{tabular}{cc}
-  \includegraphics[scale=0.28]{images/erdos_dc_nus_1.png} & \includegraphics[scale=0.28]{images/watts_dc_nus_1.png}
-  \\
-  \includegraphics[scale=0.28]{images/barabasi_dc_nus_1.png} & \includegraphics[scale=0.28]{images/fosiss_dc_nus_1.png}
+\begin{figure}[h!]
+  \caption{\csentence{Sample figure title.}
+      Figure legend text.}
+      \end{figure}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%                               %%
+%% Tables                        %%
+%%                               %%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%% Use of \listoftables is discouraged.
+%%
+\section*{Tables}
+\begin{table}[h!]
+\caption{Sample table title. This is where the description of the table should go.}
+      \begin{tabular}{cccc}
+        \hline
+           & B1  &B2   & B3\\ \hline
+        A1 & 0.1 & 0.2 & 0.3\\
+        A2 & ... & ..  & .\\
+        A3 & ..  & .   & .\\ \hline
       \end{tabular}
-\caption{Ratio of cooperators as a function of carrying capacity and time. Topologies are: A. Random, Erd\"{o}s-R\'enyi. B. Watts-Strogatz. C. Barab\'asi-Albert. D. FOSISS.
-}\label{CD}
-\end{figure}
-
-\FloatBarrier
-
-Utility and strength of interactions dynamics under different $\nu$ are similar to the
-phase transition found before. \textbf{Figures 3 and 4} show
-that there is a drop in utility and strength of interactions according to the
-drop in the number of cooperators. Erd\"{o}s-Reny\'i and Barab\'asi-Albert
-networks are quite similar in the way these variables fall in two steps, the
-first one at $\nu \approx 0.2$ and the next one at $\nu \approx 0.23$. The fall
-is sharper still in the Barab\'asi-Albert topology. Utility and strength of
-interactions phase transition in Watts-Strogatz network is significantly more
-staggered compared to the former networks. In the case of utility, there is a
-region in the limits of $\nu \approx 0.25$ and $\nu \approx 0.3$, before utility
-goes to $0$, in which it remains low but stable over time. In general, strength
-of interactions follows the same pattern as utility but in the same $\nu \approx
-0.25$ and $\nu \approx 0.3$, strength of interactions grows to a value that is
-higher than the one given by default but soon starts to decrease as the
-simulation runs. For the FOSISS network, utility and interaction strength fall
-quite steeply but smoothly, without sharp cuts. Between $\nu \approx 0.23$ and
-$\nu \approx 0.28$, utility and strength of interactions start at their lowest,
-but there is a slight increase in both of them.
-
-\begin{figure} [h!]
-\centering
-\begin{tabular}{cc}
-
-\includegraphics[scale=0.28]{images/erdos_fitness_nus_1.png} & \includegraphics[scale=0.28]{images/watts_fitness_nus_1.png} \\
-\includegraphics[scale=0.28]{images/barabasi_fitness_nus_1.png} & \includegraphics[scale=0.28]{images/fosiss_fitness_nus_1.png}
-\end{tabular}
-\caption{Utility $U$ dynamics as a function of carrying capacity $\nu$ and time. Topologies are: A. Random, Erd\"{o}s-R\'enyi. B. Watts-Strogatz. C. Barab\'asi-Albert. D. FOSISS.}\label{fitness}
-\end{figure}
-
-\FloatBarrier
-
-\begin{figure} [h!]
-\centering
-\begin{tabular}{cc}
-
-\includegraphics[scale=0.28]{images/erdos_trust_nus_1.png} & \includegraphics[scale=0.28]{images/watts_trust_nus_1.png} \\
-\includegraphics[scale=0.28]{images/barabasi_trust_nus_1.png} & \includegraphics[scale=0.28]{images/fosiss_trust_nus_1.png}
-\end{tabular}
-\caption{Strength of interactions $w$ dynamics as a function of carrying capacity $\nu$ and time.
-Topologies are: A.
-Random, Erd\"{o}s-R\'enyi.
-B.
-Watts-Strogatz.
-C.
-Barab\'asi-Albert.
-D.
-FOSISS.}\label{trust}
-\end{figure}
-
-\FloatBarrier
-
-We also measured the number of agents shifting states --between cooperating and
-defecting- under different $\nu$ values. We found that for all networks there is
-a critical point around  $\nu \approx 0.2$ in which all agents are shifting
-states. For Erd\"{o}s-Reny\'i and Barab\'asi-Albert networks, for this region,
-agents never settle to a single state. Contrary to the former cases, the number
-of shifting agents decreases considerably for the Watts-Strogatz and FOSISS
-networks, and find an equilibrium state. Once the the limits of this region are
-crossed as $\nu$ increases, the number of agents shifting states falls to $0$
-and all nodes become defectors.
-
-\begin{figure} [h!]
-\centering
-\begin{tabular}{cc}
-
-\includegraphics[scale=0.28]{images/erdos_state_nus.png} & \includegraphics[scale=0.28]{images/watts_state_nus.png} \\
-\includegraphics[scale=0.28]{images/barabasi_state_nus.png} & \includegraphics[scale=0.28]{images/fosiss_state_nus.png}
-\end{tabular}
-\caption{Shifting population between cooperators and defectors as a function of
-  carrying capacity $\nu$ and time. Topologies are: A. Random, Erd\"{o}s-R\'enyi. B. Watts-Strogatz. C. Barab\'asi-Albert. D. FOSISS.}\label{state} 
-\end{figure}
-
-\FloatBarrier
-
-Central to our argument is the differences in utility and strength of
-interactions distribution at the end of the simulation, for every topology. We
-found that utility distribution for the \textit{FOSISS} network, resembles quite
-accurately to the distribution of utility in the Barab\'asi-Albert
-network.\\
-
-The distribution of utility on each topology is induced by the degree
-distribution. This is so, since a given agent (node) will interact with its
-neighbors to either cooperate or defect, in such a way that connectivity
-influences the number of events played and thus the likelihood of increasing its
-corresponding utility. For instance, utility distribution in the random,
-Erd\"{o}s-R\'enyi network displays a normal-like curve. The algorithm that
-generates this kind of topology, assigns to every node the same probability of
-connecting with any other node, which produces a \textit{poissonian} degree
-distribution \cite{Erdos1959}. Since the Watts-Strogatz degree distribution is
-described by a function that is midways between a random distribution and a
-scale-free network \cite{Barrat2000} one may expect also  an intermediate
-behavior of the utility distribution. This assumption seems to be fulfilled by
-the distribution in Figure 6B.
-
-The resemblance of the degree-distribution and utility distribution also holds
-for the Bar\'abasi-Albert network. As mentioned in the methods section, the
-degree distribution of a Bar\'abasi-Albert topology follows a power-law that
-describes the fact that there are a small number of nodes with large $k$ and most
-nodes have a small $k$ \cite{Barabasi1999}. As it is shown in the following
-figure, most utility is concentrated in a few number of agents, while most
-agents have a small amount of it. This is consistent with other research in
-which concentration of resources, fame or citations in science decreases as a
-power-law \cite{Simon1955,Price1965,Merton1968}. FOSISS network utility
-distribution is also skewed to the left, similar to that of the
-Barab\'asi-Albert network. \\
-
-\begin{figure} [h!]
-\centering
-\begin{tabular}{cc}
-
-\includegraphics[scale=0.28]{images/erdos_fitness.png} & 
-\includegraphics[scale=0.28]{images/watts_fitness.png} \\
-\includegraphics[scale=0.28]{images/barabasi_fitness.png} & 
-\includegraphics[scale=0.28]{images/fosiss_fitness.png}
-\end{tabular}
-\caption{Utility distribution on different topologies. A. Random,
-  Erd\"{o}s-R\'enyi network displays a normal-like
-  distribution. B. Watts-Strogatz network utility distribution is highly skewed
-  to the right. C. Barab\'asi-Albert network. Utility is distributed highly
-  skewed to the left. D. FOSISS, biomedical researchers collaboration network
-  distribution of utility resembles to Barab\'asi-Albert
-  network.}\label{histo_fitness} 
-\end{figure}
-
-\FloatBarrier
-
-Regarding strength of interactions distribution, the Erd\"{o}s-R\'enyi random
-network displays a normal distribution of strength of interactions, as
-expected. Again strength of interactions values are highly influenced by the
-corresponding degree distribution (Figure 7A). However, in the Watts-Strogatz
-network topology (Figure 7B), the strength of interactions distribution is a
-highly asymmetric bimodal, with a really-low frequency mode of low strength of
-interactions and a highly probability mode for high strength of interactions. A
-possible explanation for this phenomenon is that under network topologies
-maximizing inter-node communication (by minimizing the average distance between
-nodes) such as the Watts-Strogatz, strength of interactions is favored both
-among the cooperators (constituting the majority of players) and the
-defectors. \\
-
-The Barab\'asi-Albert network (7C) presents also a symmetric unimodal
-distribution with values higher (on average) than those of the Erd\"{o}s-R\'enyi
-random network, this may be the effect of increased communication due to more
-efficient network navigability. Interestingly, the network corresponding to the
-real FOSISS collaborations (7D) is an asymmetric unimodal distribution in which
-moderate to high values of strength of interactions are more likely. We 
-hypothesize that this effect is also due to the communication properties of the
-network.
-
-\begin{figure} [h!]
-\centering
-\begin{tabular}{cc}
-
-\includegraphics[scale=0.28]{images/erdos_trust.png} & 
-\includegraphics[scale=0.28]{images/watts_trust.png} \\
-\includegraphics[scale=0.28]{images/barabasi_trust.png} & 
-\includegraphics[scale=0.28]{images/fosiss_trust.png}
-\end{tabular}
-\caption{Strength of interactions distribution on different topologies. A. Random, Erd\"{o}s-R\'enyi network displays a normal-like
-  distribution. B. Watts-Strogatz network strength of interactions distribution is bimodal and highly skewed to the right. C.
-  Barab\'asi-Albert network strength of interactions distribution is also a normal-like curve. D. FOSISS, biomedical researchers
-  collaboration network distribution of strength of interactions is skewed to
-  the right.}\label{histo_trust}  
-\end{figure}
-
-\FloatBarrier
-
-An interesting feature of highly communicated networks (characterized
-by high values of clustering coefficient) is the fact that certainty
-among players seems to be enhanced, that is, in such networks the rate
-of change of strategy is significantly lower (and smoother) than in
-poorly connected networks. This is another instance in which easier
-communication (i.e. lower average minimum path lengths) leads to better
-performance of the whole collaborative research system.\\
-
-\section{Discussion and Conclusions}
-\label{sec:3}
-
-In this work we have analyzed the influence of parameters
-  given by the underlying social structure of a science collaborative
-  network on collective strength of interactions and utility dynamical
-  behavior, based on a class of iterated PD and coordination
-  games. Such parameters include mainly local and global connectivity
-  like the degree centrality and average clustering coefficient, as
-  well as communication patterns.\\
-
-  Under the assumptions given by the model, we were able to
-  notice that, in general, communication within the social
-  collaborative networks has a positive correlation with average
-  strength of interactions between the individuals partaking in the
-  games and also with the global collective utility (given by the sum
-  of the individual payoffs). The better the communication among
-  players, the higher the strength of interactions and the utility
-  leading to an optimized functioning of the whole \emph{scientific
-    collaboration system}. This is an important result that may be
-  useful for scientific policy planning and may set a foundation for
-  the optimal use of social networks in scientific collaboration as a
-  means to improve the relationships among collaborating peers and
-  ultimately the performance of research systems.  We obviously need
-  more qualitative work in order to validate these results from a
-  sociological and anthropological perspective.\\
-
-%Furthermore, such validation is necessary because, as we said at
-%the beginning of this work, \emph{strength of
-%interactions} can have many different meanings and
-%implementations in the real world. The same we can say
-%about \emph{utility} and most of all, about the idea of the game we
-%explored here since ``playing the
-%game'' must have so, many different meanings among
-%resarchers and their communities.\\
-
- To close this article, we would like to comment on three
-  issues we consider important. The first one is about confronting our
-  results with data available to us from the biomedical research
-  community. Second, some remarks we believe are important about the
-  role of computational simulations in the social sciences. Finally we
-  would like to comment on our future work.\\
-
-  The two main results of our model are the smoothness in
-  the phase transition-like behavior for different parameters and the
-  distribution of utility and strength of interactions in the FOSISS
-  network compared to other networks and their topologies. We are
-  certain that the particular structure of FOSISS network is playing a
-  central role in the results and because of that we would like to
-  discuss it a little bit further.\\
-
-  FOSISS network is higly hierarchical according to its
-  heterogeneity of $0.873$. Because of it, one would expect to find
-  the presence of important hubs \cite{Wu-etal2008}, that is, a few
-  researchers control the whole network, as has been reported in some
-  other places \cite{yousefi-etal2008}. Surprisingly, FOSISS network
-  centralization is very low $0.023$, i.e. there are no researchers
-  that centralize the majority of connections. Our guess is that the
-  network is composed of many small communities or groups with a
-  central researcher or Principal Investigator (PI). If this is the
-  case in the FOSISS network, it means that those groups have a very
-  hierarchic structure as well.\\
-
-  Under such structure, when the clustering coefficient is
-  considered, it can be said that groups are also well connected but
-  that inter-group connections are sparse. In other words, individual
-  groups are strongly connected within but the network as a whole is
-  supported by a small number of links. We came by this idea partially
-  from another study about scientific collaborations based on
-  co-authorships in one of the research centers that is part of the
-  FOSISS network \cite{HernandezLemus2013}. In the cited reference an
-  apparently well integrated community was found (high clustering
-  coefficient and a very short characteristic path length). Such
-  integration was mostly superficial, since it depended on the
-  presence of external collaborators from other research institutions
-  (most of them from overseas).  Removing these external collaborators
-  broke down the network into small subgraphs that worked
-  independently. Remarkably those subgraphs corresponded to the real
-  groups of that research center.  What is more, several groups had a
-  hierarchical structure as the one we suspect is common in FOSISS
-  subgraphs. The results showed that collaboration was poor between
-  groups but strong among the members of each group, and that
-  collaboration among groups doesn't emerge bottom-up, instead it
-  seems to be promoted from the top, from the administrative
-  authorities.\\
-
-  We believe that the the situation just refered is also
-  true for the whole biomedical research community in M\'exico. The
-  amount of PIs who have also been collaborators in other projects is
-  about one fifth of the total number of participants.  This is a
-  number big enough to connect the whole network in one giant
-  component. Yet, due to the topological characteristics of the FOSISS
-  network, it appears to be the case that researchers can be the
-  leaders in one project and collaborators of different project of
-  \emph{its own research group}. CONACyT's funding policies makes it
-  impossible for a researcher to get a grant from a fund if that
-  researcher has an ongoing project with a grant from that same
-  fund. That is, a researcher can ask for a grant from FOSISS if and
-  only if at the moment he doesn't already have one
-  This policy has lead researchers from the same group to ask
-  for grants from the same fund in order to rise their budgets. A
-  consequence of this behavior is that group interactions get
-  reinforced, but integroup connections not necessarily so.\\
-
- As is common among scientific communities in biomedical
-  research, PIs play a central role in the network. Strong PIs and
-  well connected groups seem to be somehow responsible for the high
-  levels of strength of interactions and the centralization of utility
-  in our simulation. As for what seems to be phase transitions, in the
-  case of FOSISS networks, these are smoother than those in the other
-  networks with different topologies, even for those with a
-  small-world topology. We think that this behavior is also the result
-  of the hierarchical structure already mentioned. If this is true,
-  strength of interactions is first lost in the edges that link
-  diffrent goups and then in the edges that connect members of the
-  groups. Connections between groups would not be as dense as those
-  inside the groups, which means that there would not be enough
-  information of the behavior of one group regarding its neighbors to
-  constrain them as it seems to happen with individual researchers
-  inside their communities. Nevertheless, if values of the carrying
-  capacity $\nu$ keep increasing and it becomes more difficult to
-  strengthen interactions, then strength of interactions begins to
-  diminish inside groups.\\
-
-  Another issue that we would like to mention about FOSISS
-  network topology is that it is not a robust collaboration network.
-  At the level of groups, these might be well connected and
-  consolidated but at the level of the network, this could be no more
-  than an aggregate of individual groups. A robust network would be
-  resistant to changes in the connections between groups but in the
-  case of FOSISS, it seems that the network would brake down into
-  small research groups by cutting some edges, as it happened in our
-  co-authorship collaboration network \cite{HernandezLemus2013}. The
-  lack of robustness might be indicative of the fact that resources
-  stay inside the groups, that is, they do not circulate through or
-  articulate different communities. For example, one may think of
-  certain expensive technologies for genomic research that could be
-  bought once and shared among research groups, however, this doesn't
-  seem to happen very often. There are some other consequences, such
-  as low communication among groups, atomization of practices and
-  know-hows, redundancy in equipment tenancy, difficulties for
-  implementing community-wide infrastructures such as biobanks,
-  etc. \\
-
-%% {\color{red}Regarding simulations and social science. We believe that social scientists may learn many lessons from
-%%   computational modeling. Tipically, the use of computational modeling as part of the social sciences
-%%   has been justified by arguing that such methods allow to understand the connection between the level of the individual
-%%   and the level of the group, they make possible to explore different outcomes by tuning different parameters and to
-%%   perform --virtual-- experiementation, as well as studying different propensities as Stephen Lansing calls them
-%%   \cite{Epstein1996,Lansing2002}. All these are important arguments but we would also like to say something else about 
-%%   them. When presenting computational modeling to non-computational social scientists (specially anthropologists) one gets
-%%   confronted with several critiques from which, the most common are that computational modeling tends to ignore cultural
-%%   differences (should be noticed that cultural differences is not the same as social differences), and that it is hard to grasp the cultural
-%%   meaning or significance of the dynamics expressed in the simulation. Because of this kind of observations we are
-%%   particularly interested in not forgiving from our work the ethnographical, culturally loaded content of social life,
-%%   while recognizing the value of computational simulations.}\\
-
-%% {\color{red}We believe that computational simulations are methodologically valuable for two reasons. The first one is that
-%% simulations can play an important role in social research as heuristics. If, as we have been doing in this project, fieldwork
-%% observations influence and inspire the development of a computational simulation, parameters must be an abstraction of
-%% those observations or at least of part of them. In this sense, the outcomes of simulations are a guide towards new
-%% questions and future fieldwork explorations at the time that it constrains and helps to prioritize what is to be
-%% observed. For example, from out results it seems mandatory to interview different research groups in order to disclose
-%% internal group dynamics and how and which are the terms for collaboration between groups. The second reason emerges from
-%% the first, we think that simulations are excellent hypothesis generators for the social sciences. Due to the
-%% imposibility of ``observing'' the social dynamics on real-time, just because we can only observe locally while one is
-%% doing fieldwork, there are left a few options to see how local dynamics may produce emergent patterns. Simulations may
-%% be of great help to elaborate guesses about the mechanisms for the behaviors observed at the local scale, as well as for
-%% the global. For example, we could guess that the hierarchical structure without hubs imposes strong limits to the flow
-%% of resources and information or that we can expect certain cultural intepretation regarding collaboration due to the
-%% position of researchers in the network. Such hypothesis can be computationally tested too.}\\
-
-On these grounds, part of our future work is based on
-  the results presented here. We would like to identify researchers
-  in our simulations and corroborate their situation in the model and
-  in the real world. We are also interested in going back to the field
-  and interviewing those groups with an interesting behavior found in
-  our simulations, probably we would follow a similar strategy as the
-  one developed in \cite{Haraetal2003}. Finding communities beyond the
-  level of the groups is an important task. We think that there are
-  many possibilities that emerge from the integration of different
-  methodologies. Moreover, studying social processes in science is
-  particularly attractive due to the amounts of data already available
-  that can be easily collected. This is a privilege because
-  simulations can be designed on real world data, something that only
-  very recently has become possible \cite{Barabasi2011}.\\
-
-No doubt, social sciences are becoming more ``computational''. This can
-be seen everywhere, but curiously enough, disciplines like physicis
-and computer science are moving towards the social
-sciences and not so much the other way around. It might be the case
-that the pioneering disciplines in the computational social sciences
-will set the agenda, an agenda that will apparently be mostly based on
-taking advantage of big data and on hypothesis-free approaches. We
-believe that the social sciences have important questions that should
-be added to that agenda and those questions may not be answered only
-by big data techniques but they may require creating models and
-simulations in the style of the best hypothesis-driven research.
-
-%Text with citations \cite{RefB} and \cite{RefJ}.
-%\subsection{Subsection title}
-%\label{sec:2}
-%as required. Don't forget to give each section
-%and subsection a unique label (see Sect.~\ref{sec:1}).
-%\paragraph{Paragraph headings} Use paragraph headings as needed.
-%\begin{equation}
-%a^2+b^2=c^2
-%\end{equation}
-
-% For one-column wide figures use
-%\begin{figure}
-% Use the relevant command to insert your figure file.
-% For example, with the graphicx package use
-%  \includegraphics{images/example.eps}
-% figure caption is below the figure
-%\caption{Please write your figure caption here}
-%\label{fig:1}       % Give a unique label
-%\end{figure}
-%
-% For two-column wide figures use
-%\begin{figure*}
-% Use the relevant command to insert your figure file.
-% For example, with the graphicx package use
-%  \includegraphics[width=0.75\textwidth]{example.eps}
-% figure caption is below the figure
-%\caption{Please write your figure caption here}
-%\label{fig:2}       % Give a unique label
-%\end{figure*}
-%
-% hello, friend
-%
-% For tables use
-%\begin{table}
-% table caption is above the table
-%\section{%\caption{Please write your table caption here}}
-%\label{tab:1}       % Give a unique label
-% For LaTeX tables use
-%\begin{tabular}{lll}
-%\hline\noalign{\smallskip}
-%first & second & third  \\
-%\noalign{\smallskip}\hline\noalign{\smallskip}
-%number & number & number \\
-%number & number & number \\
-%\noalign{\smallskip}\hline
-%\end{tabular}
-%\end{table}
-
-\section{Acknowledgements}
-The authors gratefully acknowledge support by grants: CB-222220-R/2013 and
-CB-179431/2012 (Consejo Nacional de Ciencia y Tecnolog\'ia). We would also like
-to acknowledge CONACyT for letting us access their database. Finally, we
-acknowledge the help of Francisco Allende for his work curating 
-databases of researchers.
-
-%If you'd like to thank anyone, place your comments here
-%and remove the percent signs.
-
-% BibTeX users please use one of
-%\bibliographystyle{spbasic}      % basic style, author-year citations
-%\bibliographystyle{spmpsci}      % mathematics and physical sciences
-%\bibliographystyle{spphys}       % APS-like style for physics
-%\bibliography{}   % name your BibTeX data base
-
-% Non-BibTeX users please use
-
-\begin{thebibliography}{100}
-
-\bibitem{Vermeulen2013} Vermeulen, Nikki; Parker, John N \& Penders,
-  Bart, Understanding life together: A brief history of collaboration
-  in biology, \textit{Endeavour}, 37(3): 162-171 (2013)
-
-\bibitem{KnorrCetina1999} Knorr-Cetina, Karol; \textit{Epistemic
-  cultures: how the sciences make knowledge}, MIT Press, Cambridge, MA
-  (1999)
-
-\bibitem{Strasser2006} Strasser, B.J. Collecting and Experimenting:
-  The Moral Economies of Biological Research, 1960s-1980s.
-  \textit{Preprint no. 310.} Berlin: Max Planck Institute for the
-  History of Science, (2006)
-
-\bibitem{Muller2012} M\"{u}ller-Wille, S. \& Charmantier. I.  Natural
-  history and information overload: The case of Linnaeus.
-  \textit{Studies in History and Philosophy of Biological and
-    Biomedical Sciences.} 43:4-15, (2012)
-
-\bibitem{Strasser2012} Strasser, BJ. Data-driven sciences: From
-  wonder cabinets to electronic databases. \textit{Studies in History
-    and Philosophy of Biological and Biomedical Sciences} 43:85-87,
-  (2012)
-
-\bibitem{Sonnenwald2007} Sonnenwald, DH. Scientific Collaborations. \textit{Annual Review of Information Science and
-  Technology}, 41.
-
-\bibitem{Newman2001} Newman, MEJ. Clustering and preferential
-  attachment in growing networks. \textit{Physical Review E},
-  64:025102-1/025102-4, (2001)
-
-\bibitem{Newman2004} Newman, MEJ. Coauthorship networks and patterns
-  of scientific collaboration. \textit{PNAS}, 101, no. suppl 1,
-  5200-5205 (2004)
-
-\bibitem{Elango2012} Elango, B. \& Rajendran, J. Authorship Trends and
-  Collaboration Pattern in the Marine Sciences Literature: A
-  Scientometric Study. \textit{International Journal of Information
-    Dissemination and Technology}, 2(3), 166-169, (2012)
-
-\bibitem{HernandezLemus2013} Hern\'andez-Lemus, Enrique \&
-  Siqueiros-Garc\'ia JM, Information theoretical methods for complex
-  network structure reconstruction. \textit{Complex Adaptive Systems
-    Modeling}. 1: 8, doi:10.1186/2194-3206-1-8 (2013).
-
-\bibitem{Gilbert1997} Gilbert, N. A Simulation of the Structure of
-  Academic Science. \textit{Sociological Research Online}, 2(2) 3,
-  http://www.socresonline.org.uk/2/2/3.html
-
-\bibitem{Edmonds2011} Edmonds, B., Gilbert, N., Ahrweiler, P., \&
-  Scharnhorst, A. Simulating the Social Processes of Science.
-  \textit{Journal of Artificial Societies and Social Simulation},
-  14(4) 14,  http://www.jasss.soc.surrey.ac.uk/14/4/14.html
-
-\bibitem{Hara_etal_2002} Hara, N. Solomon, P. Kim SL. Sonnenwald DH. An Emerging View of Scientific Collaboration:
-  Scientists’ Perspectives on Collaboration and Factors that Impact Collaboration. \textit{Journal of the American
-    Society for Information Science and Technology}, 54(10):952–965, (2003)
-
-\bibitem{Lieberman_etal_2005} Lieberman, E. Hauert, C. \& Nowak,
-  MA. Evolutionary Dynamics on Graphs. Nature, 433, doi:0.1038/nature03204 (2005).
-
-\bibitem{Lo2004} Lo, T.S., Chan, H.Y., Hui, P.M., Johnson, N.F.,
-  Theory of networked minority games based on strategy pattern
-  dynamics, \textit{Physical Review E} 70, 056012 (2004)
-
-\bibitem{Buesser2012} Buesser, P. and Tomassini, M., Evolution of
-  cooperation on spatially embedded networks, \textit{Physical Review E} 86,
-  066107 (2012)
-
-\bibitem{Ichinose2013} Ichinose, G., Tenguishi, Y., and Tanizawa, T.,
-  Robustness of cooperation on scale-free networks under continuous
-  topological change, \textit{Physical Review E} 88, 052808 (2013)
-
-\bibitem{Ahmed2014} Ahmed, A., Karlapalem, K., Inequity aversion and
-  the evolution of cooperation, \textit{Physical Review E} 89, 022802, (2014)
-
-\bibitem{Vilone2014} Vilone, D., Ramasco, J.J., S\'anchez, A., San
-  Miguel, M., Social imitation versus strategic choice, or consensus
-  versus cooperation, in the networked Prisoner’s Dilemma,
-  \textit{Physical Review E} 90, 022810, (2014)
-
-\bibitem{Wardil2015} Wardil, L., Hauert, C., Cooperation and coauthorship in
-  scientific publishing, Physical Review E 91, 012825, (2015)
-
- \bibitem{hanauske2012} Hanauske, M., Evolutionary Game Theory and Complex Networks of Scientific Information, in A.
-Scharnhorst et al.
-(eds.), \textit{Models of Science Dynamics, Understanding Complex Systems Series}, Springer Berlin Heidelberg, (2012)
-
-\bibitem{Szabo2007} Szab\'o, Gy\"{o}rgy \& F\'ath, G\'abor,
-  Evolutionary games on graphs. \textit{Physics Reports}, 446: 97-216
-  (2007)
-
-\bibitem{Nowak1992} Nowak, Martin A. \& May, Robert M, Evolutionary
-  Games and Spatial Chaos. \textit{Nature}, 359: 826-829, (1992)
-
-\bibitem{Nowak2006} Oshtuki, Hisashi, Hauert, Christoph, Lieberman, Erez \& Nowak, Martin A, A simple rule for the evolution of cooperation on social graphs. \textit{Nature}, 441: 502-505 (2006)
-
-\bibitem{Axelrod2006} Axelrod, Robert, \textit{Evolution of cooperation: Revised edition}, Basic Books, Cambridge, MA (2006)
-
-\bibitem{Nowak2011} Nowak, Martin A. \& Highfield, Roger,
-  \textit{Supercooperators. Altruism, Evolution, and Why We Need Each
-    Other to Succeed}. Free Press, New York, NY  (2011)
-
-\bibitem{Santos2006} Santos, Francisco C., Pacheco, Jorge M., Lenaerts, Tom, Cooperation prevails when individuals adjust their social ties.
-\textit{PLoS Computational Biology}.
-2(10): 1284-1291 (2006)
-
-\bibitem{Santos2005} Santos, F.C. \& Pacheco, J.M., Scale-Free
-  Networks Provide a Unifying Framework for the Emergence of
-  Cooperation. \textit{PRL}, 95: 098104-1 to 098104-4, (2005)
-
-\bibitem{Hauert2004} Hauert, Christoph \& Doebeli, Michael, Spatial
-  structure often inhibits the evolution of cooperation in the
-  snowdrift game. \textit{Nature}, 428: 643-646,  (2004)
-
-\bibitem{Erdos1959} Erd\"{o}s, P. \& Reny\'i, A. On Random Graphs. \textit{Publ. Math}, 6:290 (1959).
-
-\bibitem{Watts1998} Watts, Duncan J. \& Strogatz, Steven H, Collective dynamics
-  of 'small-world' networks. \textit{Nature}, 393: 440-442 (1998)
-
-  \bibitem{Barrat2000} Barrat, A.; Weigt, M., On the properties of small-world network models, \textit{European Physical Journal B} 13 (3): 547–560, (2000)
-
-\bibitem{Barabasi1999} Barab\'asi, Albert-L\'aszl\'o. \& Albert, R\'eka, Emergence of Scaling in Random Networks. \textit{Science}, 286: 509-512 (1999)
-
-\bibitem{Shannon2003} Shannon P, Markiel A, Ozier O, Baliga NS, Wang JT, Ramage D, Amin N, Schwikowski B, Ideker T.
-Cytoscape: a software environment for integrated models of biomolecular interaction networks.
-\textit{Genome Research}, 13(11):2498-504, (2003)
-
-\bibitem{Wu-etal2008}Jun Wu, Yue-Jin Tan, Hong-Zhong Deng, Da-Zhi Zhu.
-A new measure of heterogeneity of complex networks based on degree sequence.
-Eds.
-Ali Minai, Dan Braha, Yaneer Bar-Yam  \emph{Unifying Themes in Complex Systems.
-Proceedings of the Sixth International Conference on Complex Systems}, Springer Berlin Heidelberg, 66-73, (2008)
-
-\bibitem{yousefi-etal2008} Yousefi-Nooraie R, Akbari-Kamrani M, Hanneman RA, Etemadi A.
-Association between co-authorship network and scientific productivity and impact indicators in academic medical research centers: A case study in Iran.
-\textit{Health Research Policy and Systems} 6:9 (2008) doi:10.1186/1478-4505-6-9.
-
-%%Discusion references
-
-\bibitem{Simon1955} Simon, HA. On a class of skew distribution functions. \textit{Biometrika}, 42 (3-4): 425-440, (1955)
-
-\bibitem{Price1965} Price, Derek JS. Networks of Scientific Papers. \textit{Science}, 149(3683): 510-515, (1965)
-
-\bibitem{Merton1968} Merton, Robert K, The Matthew Effect in Science, \textit{Science}, 159(3810): 56-63 (1968)
-
-\bibitem{Epstein1996} Epstein JM \& Axtell R. \textit{Growing artificial societies. Social science from the bottom up}. The
-  Brookings Institution Press and The MIT Press, Washington, DC. (1996)
-
-\bibitem{Lansing2002} Lansing JS. ``Artificial Societies'' and the Social
-  Sciences. \textit{Artificial Life}, 8:279-292, (2002)
-
-\bibitem{Haraetal2003} Hara N, Solomon P, Kim SL, Sonnenwald DH. An emerging
-  view of scientific collaboration: Scientists' perspectives on collaboration
-  and factors that impact collaboration. Journal of the American Society for
-  Information Science and Technology, 54(10):952–965, 2003
-
-\bibitem{Barabasi2011} Barab\'asi, AL. The network takeover. \textit{Nature}, 8:14–16, (2012)
-
-\bibitem{Conteetal2012} Conte R, Gilbert N, Bonelli G, Cioffi-Revilla C,
-  Deffuant G, Kertesz J, Loreto V, Moat S, Nadal J.-P,  Sanchez A, Nowak A,
-  Flache  A, San Miguel M, Helbing D. Manifesto of computational social
-  science. \textit{The European Physical Journal, Special Topics} 214(1):325–346, (2012)
-
-  %
-% and use \bibitem to create references. Consult the Instructions
-% for authors for reference list style.
-%
-%\bibitem{RefJ}
-% Format for Journal Reference
-%Author, Article title, Journal, Volume, page numbers (year)
-% Format for books
-%\bibitem{RefB}
-%Author, Book title, page numbers. Publisher, place (year)
-% etc
-\end{thebibliography}
-
+\end{table}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%                               %%
+%% Additional Files              %%
+%%                               %%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\section*{Additional Files}
+  \subsection*{Additional file 1 --- Sample additional file title}
+    Additional file descriptions text (including details of how to
+    view the file, if it is in a non-standard format or the file extension).  This might
+    refer to a multi-page table or a figure.
+
+  \subsection*{Additional file 2 --- Sample additional file title}
+    Additional file descriptions text.
+
+\end{backmatter}
 \end{document}
-% end of file template.tex

### 2017-01-10 casm.tex
Title page and casm version

--- 2016-11-27 manuscript_3.tex
@@
-\documentclass[11pt]{article}                     
-\usepackage{graphicx}
-\usepackage[section]{placeins}
+%% BioMed_Central_Tex_Template_v1.06
+%%                                      %
+%  bmc_article.tex            ver: 1.06 %
+%                                       %
+
+%%IMPORTANT: do not delete the first line of this template
+%%It must be present to enable the BMC Submission system to
+%%recognise this template!!
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%                                     %%
+%%  LaTeX template for BioMed Central  %%
+%%     journal article submissions     %%
+%%                                     %%
+%%          <8 June 2012>              %%
+%%                                     %%
+%%                                     %%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%                                                                 %%
+%% For instructions on how to fill out this Tex template           %%
+%% document please refer to Readme.html and the instructions for   %%
+%% authors page on the biomed central website                      %%
+%% http://www.biomedcentral.com/info/authors/                      %%
+%%                                                                 %%
+%% Please do not use \input{...} to include other tex files.       %%
+%% Submit your LaTeX manuscript as one .tex document.              %%
+%%                                                                 %%
+%% All additional figures and files should be attached             %%
+%% separately and not embedded in the \TeX\ document itself.       %%
+%%                                                                 %%
+%% BioMed Central currently use the MikTex distribution of         %%
+%% TeX for Windows) of TeX and LaTeX.  This is available from      %%
+%% http://www.miktex.org                                           %%
+%%                                                                 %%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%% additional documentclass options:
+%  [doublespacing]
+%  [linenumbers]   - put the line numbers on margins
+
+%%% loading packages, author definitions
+
+%\documentclass[twocolumn]{bmcart}% uncomment this for twocolumn layout and comment line below
+\documentclass{bmcart}
+
+%%% Load packages
+%\usepackage{amsthm,amsmath}
+%\RequirePackage{natbib}
+%\RequirePackage[authoryear]{natbib}% uncomment this for author-year bibliography
+%\RequirePackage{hyperref}
+\usepackage[utf8]{inputenc} %unicode support
 \usepackage{color}
-\usepackage{lineno}
-\linenumbers
-%
-% \usepackage{mathptmx}      % use Times fonts if available on your TeX system
-%
-% insert here the call for the packages your document requires
-%\usepackage{latexsym}
-% etc.
-%
-% please place your own definitions here and don't use \def but
-% \newcommand{}{}
-%
-% Insert the name of "your journal" with
-% \journalname{myjournal}
-%
+% \usepackage[applemac]{inputenc} %applemac support if unicode package fails
+%\usepackage[latin1]{inputenc} %UNIX support if unicode package fails
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%                                             %%
+%%  If you wish to display your graphics for   %%
+%%  your own use using includegraphic or       %%
+%%  includegraphics, then comment out the      %%
+%%  following two lines of code.               %%
+%%  NB: These line *must* be included when     %%
+%%  submitting to BMC.                         %%
+%%  All figure files must be submitted as      %%
+%%  separate graphics through the BMC          %%
+%%  submission process, not included in the    %%
+%%  submitted article.                         %%
+%%                                             %%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\def\includegraphic{}
+\def\includegraphics{}
+
+%%% Put your definitions there:
+\startlocaldefs
+\endlocaldefs
+
+%%% Begin ...
 \begin{document}
 
-\title{A game-theory modeling approach to utility
-  and strength of interactions dynamics in biomedical research social networks}
-%\title{Two games modeling approach to collaboration dynamics in biomedical
-%research social networks}
-
-%\thanks{Grants or other notes
-%about the article that should go on the front page should be
-%placed here. General acknowledgments should be placed at the end of the article.}
-
-%\subtitle{Do you have a subtitle?\\ If so, write it here}
-
-%\titlerunning{Fitness \& trust in biomedical research networks}
-
-%\titlerunning{Short form of title}        % if too long for running head
-
-\author{J. Mario Siqueiros-Garc\'ia         \and      Rodrigo Garc\'ia-Herrera \and         Enrique Hern\'andez-Lemus \and
-        Sergio A. Alcal\'a-Corona  %etc.
+%%% Start of article front matter
+\begin{frontmatter}
+
+\begin{fmbox}
+\dochead{Research}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%                                          %%
+%% Enter the title of your article here     %%
+%%                                          %%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\title{A game-theory modeling approach to utility and strength of interactions dynamics in biomedical research social networks}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%                                          %%
+%% Enter the authors here                   %%
+%%                                          %%
+%% Specify information, if available,       %%
+%% in the form:                             %%
+%%   <key>={<id1>,<id2>}                    %%
+%%   <key>=                                 %%
+%% Comment or delete the keys which are     %%
+%% not used. Repeat \author command as much %%
+%% as required.                             %%
+%%                                          %%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\author[
+   addressref={aff1,aff2},                   % id's of addresses, e.g. {aff1,aff2}
+   corref={aff1},                       % id of corresponding address, if any
+   noteref={n1},                        % id's of article notes, if any
+   email={jmario.siqueiros@iimas.unam.mx}   % email address
+]{\inits{JMSG}\fnm{J. Mario} \snm{Siqueiros-Garc\'ia}}
+\author[
+   addressref={aff2},
+   email={rgarcia@ie.unam.mx}
+]{\inits{RGH}\fnm{Rodrigo} \snm{Garc\'ia-Herrera}}
+\author[
+   addressref={aff3},
+   email={ehernandez@inmegen.mx}
+]{\inits{EHL}\fnm{Enrique} \snm{Hern\'andez-Lemus}}
+\author[
+   addressref={aff3},
+   email={sergio.alcala@ciencias.unam.mx}
+]{\inits{SAC}\fnm{Sergio} \snm{Alcal\'a-Corona}}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%                                          %%
+%% Enter the authors' addresses here        %%
+%%                                          %%
+%% Repeat \address commands as much as      %%
+%% required.                                %%
+%%                                          %%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\address[id=aff1]{%                           % unique id
+  \orgname{IIMAS, Universidad Nacional Aut\'onoma de M\'exico}, % university, etc
+  \street{Circuito Escolar 3000, Cd. Universitaria},                     %
+  \postcode{04510}                                % post or zip code
+  \city{Mexico City},                              % city
+  \cny{Mexico}                                    % country
 }
-
-%\authorrunning{Short form of author list} % if too long for running head
-
-%% \institute{J. Mario Siqueiros-Garc\'ia \at
-%%   IIMAS-UNAM. Circuito Escolar 3000, Cd Universitaria, Coyoacán, Ciudad de México, D.F. \\
-%%               Tel.: +123-45-678910\\
-%%               Fax: +123-45-678910\\
-%%               \email{jmario.siqueiros@iimas.unam.mx}           %  \\
-%% %             \emph{Present address:} of F. Author  %  if needed
-%%               \and
-%%               Rodrigo Garc\'ia-Herrera,\\ Enrique Hern\'andez-Lemus, \\ Sergio A. Alcal\'a-Corona \at
-%%               National Institute of Genomic Medicine\\
-%%               Perif\'erico Sur 4809, Arenal Tepepan, Tlalpan, 14610, \\
-%%               Ciudad de M\'exico, D.F., M\'exico  
-%%            %% S. Author \at
-%%            %%    second address
-%% }
-
-\date{\today}
-% The correct dates will be entered by the editor
-
-\maketitle
-
-\begin{abstract}
-
+\address[id=aff2]{%
+  \orgname{LANCIS-IE, Universidad Nacional Aut\'onoma de M\'exico},
+  \street{Ciudad Universitaria},
+  \postcode{04510}
+  \city{Mexico City},
+  \cny{Mexico}
+}
+\address[id=aff3]{%
+  \orgname{Instituto Nacional de Medicina Gen\'omica},
+  \street{Periferico Sur 4809},
+  \postcode{14610}
+  \city{Mexico City},
+  \cny{Mexico}
+}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%                                          %%
+%% Enter short notes here                   %%
+%%                                          %%
+%% Short notes will be after addresses      %%
+%% on first page.                           %%
+%%                                          %%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\begin{artnotes}
+%\note{Sample of title note}     % note to the article
+\note[id=n1]{Equal contributor} % note, connected to author
+\end{artnotes}
+
+\end{fmbox}% comment this for two column layout
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%                                          %%
+%% The Abstract begins here                 %%
+%%                                          %%
+%% Please refer to the Instructions for     %%
+%% authors on http://www.biomedcentral.com  %%
+%% and include the section headings         %%
+%% accordingly for your article type.       %%
+%%                                          %%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\begin{abstractbox}
+
+\begin{abstract} % abstract
+%\parttitle{First part title} %if any
 Collaboration has become a cornerstone in biomedical research today.
@@
 collaborative projects, biology is only recently becoming an evermore
-collaborative discipline.  In this article we explore the effect of
-collaboraion on the distribution of players' access to resources from
-other players in the network and the distribution of the strength of
-interactions among them. Particularly, we implemented two games played
-simultaneously: one for maximazing individual utility based on the
-iterated Prisoner's Dilemma; the other, a coordination game for
-maximazing the connection strength between players. We are interested
-in how they affect each other in the context of a network of
-scientific collaboration under the idea that while researchers are
-interested in maximazing their individual utilities, they also know
-that it is important to invest in building collaborative
-relationships.  We tested our simulation on a biomedical research
-community network of M\'exico and compared the results with an
-Erd\"{o}s-Reny\'i, a Watts-Strogatz small-world and Barab\'asi-Albert
-topologies. Different topologies display different utility and
-interaction strength distributions. Moreover, the distribution of
-utility and interaction strength in the researchers network is similar
-to that of Barab\'asi-Albert and Watts-Strogatz topologies,
-respectively. We believe that utility distribution in the researchers
-network suggests that there are socio-cultural mechanisms governing
-the network that produce an asymmetric distribution of resources. The
-high distribution of strong interactions might reflect some sort of
+collaborative discipline.
+In this article we explore the effect of a collaboration network on the distribution
+of players having access to certain amount of resources from other players in the
+network and the distribution of the strength of connections among
+them. Particularly, we implemented two games played simultaneously:
+one for maximazing individual utility based on the iterated Prisoner's
+Dilemma; the other, a coordination game for maximazing the connection strength
+between players. We are interested in how they affect each other in 
+the context of a network of scientific collaboration under the idea that while
+researchers are interested in maximazing their utilities, they also know that
+it is important to invest in building collaborative relationships.
+We tested our simulation on a biomedical research community network of M\'exico and
+compared the results with an Erd\"{o}s-Reny\'i, a Watts-Strogatz
+small-world and Barab\'asi-Albert topologies. Different topologies
+display different global utility and global strength of interaction
+distributions. Moreover, the distribution of utility and strength of interaction
+in the researchers network is similar to that of 
+Barab\'asi-Albert and Watts-Strogatz topologies, respectively. We
+believe that utility distribution in the researchers network
+suggests that there are socio-cultural mechanisms governing the
+network that produce an asymmetric distribution of resources. The
+high distribution of strong connections might reflect some sort of
 subordination among researchers by which they are morally obliged to
-cooperate by the same socio-cultural mechanisms. The range around the
-threshold that regulates the decision to cooperate or defect according
-to the agent's historical balance between utility and strength of
-collaborative relationships and carrying capacity of the system is
-small, suggesting that there is a region in which a phase transition
-takes place from a population of cooperators to a population of
-defectors. Simulations like this may help to develop science policies
-to promote fair distribution of resources.
-
+cooperate by the same socio-cultural mechanisms. Finally, the range around
+the threshold that regulates the decision to cooperate or defect
+according to the agent's historical balance between utility and
+strength of collaborative relationships and carrying capacity of the
+system is small, suggesting that there is a region in which a phase
+transition takes place from a population of cooperators to a
+population of defectors. Simulations like ours may help to develop
+science policies to promote fair distribution of resources.
+
+%\parttitle{Second part title} %if any
 \end{abstract}
 
-\section{Introduction}
-\label{intro}
-
-%% \textbf{Notes:}
-
-%% \begin{itemize}
-
-%% %% \item In this paper there are two games played simultaneously: One for
-%% %% maximazing individual utility; the second for maximazing the connection
-%% %% strength. We are interested in how they affect eachother in the context of a
-%% %% network of collaboration.
-
-%% \item We change utility for fitness. Utility seems a better concept in order to
-%%   reflect players' preferences.
-
-%% %% \item In the context of our paper, utility represents
-%% %%   the preference for having access to the resources of others. Maximazing
-%% %%   utility means that the player is increasing its access to the resources of
-%% %%   other players.  Utility function is just the sum of the payoffs of playing
-%% %%   with its neighbors. As for the payoff matrix, the best strategy for a player
-%% %%   is to defect. Any other option will not be an optimal payoff. The opossing
-%% %%   force is in the other game. The game for maximazing the strength of the
-%% %%   connection among players. In this case defecting or cooperating? is the best
-%% %%   strategy as it pays the most when coordinating regardeless they both cooperate
-%% %%   or defect, this is because when both cooperate the interaction gets a positive
-%% %%   payoff, when both defect, the interaction doesn't get affected; but if they
-%% %%   anti-coordinate, then the interaction looses. In this sense, this might be a
-%% %%   game were there are multiple (i.e., 2 points or strategies) equilibria. It
-%% %%   seems that there is no single dominant strategy.}\\
-
-%% \item Choosing a strategy depends on the balance $\eta'$ equation --look at page
-%%   9. This
-%%   equation states that the probability of an agent to cooperate increases as: a)
-%%   its utility increases --as it moves away from 0, or; b) The strength of the
-%%   connection with its peers increases --as it moves away from 0, or; c) both
-%%   increases.
-
-%%   $\eta_i = \frac{\langle f_i \rangle + \langle w_{ij} \rangle _j}{2}$\\
-
-%% \item{En la pagina 9 decimos que ``In order for the agent to choose to cooperate
-%%   or defect, a degree of willingness to cooperate is assigned to each agent.'' No estoy
-%%   seguro que ``degree of willingness to cooperate'' sea la mejor manera de
-%%   decirlo, mi duda está en la palabra ``degree'', por lo que cambi\'e la
-%%   oraci\'on a: The probability for an agent to cooperate or defect depends on a
-%% number that referes to a historical balance between average utility and the average strength of
-%% the connections with its neigbors. }
-
-%% \end{itemize}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%                                          %%
+%% The keywords begin here                  %%
+%%                                          %%
+%% Put each keyword in separate \kwd{}.     %%
+%%                                          %%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\begin{keyword}
+\kwd{Collaboration networks}
+\kwd{Social Networks Analysis}
+\kwd{Biomedicine}
+\kwd{Game theory}
+\end{keyword}
+
+% MSC classifications codes, if any
+%\begin{keyword}[class=AMS]
+%\kwd[Primary ]{}
+%\kwd{}
+%\kwd[; secondary ]{}
+%\end{keyword}
+
+\end{abstractbox}
+%
+%\end{fmbox}% uncomment this for twcolumn layout
+
+\end{frontmatter}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%                                          %%
+%% The Main Body begins here                %%
+%%                                          %%
+%% Please refer to the instructions for     %%
+%% authors on:                              %%
+%% http://www.biomedcentral.com/info/authors%%
+%% and include the section headings         %%
+%% accordingly for your article type.       %%
+%%                                          %%
+%% See the Results and Discussion section   %%
+%% for details on how to create sub-sections%%
+%%                                          %%
+%% use \cite{...} to cite references        %%
+%%  \cite{koon} and                         %%
+%%  \cite{oreg,khar,zvai,xjon,schn,pond}    %%
+%%  \nocite{smith,marg,hunn,advi,koha,mouse}%%
+%%                                          %%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%%%%%%%%%%%%%%%%%%%%%%%% start of article main body
+% <put your article body there>
+
+%%%%%%%%%%%%%%%%
+%% Background %%
+%%
+
+\section*{Introduction}
 
@@
 collaborative projects, biology is only recently becoming an evermore
-collaborative discipline\cite{Vermeulen2013}. Biology has an
+collaborative discipline\cite{VermeulenPenders:2013}. Biology has an
 interesting record in such matters because scientific collaboration
@@
 biology has traditionally been a research activity of small
-laboratories\cite{KnorrCetina1999,Strasser2006}, whereas in natural
+laboratories\cite{KnorrCetina:1999,Strasser:2006}, whereas in natural
 history there has been data and samples exchange since the $XVII^{th}$
-century\cite{Muller2012,Strasser2012}. Despite the differences in
+century\cite{MullerWille-etal:2012,Strasser:2012}. Despite the differences in
 culture and practices, the Human Genome Project made collaboration a
@@
 number of studies
-\cite{Vermeulen2013,Newman2001,Newman2004,Elango2012,HernandezLemus2013,Strasser2006,Strasser2012}. This
+\cite{VermeulenPenders:2013,Newman:2001,Newman:2004,Elango-etal:2012,HernandezLemus:2013,Strasser:2006,Strasser:2012}. This
 is not surprising since cooperation and competition are quite important in
@@
 academic environment and what kind of payoff is present in these settings were
-questions considered recently by Wardil and Hauert \cite{Wardil2015} in the
+questions considered recently by Wardil and Hauert \cite{Wardil-etal:2015} in the
 context of cooperation in multi-authored publications. Also, the role of game
@@
 attracted attention, mainly focusing on how long-term strategies may shape
-different scenarios for Nash equilibria \cite{hanauske2012}. Prisoner's Dilemma
+different scenarios for Nash equilibria \cite{Hanauske-etal:2012}. Prisoner's Dilemma
 has been used in the study of impact factor and collaboration
-\cite{Hara_etal_2002,Lieberman_etal_2005}. \\
+\cite{Hara-etal:2003,LiebermanNowak:2005}. \\
 
@@
 \footnote{For an account of scientific collaboration and definitions,
-  please refer to \cite{Sonnenwald2007}.}. Our work aims to contribute
+  please refer to \cite{Sonnenwald:2007}.}. Our work aims to contribute
 to our current understanding on the matter, specially when agents have
 to maximize their access to resources while taking care of their collaboration links.\\
-
-  %% nevertheless
-  %% and to a certain degree, the idea behind the model is ethnographically
-  %% inspired\footnote{For a mixed methodology approach to scientific
-  %%   collaboration refer to Hara et al., 2002 \cite{Hara_etal_2002}.}. In
-  %% previous work we observed that members of biomedical research groups interact
-  %% strongly with each other but interactions between groups are only
-  %% superficial. Our ethnographic work also allowed us to see how difficult is for
-  %% Principal Investigators to collaborate with peer groups that are considered
-  %% somehow equal in terms of different criteria such a productivity or power. On
-  %% the other hand, collaboration may be easier with groups that are far beyond in
-  %% some of these terms. This seems to be so because when dealing with a smaller
-  %% group, the stronger one can establish conditions of collaboration; when the
-  %% group is weaker, there might be a lot to win. For example, this latter
-  %% situation can be seen when local groups collaborate with research groups form
-  %% overseas, specially from the US.}\\
-
-%% {\color{red}The question behind our model rests on three premises: Scientist
-%%   have self-interests and may act seeking their own interests; Scientific
-%%   collaboration needs researchers to cooperate and build relationships that can
-%%   last; Scientific collaboration networks have a particular topology. Under such
-%%   context, if the same amount of resources were given to every researcher at the
-%%   same point in time, how would the access to resources be distributed, in the
-%%   long run, in a population of interacting researchers that seek to improve
-%%   their profits but at the same time have to invest in building trustworthy
-%%   relationships with their colleagues?}
-%%\\
-
-  %% Seen from a different point of view, how would trust be
-  %% distributed in a population of researchers that are mainly interested in
-  %% improving their profits, even when acting selfishly always could have a
-  %% negative impact on that primary objective?}\\
 
@@
 
-In the context of our paper, utility represents
+In the context of our model, utility represents
   access to resources shared by others.
-  The value of the Utility function for a player is the sum of the payoffs of playing
+  The value of the utility function for a player is the sum of the payoffs of playing
   with its neighbors. The opossing force comes from the other concurrent game: players
   trying to maximize the strength of their interactions with other players. In the coordinating game
-  the best strategy is to adopt the same strategy as the other player, as it pays the most
+  the best strategy is to adopt the same strategy as the other player, as it pays the most,
   regardless of cooperation or defection in the utility game. When
@@
 
-The manuscript is structured in five sections. First we describe
+The manuscript is structured in four sections. First we describe
 \textit{FOSISS}, the main program for grants destined to biomedical applied
@@
 call for funds limited to a set of health research areas previously defined by a
-group of experts. Such areas range from public health issues to chronic and
-degenerative diseases.\\
-
-Most applicants are public universities and research institutions, but
-eligibility is open to public and private health research sectors.
+group of experts. Most applicants are public universities and research
+institutions, but eligibility is open to public and private health research sectors.
 From 2002 through 2013, there were 91 institutions funded that
@@
 research aimed to understand the evolution of cooperation in networks populated
-by selfish agents \cite{Szabo2007,Nowak1992,Nowak2006,Santos2005,Santos2006}. In many network models
+by selfish agents \cite{SzaboFath:2007,Nowak-etal:92,OshtukiNowak:2006,Santos-etal:2005,Santos-etal:2006}. In many network models
 on which some of game theory games are simulated, agents' decision to cooperate
 or defect depend on a specific strategy, such as the well known
-\textit{tit-for-tat} \cite{Axelrod2006,Nowak2011}. In some other cases, agents
+\textit{tit-for-tat} \cite{Axelrod:2006,Nowak-etal:2011}. In some other cases, agents
 can modify the weight of the interactions with their neighbors
-\cite{Santos2006}. From a different perspective others have explored the effect
+\cite{Santos-etal:2006}. From a different perspective others have explored the effect
 of different topologies on the emergence of cooperation
-\cite{Santos2005,Hauert2004}. In our model, an agent's decision to cooperate or
-defect depends on a balance between
+\cite{Santos-etal:2005,HauertDoebeli:2004}. In our model, an agent's decision to
+cooperate or defect depends on a balance between
 utilities and the current strength of its collaboration relationships. Such
@@
 strength of connections or $W$ is the sum of every pair of agents' links
-$w$. The strength of interaction can 
-be thought as some sort of ``trust''.\\
+$w$. The strength of interaction can be thought as some sort of ``trust''.\\
 
@@
 
-The probability for an agent to cooperate or defect depends on a
-number ($\eta$) that referes to a historical balance between average utility and
-the average strength of the connections with its neigbors. This is so
-  because we assume that whatever the result in utility or strength of
-  connection, as long as one of them increases, the player will be confident in
-  the strategy followed so far.\\
+The probability for an agent to cooperate or defect depends on a number ($\eta$)
+that referes to a historical balance between average utility and the average
+strength of the connections with its neigbors. This is so because we assume that
+whatever the result in utility or strength of connection, as long as one of them
+increases, the player will be confident in the strategy followed so
+far. In every simulation step, each player will play both games
+  with every neighbor, but set its decision to cooperate or defect beforehand by
+  assesing the overall situation of its relationships. This may sound odd, since
+  one may think that a person decides for each relationship separately. However
+  in this way players are optimizing access to resources and the strength of
+  interactions to their neighbors at the same time, since their state is set by
+  considering both together.\\
 
@@
   agents' $\eta$ must cross in order to decide to cooperate. In this way,
-  $\eta$ can limit the size of the population of cooperators. Due
+  $\nu$ can limit the size of the population of cooperators. Due
   to what the system and the game can offer to agents in terms of utilities and the strength
-  of collaboration relationships, $\eta$ represents the carrying capacity of the
+  of collaboration relationships, $\nu$ represents the carrying capacity of the
   system for the population of cooperators.\\
@@
 
-\subsection{Erd\"{o}s-Reny\'i}
-
-Erd\"{o}s-Reny\'i networks \cite{Erdos1959} (random networks) are constructed by randomly selecting a pair of $N$ possible nodes and attaching them with an edge, given a probability $p$, as long as there is no edge between them.
+\subsection*{Erd\"{o}s-Reny\'i}
+
+Erd\"{o}s-Reny\'i networks \cite{ErdosRenyi:59} (random networks) are constructed by randomly selecting a pair of $N$ possible nodes and attaching them with an edge, given a probability $p$, as long as there is no edge between them.
 The result is a Poisson distribution for connectivity of nodes $P(k)$, where each node has a degree quite close to the average $\langle k \rangle$.
@@
 
-\subsection{Small-World}
-
-Watts-Strogatz networks \cite{Watts1998} (small-world networks) are in a regime between a fully regular grid (lattice) and a random network (Erd\"{o}s-R\'enyi).
+\subsection*{Small-World}
+
+Watts-Strogatz networks \cite{WattsStrogatz:98} (small-world networks) are in a regime between a fully regular grid (lattice) and a random network (Erd\"{o}s-R\'enyi).
 In order to build them, a node is chosen from a lattice (a ring) and the edge that connects it to nearest neighbor in a clockwise sense.
@@
 
-\subsection{Barb\'asi-Albert}
-
-Barb\'asi-Albert networks \cite{Barabasi1999} (scale-free networks) are generated by adding new nodes to a network.
+\subsection*{Barb\'asi-Albert}
+
+Barb\'asi-Albert networks \cite{BarabasiAlbert:99} (scale-free networks) are generated by adding new nodes to a network.
 Each new node is added connecting it to an existing node with a probability proportional to the degree $k$ (connectivity) of each node (\textit{preferential attachment}).
@@
 
-\section{Results}
-\label{sec:3}
+\section*{Results}
 
@@
 $\langle l \rangle = 5.493$  and a density of $p = 0.003$. Such properties
-recall a small-world topology \cite{Watts1998}, and a great deal of
+recall a small-world topology \cite{WattsStrogatz:98}, and a great deal of
 self-organization when compared to a random network with the same density and
@@
 power-law with an exponent of $1.7$, similar to other social networks described
-as scale-free topology networks \cite{Barabasi1999}. Finally, the average number
-of neighbors of each node is $11.39$ \cite{Shannon2003}.\\
+as scale-free topology networks \cite{BarabasiAlbert:99}. Finally, the average number
+of neighbors of each node is $11.39$ \cite{Shannon:2003}.\\
 
@@
 \centering
-\includegraphics[scale=0.5]{images/Fosiss_GC_final.png}
+% \includegraphics[scale=0.5]{images/Fosiss_GC_final.png}
 \caption{Bioemdical research collaboration network (FOSISS) giant component.}\label{Fosiss_GC}
@@
 
-\FloatBarrier
+%\FloatBarrier
 
@@
 different variables. It is worth noting that the shape
-of the phase transition is different according to the topology of the
+of the phase transition-like behavior is different according to the topology of the
 network under study. When $\nu$ is between $0.0$ and $0.2$, that is, when there is
 no space or a very short one for suspiciousness, all agents cooperate, when
-\textit{carrying capacity} is above $0.25$, all agents defect. \textit{Utility},
+$\nu$ is above $0.25$, all agents defect. \textit{Utility},
 \textit{strength of interactions}, and \textit{changing state population}
@@
 \approx 0.5$ the number of cooperators converge to a certain degree
-and stays constant for the rest of the simulation.
+and stays constant for the rest of the simulation.\\
 
@@
 \begin{tabular}{cc}
-  \includegraphics[scale=0.28]{images/erdos_dc_nus_1.png} & \includegraphics[scale=0.28]{images/watts_dc_nus_1.png}
-  \\
-  \includegraphics[scale=0.28]{images/barabasi_dc_nus_1.png} & \includegraphics[scale=0.28]{images/fosiss_dc_nus_1.png}
+%   \includegraphics[scale=0.28]{images/erdos_dc_nus_1.png} & \includegraphics[scale=0.28]{images/watts_dc_nus_1.png}
+%   \\
+%   \includegraphics[scale=0.28]{images/barabasi_dc_nus_1.png} & \includegraphics[scale=0.28]{images/fosiss_dc_nus_1.png}
 \end{tabular}
@@
 
-\FloatBarrier
+% \FloatBarrier
 
@@
 $\nu \approx 0.28$, utility and strength of interactions start at their lowest,
-but there is a slight increase in both of them.
+but there is a slight increase in both of them.\\
 
@@
 
-\includegraphics[scale=0.28]{images/erdos_fitness_nus_1.png} & \includegraphics[scale=0.28]{images/watts_fitness_nus_1.png} \\
-\includegraphics[scale=0.28]{images/barabasi_fitness_nus_1.png} & \includegraphics[scale=0.28]{images/fosiss_fitness_nus_1.png}
+% \includegraphics[scale=0.28]{images/erdos_fitness_nus_1.png} & \includegraphics[scale=0.28]{images/watts_fitness_nus_1.png} \\
+% \includegraphics[scale=0.28]{images/barabasi_fitness_nus_1.png} & \includegraphics[scale=0.28]{images/fosiss_fitness_nus_1.png}
 \end{tabular}
@@
 
-\includegraphics[scale=0.28]{images/erdos_trust_nus_1.png} & \includegraphics[scale=0.28]{images/watts_trust_nus_1.png} \\
-\includegraphics[scale=0.28]{images/barabasi_trust_nus_1.png} & \includegraphics[scale=0.28]{images/fosiss_trust_nus_1.png}
+% \includegraphics[scale=0.28]{images/erdos_trust_nus_1.png} & \includegraphics[scale=0.28]{images/watts_trust_nus_1.png} \\
+% \includegraphics[scale=0.28]{images/barabasi_trust_nus_1.png} & \includegraphics[scale=0.28]{images/fosiss_trust_nus_1.png}
 \end{tabular}
@@
 crossed as $\nu$ increases, the number of agents shifting states falls to $0$
-and all nodes become defectors.
+and all nodes become defectors. \\
 
@@
 
-\includegraphics[scale=0.28]{images/erdos_state_nus.png} & \includegraphics[scale=0.28]{images/watts_state_nus.png} \\
-\includegraphics[scale=0.28]{images/barabasi_state_nus.png} & \includegraphics[scale=0.28]{images/fosiss_state_nus.png}
+% \includegraphics[scale=0.28]{images/erdos_state_nus.png} & \includegraphics[scale=0.28]{images/watts_state_nus.png} \\
+% \includegraphics[scale=0.28]{images/barabasi_state_nus.png} & \includegraphics[scale=0.28]{images/fosiss_state_nus.png}
 \end{tabular}
@@
 connecting with any other node, which produces a \textit{poissonian} degree
-distribution \cite{Erdos1959}. Since the Watts-Strogatz degree distribution is
+distribution \cite{ErdosRenyi:59}. Since the Watts-Strogatz degree distribution is
 described by a function that is midways between a random distribution and a
-scale-free network \cite{Barrat2000} one may expect also  an intermediate
+scale-free network \cite{Barratmodels:2000} one may expect also  an intermediate
 behavior of the utility distribution. This assumption seems to be fulfilled by
-the distribution in Figure 6B.
+the distribution in Figure 6B. \\
 
@@
 describes the fact that there are a small number of nodes with large $k$ and most
-nodes have a small $k$ \cite{Barabasi1999}. As it is shown in the following
+nodes have a small $k$ \cite{BarabasiAlbert:99}. As it is shown in the following
 figure, most utility is concentrated in a few number of agents, while most
@@
 which concentration of resources, fame or citations in science decreases as a
-power-law \cite{Simon1955,Price1965,Merton1968}. FOSISS network utility
+power-law \cite{Simon:55,Price:1965,Merton:1968}. FOSISS network utility
 distribution is also skewed to the left, similar to that of the
@@
 
-\includegraphics[scale=0.28]{images/erdos_fitness.png} & 
-\includegraphics[scale=0.28]{images/watts_fitness.png} \\
-\includegraphics[scale=0.28]{images/barabasi_fitness.png} & 
-\includegraphics[scale=0.28]{images/fosiss_fitness.png}
+% \includegraphics[scale=0.28]{images/erdos_fitness.png} & 
+% \includegraphics[scale=0.28]{images/watts_fitness.png} \\
+% \includegraphics[scale=0.28]{images/barabasi_fitness.png} & 
+% \includegraphics[scale=0.28]{images/fosiss_fitness.png}
 \end{tabular}
@@
 hypothesize that this effect is also due to the communication properties of the
-network.
+network. \\
 
@@
 
-\includegraphics[scale=0.28]{images/erdos_trust.png} & 
-\includegraphics[scale=0.28]{images/watts_trust.png} \\
-\includegraphics[scale=0.28]{images/barabasi_trust.png} & 
-\includegraphics[scale=0.28]{images/fosiss_trust.png}
+% \includegraphics[scale=0.28]{images/erdos_trust.png} & 
+% \includegraphics[scale=0.28]{images/watts_trust.png} \\
+% \includegraphics[scale=0.28]{images/barabasi_trust.png} & 
+% \includegraphics[scale=0.28]{images/fosiss_trust.png}
 \end{tabular}
@@
 distribution. B. Watts-Strogatz network strength of interactions distribution is bimodal and highly skewed to the right. C.
-  Barab\'asi-Albert network strength of interactions distribution is also a normal-like curve. D. FOSISS, biomedical researchers
-  collaboration network distribution of strength of interactions is skewed to
-  the right.}\label{histo_trust}  
+Barab\'asi-Albert network strength of interactions distribution is also a
+normal-like curve. D. FOSISS, biomedical researchers collaboration network distribution of strength of interactions is skewed to the right.}\label{histo_trust}  
 \end{figure}
 
-\FloatBarrier
+% \FloatBarrier
 
@@
 
-\section{Discussion and Conclusions}
+\section*{Discussion}
 \label{sec:3}
@@
 
+  \section*{Conclusions}
+
  To close this article, we would like to comment on three
@@
   heterogeneity of $0.873$. Because of it, one would expect to find
-  the presence of important hubs \cite{Wu-etal2008}, that is, a few
+  the presence of important hubs \cite{Wu:2008}, that is, a few
   researchers control the whole network, as has been reported in some
-  other places \cite{yousefi-etal2008}. Surprisingly, FOSISS network
+  other places \cite{yousefi-etal:2008}. Surprisingly, FOSISS network
   centralization is very low $0.023$, i.e. there are no researchers
@@
   co-authorships in one of the research centers that is part of the
-  FOSISS network \cite{HernandezLemus2013}. In the cited reference an
+  FOSISS network \cite{HernandezLemus:2013}. In the cited reference an
   apparently well integrated community was found (high clustering
@@
   (most of them from overseas).  Removing these external collaborators
-  broke down the network into small subgraphs that worked
+  brakes down the network into small subgraphs that worked
   independently. Remarkably those subgraphs corresponded to the real
@@
   small research groups by cutting some edges, as it happened in our
-  co-authorship collaboration network \cite{HernandezLemus2013}. The
+  co-authorship collaboration network \cite{HernandezLemus:2013}. The
   lack of robustness might be indicative of the fact that resources
@@
 
-%% {\color{red}Regarding simulations and social science. We believe that social scientists may learn many lessons from
-%%   computational modeling. Tipically, the use of computational modeling as part of the social sciences
-%%   has been justified by arguing that such methods allow to understand the connection between the level of the individual
-%%   and the level of the group, they make possible to explore different outcomes by tuning different parameters and to
-%%   perform --virtual-- experiementation, as well as studying different propensities as Stephen Lansing calls them
-%%   \cite{Epstein1996,Lansing2002}. All these are important arguments but we would also like to say something else about 
-%%   them. When presenting computational modeling to non-computational social scientists (specially anthropologists) one gets
-%%   confronted with several critiques from which, the most common are that computational modeling tends to ignore cultural
-%%   differences (should be noticed that cultural differences is not the same as social differences), and that it is hard to grasp the cultural
-%%   meaning or significance of the dynamics expressed in the simulation. Because of this kind of observations we are
-%%   particularly interested in not forgiving from our work the ethnographical, culturally loaded content of social life,
-%%   while recognizing the value of computational simulations.}\\
-
-%% {\color{red}We believe that computational simulations are methodologically valuable for two reasons. The first one is that
-%% simulations can play an important role in social research as heuristics. If, as we have been doing in this project, fieldwork
-%% observations influence and inspire the development of a computational simulation, parameters must be an abstraction of
-%% those observations or at least of part of them. In this sense, the outcomes of simulations are a guide towards new
-%% questions and future fieldwork explorations at the time that it constrains and helps to prioritize what is to be
-%% observed. For example, from out results it seems mandatory to interview different research groups in order to disclose
-%% internal group dynamics and how and which are the terms for collaboration between groups. The second reason emerges from
-%% the first, we think that simulations are excellent hypothesis generators for the social sciences. Due to the
-%% imposibility of ``observing'' the social dynamics on real-time, just because we can only observe locally while one is
-%% doing fieldwork, there are left a few options to see how local dynamics may produce emergent patterns. Simulations may
-%% be of great help to elaborate guesses about the mechanisms for the behaviors observed at the local scale, as well as for
-%% the global. For example, we could guess that the hierarchical structure without hubs imposes strong limits to the flow
-%% of resources and information or that we can expect certain cultural intepretation regarding collaboration due to the
-%% position of researchers in the network. Such hypothesis can be computationally tested too.}\\
-
 On these grounds, part of our future work is based on
@@
   our simulations, probably we would follow a similar strategy as the
-  one developed in \cite{Haraetal2003}. Finding communities beyond the
+  one developed in \cite{Hara:2003}. Finding communities beyond the
   level of the groups is an important task. We think that there are
@@
   simulations can be designed on real world data, something that only
-  very recently has become possible \cite{Barabasi2011}.\\
+  very recently has become possible \cite{Barabasi:2012}.\\
 
@@
 
-%Text with citations \cite{RefB} and \cite{RefJ}.
-%\subsection{Subsection title}
-%\label{sec:2}
-%as required. Don't forget to give each section
-%and subsection a unique label (see Sect.~\ref{sec:1}).
-%\paragraph{Paragraph headings} Use paragraph headings as needed.
-%\begin{equation}
-%a^2+b^2=c^2
-%\end{equation}
-
-% For one-column wide figures use
-%\begin{figure}
-% Use the relevant command to insert your figure file.
-% For example, with the graphicx package use
-%  \includegraphics{images/example.eps}
-% figure caption is below the figure
-%\caption{Please write your figure caption here}
-%\label{fig:1}       % Give a unique label
-%\end{figure}
-%
-% For two-column wide figures use
-%\begin{figure*}
-% Use the relevant command to insert your figure file.
-% For example, with the graphicx package use
-%  \includegraphics[width=0.75\textwidth]{example.eps}
-% figure caption is below the figure
-%\caption{Please write your figure caption here}
-%\label{fig:2}       % Give a unique label
-%\end{figure*}
-%
-% hello, friend
-%
-% For tables use
-%\begin{table}
-% table caption is above the table
-%\section{%\caption{Please write your table caption here}}
-%\label{tab:1}       % Give a unique label
-% For LaTeX tables use
-%\begin{tabular}{lll}
-%\hline\noalign{\smallskip}
-%first & second & third  \\
-%\noalign{\smallskip}\hline\noalign{\smallskip}
-%number & number & number \\
-%number & number & number \\
-%\noalign{\smallskip}\hline
-%\end{tabular}
-%\end{table}
-
-\section{Acknowledgements}
+% \section*{Content}
+% Text and results for this section, as per the individual journal's instructions for authors. %\cite{koon,oreg,khar,zvai,xjon,schn,pond,smith,marg,hunn,advi,koha,mouse}
+
+% \section*{Section title}
+% Text for this section \ldots
+% \subsection*{Sub-heading for section}
+% Text for this sub-heading \ldots
+% \subsubsection*{Sub-sub heading for section}
+% Text for this sub-sub-heading \ldots
+% \paragraph*{Sub-sub-sub heading for section}
+% Text for this sub-sub-sub-heading \ldots
+% In this section we examine the growth rate of the mean of $Z_0$, $Z_1$ and $Z_2$. In
+% addition, we examine a common modeling assumption and note the
+% importance of considering the tails of the extinction time $T_x$ in
+% studies of escape dynamics.
+% We will first consider the expected resistant population at $vT_x$ for
+% some $v>0$, (and temporarily assume $\alpha=0$)
+% %
+% \[
+%  E \bigl[Z_1(vT_x) \bigr]= E
+% \biggl[\mu T_x\int_0^{v\wedge
+% 1}Z_0(uT_x)
+% \exp \bigl(\lambda_1T_x(v-u) \bigr)\,du \biggr].
+% \]
+% %
+% If we assume that sensitive cells follow a deterministic decay
+% $Z_0(t)=xe^{\lambda_0 t}$ and approximate their extinction time as
+% $T_x\approx-\frac{1}{\lambda_0}\log x$, then we can heuristically
+% estimate the expected value as
+% %
+% \begin{eqnarray}\label{eqexpmuts}
+% E\bigl[Z_1(vT_x)\bigr] &=& \frac{\mu}{r}\log x
+% \int_0^{v\wedge1}x^{1-u}x^{({\lambda_1}/{r})(v-u)}\,du
+% \nonumber\\
+% &=& \frac{\mu}{r}x^{1-{\lambda_1}/{\lambda_0}v}\log x\int_0^{v\wedge
+% 1}x^{-u(1+{\lambda_1}/{r})}\,du
+% \nonumber\\
+% &=& \frac{\mu}{\lambda_1-\lambda_0}x^{1+{\lambda_1}/{r}v} \biggl(1-\exp \biggl[-(v\wedge1) \biggl(1+
+% \frac{\lambda_1}{r}\biggr)\log x \biggr] \biggr).
+% \end{eqnarray}
+% %
+% Thus we observe that this expected value is finite for all $v>0$ (also see \cite{koon,khar,zvai,xjon,marg}).
+%\nocite{oreg,schn,pond,smith,marg,hunn,advi,koha,mouse}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%                                          %%
+%% Backmatter begins here                   %%
+%%                                          %%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\begin{backmatter}
+
+\section*{Competing interests}
+  The authors declare that they have no competing interests.
+
+\section*{Author's contributions}
+    J.M.S.G jointly conceived the study with  R.G.H. and E.H.L., designed and
+    implemented the simulation model. All authors prepared the manuscript,
+    supervised its analysis and edited the manuscript.
+
+\section*{Acknowledgements}
+    We acknowledge the help of Francisco Allende for his work curating 
+databases of researchers.
+
+\section*{Funding}
   The authors gratefully acknowledge support by grants: CB-222220-R/2013 and
-CB-179431/2012 (Consejo Nacional de Ciencia y Tecnolog\'ia). We would also like
-to acknowledge CONACyT for letting us access their database. Finally, we
-acknowledge the help of Francisco Allende for his work curating 
-databases of researchers.
-
-%If you'd like to thank anyone, place your comments here
-%and remove the percent signs.
-
-% BibTeX users please use one of
-%\bibliographystyle{spbasic}      % basic style, author-year citations
-%\bibliographystyle{spmpsci}      % mathematics and physical sciences
-%\bibliographystyle{spphys}       % APS-like style for physics
-%\bibliography{}   % name your BibTeX data base
-
-% Non-BibTeX users please use
-
-\begin{thebibliography}{100}
-
-\bibitem{Vermeulen2013} Vermeulen, Nikki; Parker, John N \& Penders,
-  Bart, Understanding life together: A brief history of collaboration
-  in biology, \textit{Endeavour}, 37(3): 162-171 (2013)
-
-\bibitem{KnorrCetina1999} Knorr-Cetina, Karol; \textit{Epistemic
-  cultures: how the sciences make knowledge}, MIT Press, Cambridge, MA
-  (1999)
-
-\bibitem{Strasser2006} Strasser, B.J. Collecting and Experimenting:
-  The Moral Economies of Biological Research, 1960s-1980s.
-  \textit{Preprint no. 310.} Berlin: Max Planck Institute for the
-  History of Science, (2006)
-
-\bibitem{Muller2012} M\"{u}ller-Wille, S. \& Charmantier. I.  Natural
-  history and information overload: The case of Linnaeus.
-  \textit{Studies in History and Philosophy of Biological and
-    Biomedical Sciences.} 43:4-15, (2012)
-
-\bibitem{Strasser2012} Strasser, BJ. Data-driven sciences: From
-  wonder cabinets to electronic databases. \textit{Studies in History
-    and Philosophy of Biological and Biomedical Sciences} 43:85-87,
-  (2012)
-
-\bibitem{Sonnenwald2007} Sonnenwald, DH. Scientific Collaborations. \textit{Annual Review of Information Science and
-  Technology}, 41.
-
-\bibitem{Newman2001} Newman, MEJ. Clustering and preferential
-  attachment in growing networks. \textit{Physical Review E},
-  64:025102-1/025102-4, (2001)
-
-\bibitem{Newman2004} Newman, MEJ. Coauthorship networks and patterns
-  of scientific collaboration. \textit{PNAS}, 101, no. suppl 1,
-  5200-5205 (2004)
-
-\bibitem{Elango2012} Elango, B. \& Rajendran, J. Authorship Trends and
-  Collaboration Pattern in the Marine Sciences Literature: A
-  Scientometric Study. \textit{International Journal of Information
-    Dissemination and Technology}, 2(3), 166-169, (2012)
-
-\bibitem{HernandezLemus2013} Hern\'andez-Lemus, Enrique \&
-  Siqueiros-Garc\'ia JM, Information theoretical methods for complex
-  network structure reconstruction. \textit{Complex Adaptive Systems
-    Modeling}. 1: 8, doi:10.1186/2194-3206-1-8 (2013).
-
-\bibitem{Gilbert1997} Gilbert, N. A Simulation of the Structure of
-  Academic Science. \textit{Sociological Research Online}, 2(2) 3,
-  http://www.socresonline.org.uk/2/2/3.html
-
-\bibitem{Edmonds2011} Edmonds, B., Gilbert, N., Ahrweiler, P., \&
-  Scharnhorst, A. Simulating the Social Processes of Science.
-  \textit{Journal of Artificial Societies and Social Simulation},
-  14(4) 14,  http://www.jasss.soc.surrey.ac.uk/14/4/14.html
-
-\bibitem{Hara_etal_2002} Hara, N. Solomon, P. Kim SL. Sonnenwald DH. An Emerging View of Scientific Collaboration:
-  Scientists’ Perspectives on Collaboration and Factors that Impact Collaboration. \textit{Journal of the American
-    Society for Information Science and Technology}, 54(10):952–965, (2003)
-
-\bibitem{Lieberman_etal_2005} Lieberman, E. Hauert, C. \& Nowak,
-  MA. Evolutionary Dynamics on Graphs. Nature, 433, doi:0.1038/nature03204 (2005).
-
-\bibitem{Lo2004} Lo, T.S., Chan, H.Y., Hui, P.M., Johnson, N.F.,
-  Theory of networked minority games based on strategy pattern
-  dynamics, \textit{Physical Review E} 70, 056012 (2004)
-
-\bibitem{Buesser2012} Buesser, P. and Tomassini, M., Evolution of
-  cooperation on spatially embedded networks, \textit{Physical Review E} 86,
-  066107 (2012)
-
-\bibitem{Ichinose2013} Ichinose, G., Tenguishi, Y., and Tanizawa, T.,
-  Robustness of cooperation on scale-free networks under continuous
-  topological change, \textit{Physical Review E} 88, 052808 (2013)
-
-\bibitem{Ahmed2014} Ahmed, A., Karlapalem, K., Inequity aversion and
-  the evolution of cooperation, \textit{Physical Review E} 89, 022802, (2014)
-
-\bibitem{Vilone2014} Vilone, D., Ramasco, J.J., S\'anchez, A., San
-  Miguel, M., Social imitation versus strategic choice, or consensus
-  versus cooperation, in the networked Prisoner’s Dilemma,
-  \textit{Physical Review E} 90, 022810, (2014)
-
-\bibitem{Wardil2015} Wardil, L., Hauert, C., Cooperation and coauthorship in
-  scientific publishing, Physical Review E 91, 012825, (2015)
-
- \bibitem{hanauske2012} Hanauske, M., Evolutionary Game Theory and Complex Networks of Scientific Information, in A.
-Scharnhorst et al.
-(eds.), \textit{Models of Science Dynamics, Understanding Complex Systems Series}, Springer Berlin Heidelberg, (2012)
-
-\bibitem{Szabo2007} Szab\'o, Gy\"{o}rgy \& F\'ath, G\'abor,
-  Evolutionary games on graphs. \textit{Physics Reports}, 446: 97-216
-  (2007)
-
-\bibitem{Nowak1992} Nowak, Martin A. \& May, Robert M, Evolutionary
-  Games and Spatial Chaos. \textit{Nature}, 359: 826-829, (1992)
-
-\bibitem{Nowak2006} Oshtuki, Hisashi, Hauert, Christoph, Lieberman, Erez \& Nowak, Martin A, A simple rule for the evolution of cooperation on social graphs. \textit{Nature}, 441: 502-505 (2006)
-
-\bibitem{Axelrod2006} Axelrod, Robert, \textit{Evolution of cooperation: Revised edition}, Basic Books, Cambridge, MA (2006)
-
-\bibitem{Nowak2011} Nowak, Martin A. \& Highfield, Roger,
-  \textit{Supercooperators. Altruism, Evolution, and Why We Need Each
-    Other to Succeed}. Free Press, New York, NY  (2011)
-
-\bibitem{Santos2006} Santos, Francisco C., Pacheco, Jorge M., Lenaerts, Tom, Cooperation prevails when individuals adjust their social ties.
-\textit{PLoS Computational Biology}.
-2(10): 1284-1291 (2006)
-
-\bibitem{Santos2005} Santos, F.C. \& Pacheco, J.M., Scale-Free
-  Networks Provide a Unifying Framework for the Emergence of
-  Cooperation. \textit{PRL}, 95: 098104-1 to 098104-4, (2005)
-
-\bibitem{Hauert2004} Hauert, Christoph \& Doebeli, Michael, Spatial
-  structure often inhibits the evolution of cooperation in the
-  snowdrift game. \textit{Nature}, 428: 643-646,  (2004)
-
-\bibitem{Erdos1959} Erd\"{o}s, P. \& Reny\'i, A. On Random Graphs. \textit{Publ. Math}, 6:290 (1959).
-
-\bibitem{Watts1998} Watts, Duncan J. \& Strogatz, Steven H, Collective dynamics
-  of 'small-world' networks. \textit{Nature}, 393: 440-442 (1998)
-
-  \bibitem{Barrat2000} Barrat, A.; Weigt, M., On the properties of small-world network models, \textit{European Physical Journal B} 13 (3): 547–560, (2000)
-
-\bibitem{Barabasi1999} Barab\'asi, Albert-L\'aszl\'o. \& Albert, R\'eka, Emergence of Scaling in Random Networks. \textit{Science}, 286: 509-512 (1999)
-
-\bibitem{Shannon2003} Shannon P, Markiel A, Ozier O, Baliga NS, Wang JT, Ramage D, Amin N, Schwikowski B, Ideker T.
-Cytoscape: a software environment for integrated models of biomolecular interaction networks.
-\textit{Genome Research}, 13(11):2498-504, (2003)
-
-\bibitem{Wu-etal2008}Jun Wu, Yue-Jin Tan, Hong-Zhong Deng, Da-Zhi Zhu.
-A new measure of heterogeneity of complex networks based on degree sequence.
-Eds.
-Ali Minai, Dan Braha, Yaneer Bar-Yam  \emph{Unifying Themes in Complex Systems.
-Proceedings of the Sixth International Conference on Complex Systems}, Springer Berlin Heidelberg, 66-73, (2008)
-
-\bibitem{yousefi-etal2008} Yousefi-Nooraie R, Akbari-Kamrani M, Hanneman RA, Etemadi A.
-Association between co-authorship network and scientific productivity and impact indicators in academic medical research centers: A case study in Iran.
-\textit{Health Research Policy and Systems} 6:9 (2008) doi:10.1186/1478-4505-6-9.
-
-%%Discusion references
-
-\bibitem{Simon1955} Simon, HA. On a class of skew distribution functions. \textit{Biometrika}, 42 (3-4): 425-440, (1955)
-
-\bibitem{Price1965} Price, Derek JS. Networks of Scientific Papers. \textit{Science}, 149(3683): 510-515, (1965)
-
-\bibitem{Merton1968} Merton, Robert K, The Matthew Effect in Science, \textit{Science}, 159(3810): 56-63 (1968)
-
-\bibitem{Epstein1996} Epstein JM \& Axtell R. \textit{Growing artificial societies. Social science from the bottom up}. The
-  Brookings Institution Press and The MIT Press, Washington, DC. (1996)
-
-\bibitem{Lansing2002} Lansing JS. ``Artificial Societies'' and the Social
-  Sciences. \textit{Artificial Life}, 8:279-292, (2002)
-
-\bibitem{Haraetal2003} Hara N, Solomon P, Kim SL, Sonnenwald DH. An emerging
-  view of scientific collaboration: Scientists' perspectives on collaboration
-  and factors that impact collaboration. Journal of the American Society for
-  Information Science and Technology, 54(10):952–965, 2003
-
-\bibitem{Barabasi2011} Barab\'asi, AL. The network takeover. \textit{Nature}, 8:14–16, (2012)
-
-\bibitem{Conteetal2012} Conte R, Gilbert N, Bonelli G, Cioffi-Revilla C,
-  Deffuant G, Kertesz J, Loreto V, Moat S, Nadal J.-P,  Sanchez A, Nowak A,
-  Flache  A, San Miguel M, Helbing D. Manifesto of computational social
-  science. \textit{The European Physical Journal, Special Topics} 214(1):325–346, (2012)
-
-  %
-% and use \bibitem to create references. Consult the Instructions
-% for authors for reference list style.
-%
-%\bibitem{RefJ}
-% Format for Journal Reference
-%Author, Article title, Journal, Volume, page numbers (year)
-% Format for books
-%\bibitem{RefB}
-%Author, Book title, page numbers. Publisher, place (year)
-% etc
-\end{thebibliography}
-
+CB-179431/2012 (Consejo Nacional de Ciencia y Tecnolog\'ia), PAPIIT A301016 (UNAM). We would also like
+to acknowledge CONACyT for letting us access their database.
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%                  The Bibliography                       %%
+%%                                                         %%
+%%  Bmc_mathpys.bst  will be used to                       %%
+%%  create a .BBL file for submission.                     %%
+%%  After submission of the .TEX file,                     %%
+%%  you will be prompted to submit your .BBL file.         %%
+%%                                                         %%
+%%                                                         %%
+%%  Note that the displayed Bibliography will not          %%
+%%  necessarily be rendered by Latex exactly as specified  %%
+%%  in the online Instructions for Authors.                %%
+%%                                                         %%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+% if your bibliography is in bibtex format, use those commands:
+\bibliographystyle{vancouver} % Style BST file (bmc-mathphys, vancouver, spbasic).
+\bibliography{casm}% Bibliography file (usually '*.bib' )
+% for author-year bibliography (bmc-mathphys or spbasic)
+% a) write to bib file (bmc-mathphys only)
+% @settings{label, options="nameyear"}
+% b) uncomment next line
+%\nocite{label}
+
+% or include bibliography directly:
+% \begin{thebibliography}
+% \bibitem{b1}
+% \end{thebibliography}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%                               %%
+%% Figures                       %%
+%%                               %%
+%% NB: this is for captions and  %%
+%% Titles. All graphics must be  %%
+%% submitted separately and NOT  %%
+%% included in the Tex document  %%
+%%                               %%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%
+%% Do not use \listoffigures as most will included as separate files
+
+% \section*{Figures}
+%   \begin{figure}[h!]
+%   \caption{\csentence{Sample figure title.}
+%       A short description of the figure content
+%       should go here.}
+%       \end{figure}
+
+% \begin{figure}[h!]
+%   \caption{\csentence{Sample figure title.}
+%       Figure legend text.}
+%       \end{figure}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%                               %%
+%% Tables                        %%
+%%                               %%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%% Use of \listoftables is discouraged.
+%%
+% \section*{Tables}
+% \begin{table}[h!]
+% \caption{Sample table title. This is where the description of the table should go.}
+%       \begin{tabular}{cccc}
+%         \hline
+%            & B1  &B2   & B3\\ \hline
+%         A1 & 0.1 & 0.2 & 0.3\\
+%         A2 & ... & ..  & .\\
+%         A3 & ..  & .   & .\\ \hline
+%       \end{tabular}
+% \end{table}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%x
+%%                               %%
+%% Additional Files              %%
+%%                               %%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+% \section*{Additional Files}
+%   \subsection*{Additional file 1 --- Sample additional file title}
+%     Additional file descriptions text (including details of how to
+%     view the file, if it is in a non-standard format or the file extension).  This might
+%     refer to a multi-page table or a figure.
+
+%   \subsection*{Additional file 2 --- Sample additional file title}
+%     Additional file descriptions text.
+
+\end{backmatter}
 \end{document}
-% end of file template.tex

### 2017-03-22 casm.tex
spell-check

@@
 them. Particularly, we implemented two games played simultaneously:
-one for maximazing individual utility based on the iterated Prisoner's
-Dilemma; the other, a coordination game for maximazing the connection strength
+one for maximizing individual utility based on the iterated Prisoner's
+Dilemma; the other, a coordination game for maximizing the connection strength
 between players. We are interested in how they affect each other in 
 the context of a network of scientific collaboration under the idea that while
-researchers are interested in maximazing their utilities, they also know that
+researchers are interested in maximizing their utilities, they also know that
 it is important to invest in building collaborative relationships.
@@
   The value of the utility function for a player is the sum of the payoffs of playing
-  with its neighbors. The opossing force comes from the other concurrent game: players
+  with its neighbors. The opposing force comes from the other concurrent game: players
   trying to maximize the strength of their interactions with other players. In the coordinating game
@@
 The probability for an agent to cooperate or defect depends on a number ($\eta$)
-that referes to a historical balance between average utility and the average
-strength of the connections with its neigbors. This is so because we assume that
+that referees to a historical balance between average utility and the average
+strength of the connections with its neighbors. This is so because we assume that
 whatever the result in utility or strength of connection, as long as one of them
@@
   with every neighbor, but set its decision to cooperate or defect beforehand by
-  assesing the overall situation of its relationships. This may sound odd, since
+  assessing the overall situation of its relationships. This may sound odd, since
   one may think that a person decides for each relationship separately. However
@@
 % \includegraphics[scale=0.5]{images/Fosiss_GC_final.png}
-\caption{Bioemdical research collaboration network (FOSISS) giant component.}\label{Fosiss_GC}
+\caption{Biomedical research collaboration network (FOSISS) giant component.}\label{Fosiss_GC}
 \end{figure}
@@
 
-  We believe that the the situation just refered is also
+  We believe that the the situation just referred is also
   true for the whole biomedical research community in M\'exico. The
@@
 
-\section*{Acknowledgements}
+\section*{Acknowledgments}
     We acknowledge the help of Francisco Allende for his work curating 
-databases of researchers.
+databases of researchers. We acknowledge Be Luecke for her critical review.
 

### 2017-03-23 casm.tex
many spell and grammar errors, thanks Be

@@
 it is important to invest in building collaborative relationships.
-We tested our simulation on a biomedical research community network of M\'exico and
+We tested our simulation on a biomedical research community network in M\'exico and
 compared the results with an Erd\"{o}s-Reny\'i, a Watts-Strogatz
@@
 laboratories\cite{KnorrCetina:1999,Strasser:2006}, whereas in natural
-history there has been data and samples exchange since the $XVII^{th}$
+history there has been an exchange of data and samples since the $XVII^{th}$
 century\cite{MullerWille-etal:2012,Strasser:2012}. Despite the differences in
@@
   please refer to \cite{Sonnenwald:2007}.}. Our work aims to contribute
-to our current understanding on the matter, specially when agents have
+to our current understanding on the matter, especially when agents have
 to maximize their access to resources while taking care of their collaboration links.\\
@@
    it is important to invest in building collaborative relationships. These two
-   behaviors are explored in a biomedical research community of M\'exico.\\
+   behaviors are explored in a biomedical research community in M\'exico.\\
 
@@
   with its neighbors. The opposing force comes from the other concurrent game: players
-  trying to maximize the strength of their interactions with other players. In the coordinating game
+  trying to maximize the strength of their interactions with other players. In the coordination game
   the best strategy is to adopt the same strategy as the other player, as it pays the most,
@@
   both cooperate the interaction gets a positive payoff, when both defect, the
-  interaction doesn't get affected; but if they anti-coordinate, then the
-  interaction looses. Finally, cooperation is a central feature of scientific work.
+  interaction doesn't get affected; but if they do not coordinate, then the
+  interaction loses. Finally, cooperation is a central feature of scientific work.
   For our biomedical network, cooperation can be thought of
@@
 The manuscript is structured in four sections. First we describe
-\textit{FOSISS}, the main program for grants destined to biomedical applied
+\textit{FOSISS}, the main program for grants destined to applied biomedical 
 research in M\'exico. This is the source of the
@@
 describe our model
-and the different network topologies on which we explored it.
+and the different network topologies in which we explored it.
 We then present our results and discuss them. In the last section
@@
 
-CONACyT (National Council of Science and Technology) is the Mexican government
+CONACyT or National Council of Science and Technology (\emph{Consejo
+  Nacional de Ciencia y Tecnolog\'ia}) is the Mexican government
 entity in charge of promoting the development of science and
-technology.
-Among CONACyT's functions are to develop science and technology
-policies according to national needs and demands, to advise the different
-instances of government on scientific and technological topics, to promote the
-creation of research networks among the scientific community, to grant
-scholarships for masters and doctoral studies, and to manage different trusts 
-intended to fund individuals and groups for scientific and
+technology.  Among CONACyT's functions are to develop science and
+technology policies according to national needs and demands, to advise
+the different instances of government on scientific and technological
+topics, to promote the creation of research networks among the
+scientific community, to grant scholarships for masters and doctoral
+studies, and to manage different trusts intended to fund individuals
+and groups for scientific and
 technological research.\\
@@
 such funds. FOSISS is constituted by CONACyT, SSA, IMSS and ISSSTE,\footnote{SSA
-  is the acronym for Secretariat of Health \emph{Secretar\'ia de Salud}; IMSS is
+  is the acronym for Department of Health (\emph{Secretar\'ia de Salud}); IMSS is
   the acronym for Social Security Mexican Institute (\emph{Instituto Mexicano
@@
 From 2002 through 2013, there were 91 institutions funded that
-comprised 4988 researchers.\\
+comprised 4,988 researchers.\\
 
@@
 Besides the characteristics of the population there are some other boundary
-conditions that play an important role on the network topology and dynamics,
+conditions that play an important role on the network topology and dynamics
 that motivated the development of our model. Biomedical research in M\'exico
@@
 work. However, M\'exico does not have public biobanks for research purposes
-(which are specially relevant for research in genomics, for example), there is
+(which are especially relevant for research in genomics, for example), there is
 no regulation on the access to biological samples such as tissue, cells, DNA,
@@
 doctors but chemists, biologists, physicists, and mathematicians. There is
-another group of researchers that are placed on hospitals which is able to do
+another group of researchers placed on hospitals that are able to do
 research and have access to biological samples from their own patients. It seems
 that this group is the most privileged one, and the one with the least pressure to establish
-collaboration at whatever cost. Finally, there is one more group formed by those
+collaboration at any cost. Finally, there is one more group formed by those
 who work as clinicians at small hospitals with no research infrastructure
@@
 by selfish agents \cite{SzaboFath:2007,Nowak-etal:92,OshtukiNowak:2006,Santos-etal:2005,Santos-etal:2006}. In many network models
-on which some of game theory games are simulated, agents' decision to cooperate
+in which some game theory games are simulated, agents' decision to cooperate
 or defect depend on a specific strategy, such as the well known
@@
 
-In our model, agents are embedded in a network with varying number of
+In our model, agents are embedded in a network with a varying number of
 neighbors. Following the traditional PD game, the strategy chosen by an agent
-and the strategy chosen by its neighbors will produce a pay-off. Pay-off follows
+and the strategy chosen by its neighbors will produce a payoff. Payoff follows
 the traditional PD rule: $T > R > P > S$. $T$ is for temptation to defect. It is the highest
-pay-off and it takes place when the player defects and the other cooperates. $R$
-is for reward for when both players cooperate. $P$ is the punishment for when
-both players defect. And $S$ is for suckers pay-off, the worst outcome that
+payoff and it takes place when the player defects and the other cooperates. $R$
+is for reward for when both players cooperate. $P$ is for punishment for when
+both players defect. And $S$ is for suckers payoff, the worst outcome that
 takes place when the player cooperates but its neighbor defects. Utility is a
-property of agents in which pay-off is accumulated.\\
-
-{\bf PD utility pay-off matrix}\\
+property of agents in which payoff is accumulated.\\
+
+{\bf PD utility payoff matrix}\\
 
@@
 gets updated according to an $A_{ij}$ matrix of a coordination game. In the $w$ matrix, the highest value
-goes to an edge when both agents cooperate, getting an $R$ for reward, if one of
+goes to an edge when both agents cooperate, getting an $R$ for reward; if one of
 them defects, the connection gets weaker getting $P$ for the collaborative
@@
 $N$. In this game, the best action for any agent is to coordinate with its
-neighbor, either because it wins or because it doesn't loose. \\
-
-{\bf $w$ pay-off matrix}\\
+neighbor, either because it wins or because it doesn't lose. \\
+
+{\bf $w$ payoff matrix}\\
 
@@
 
-After each game, the agent adds-up utility ($u$), which is the sum of the
-pay-offs following the PD matrix. A pair of neighbors will add-up to the strength of
-their interaction ($w_{ji}$) as they coordinate or anti-coordinate, being $w$
+After each game, the agent adds up utility ($u$), which is the sum of the
+payoffs following the PD matrix. A pair of neighbors will add or substract from the strength of
+their interaction ($w_{ji}$) as they coordinate or not, being $w$
 also cumulative. We measure global utility and connection strength for the whole
@@
 strength of connections or $W$ is the sum of every pair of agents' links
-$w$. The strength of interaction can be thought as some sort of ``trust''.\\
+$w$. The strength of interaction can be thought of as some sort of ``trust''.\\
 
@@
 
-All networks are initialized equally. The number of nodes for every network is 4122, the same as in the FOSISS network.
-The same utility is given to every agent and all edges are assigned the same weight. In the case of the FOSISS
-network, edge weight is given by the number of collaborations among researchers, utility remains the same for all nodes as in
-the other networks.\\
-
-The probability for an agent to cooperate or defect depends on a number ($\eta$)
-that referees to a historical balance between average utility and the average
-strength of the connections with its neighbors. This is so because we assume that
-whatever the result in utility or strength of connection, as long as one of them
+All networks are initialized equally. The number of nodes for every
+network is 4,122, the same as in the FOSISS network.  The same utility
+is given to every agent and all edges are assigned the same weight. In
+the case of the FOSISS network, edge weight is given by the number of
+collaborations among researchers, utility remains the same for all
+nodes as in the other networks.\\
+
+The probability for an agent to cooperate or defect depends on a
+number ($\eta$) that refers to a historical balance between average
+utility and the average strength of the connections with its
+neighbors. It is modeled so because we assume that whatever the result
+in utility or strength of connection, as long as one of them
 increases, the player will be confident in the strategy followed so
-far. In every simulation step, each player will play both games
-  with every neighbor, but set its decision to cooperate or defect beforehand by
-  assessing the overall situation of its relationships. This may sound odd, since
-  one may think that a person decides for each relationship separately. However
-  in this way players are optimizing access to resources and the strength of
-  interactions to their neighbors at the same time, since their state is set by
+far. In every simulation step, each player will play both games with
+every neighbor, but set its decision to cooperate or defect beforehand
+by assessing the overall situation of its relationships. This may
+sound odd, since one may think that a person decides for each
+relationship separately. However in this way players are optimizing
+access to resources and the strength of interactions to their
+neighbors at the same time, since their state is set by
 considering both together.\\
@@
 For the agent to decide whether to cooperate or not, $\eta$ is
-  compared to a global threshold $\nu$. If the agents' $\eta$ $>$ $\nu$,
-  then the agent will cooperate, otherwise he will be suspicious and will
-  defect. $\nu$ is a global parameter that establishes a threshold that an
-  agents' $\eta$ must cross in order to decide to cooperate. In this way,
-  $\nu$ can limit the size of the population of cooperators. Due
-  to what the system and the game can offer to agents in terms of utilities and the strength
-  of collaboration relationships, $\nu$ represents the carrying capacity of the
+compared to a global threshold $\nu$. If the agent's $\eta$ $>$ $\nu$,
+then he will cooperate, otherwise he will be suspicious and
+will defect. $\nu$ is a global parameter that establishes a threshold
+that an agent's $\eta$ must cross in order to decide to cooperate. In
+this way, $\nu$ can limit the size of the population of
+cooperators. Due to what the system and the game can offer to agents
+in terms of utilities and the strength of collaboration relationships,
+$\nu$ represents the carrying capacity of the
 system for the population of cooperators.\\
@@
 
-We ran two different experiments. In the first we simulated different
+We ran two different experiments. In the first one we simulated different
 values of carrying capacity $\nu$. With this experiment we were able
@@
 
-Erd\"{o}s-Reny\'i networks \cite{ErdosRenyi:59} (random networks) are constructed by randomly selecting a pair of $N$ possible nodes and attaching them with an edge, given a probability $p$, as long as there is no edge between them.
-The result is a Poisson distribution for connectivity of nodes $P(k)$, where each node has a degree quite close to the average $\langle k \rangle$.
-Also for this type of network, average clustering coefficient  $\langle C \rangle$ is small, actually it is equal to $p$ (the probability of connecting two nodes) and the average shortest path length $\langle l \rangle = \frac{lnN}{ln\langle k \rangle}$.
+Erd\"{o}s-Reny\'i networks \cite{ErdosRenyi:59} (random networks) are
+constructed by randomly selecting a pair of $N$ possible nodes and
+attaching them with an edge, given a probability $p$, as long as there
+is no edge between them. The result is a Poisson distribution for
+connectivity of nodes $P(k)$, where each node has a degree quite close
+to the average $\langle k \rangle$. Also for this type of network,
+average clustering coefficient $\langle C \rangle$ is small, actually
+it is equal to $p$ (the probability of connecting two nodes) and the
+average shortest path length
+$\langle l \rangle = \frac{lnN}{ln\langle k \rangle}$.
 
@@
 
-Watts-Strogatz networks \cite{WattsStrogatz:98} (small-world networks) are in a regime between a fully regular grid (lattice) and a random network (Erd\"{o}s-R\'enyi).
-In order to build them, a node is chosen from a lattice (a ring) and the edge that connects it to nearest neighbor in a clockwise sense.
-With probability $p$, this edge is reconnected to a node chosen uniformly at random over the entire ring, with duplicate edges forbidden; otherwise the edge is left in place.
-This process is repeated by moving clockwise around the ring, considering each node in turn until one lap is completed.
-Next, the edges connect nodes to their second-nearest neighbors clockwise.
-As before, each of these edges is randomly rewired with probability $p$.
-This process continues, circulating around the ring and proceeding outward to more distant neighbors after each lap, until each edge in the original lattice has been considered once.
-The main characteristic of these networks is that the average shortest path length is small and grows as $log(N)$ ($\langle l \rangle \sim log(N)$).
-Also, the average clustering coefficient $\langle C \rangle$ remains large in terms of $p$.
-For $p < 0.1$, $\langle C \rangle \sim 1$.
+Watts-Strogatz networks \cite{WattsStrogatz:98} (small-world networks)
+are in a regime between a fully regular grid (lattice) and a random
+network (Erd\"{o}s-R\'enyi). In order to build them, a node is chosen
+from a lattice (a ring) and the edge that connects it to its nearest
+neighbor in a clockwise sense. With probability $p$, this edge is
+reconnected to a node chosen uniformly at random over the entire ring,
+with duplicate edges forbidden; otherwise the edge is left in
+place. This process is repeated by moving clockwise around the ring,
+considering each node in turn until one lap is completed. Next, the
+edges connect nodes to their second nearest neighbors clockwise. As
+before, each of these edges is randomly rewired with probability
+$p$. This process continues, circulating around the ring and
+proceeding outward to more distant neighbors after each lap, until
+each edge in the original lattice has been considered once. The main
+characteristic of these networks is that the average shortest path
+length is small and grows as $log(N)$
+($\langle l \rangle \sim log(N)$). Also, the average clustering
+coefficient $\langle C \rangle$ remains large in terms of $p$. For
+$p < 0.1$, $\langle C \rangle \sim 1$.
 
@@
 
-Barb\'asi-Albert networks \cite{BarabasiAlbert:99} (scale-free networks) are generated by adding new nodes to a network.
-Each new node is added connecting it to an existing node with a probability proportional to the degree $k$ (connectivity) of each node (\textit{preferential attachment}).
-The result is a a power law distribution for connectivity of nodes $P(k)$ where few nodes have many connections and the most have very few connections.
-Furthermore these networks are also small world networks, showing a quite small $\langle l \rangle$.
+Barb\'asi-Albert networks \cite{BarabasiAlbert:99} (scale-free
+networks) are generated by adding new nodes to a network. Each new
+node is added connecting it to an existing node with a probability
+proportional to the degree $k$ (connectivity) of each node
+(\textit{preferential attachment}). The result is a power law
+distribution for connectivity of nodes $P(k)$ where few nodes have
+many connections and the most have very few connections. Furthermore
+these networks are also small world networks, showing a quite small
+$\langle l \rangle$.
 
@@
 
-The biomedical research network on which we are running our model was generated 
-with data from collaborative projects.
-Our data was obtained from CONACyT and includes information for twelve years of \textit{FOSISS} grants.
-Data included names of Principal Investigators, collaborators, research topics, etc.
-The network we are using here has researchers as nodes and edges represent the connection of two scientists when they collaborate on the same project.
-Edges are also weighted according to the number of projects shared by any pair of scientists.\\
+The biomedical research network on which we are running our model was
+generated with data from collaborative projects. Our data was obtained
+from CONACyT and includes twelve years of information of
+\textit{FOSISS} grants. Data included names of principal
+Investigators, collaborators, research topics, etc. The network we are
+using here has researchers as nodes and edges represent the connection
+of two scientists when they collaborate on the same project. Edges are
+also weighted according to the number of projects shared by any pair
+of scientists.
 
@@
 
-In this section we present the main results of the study, namely the topological
-structure of the underlying network models, the dynamics of the games under
-different parameters and network topologies and the distribution of utility and
-of the strength of interaction resulting of playing the games in all the
-different scenarios considered, including the real FOSISS network.\\
-
-FOSISS network summed-up a total of 145 components or subnetworks, but we ran
-the model on the giant component made-up of 4122 researchers, and 23391 edges.
-The giant component was analyzed using \textit{Cytoscape} \textbf{Figure
-  1}. Results show that it is a well integrated network, with a clustering
-coefficient $\langle C \rangle = 0.870$, an average shortest path length of
-$\langle l \rangle = 5.493$  and a density of $p = 0.003$. Such properties
-recall a small-world topology \cite{WattsStrogatz:98}, and a great deal of
-self-organization when compared to a random network with the same density and
-number of nodes. Network centralization is $0.023$, since there are no visible
-researchers that play as hubs in the network. Nevertheless the network
-heterogeneity is $0.873$, which means that the network is highly
-hierarchical. When the degree distribution is analyzed, degree decreases as a
-power-law with an exponent of $1.7$, similar to other social networks described
-as scale-free topology networks \cite{BarabasiAlbert:99}. Finally, the average number
+In this section we present the main results of the study, namely the
+topological structure of the underlying network models, the dynamics
+of the games under different parameters and network topologies and the
+distribution of utility and of the strength of interaction resulting
+from playing the games in all the different scenarios considered,
+including the real FOSISS network.\\
+
+FOSISS network summed up a total of 145 components or subnetworks, but
+we ran the model on the giant component made up of 4,122 researchers,
+and 23,391 edges.  The giant component was analyzed using
+\textit{Cytoscape} and is shown in \textbf{Figure 1}. Results show
+that it is a well integrated network, with a clustering coefficient
+$\langle C \rangle = 0.870$, an average shortest path length of
+$\langle l \rangle = 5.493$ and a density of $p = 0.003$. Such
+properties recall a small-world topology \cite{WattsStrogatz:98}, and
+a great deal of self-organization when compared to a random network
+with the same density and number of nodes. Network centralization is
+$0.023$, since there are no visible researchers that play as hubs in
+the network. Nevertheless the network heterogeneity is $0.873$, which
+means that the network is highly hierarchical. When the degree
+distribution is analyzed, degree decreases as a power-law with an
+exponent of $1.7$, similar to other social networks described as
+scale-free topology networks \cite{BarabasiAlbert:99}. Finally, the
+average number
 of neighbors of each node is $11.39$ \cite{Shannon:2003}.\\
@@
 
-In the case of the Watts-Strogatz, small-world network, the whole
+In the case of the Watts-Strogatz small-world network, the whole
 population remains cooperating for ranges between $0$ and $0.2$ but as
@@
 represent only half of the population and such number of them will be
-constant up to $\nu \approx 0.25$ forming a short plateau. From $\nu
-\approx 0.25$ to $\nu \approx 0.6$ cooperators will be present at the
-beginning of the simulation but will diminish as time goes on.  In the
-case of the Barab\'asi-Albert network, crossing the threshold of $\nu
-\approx 0.2$, there is a sharp decrease in the number of cooperators,
-but stays constant over time. Such behavior is present for a very
-short range of $\nu$, and before $\nu \approx 0.24$, cooperators
-disappear for the rest of values of $\nu$. Finally, FOSISS network
-behaves similarly to the other networks in that there is a fall in the
-number of cooperators close to $\nu \approx 0.2$. In contrast with the
-other networks, the FOSISS network lacks the sharp reduction of
-cooperators, instead this population declines smoothly and
-progressively; specially, when it reaches a $\nu \approx 0.25$
+constant up to $\nu \approx 0.25$, forming a short plateau. From
+$\nu \approx 0.25$ to $\nu \approx 0.6$ cooperators will be present at
+the beginning of the simulation but will diminish as time goes on.  In
+the case of the Barab\'asi-Albert network, there is a sharp decrease
+in the number of cooperators when the threshold of $\nu \approx 0.2$
+is crossed, but stays constant over time. Such behavior is present for
+a very short range of $\nu$, and before $\nu \approx 0.24$,
+cooperators disappear for the rest of the values of $\nu$. Finally, FOSISS
+network behaves similarly to the other networks in that there is a
+fall in the number of cooperators close to $\nu \approx 0.2$. In
+contrast with the other networks, the FOSISS network lacks the sharp
+reduction of cooperators, instead this population declines smoothly
+and progressively; especially, when it reaches a $\nu \approx 0.25$,
 cooperators decrease in a less dramatic manner all the way to
-$\nu \approx 0.5$. It is also noteworthy that from $\nu = 0$ to $\nu
-\approx 0.5$ the number of cooperators converge to a certain degree
-and stays constant for the rest of the simulation.\\
+$\nu \approx 0.5$. It is also noteworthy that from $\nu = 0$ to
+$\nu \approx 0.5$ the number of cooperators converge to a certain
+degree and stays constant for the rest of the simulation.\\
 
@@
 
-Utility and strength of interactions dynamics under different $\nu$ are similar to the
-phase transition found before. \textbf{Figures 3 and 4} show
-that there is a drop in utility and strength of interactions according to the
-drop in the number of cooperators. Erd\"{o}s-Reny\'i and Barab\'asi-Albert
-networks are quite similar in the way these variables fall in two steps, the
-first one at $\nu \approx 0.2$ and the next one at $\nu \approx 0.23$. The fall
-is sharper still in the Barab\'asi-Albert topology. Utility and strength of
-interactions phase transition in Watts-Strogatz network is significantly more
-staggered compared to the former networks. In the case of utility, there is a
-region in the limits of $\nu \approx 0.25$ and $\nu \approx 0.3$, before utility
-goes to $0$, in which it remains low but stable over time. In general, strength
-of interactions follows the same pattern as utility but in the same $\nu \approx
-0.25$ and $\nu \approx 0.3$, strength of interactions grows to a value that is
-higher than the one given by default but soon starts to decrease as the
-simulation runs. For the FOSISS network, utility and interaction strength fall
-quite steeply but smoothly, without sharp cuts. Between $\nu \approx 0.23$ and
-$\nu \approx 0.28$, utility and strength of interactions start at their lowest,
+Utility and strength of interactions dynamics under different $\nu$ are
+similar to the phase transition found before. \textbf{Figures 3 and 4}
+show that there is a drop in utility and strength of interactions
+according to the drop in the number of cooperators. Erd\"{o}s-Reny\'i
+and Barab\'asi-Albert networks are quite similar in the way these
+variables fall in two steps, the first one at $\nu \approx 0.2$ and
+the next one at $\nu \approx 0.23$. The fall is even sharper in the
+Barab\'asi-Albert topology. Utility and strength of interactions phase
+transition in Watts-Strogatz network is significantly more staggered
+compared to the former networks. In the case of utility, there is a
+region in the limits of $\nu \approx 0.25$ and $\nu \approx 0.3$,
+before utility goes to $0$, in which it remains low but stable over
+time. In general, strength of interactions follows the same pattern as
+utility but in the same $\nu \approx 0.25$ and $\nu \approx 0.3$
+strength of interactions grows to a value that is higher than the one
+given by default but soon starts to decrease as the simulation
+runs. For the FOSISS network, utility and strength of interactions fall
+quite steeply but smoothly, without sharp cuts. Between
+$\nu \approx 0.23$ and $\nu \approx 0.28$, utility and strength of
+interactions start at their lowest,
 but there is a slight increase in both of them.\\
@@
 
-Central to our argument is the differences in utility and strength of
+Central to our argument are the differences in utility and strength of
 interactions distribution at the end of the simulation, for every topology. We
-found that utility distribution for the \textit{FOSISS} network, resembles quite
-accurately to the distribution of utility in the Barab\'asi-Albert
+found that utility distribution for the \textit{FOSISS} network resembles quite
+accurately the distribution of utility in the Barab\'asi-Albert
 network.\\
@@
 The distribution of utility on each topology is induced by the degree
-distribution. This is so, since a given agent (node) will interact with its
-neighbors to either cooperate or defect, in such a way that connectivity
+distribution. This is so since a given agent (node) will interact with its
+neighbors to either cooperate or defect in such a way that connectivity
 influences the number of events played and thus the likelihood of increasing its
-corresponding utility. For instance, utility distribution in the random,
+corresponding utility. For instance, utility distribution in the random
 Erd\"{o}s-R\'enyi network displays a normal-like curve. The algorithm that
@@
 distribution \cite{ErdosRenyi:59}. Since the Watts-Strogatz degree distribution is
-described by a function that is midways between a random distribution and a
+described by a function that is midway between a random distribution and a
 scale-free network \cite{Barratmodels:2000} one may expect also  an intermediate
@@
 
-The resemblance of the degree-distribution and utility distribution also holds
+The resemblance of the degree distribution and utility distribution also holds
 for the Bar\'abasi-Albert network. As mentioned in the methods section, the
 degree distribution of a Bar\'abasi-Albert topology follows a power-law that
-describes the fact that there are a small number of nodes with large $k$ and most
+describes the fact that there is a small number of nodes with large $k$ and most
 nodes have a small $k$ \cite{BarabasiAlbert:99}. As it is shown in the following
@@
   distribution. B. Watts-Strogatz network utility distribution is highly skewed
-  to the right. C. Barab\'asi-Albert network. Utility is distributed highly
+  to the right. C. Barab\'asi-Albert network utility is distributed highly
   skewed to the left. D. FOSISS, biomedical researchers collaboration network
-  distribution of utility resembles to Barab\'asi-Albert
+  distribution of utility resembles that of the Barab\'asi-Albert
   network.}\label{histo_fitness} 
@@
 network topology (Figure 7B), the strength of interactions distribution is a
-highly asymmetric bimodal, with a really-low frequency mode of low strength of
-interactions and a highly probability mode for high strength of interactions. A
+highly asymmetric bimodal, with a really low frequency mode of low strength of
+interactions and a high probability mode for high strength of interactions. A
 possible explanation for this phenomenon is that under network topologies
@@
 
-The Barab\'asi-Albert network (7C) presents also a symmetric unimodal
-distribution with values higher (on average) than those of the Erd\"{o}s-R\'enyi
-random network, this may be the effect of increased communication due to more
-efficient network navigability. Interestingly, the network corresponding to the
-real FOSISS collaborations (7D) is an asymmetric unimodal distribution in which
-moderate to high values of strength of interactions are more likely. We 
-hypothesize that this effect is also due to the communication properties of the
+The Barab\'asi-Albert network (7C) also presents a symmetric unimodal
+distribution with values higher (on average) than those of the
+Erd\"{o}s-R\'enyi random network, this may be the effect of increased
+communication due to more efficient network
+navigability. Interestingly, the network corresponding to the real
+FOSISS collaborations (7D) is an asymmetric unimodal distribution in
+which moderate to high values of strength of interactions are more
+likely. We hypothesize that this effect is also due to the
+communication properties of the
 network. \\
@@
 among players seems to be enhanced, that is, in such networks the rate
-of change of strategy is significantly lower (and smoother) than in
+of strategy change is significantly lower (and smoother) than in
 poorly connected networks. This is another instance in which easier
@@
   case in the FOSISS network, it means that those groups have a very
-  hierarchic structure as well.\\
+  hierarchical structure as well.\\
 
@@
   co-authorships in one of the research centers that is part of the
-  FOSISS network \cite{HernandezLemus:2013}. In the cited reference an
+  FOSISS network \cite{HernandezLemus:2013}. In the cited reference, an
   apparently well integrated community was found (high clustering
@@
   brakes down the network into small subgraphs that worked
-  independently. Remarkably those subgraphs corresponded to the real
+  independently. Remarkably, those subgraphs corresponded to the real
   groups of that research center.  What is more, several groups had a
@@
 
-  We believe that the the situation just referred is also
+  We believe that the situation just referred is also
   true for the whole biomedical research community in M\'exico. The
@@
   network, it appears to be the case that researchers can be the
-  leaders in one project and collaborators of different project of
+  leaders in one project and collaborators in a different project of
   \emph{its own research group}. CONACyT's funding policies makes it
@@
   consequence of this behavior is that group interactions get
-  reinforced, but intergroup connections not necessarily so.\\
+  reinforced, but inter-group connections not necessarily so.\\
 
@@
   inside the groups, which means that there would not be enough
-  information of the behavior of one group regarding its neighbors to
+  information on the behavior of one group regarding its neighbors to
   constrain them as it seems to happen with individual researchers
@@
 
-  Another issue that we would like to mention about FOSISS
-  network topology is that it is not a robust collaboration network.
-  At the level of groups, these might be well connected and
-  consolidated but at the level of the network, this could be no more
-  than an aggregate of individual groups. A robust network would be
-  resistant to changes in the connections between groups but in the
-  case of FOSISS, it seems that the network would brake down into
-  small research groups by cutting some edges, as it happened in our
-  co-authorship collaboration network \cite{HernandezLemus:2013}. The
-  lack of robustness might be indicative of the fact that resources
-  stay inside the groups, that is, they do not circulate through or
+  Another issue that we would like to mention about FOSISS network
+  topology is that it is not a robust collaboration network.  At the
+  level of groups, nodes might be well connected and consolidated but
+  at the level of the network, they could be no more than an aggregate
+  of individual groups. A robust network would be resistant to changes
+  in the connections between groups but in the case of FOSISS, it
+  seems that the network would brake down into small research groups
+  by cutting some edges, as it happened in our co-authorship
+  collaboration network \cite{HernandezLemus:2013}. The lack of
+  robustness might be indicative of the fact that resources stay
+  inside the groups, that is, they do not circulate through or
   articulate different communities. For example, one may think of
@@
   as low communication among groups, atomization of practices and
-  know-hows, redundancy in equipment tenancy, difficulties for
+  know-hows, redundancy in equipment tenancy, difficulties in
   implementing community-wide infrastructures such as biobanks,
@@
 
-On these grounds, part of our future work is based on
-  the results presented here. We would like to identify researchers
-  in our simulations and corroborate their situation in the model and
-  in the real world. We are also interested in going back to the field
-  and interviewing those groups with an interesting behavior found in
-  our simulations, probably we would follow a similar strategy as the
-  one developed in \cite{Hara:2003}. Finding communities beyond the
-  level of the groups is an important task. We think that there are
-  many possibilities that emerge from the integration of different
+  On these grounds, part of our future work is based on the results
+  presented here. We would like to identify researchers in our
+  simulations and corroborate their situation in the model and in the
+  real world. We are also interested in going back to the field and
+  interviewing those groups with an interesting behavior found in our
+  simulations, we would probably follow a similar strategy as the one
+  developed in \cite{Hara:2003}. Finding communities beyond the level
+  of the groups is an important task. We think that there are many
+  possibilities that emerge from the integration of different
   methodologies. Moreover, studying social processes in science is
@@
 
-No doubt, social sciences are becoming more ``computational''. This can
+No doubt social sciences are becoming more ``computational''. This can
 be seen everywhere, but curiously enough, disciplines like physics

### 2017-03-27 casm.tex
Strength of interaction everywhere

@@
 of players having access to certain amount of resources from other players in the
-network and the distribution of the strength of connections among
+network and the distribution of the strength of interactions among
 them. Particularly, we implemented two games played simultaneously:
@@
 their interaction ($w_{ji}$) as they coordinate or not, being $w$
-also cumulative. We measure global utility and connection strength for the whole
+also cumulative. We measure global utility and strength of interaction for the whole
 network. Global utility $U$ is the sum of all individual utilities and global
-strength of connections or $W$ is the sum of every pair of agents' links
+strength of interaction or $W$ is the sum of every pair of agents' links
 $w$. The strength of interaction can be thought of as some sort of ``trust''.\\
@@
 neighbors. It is modeled so because we assume that whatever the result
-in utility or strength of connection, as long as one of them
+in utility or strength of interaction, as long as one of them
 increases, the player will be confident in the strategy followed so
@@
 values of carrying capacity $\nu$. With this experiment we were able
-to see how the number of cooperators, utility, strength of connections
+to see how the number of cooperators, utility, strength of interactions
 among agents and the ratio of shifting state population would change

### 2017-03-27 casm.tex
Comentario 1 revisor 3, integrado.

@@
   with its neighbors. The opposing force comes from the other concurrent game: players
-  trying to maximize the strength of their interactions with other players. In the coordination game
+  trying to maximize the strength of their interactions with other players.
+
+%%Strength of connection may have different meaning.
+From an empirical point of view, it simply means the number of times two researchers have collaborated together in a comon research project.
+From a sociological and qualitative point of view, if these two scientists have been willing to collaborate more than once, it may signify some form of trust among them.
+But this may not be the only interpreation since it can depend on each case.
+For instance students are expected to collaborate with their advisors, still there can be cases in which students are subdued to collaborate with them.
+In such a case, instead of trust there would be an asymmetry of power.
+This situation may not be limited to advisor-students relationships; we are aware of cases between a politically powerful scientist “recruting” other scientists that are somehow obligated to collaborate with them.
+The risk of refusing to collaborate in this situation can represent a politically bad move.
+
+%%Since the strength of connection can be sociologically interpreted in so many ways, we decided to just quantify the  times two researchers collaborate, and by doing this avoiding any generalized interpretation of the quality of the interactions among researchers.
+Still we are aware that naming strength of connection to the number of times scientists collaborate, can be quite abstract and it needs to be expressed in more concrete ways.
+In the coordination game
   the best strategy is to adopt the same strategy as the other player, as it pays the most,
@@
 strength of interaction or $W$ is the sum of every pair of agents' links
-$w$. The strength of interaction can be thought of as some sort of ``trust''.\\
+$w$.
+Strength of interaction may have different meanings.
+From an empirical point of view, it simply means the number of times two researchers have collaborated together in a comon research project.
+From a sociological and qualitative point of view, if these two scientists have been willing to collaborate more than once, it may signify some form of "trust" among them.
+But this may not be the only possible interpreation since it can be different for each case.
+Since the strength of interactions can be sociologically interpreted in so many ways, we decided to just quantify the  times two researchers collaborate, and by doing this avoiding any generalized interpretation of the quality of the interactions among researchers.
+\\
 

### 2017-03-27 casm.tex
Respuesta a revisor 3, pregunta 3

@@
 
-\subsection*{Network initialization and agent state update}
+\subsection*{Model update}
 
@@
 increases, the player will be confident in the strategy followed so
-far. In every simulation step, each player will play both games with
-every neighbor, but set its decision to cooperate or defect beforehand
+far. In every simulation step, each agent will independently play both games with
+every neighbor. Nonetheless, the agent sets its decision to cooperate or defect beforehand
 by assessing the overall situation of its relationships. This may
@@
 neighbors at the same time, since their state is set by
-considering both together.\\
+considering both together.
+The strength of interaction is updated independently for each pair of agents.
+In a single play some interactions might be weakened, some may get strengthened and others may remain unaffected.
+Moreover, in this model, history is kept in the network as strength of interactions and it conditions the agent\'s disposition to cooperate or to defect.
+As the sayings go: Burnt children dread fire; A bad dog is not born but made.\\
 

### 2017-03-28 casm.tex
Revisor 3, pregunta 6 respondida

@@
   The value of the utility function for a player is the sum of the payoffs of playing
-  with its neighbors. The opposing force comes from the other concurrent game: players
-  trying to maximize the strength of their interactions with other players.
-
-%%Strength of connection may have different meaning.
-From an empirical point of view, it simply means the number of times two researchers have collaborated together in a comon research project.
-From a sociological and qualitative point of view, if these two scientists have been willing to collaborate more than once, it may signify some form of trust among them.
-But this may not be the only interpreation since it can depend on each case.
-For instance students are expected to collaborate with their advisors, still there can be cases in which students are subdued to collaborate with them.
-In such a case, instead of trust there would be an asymmetry of power.
-This situation may not be limited to advisor-students relationships; we are aware of cases between a politically powerful scientist “recruting” other scientists that are somehow obligated to collaborate with them.
-The risk of refusing to collaborate in this situation can represent a politically bad move.
-
-%%Since the strength of connection can be sociologically interpreted in so many ways, we decided to just quantify the  times two researchers collaborate, and by doing this avoiding any generalized interpretation of the quality of the interactions among researchers.
-Still we are aware that naming strength of connection to the number of times scientists collaborate, can be quite abstract and it needs to be expressed in more concrete ways.
-In the coordination game
-  the best strategy is to adopt the same strategy as the other player, as it pays the most,
+  prisoner\'s dilemma with its neighbors. The the other concurrent game consists of players
+  trying to maximize the strength of their interactions with other players. In the coordination game the best strategy is to adopt the same strategy as the other player, as it pays the most,
   regardless of cooperation or defection in the utility game. When
@@
   interaction doesn't get affected; but if they do not coordinate, then the
-  interaction loses. Finally, cooperation is a central feature of scientific work.
-  For our biomedical network, cooperation can be thought of
-  as sharing resources such as time, students, equipment, even money. Examples of defection
-  to a cooperator are ghost authorship or
-  prestige authorship.\\
+  interaction loses. The payoffs resulting from the coordination games are not part of the utility function, however, both are considered by the agent to decide whether to cooperate or defect. \\
 

### 2017-03-28 casm.tex
literature review en introducción

@@
 
- In this article we explore the network effect on the distribution
+ We explore the network effect on the distribution
    of players having access to certain amount of resources shared by other players in the
    network and the distribution of the strength of interactions among
-   them. Particularly, we implemented two games played simultaneously: 
+   them. Implementing games on networks is an active area of
+research aimed to understand the evolution of cooperation in networks populated
+by selfish agents \cite{SzaboFath:2007,Nowak-etal:92,OshtukiNowak:2006,Santos-etal:2005,Santos-etal:2006}.
+In many network models in which some game theory games are simulated, agents' decision to cooperate
+or defect depend on a specific strategy, such as the well known
+\textit{tit-for-tat} \cite{Axelrod:2006,Nowak-etal:2011}. In some other cases, agents
+can modify the weight of the interactions with their neighbors
+\cite{Santos-etal:2006}. From a different perspective others have explored the effect
+of different topologies on the emergence of cooperation
+\cite{Santos-etal:2005,HauertDoebeli:2004}.
+
+   Particularly, we implemented two games played simultaneously: 
    one for maximizing individual utility based on the iterated Prisoner's
@@
 coordination game instantiated on
-networks. Implementing games on networks is not new and it's an active area of
-research aimed to understand the evolution of cooperation in networks populated
-by selfish agents \cite{SzaboFath:2007,Nowak-etal:92,OshtukiNowak:2006,Santos-etal:2005,Santos-etal:2006}. In many network models
-in which some game theory games are simulated, agents' decision to cooperate
-or defect depend on a specific strategy, such as the well known
-\textit{tit-for-tat} \cite{Axelrod:2006,Nowak-etal:2011}. In some other cases, agents
-can modify the weight of the interactions with their neighbors
-\cite{Santos-etal:2006}. From a different perspective others have explored the effect
-of different topologies on the emergence of cooperation
-\cite{Santos-etal:2005,HauertDoebeli:2004}. In our model, an agent's decision to
+networks. In our model, an agent's decision to
 cooperate or defect depends on a balance between

### 2017-03-29 casm.tex
Introduction updated, and new references to bib file

@@
 is not surprising since cooperation and competition are quite important in
-today's academic success. How does collaboration happen within a competitive
-academic environment and what kind of payoff is present in these settings were
-questions considered recently by Wardil and Hauert \cite{Wardil-etal:2015} in the
-context of cooperation in multi-authored publications. Also, the role of game
-theory over complex scientific information and collaboration networks has
-attracted attention, mainly focusing on how long-term strategies may shape
-different scenarios for Nash equilibria \cite{Hanauske-etal:2012}. Prisoner's Dilemma
-has been used in the study of impact factor and collaboration
-\cite{Hara-etal:2003,LiebermanNowak:2005}. \\
-
-Even with all these research efforts, cooperation in the context of
-scientific collaboration is still loosely defined and the long term
-dynamics of academic cooperation (and its consequences) are yet to be
-fully elucidated. Furthermore, to our current knowledge, there has
-been no use of game theory and complex network analysis for
-understanding how the topology of scientific collaboration networks
-affects access to resources among individuals present in the network
-\footnote{For an account of scientific collaboration and definitions,
-  please refer to \cite{Sonnenwald:2007}.}. Our work aims to contribute
-to our current understanding on the matter, especially when agents have
-to maximize their access to resources while taking care of their collaboration links.\\
-
- We explore the network effect on the distribution
-   of players having access to certain amount of resources shared by other players in the
-   network and the distribution of the strength of interactions among
-   them. Implementing games on networks is an active area of
-research aimed to understand the evolution of cooperation in networks populated
-by selfish agents \cite{SzaboFath:2007,Nowak-etal:92,OshtukiNowak:2006,Santos-etal:2005,Santos-etal:2006}.
-In many network models in which some game theory games are simulated, agents' decision to cooperate
-or defect depend on a specific strategy, such as the well known
-\textit{tit-for-tat} \cite{Axelrod:2006,Nowak-etal:2011}. In some other cases, agents
-can modify the weight of the interactions with their neighbors
-\cite{Santos-etal:2006}. From a different perspective others have explored the effect
-of different topologies on the emergence of cooperation
-\cite{Santos-etal:2005,HauertDoebeli:2004}.
-
-   Particularly, we implemented two games played simultaneously: 
-   one for maximizing individual utility based on the iterated Prisoner's
-   Dilemma; the other, a coordination game for maximizing the connection strength between
-   players. We are interested in how they affect each other in 
-   the context of a network of scientific collaboration under the idea that while
-   researchers are interested in maximizing their utilities, they also know that
-   it is important to invest in building collaborative relationships. These two
-   behaviors are explored in a biomedical research community in M\'exico.\\
-
-In the context of our model, utility represents
-  access to resources shared by others.
-  The value of the utility function for a player is the sum of the payoffs of playing
-  prisoner\'s dilemma with its neighbors. The the other concurrent game consists of players
-  trying to maximize the strength of their interactions with other players. In the coordination game the best strategy is to adopt the same strategy as the other player, as it pays the most,
-  regardless of cooperation or defection in the utility game. When
-  both cooperate the interaction gets a positive payoff, when both defect, the
+today's academic success. Moreover, the quantitative analysis of cooperation in
+science also has a long history of more than 50 years
+\cite{Mali-etal:2012,Scharnhorst-etal:2012}. Particularly appealing to researchers studying
+this topic has been the use of network analysis, especially in the area of
+bibliometrics and scientometrics. The approach we follow here articulates game theory
+together with complex network analysis. Putting together game-theoretic modeling
+on complex networks is common in studies about the emergence of cooperation
+\cite{SzaboFath:2007,Nowak-etal:92,OshtukiNowak:2006,Santos-etal:2005,Santos-etal:2006}.
+However, in the context of science studies, it is far from being a unified, active
+field of research. There is no common set of questions and problems or a
+coherent body of models and theory aimed to understand the quirks and twists of
+cooperation in scientific communities. It is more likely to say that there is a
+desarticulated collection of works, implementing game theory and
+complex networks to different situations related to the social life of science.\\
+
+Nevertheless, there is work done. For instance Wardil and Hauert have analyzed
+how does collaboration happen within co-authorship networks
+\cite{Wardil-etal:2015}. Using the \emph{Physical Review} journal historic database,
+these authors show the payoff differences between being the first author and the
+last author, where the first author is a cooperator that takes the highest load
+of work, while the last author is the \emph{laird} that can benefit from the
+work of the former and get engaged in many other projects. They argue that
+cooperation in a multi-authored paper resambles more to a snow-drift game than a
+prisoner's dilemma situation, since when co-authoring a paper, every body wins
+but each author pays a different price. Though this work takes into account the
+topology of the network as informative regarding cooperation patterns, the role
+of topology framing or
+fostering cooperation is not part of the study. \\
+
+Game theory over complex scientific information and collaboration networks has
+also attracted attention, for instance Hanauske has focused on how long-term
+strategies may shape different scenarios for Nash equilibria in the interaction
+between scientists and journals \cite{Hanauske-etal:2012}. And Hara and
+collaborators have used Prisoner's Dilemma in the study of impact factor and
+collaboration \cite{Hara-etal:2003,LiebermanNowak:2005}. \\
+
+% In general and beyond the area of scientific collaboration,
+% implementing games on networks is an active area of research aimed to understand
+% the evolution of cooperation in networks populated by selfish agents
+% \cite{SzaboFath:2007,Nowak-etal:92,OshtukiNowak:2006,Santos-etal:2005,Santos-etal:2006},
+% for example, by exploring different games such as the prisoner's dilemma,
+% snow-drift, etc., \cite{Axelrod:2006,Nowak-etal:2011}, or implementing models in
+% which agents can modify the weight of the interactions with their neighbors
+% \cite{Santos-etal:2006}. \\
+
+Even with all these research efforts, cooperation in the context of scientific
+collaboration is still loosely defined and the long term dynamics of academic
+cooperation (and its consequences) are yet to be fully elucidated. Furthermore,
+to our current knowledge, there has been no use of game theory and complex
+network analysis for understanding how the topology of scientific collaboration
+networks affects access to resources among individuals present in the network
+\footnote{For an account of scientific collaboration and definitions, please
+  refer to \cite{Sonnenwald:2007}.}. From a different perspective others have
+explored the effect of different topologies on the emergence of cooperation
+\cite{Santos-etal:2005,HauertDoebeli:2004}. Our work aims to contribute to our
+current understanding on the matter, especially when agents have to maximize
+their access to resources while taking care of their collaboration links. We
+explore the network effect on the distribution of players having access to
+certain amount of resources shared by other players in the network and the
+distribution of the strength of interactions among them. Particularly, we
+implemented two games played simultaneously: one for maximizing individual
+utility based on the iterated Prisoner's Dilemma; the other, a coordination game
+for maximizing the connection strength between players. We are interested in how
+they affect each other in the context of a network of scientific collaboration
+under the idea that while researchers are interested in maximizing their
+utilities, they also know that it is important to invest in building
+collaborative relationships. These two behaviors are explored in a biomedical
+research community in M\'exico.\\
+
+   In the context of our model, utility represents access to resources shared by
+   others.  The value of the utility function for a player is the sum of the
+   payoffs of playing prisoner's dilemma with its neighbors. The other
+   concurrent game consists of players trying to maximize the strength of their
+   interactions with other players. In the coordination game the best strategy
+   is to adopt the same strategy as the other player, as it pays the most,
+   regardless of cooperation or defection in the utility game. When both
+   cooperate the interaction gets a positive payoff, when both defect, the
    interaction doesn't get affected; but if they do not coordinate, then the
-  interaction loses. The payoffs resulting from the coordination games are not part of the utility function, however, both are considered by the agent to decide whether to cooperate or defect. \\
+   interaction loses. The payoffs resulting from the coordination games are not
+   part of the utility function, however, both are considered by the agent to
+   decide whether to cooperate or defect. \\
 
@@
 \section*{Acknowledgments}
-    We acknowledge the help of Francisco Allende for his work curating 
+    We acknowledge the help of Ma. del Pilar Galarza and Francisco Allende for their work curating 
 databases of researchers. We acknowledge Be Luecke for her critical review.

### 2017-03-29 casm.tex
Introduction updated, and new references to bib file. Included work of Li and Cao that has similar conlcusions to our work.

@@
 science also has a long history of more than 50 years
-\cite{Mali-etal:2012,Scharnhorst-etal:2012}. Particularly appealing to researchers studying
-this topic has been the use of network analysis, especially in the area of
-bibliometrics and scientometrics. The approach we follow here articulates game theory
+\cite{Mali-etal:2012,Scharnhorst-etal:2012}. Particularly appealing to
+researchers studying this topic is the use of network analysis, especially in
+the area of bibliometrics and scientometrics such as in citation networks that
+date as back as 1972 \cite{Garfield:1972}, co-authorship and collaboration networks also have a
+long tradition \cite{Todorov-etal:1991,Wagner-etal:2017}.\\
+
+The approach we follow here articulates game theory
 together with complex network analysis. Putting together game-theoretic modeling
@@
 \cite{SzaboFath:2007,Nowak-etal:92,OshtukiNowak:2006,Santos-etal:2005,Santos-etal:2006}.
-However, in the context of science studies, it is far from being a unified, active
-field of research. There is no common set of questions and problems or a
+However, in the context of science studies, it is far from being a unified,
+active field of research. There is no common set of questions and problems or a
 coherent body of models and theory aimed to understand the quirks and twists of
-cooperation in scientific communities. It is more likely to say that there is a
-desarticulated collection of works, implementing game theory and
-complex networks to different situations related to the social life of science.\\
+cooperation in scientific communities. It is more likely to say that work of
+this kind are scarce and their implementatoin is on different situations related
+to the social life of science, where sometimes models are run on science
+collaboration networks because access to these kind of data is relatively easy
+to access.\\
 
@@
 topology of the network as informative regarding cooperation patterns, the role
-of topology framing or
-fostering cooperation is not part of the study. \\
+of topology framing or fostering cooperation is not part of the study. \\
 
 Game theory over complex scientific information and collaboration networks has
-also attracted attention, for instance Hanauske has focused on how long-term
-strategies may shape different scenarios for Nash equilibria in the interaction
-between scientists and journals \cite{Hanauske-etal:2012}. And Hara and
-collaborators have used Prisoner's Dilemma in the study of impact factor and
-collaboration \cite{Hara-etal:2003,LiebermanNowak:2005}. \\
+also attracted attention. Hanauske has applied \emph{Evolutionary Game Theory}
+to have a better understanding of the market of scientific information, that
+involves scientists as producers but also journal, that are in charge of its
+dissemination. One of his models connects scientist interest in maximazing their
+reputation and their decissions to publish in an Open Access Journal or in a
+journal that works under the traditional publication framework. He has also
+modeled a game-theretic interactions between scientists and journals for both
+players to go open access or not. Only this second model incorporates networks
+analysis \cite{Hanauske-etal:2012}.\\
+
+Another interesting behavior explored by game-theoretical modeling and complex
+networks has been done by Li and Cao \cite{Li-etal:2009}. This authors analyze the role of
+punishment in a science collaboration network. More precisely, they implemented
+an ultimatum bargaining model to understand the impact of the topology of a
+social network and the emergence of a population of punishers. In the ultimatum
+game, there are two players, one of them (the proponent) suggest to split a sum
+in two and its connected neighbor (the respondent), can decide to accept or
+reject the offer as it may be perceived more or less fair. If the respondent
+accepts, the sum is devided and the shares are divided according to the
+offer. If the offer is rejected the players do not get anything. According to
+the authors, the act of rejecting a selfish offer can be interpreted as a
+punishment since the player that rejects it is paying a cost of not receiving
+anything but the proponent looses even more, since his offer was selfish. Their
+results show that the population of punishers will emerge as a phase transition
+as the degree of selfishness increses among players. More over, they found a
+dependence relation between the tolerance to selfish behaviors and the
+topologies of networks.\\
+
+%%\cite{Hara-etal:2003,LiebermanNowak:2005}. \\
 
@@
 
-Even with all these research efforts, cooperation in the context of scientific
-collaboration is still loosely defined and the long term dynamics of academic
-cooperation (and its consequences) are yet to be fully elucidated. Furthermore,
-to our current knowledge, there has been no use of game theory and complex
-network analysis for understanding how the topology of scientific collaboration
-networks affects access to resources among individuals present in the network
-\footnote{For an account of scientific collaboration and definitions, please
-  refer to \cite{Sonnenwald:2007}.}. From a different perspective others have
-explored the effect of different topologies on the emergence of cooperation
-\cite{Santos-etal:2005,HauertDoebeli:2004}. Our work aims to contribute to our
-current understanding on the matter, especially when agents have to maximize
-their access to resources while taking care of their collaboration links. We
-explore the network effect on the distribution of players having access to
-certain amount of resources shared by other players in the network and the
-distribution of the strength of interactions among them. Particularly, we
-implemented two games played simultaneously: one for maximizing individual
-utility based on the iterated Prisoner's Dilemma; the other, a coordination game
-for maximizing the connection strength between players. We are interested in how
-they affect each other in the context of a network of scientific collaboration
-under the idea that while researchers are interested in maximizing their
-utilities, they also know that it is important to invest in building
-collaborative relationships. These two behaviors are explored in a biomedical
+% Even with all these research efforts, cooperation in the context of scientific
+% collaboration is still loosely defined and the long term dynamics of academic
+% cooperation (and its consequences) are yet to be fully elucidated. Furthermore,
+% to our current knowledge, there has been no use of game theory and complex
+% network analysis for understanding how the topology of scientific collaboration
+% networks affects access to resources among individuals present in the network
+% \footnote{For an account of scientific collaboration and definitions, please
+%   refer to \cite{Sonnenwald:2007}.}. From a different perspective others have
+% explored the effect of different topologies on the emergence of cooperation
+% \cite{Santos-etal:2005,HauertDoebeli:2004}.
+
+In a similar vein to the work of Li and Cao, we explore the network effect on
+the distribution of players having access to certain amount of resources shared
+by other players in the network and the distribution of the strength of
+interactions among them. Particularly, we implemented two games played
+simultaneously: one for maximizing individual utility based on the iterated
+Prisoner's Dilemma; the other, a coordination game for maximizing the connection
+strength between players. We are interested in how they affect each other in the
+context of a network of scientific collaboration under the idea that while
+researchers are interested in maximizing their utilities, they also know that it
+is important to invest in building collaborative relationships. These two
+behaviors are explored in a biomedical
 research community in M\'exico.\\

### 2017-03-30 casm.tex
some typos, better wording on the concurrent games

@@
 collaborative projects, biology is only recently becoming an evermore
-collaborative discipline.
-In this article we explore the effect of a collaboration network on the distribution
-of players having access to certain amount of resources from other players in the
-network and the distribution of the strength of interactions among
-them. Particularly, we implemented two games played simultaneously:
-one for maximizing individual utility based on the iterated Prisoner's
-Dilemma; the other, a coordination game for maximizing the connection strength
+collaborative discipline.  In this article we explore the effect of a
+collaboration network on the distribution of players having access to
+certain amount of resources from other players in the network and the
+distribution of the strength of interactions among them. Particularly,
+we implemented two games played simultaneously: one for maximizing
+individual utility based on the iterated Prisoner's Dilemma; the
+other, a coordination game for maximizing the connection strength
 between players. We are interested in how they affect each other in
-the context of a network of scientific collaboration under the idea that while
-researchers are interested in maximizing their utilities, they also know that
-it is important to invest in building collaborative relationships.
-We tested our simulation on a biomedical research community network in M\'exico and
-compared the results with an Erd\"{o}s-Reny\'i, a Watts-Strogatz
-small-world and Barab\'asi-Albert topologies. Different topologies
-display different global utility and global strength of interaction
-distributions. Moreover, the distribution of utility and strength of interaction
-in the researchers network is similar to that of 
+the context of a network of scientific collaboration under the idea
+that while researchers are interested in maximizing their utilities,
+they also know that it is important to invest in building
+collaborative relationships.  We tested our simulation on a biomedical
+research community network in M\'exico and compared the results with
+an Erd\"{o}s-Reny\'i, a Watts-Strogatz small-world and
+Barab\'asi-Albert topologies. Different topologies display different
+global utility and global strength of interaction
+distributions. Moreover, the distribution of utility and strength of
+interaction in the researchers network is similar to that of
 Barab\'asi-Albert and Watts-Strogatz topologies, respectively. We
-believe that utility distribution in the researchers network
-suggests that there are socio-cultural mechanisms governing the
-network that produce an asymmetric distribution of resources. The
-high distribution of strong connections might reflect some sort of
-subordination among researchers by which they are morally obliged to
-cooperate by the same socio-cultural mechanisms. Finally, the range around
-the threshold that regulates the decision to cooperate or defect
-according to the agent's historical balance between utility and
-strength of collaborative relationships and carrying capacity of the
-system is small, suggesting that there is a region in which a phase
-transition takes place from a population of cooperators to a
-population of defectors. Simulations like ours may help to develop
-science policies to promote fair distribution of resources.
+believe that utility distribution in the researchers network suggests
+that there are socio-cultural mechanisms governing the network that
+produce an asymmetric distribution of resources. The high distribution
+of strong connections might reflect some sort of subordination among
+researchers by which they are morally obliged to cooperate by the same
+socio-cultural mechanisms. Finally, the range around the threshold
+that regulates the decision to cooperate or defect according to the
+agent's historical balance between utility and strength of
+collaborative relationships and carrying capacity of the system is
+small, suggesting that there is a region in which a phase transition
+takes place from a population of cooperators to a population of
+defectors. Simulations like ours may help to develop science policies
+to promote fair distribution of resources.
 
@@
 funds, and time is critical; building trust among scientists is
-fundamental. Also, resources are mobilized in order to create strategic alliances.\\
-
-The analysis of cooperation in scientific research has been the subject of a
-number of studies
+fundamental. Also, resources are mobilized in order to create
+strategic alliances.\\
+
+The analysis of cooperation in scientific research has been the
+subject of a number of studies
 \cite{VermeulenPenders:2013,Newman:2001,Newman:2004,Elango-etal:2012,HernandezLemus:2013,Strasser:2006,Strasser:2012}. This
-is not surprising since cooperation and competition are quite important in
-today's academic success. Moreover, the quantitative analysis of cooperation in
-science also has a long history of more than 50 years
+is not surprising since cooperation and competition are quite
+important in today's academic success. Moreover, the quantitative
+analysis of cooperation in science also has a long history of more
+than 50 years
 \cite{Mali-etal:2012,Scharnhorst-etal:2012}. Particularly appealing to
-researchers studying this topic is the use of network analysis, especially in
-the area of bibliometrics and scientometrics such as in citation networks that
-date as back as 1972 \cite{Garfield:1972}, co-authorship and collaboration networks also have a
-long tradition \cite{Todorov-etal:1991,Wagner-etal:2017}.\\
-
-The approach we follow here articulates game theory
-together with complex network analysis. Putting together game-theoretic modeling
-on complex networks is common in studies about the emergence of cooperation
+researchers studying this topic is the use of network analysis,
+especially in the area of bibliometrics and scientometrics such as in
+citation networks that date as back as 1972 \cite{Garfield:1972},
+co-authorship and collaboration networks also have a long tradition
+\cite{Todorov-etal:1991,Wagner-etal:2017}.\\
+
+The approach we follow here articulates game theory together with
+complex network analysis. Putting together game-theoretic modeling on
+complex networks is common in studies about the emergence of
+cooperation
 \cite{SzaboFath:2007,Nowak-etal:92,OshtukiNowak:2006,Santos-etal:2005,Santos-etal:2006}.
-However, in the context of science studies, it is far from being a unified,
-active field of research. There is no common set of questions and problems or a
-coherent body of models and theory aimed to understand the quirks and twists of
-cooperation in scientific communities. It is more likely to say that work of
-this kind are scarce and their implementatoin is on different situations related
-to the social life of science, where sometimes models are run on science
-collaboration networks because access to these kind of data is relatively easy
-to access.\\
-
-Nevertheless, there is work done. For instance Wardil and Hauert have analyzed
-how does collaboration happen within co-authorship networks
-\cite{Wardil-etal:2015}. Using the \emph{Physical Review} journal historic database,
-these authors show the payoff differences between being the first author and the
-last author, where the first author is a cooperator that takes the highest load
-of work, while the last author is the \emph{laird} that can benefit from the
-work of the former and get engaged in many other projects. They argue that
-cooperation in a multi-authored paper resambles more to a snow-drift game than a
-prisoner's dilemma situation, since when co-authoring a paper, every body wins
-but each author pays a different price. Though this work takes into account the
-topology of the network as informative regarding cooperation patterns, the role
-of topology framing or fostering cooperation is not part of the study. \\
-
-Game theory over complex scientific information and collaboration networks has
-also attracted attention. Hanauske has applied \emph{Evolutionary Game Theory}
-to have a better understanding of the market of scientific information, that
-involves scientists as producers but also journal, that are in charge of its
-dissemination. One of his models connects scientist interest in maximazing their
-reputation and their decissions to publish in an Open Access Journal or in a
-journal that works under the traditional publication framework. He has also
-modeled a game-theretic interactions between scientists and journals for both
-players to go open access or not. Only this second model incorporates networks
+However, in the context of science studies, it is far from being a
+unified, active field of research. There is no common set of questions
+and problems or a coherent body of models and theory aimed to
+understand the quirks and twists of cooperation in scientific
+communities. It is more likely to say that work of this kind is
+scarce and their implementatoin is on different situations related to
+the social life of science, where sometimes models are run on science
+collaboration networks because access to these kind of data is
+relatively easy to access.\\
+
+Nevertheless, there is work done. For instance Wardil and Hauert have
+analyzed how does collaboration happen within co-authorship networks
+\cite{Wardil-etal:2015}. Using the \emph{Physical Review} journal
+historic database, these authors show the payoff differences between
+being the first author and the last author, where the first author is
+a cooperator that takes the highest load of work, while the last
+author is the \emph{laird} that can benefit from the work of the
+former and get engaged in many other projects. They argue that
+cooperation in a multi-authored paper resambles more to a snow-drift
+game than a prisoner's dilemma situation, since when co-authoring a
+paper, every body wins but each author pays a different price. Though
+this work takes into account the topology of the network as
+informative regarding cooperation patterns, the role of topology
+framing or fostering cooperation is not part of the study. \\
+
+Game theory over complex scientific information and collaboration
+networks has also attracted attention. Hanauske has applied
+\emph{Evolutionary Game Theory} to have a better understanding of the
+market of scientific information, that involves scientists as
+producers but also journal, that are in charge of its
+dissemination. One of his models connects scientist interest in
+maximazing their reputation and their decissions to publish in an Open
+Access Journal or in a journal that works under the traditional
+publication framework. He has also modeled a game-theoretic
+interactions between scientists and journals for both players to go
+open access or not. Only this second model incorporates networks
 analysis \cite{Hanauske-etal:2012}.\\
 
-Another interesting behavior explored by game-theoretical modeling and complex
-networks has been done by Li and Cao \cite{Li-etal:2009}. This authors analyze the role of
-punishment in a science collaboration network. More precisely, they implemented
-an ultimatum bargaining model to understand the impact of the topology of a
-social network and the emergence of a population of punishers. In the ultimatum
-game, there are two players, one of them (the proponent) suggest to split a sum
-in two and its connected neighbor (the respondent), can decide to accept or
-reject the offer as it may be perceived more or less fair. If the respondent
-accepts, the sum is devided and the shares are divided according to the
-offer. If the offer is rejected the players do not get anything. According to
-the authors, the act of rejecting a selfish offer can be interpreted as a
-punishment since the player that rejects it is paying a cost of not receiving
-anything but the proponent looses even more, since his offer was selfish. Their
-results show that the population of punishers will emerge as a phase transition
-as the degree of selfishness increses among players. More over, they found a
+Another interesting behavior explored by game-theoretical modeling and
+complex networks has been done by Li and Cao \cite{Li-etal:2009}. This
+authors analyze the role of punishment in a science collaboration
+network. More precisely, they implemented an ultimatum bargaining
+model to understand the impact of the topology of a social network and
+the emergence of a population of punishers. In the ultimatum game,
+there are two players, one of them (the proponent) suggest to split a
+sum in two and its connected neighbor (the respondent), can decide to
+accept or reject the offer as it may be perceived more or less
+fair. If the respondent accepts, the sum is divided according to the
+offer. If the offer is rejected both players do not get
+anything. According to the authors, the act of rejecting a selfish
+offer can be interpreted as a punishment since the player that rejects
+it is paying a cost of not receiving anything but the proponent looses
+even more, since his offer was selfish. Their results show that the
+population of punishers will emerge as a phase transition as the
+degree of selfishness increses among players. Moreover, they found a
 dependence relation between the tolerance to selfish behaviors and the
@@
 
-In a similar vein to the work of Li and Cao, we explore the network effect on
-the distribution of players having access to certain amount of resources shared
-by other players in the network and the distribution of the strength of
-interactions among them. Particularly, we implemented two games played
-simultaneously: one for maximizing individual utility based on the iterated
-Prisoner's Dilemma; the other, a coordination game for maximizing the connection
-strength between players. We are interested in how they affect each other in the
-context of a network of scientific collaboration under the idea that while
-researchers are interested in maximizing their utilities, they also know that it
-is important to invest in building collaborative relationships. These two
-behaviors are explored in a biomedical
-research community in M\'exico.\\
-
-   In the context of our model, utility represents access to resources shared by
-   others.  The value of the utility function for a player is the sum of the
-   payoffs of playing prisoner's dilemma with its neighbors. The other
-   concurrent game consists of players trying to maximize the strength of their
-   interactions with other players. In the coordination game the best strategy
-   is to adopt the same strategy as the other player, as it pays the most,
-   regardless of cooperation or defection in the utility game. When both
-   cooperate the interaction gets a positive payoff, when both defect, the
-   interaction doesn't get affected; but if they do not coordinate, then the
-   interaction loses. The payoffs resulting from the coordination games are not
-   part of the utility function, however, both are considered by the agent to
-   decide whether to cooperate or defect. \\
+In a similar vein to the work of Li and Cao, we explore the network
+effect on the distribution of players having access to certain amount
+of resources shared by other players in the network and the
+distribution of the strength of interactions among them. Particularly,
+we implemented two games played simultaneously: one for maximizing
+individual utility based on the iterated Prisoner's Dilemma; the
+other, a coordination game for maximizing the connection strength
+between players. We are interested in how they affect each other in
+the context of a network of scientific collaboration under the idea
+that while researchers are interested in maximizing their utilities,
+they also know that it is important to invest in building
+collaborative relationships. These two behaviors are explored in a
+biomedical research community in M\'exico.\\
+
+In the context of our model, utility represents access to resources
+shared by others. The value of the utility function for a player is
+the sum of the payoffs of playing prisoner's dilemma with its
+neighbors. In the other concurrent game players try to maximize the
+strength of their interactions by coordinating their strategy to that
+of their neighbors. Interaction strength is updated with no regard to
+cooperation or defection in the utility game. When both cooperate the
+interaction gets a positive payoff, when both defect, the interaction
+doesn't get affected; but if they do not coordinate, then the
+interaction loses. The payoffs resulting from the coordination games
+are not part of the utility function, however both are considered by
+the agent to decide whether to cooperate or defect. \\
 
 The manuscript is structured in four sections. First we describe
-\textit{FOSISS}, the main program for grants destined to applied biomedical 
-research in M\'exico. This is the source of the
-database from which we created the researchers collaboration network. Next we
-describe our model
-and the different network topologies in which we explored it.
-We then present our results and discuss them. In the last section
-we draw some final remarks and conclusions.
+\textit{FOSISS}, the main program for grants destined to applied
+biomedical research in M\'exico. This is the source of the database
+from which we created the researchers collaboration network. Next we
+describe our model and the different network topologies in which we
+explored it.  We then present our results and discuss them. In the
+last section we draw some final remarks and conclusions.
 

### 2017-03-30 casm.tex
acknowledge copy editing
Added new references as requested by reviewer 1. Also, marked in red additions and modifications to the text. New references in the .bib file.

@@
 
-Nowadays it is widely acknowledged that collaboration takes many
-forms, from sharing of biological samples and biobanking to
-international groups in charge of helping research communities to
-harmonize and share their data. Sharing resources such as equipment,
-funds, and time is critical; building trust among scientists is
-fundamental. Also, resources are mobilized in order to create
-strategic alliances.\\
-
-The analysis of cooperation in scientific research has been the
+Nowadays it is widely acknowledged that collaboration takes many forms, from
+sharing of biological samples and biobanking to international groups in charge
+of helping research communities to harmonize and share their data {\color{red}
+\cite{VermeulenPenders:2013,Barrett-etal:2013,Federer-etal:2015,Karimi-Busheri:2015,Vallance-etal:2016,Warner-etal:2017}. Sharing
+resources such as equipment, funds, and time is critical; building trust among
+scientists is fundamental \cite{Bennett-etal:2010,Leite:2017}. Also, resources are mobilized
+in order to create strategic alliances.}\\
+
+{\color{red}The analysis of cooperation in scientific research has been the
 subject of a number of studies
@@
 co-authorship and collaboration networks also have a long tradition
-\cite{Todorov-etal:1991,Wagner-etal:2017}.\\
-
-The approach we follow here articulates game theory together with
+\cite{Todorov-etal:1991,Wagner-etal:2017}.}\\
+
+{\color{red}The approach we follow here articulates game theory together with
 complex network analysis. Putting together game-theoretic modeling on
@@
 collaboration networks because access to these kind of data is
-relatively easy to access.\\
-
-Nevertheless, there is work done. For instance Wardil and Hauert have
+relatively easy to access.}\\
+
+{\color{red}Nevertheless, there is work done. For instance Wardil and Hauert have
 analyzed how does collaboration happen within co-authorship networks
@@
 informative regarding cooperation patterns, the role of topology
-framing or fostering cooperation is not part of the study. \\
-
-Game theory over complex scientific information and collaboration
+framing or fostering cooperation is not part of the study.} \\
+
+{\color{red}Game theory over complex scientific information and collaboration
 networks has also attracted attention. Hanauske has applied
@@
 open access or not. Only this second model incorporates networks
-analysis \cite{Hanauske-etal:2012}.\\
-
-Another interesting behavior explored by game-theoretical modeling and
+analysis \cite{Hanauske-etal:2012}.}\\
+
+{\color{red}Another interesting behavior explored by game-theoretical modeling and
 complex networks has been done by Li and Cao \cite{Li-etal:2009}. This
@@
 dependence relation between the tolerance to selfish behaviors and the
-topologies of networks.\\
+topologies of networks.}\\
 
@@
 
-In a similar vein to the work of Li and Cao, we explore the network
+{\color{red}In a similar vein to the work of Li and Cao,} we explore the network
 effect on the distribution of players having access to certain amount
@@
 will be the product of applied research that attends national public
-needs, and promotes economic growth.\\
-
-\emph{FOSISS} or Sectoral Fund for Health and Social Security Research
-(\emph{Fondo Sectorial en Investigaci\'on en Salud y Seguridad Social}) is one of
-such funds. FOSISS is constituted by CONACyT, SSA, IMSS and ISSSTE,\footnote{SSA
+needs, and promotes economic growth.  {\color{red} \emph{FOSISS} or Sectoral
+Fund for Health and Social Security Research (\emph{Fondo Sectorial en
+  Investigaci\'on en Salud y Seguridad Social}) is one of
+such funds \cite{Gonzalez-etal:2008}}.\\
+
+FOSISS is constituted by CONACyT, SSA, IMSS and ISSSTE,\footnote{SSA
   is the acronym for Department of Health (\emph{Secretar\'ia de Salud}); IMSS is
@@
 Besides the characteristics of the population there are some other boundary
-conditions that play an important role on the network topology and dynamics
-that motivated the development of our model. Biomedical research in M\'exico
+conditions that play an important role on the network topology and dynamics that
+motivated the development of our model. Biomedical research in M\'exico
 constitutes a vibrant community and collaboration is part of everyday
 work. However, M\'exico does not have public biobanks for research purposes
-(which are especially relevant for research in genomics, for example), there is
-no regulation on the access to biological samples such as tissue, cells, DNA,
-RNA, etc.\footnote{Regulation exists regarding researcher-subject relations
-  based on legal and ethical grounds. Also, all projects need to be approved by
-  the Ethics Committee and IRB.} Something similar happens with data. There have
-been some attempts to create open data repositories for biomedical research, but
-they have not been established yet. Regulation on these subjects is still
-missing. Finally, technologically advanced equipment such as high throughput sequencers
-are kept by institutions with the highest research
-profiles and sometimes PIs manage them in a self serving way.\\
+(which are especially relevant for research in genomics, for example), and the
+current regulation on the access to biological samples such as tissue,
+cells, DNA, RNA, etc., is very general in scope 
+{\color{red}\cite{Motta-Saruwatari:2016}}.\footnote{Regulation exists regarding
+  researcher-subject relations based on legal and ethical grounds. Also, all
+  projects need to be approved by the Ethics Committee and IRB.} Something
+similar happens with data. There have been some attempts to create open data
+repositories for biomedical research, but they have not been established
+yet. Regulation on these subjects is still missing. Finally, technologically
+advanced equipment such as high throughput sequencers are kept by institutions
+with the highest research profiles and sometimes PIs manage them in a self serving way.\\
 
@@
 \section*{Acknowledgments}
-    We acknowledge the help of Ma. del Pilar Galarza and Francisco Allende for their work curating 
-databases of researchers. We acknowledge Be Luecke for her critical review.
+
+We acknowledge the help of Ma. del Pilar Galarza and Francisco Allende
+for their work curating databases of researchers. We are grateful to
+Be Luecke for copy editing the manuscript.
 

### 2017-03-30 casm.tex
Added new references as requested by reviewer 1.Fixed reference Li and Cao in the .bib file. Also, marked in red additions and modifications to the text.

@@
 Our model is based on the iterated version of the Prisoner's Dilemma (PD) and a
-coordination game instantiated on
-networks. In our model, an agent's decision to
-cooperate or defect depends on a balance between
-utilities and the current strength of its collaboration relationships. Such
-balance reflects the overall success or failure of its strategies. We
-study the behavior of the system under different topologies, including a
+coordination game instantiated on networks. In our model, an agent's decision to
+cooperate or defect depends on a balance between utilities and the current
+strength of its collaboration relationships. Such balance reflects the overall
+success or failure of its strategies. We study the behavior of the system under
+different topologies, including a
 real-world network.\\
@@
 The strength of the interaction, represented by $w$, is a property of the link between two agents and
-gets updated according to an $A_{ij}$ matrix of a coordination game. In the $w$ matrix, the highest value
+gets updated according to the payoff matrix of a coordination game. In the $w$ matrix, the highest value
 goes to an edge when both agents cooperate, getting an $R$ for reward; if one of
@@
 After each game, the agent adds up utility ($u$), which is the sum of the
-payoffs following the PD matrix. A pair of neighbors will add or substract from the strength of
-their interaction ($w_{ji}$) as they coordinate or not, being $w$
-also cumulative. We measure global utility and strength of interaction for the whole
-network. Global utility $U$ is the sum of all individual utilities and global
-strength of interaction or $W$ is the sum of every pair of agents' links
-$w$.
-Strength of interaction may have different meanings.
-From an empirical point of view, it simply means the number of times two researchers have collaborated together in a comon research project.
-From a sociological and qualitative point of view, if these two scientists have been willing to collaborate more than once, it may signify some form of "trust" among them.
-But this may not be the only possible interpreation since it can be different for each case.
-Since the strength of interactions can be sociologically interpreted in so many ways, we decided to just quantify the  times two researchers collaborate, and by doing this avoiding any generalized interpretation of the quality of the interactions among researchers.
-\\
+payoffs following the PD matrix. A pair of neighbors will add or substract from
+the strength of their interaction ($w_{ji}$) as they coordinate or not, being
+$w$ also cumulative. We measure global utility and strength of interaction for
+the whole network. Global utility $U$ is the sum of all individual utilities and
+global strength of interaction or $W$ is the sum of every pair of agents' links
+$w$. {\color{red}Strength of interaction may have different meanings. From an empirical
+point of view, it simply means the number of times two researchers have
+collaborated together in a common research project. From a sociological and
+qualitative point of view, if these two scientists have been willing to
+collaborate more than once, it may signify some form of ``loyalty'' among them. But
+this may not be the only possible interpreation since it can be different for
+each case. Since the strength of interactions can be sociologically interpreted
+in so many ways, we decided to just quantify the  times two researchers
+collaborate, and by doing this avoiding any generalized interpretation of the
+quality of the interactions among researchers.} \\
 
@@
 
-The probability for an agent to cooperate or defect depends on a
-number ($\eta$) that refers to a historical balance between average
-utility and the average strength of the connections with its
-neighbors. It is modeled so because we assume that whatever the result
-in utility or strength of interaction, as long as one of them
-increases, the player will be confident in the strategy followed so
-far. In every simulation step, each agent will independently play both games with
-every neighbor. Nonetheless, the agent sets its decision to cooperate or defect beforehand
-by assessing the overall situation of its relationships. This may
-sound odd, since one may think that a person decides for each
-relationship separately. However in this way players are optimizing
-access to resources and the strength of interactions to their
-neighbors at the same time, since their state is set by
-considering both together.
-The strength of interaction is updated independently for each pair of agents.
-In a single play some interactions might be weakened, some may get strengthened and others may remain unaffected.
-Moreover, in this model, history is kept in the network as strength of interactions and it conditions the agent\'s disposition to cooperate or to defect.
-As the sayings go: Burnt children dread fire; A bad dog is not born but made.\\
+The probability for an agent to cooperate or defect depends on a number ($\eta$)
+that refers to a historical balance between average utility and the average
+strength of the connections with its neighbors. It is modeled so because we
+assume that whatever the result in utility or strength of interaction, as long
+as one of them increases, the player will be confident in the strategy followed
+so far. {\color{red}In every simulation step, each agent will independently play both games
+with every neighbor. Nonetheless, the agent sets its decision to cooperate or
+defect beforehand by assessing the overall situation of its relationships. This
+may sound odd, since one may think that a person decides for each relationship
+separately. However in this way players are optimizing access to resources and
+the strength of interactions to their neighbors at the same time, since their
+state is set by considering both together. The strength of interaction is
+updated independently for each pair of agents.  In a single play some
+interactions might be weakened, some may get strengthened and others may remain
+unaffected. Moreover, in this model, history is kept in the network as strength
+of interactions and it conditions the agent\'s disposition to cooperate or to
+defect. As the sayings go: Burnt children dread fire; A bad dog is not born but made.}\\
 
@@
 
-$\eta_i = \frac{\langle f_i \rangle + \langle w_{ij} \rangle _j}{2}$\\
+$\eta_i = \frac{\langle u_i \rangle + \langle w_{ij} \rangle _j}{2}$\\
 

### 2017-04-02 casm.tex
One problematic reference fixed and changed of position the conclusions all the way to the last paragraph.
proof-read to just before methodology

@@
 especially in the area of bibliometrics and scientometrics such as in
-citation networks that date as back as 1972 \cite{Garfield:1972},
+citation networks that date as far back as 1972 \cite{Garfield:1972},
 co-authorship and collaboration networks also have a long tradition
@@
 understand the quirks and twists of cooperation in scientific
-communities. It is more likely to say that work of this kind is
-scarce and their implementatoin is on different situations related to
-the social life of science, where sometimes models are run on science
-collaboration networks because access to these kind of data is
-relatively easy to access.}\\
+communities. It is more earnest to say that work of this kind is
+rather scarce and focused around situations related to
+the social life of science, where sometimes models are run on
+collaboration networks because access to that kind of data is
+relatively easy.}\\
 
 {\color{red}Nevertheless, there is work done. For instance Wardil and Hauert have
-analyzed how does collaboration happen within co-authorship networks
+analyzed how collaboration happens within co-authorship networks
 \cite{Wardil-etal:2015}. Using the \emph{Physical Review} journal
@@
 former and get engaged in many other projects. They argue that
-cooperation in a multi-authored paper resambles more to a snow-drift
-game than a prisoner's dilemma situation, since when co-authoring a
-paper, every body wins but each author pays a different price. Though
+cooperation in a multi-authored paper is a game more similar to ``snow-drift''
+than to ``prisoner's dilemma'' since when co-authoring a
+paper everybody wins but each author pays a different price. Though
 this work takes into account the topology of the network as
@@
 
-{\color{red}Game theory over complex scientific information and collaboration
-networks has also attracted attention. Hanauske has applied
-\emph{Evolutionary Game Theory} to have a better understanding of the
-market of scientific information, that involves scientists as
-producers but also journal, that are in charge of its
-dissemination. One of his models connects scientist interest in
-maximazing their reputation and their decissions to publish in an Open
-Access Journal or in a journal that works under the traditional
-publication framework. He has also modeled a game-theoretic
-interactions between scientists and journals for both players to go
-open access or not. Only this second model incorporates networks
-analysis \cite{Hanauske-etal:2012}.}\\
-
-{\color{red}Another interesting behavior explored by game-theoretical modeling and
+{\color{red}
+
+Game theory over complex scientific information and collaboration
+networks has also attracted attention. To have a better understanding
+of the market of scientific information Hanauske has applied
+\emph{Evolutionary Game Theory} involving scientists as producers but
+also journals as disseminators. One of his models connects scientists'
+interest in maximazing their reputation and their decissions to
+publish in an Open Access Journal or in a journal that works under the
+traditional publication framework. He has also modeled game-theoretic
+interactions between scientists and journals concerning the decision
+of both players to go open access or not. Only this second model
+incorporates networks analysis \cite{Hanauske-etal:2012}.}\\
+
+{\color{red}
+
+Another interesting behavior explored by game-theoretical modeling and
 complex networks has been done by Li and Cao \cite{Li-etal:2009}. This
@@
 the emergence of a population of punishers. In the ultimatum game,
-there are two players, one of them (the proponent) suggest to split a
-sum in two and its connected neighbor (the respondent), can decide to
+there are two players, one of them (the proponent) suggests to split a
+sum in two and its connected neighbor (the respondent) can decide to
 accept or reject the offer as it may be perceived more or less
 fair. If the respondent accepts, the sum is divided according to the
-offer. If the offer is rejected both players do not get
-anything. According to the authors, the act of rejecting a selfish
-offer can be interpreted as a punishment since the player that rejects
-it is paying a cost of not receiving anything but the proponent looses
-even more, since his offer was selfish. Their results show that the
-population of punishers will emerge as a phase transition as the
-degree of selfishness increses among players. Moreover, they found a
-dependence relation between the tolerance to selfish behaviors and the
-topologies of networks.}\\
+offer. If the offer is rejected both players get nothing. According to
+the authors, the act of rejecting a selfish offer can be interpreted
+as a punishment since the player that rejects it is paying the cost of
+not receiving anything, but because of a selfish offer the proponent
+looses even more. Their results show that a phase transition will
+emerge in the population of punishers as the degree of selfishness
+increses among players. Moreover, they found a dependence relation
+between the tolerance to selfish behaviors and the topologies of
+networks.}\\
 
@@
 studies, and to manage different trusts intended to fund individuals
-and groups for scientific and
-technological research.\\
+and groups for scientific and technological research.\\
 
 In the year 2002 CONACyT, along with other government agencies and
-entities, created sectoral funds
-to cover and equally
-promote research capacities of different areas such as energy, agriculture
-and health. Technological innovation is fostered by the generation of human resources
-and by helping research groups to consolidate. It is expected that the
-knowledge generated under the sponsorship of these funds
-will be the product of applied research that attends national public
-needs, and promotes economic growth.  {\color{red} \emph{FOSISS} or Sectoral
-Fund for Health and Social Security Research (\emph{Fondo Sectorial en
-  Investigaci\'on en Salud y Seguridad Social}) is one of
-such funds \cite{Gonzalez-etal:2008}}.\\
+entities, created sectoral funds to cover and equally promote research
+capacities of different areas such as energy, agriculture and
+health. Technological innovation is fostered by the generation of
+human resources and by helping research groups to consolidate. It is
+expected that the knowledge generated under the sponsorship of these
+funds will be the product of applied research that attends national
+public needs, and promotes economic growth.  {\color{red}
+  \emph{FOSISS} or Sectoral Fund for Health and Social Security
+  Research (\emph{Fondo Sectorial en Investigaci\'on en Salud y
+    Seguridad Social}) is one of such funds
+  \cite{Gonzalez-etal:2008}}.\\
 
 FOSISS is constituted by CONACyT, SSA, IMSS and ISSSTE,\footnote{SSA
-  is the acronym for Department of Health (\emph{Secretar\'ia de Salud}); IMSS is
-  the acronym for Social Security Mexican Institute (\emph{Instituto Mexicano
-    del Seguro Social}); ISSSTE stands for Institute for Social Security and
-  Services for State Workers (\emph{Instituto de Seguridad y Servicios Sociales
-    de los Trabajadores del Estado})} all of them being the major public health
-providers and research institutions in the country. Every year CONACyT opens a
-call for funds limited to a set of health research areas previously defined by a
-group of experts. Most applicants are public universities and research
-institutions, but eligibility is open to public and private health research sectors.
-From 2002 through 2013, there were 91 institutions funded that
-comprised 4,988 researchers.\\
+  is the acronym for Department of Health (\emph{Secretar\'ia de
+    Salud}); IMSS is the acronym for Social Security Mexican Institute
+  (\emph{Instituto Mexicano del Seguro Social}); ISSSTE stands for
+  Institute for Social Security and Services for State Workers
+  (\emph{Instituto de Seguridad y Servicios Sociales de los
+    Trabajadores del Estado})} all of them being the major public
+health providers and research institutions in the country. Every year
+CONACyT opens a call for funds limited to a set of health research
+areas previously defined by a group of experts. Most applicants are
+public universities and research institutions, but eligibility is open
+to public and private health research sectors.  From 2002 through
+2013, there were 91 institutions funded that comprised 4,988
+researchers.\\
 
@@
 investigators (PIs), associate researchers, postdoctoral associates,
-postgraduate and undergraduate students.
-Unfortunately, information on these roles is not specified in the database.
-We acknowledge the importance of this deficiency because
-researchers in our network act under different circumstances and we know
-that this diversity has a real impact on the structure and eventually on the
-dynamics of the network, as well as on the results of our model.\\
-
-Our database includes the
-name of the project, the year it was approved for funding and the research area
-to which it was assigned. It specifies the names of PIs or the people 
-responsible for the project and the names of collaborators.
-Researchers can be PIs in one project and collaborators on a different project. The institutional
-affiliation of all participants is included. Through this affiliation
-we determine the principal institution
-behind every project.\\
-
-Even though curation and analysis work of this database is still going on, some
-relevant facts about the biomedical research can be said. Over the period of 12
-years, 32 general research areas have been defined, the three most funded
-research areas are \emph{chronic and degenerative diseases}, \emph{malignant
-  neoplasms}, and \emph{infectious and parasitic diseases}. The least funded
-area is \emph{Ethics and medicine}. The area with the most researchers is
+postgraduate and undergraduate students.  Unfortunately, information
+on these roles is not specified in the database.  We acknowledge the
+importance of this deficiency because researchers in our network act
+under different circumstances and we know that this diversity has a
+real impact on the structure and eventually on the dynamics of the
+network, as well as on the results of our model.\\
+
+Our database includes the name of the project, the year it was
+approved for funding and the research area to which it was
+assigned. It specifies the names of PIs or the people responsible for
+the project and the names of collaborators.  Researchers can be PIs in
+one project and collaborators on a different project. The
+institutional affiliation of all participants is included. Through
+this affiliation we determine the principal institution behind every
+project.\\
+
+Even though curation and analysis work of this database is still going
+on, some relevant facts about the biomedical research can be
+said. Over the period of 12 years, 32 general research areas have been
+defined, the three most funded research areas are \emph{chronic and
+  degenerative diseases}, \emph{malignant neoplasms}, and
+\emph{infectious and parasitic diseases}. The least funded area is
+\emph{Ethics and medicine}. The area with the most researchers is
 \emph{malignant neoplasms}. Other areas of relevance for M\'exico are
-\emph{diseases related to poverty} and \emph{Health and vulnerable groups}. \\
+\emph{diseases related to poverty} and \emph{Health and vulnerable
+  groups}. \\
 
@@
 
-  \section*{Conclusions}
-
  To close this article, we would like to comment on three
@@
   very recently has become possible \cite{Barabasi:2012}.\\
+
+\section*{Conclusions}
 

### 2017-04-02 casm.tex
clear up which plots are from which experiment

@@
-%% BioMed_Central_Tex_Template_v1.06
+% BioMed_Central_Tex_Template_v1.06
 %%                                      %
@@
 
-%% In this work we developed a model in order to have a better understanding of the
-%% distribution of utility and trust in real networks of biomedical research
-%% collaboration under certain social constraints  or topological properties.\\
-
 Our model is based on the iterated version of the Prisoner's Dilemma (PD) and a
@@
 success or failure of its strategies. We study the behavior of the system under
-different topologies, including a
-real-world network.\\
+different topologies, including a real-world network.\\
 
@@
 
-The strength of the interaction, represented by $w$, is a property of the link between two agents and
-gets updated according to the payoff matrix of a coordination game. In the $w$ matrix, the highest value
-goes to an edge when both agents cooperate, getting an $R$ for reward; if one of
-them defects, the connection gets weaker getting $P$ for the collaborative
-connection being punished. If both agents defect, the value $w$ doesn't change,
-which means that agents didn't interact or that the interaction gets nullified
-$N$. In this game, the best action for any agent is to coordinate with its
-neighbor, either because it wins or because it doesn't lose. \\
+The strength of the interaction, represented by $w$, is a property of
+the link between two agents and gets updated according to the payoff
+matrix of a coordination game. In the $w$ matrix, the highest value
+goes to an edge when both agents cooperate, getting an $R$ for reward;
+if one of them defects, the connection gets weaker getting $P$ for the
+collaborative connection being punished. If both agents defect, the
+value $w$ doesn't change, which means that agents didn't interact or
+that the interaction gets nullified $N$. In this game, the best action
+for any agent is to coordinate with its neighbor, either because it
+wins or because it doesn't lose. \\
 
@@
 
-It should be noted that the same actions or behaviors work for
-  both $u$ and $w$. There are two reasons for this decision in the design of the
-model. The most general one is that we believe that in the real world,
-actions such as cooperating and defecting affect the strength of the interaction
-among people. The second one is that we think that selfishly maximizing access to resources and
-strengthening relationships are \emph{opposing forces} acting on the same set of
-behaviors. The actions of an agent imply a trade-off in which defecting may
-increase its utility at the expense of its collaborative relationships. If
-collaborators have nourished their relationships, they might be strong enough to
-endure occasional defection. Cooperating may build up relationships but it can be
+It should be noted that the same actions or behaviors work for both
+$u$ and $w$. There are two reasons for this decision in the design of
+the model. The most general one is that we believe that in the real
+world, actions such as cooperating and defecting affect the strength
+of the interaction among people. The second one is that we think that
+selfishly maximizing access to resources and strengthening
+relationships are \emph{opposing forces} acting on the same set of
+behaviors. The actions of an agent imply a trade-off in which
+defecting may increase its utility at the expense of its collaborative
+relationships. If collaborators have nourished their relationships,
+they might be strong enough to endure occasional
+defection. Cooperating may build up relationships but it can be
 expensive for the player.
@@
 
-We ran two different experiments. In the first one we simulated different
+We ran two different experiments. In the First Experiment we simulated different
 values of carrying capacity $\nu$. With this experiment we were able
@@
 
-The second experiment consisted in running the simulation under the
+The Second Experiment consisted in running the simulation under the
 same degree of carrying capacity $\nu$ but randomizing the initial
@@
 \end{tabular}
-\caption{Ratio of cooperators as a function of carrying capacity and time. Topologies are: A. Random, Erd\"{o}s-R\'enyi. B. Watts-Strogatz. C. Barab\'asi-Albert. D. FOSISS.
+\caption{Ratio of cooperators as a function of carrying capacity and time during First Experiment. Topologies are: A. Random, Erd\"{o}s-R\'enyi. B. Watts-Strogatz. C. Barab\'asi-Albert. D. FOSISS.
 }\label{CD}
@@
 \end{tabular}
-\caption{Utility $U$ dynamics as a function of carrying capacity $\nu$ and time. Topologies are: A. Random, Erd\"{o}s-R\'enyi. B. Watts-Strogatz. C. Barab\'asi-Albert. D. FOSISS.}\label{fitness}
+\caption{First Experiment's utility $U$ dynamics as a function of carrying capacity $\nu$ and time.
+Topologies are: A.
+Random, Erd\"{o}s-R\'enyi.
+B.
+Watts-Strogatz.
+C.
+Barab\'asi-Albert.
+D.
+FOSISS.}\label{fitness}
 \end{figure}
@@
 \end{tabular}
-\caption{Strength of interactions $w$ dynamics as a function of carrying capacity $\nu$ and time.
+\caption{Strength of interactions $w$ dynamics as a function of carrying capacity $\nu$ and time during First Experiment.
 Topologies are: A.
@@
 \caption{Shifting population between cooperators and defectors as a function of
-carrying capacity $\nu$ and time. Topologies are: A. Random, Erd\"{o}s-R\'enyi. B. Watts-Strogatz. C. Barab\'asi-Albert. D. FOSISS.}\label{state} 
+carrying capacity $\nu$ and time during First Experiment. Topologies are: A. Random, Erd\"{o}s-R\'enyi. B. Watts-Strogatz. C. Barab\'asi-Albert. D. FOSISS.}\label{state} 
 \end{figure}
@@
 \end{tabular}
-\caption{Utility distribution on different topologies. A. Random,
+\caption{Second Experiment's utility distribution on different topologies. A. Random,
   Erd\"{o}s-R\'enyi network displays a normal-like
@@
 \end{tabular}
-\caption{Strength of interactions distribution on different topologies. A. Random, Erd\"{o}s-R\'enyi network displays a normal-like
+\caption{Strength of interactions distribution on different topologies during Second Experiment. A. Random, Erd\"{o}s-R\'enyi network displays a normal-like
 distribution. B. Watts-Strogatz network strength of interactions distribution is bimodal and highly skewed to the right. C.
@@
   researchers control the whole network, as has been reported in some
-  other places \cite{yousefi-etal:2008}. Surprisingly, FOSISS network
+  other places \cite{Yousefi-etal:2008}. Surprisingly, FOSISS network
   centralization is very low $0.023$, i.e. there are no researchers

### 2017-04-03 casm.tex
fixed som reference, created research areas table.

@@
 agent's historical balance between utility and strength of
-collaborative relationships and carrying capacity of the system is
+collaborative relationships and an a parameter of confidence of the system is
 small, suggesting that there is a region in which a phase transition
@@
 on, some relevant facts about the biomedical research can be
-said. Over the period of 12 years, 32 general research areas have been
+said. Over the period of 12 years, 37 general research areas have been
 defined, the three most funded research areas are \emph{chronic and
@@
 The probability for an agent to cooperate or defect depends on a number ($\eta$)
-that refers to a historical balance between average utility and the average
-strength of the connections with its neighbors. It is modeled so because we
+that refers to a historical balance between average utility $\langle u_i \rangle$ and the average
+strength of the connections with its neighbors $\langle w_{ij} \rangle _j$. It is modeled so because we
 assume that whatever the result in utility or strength of interaction, as long
@@
 
-For the agent to decide whether to cooperate or not, $\eta$ is
-compared to a global threshold $\nu$. If the agent's $\eta$ $>$ $\nu$,
-then he will cooperate, otherwise he will be suspicious and
-will defect. $\nu$ is a global parameter that establishes a threshold
-that an agent's $\eta$ must cross in order to decide to cooperate. In
-this way, $\nu$ can limit the size of the population of
-cooperators. Due to what the system and the game can offer to agents
-in terms of utilities and the strength of collaboration relationships,
-$\nu$ represents the carrying capacity of the
-system for the population of cooperators.\\
+For the agent to decide whether to cooperate or not, $\eta$ is compared to a
+global parameter $\nu$. This is a parameter that represents the minimum value of
+$\eta$ that a player must achieve in order to cooperate. If the agent's
+$\eta$ $>$ $\nu$, then he will cooperate, otherwise he will be suspicious and
+will defect. In this way, as we arbitrarily control the value of $\nu$ we can
+identify the values of $\eta$ where the population stops cooperating and begins
+to defect; also it makes possible to see how this transition takes place for the
+different network topologies.  \\
+
+%{\color {red}Due to what the system and the game can offer to agents
+%in terms of utilities and the strength of collaboration relationships,
+%$\nu$ represents a parameter of confidence of the system.}\\
 
@@
 We ran two different experiments. In the First Experiment we simulated different
-values of carrying capacity $\nu$. With this experiment we were able
+values of the parameter of confidence $\nu$. With this experiment we were able
 to see how the number of cooperators, utility, strength of interactions
 among agents and the ratio of shifting state population would change
-in the range of the carrying capacity. The states of the agents were
-the same at initialization, for all values of the carrying
-capacity. Since the model is deterministic, it will return the same
+in the range of the parameter of confidence. The states of the agents were
+the same at initialization, for all values of $\nu$. Since the model is deterministic, it will return the same
 result if run under the same conditions.\\
@@
 The Second Experiment consisted in running the simulation under the
-same degree of carrying capacity $\nu$ but randomizing the initial
+same value of the parameter of confidence $\nu$ but randomizing the initial
 states of the agents. This would show that the system converges to a
@@
 Other results to report are those of the dynamics of different
-variables as the carrying capacity $\nu$ changes. The  most salient
+variables as the parameter of confidence $\nu$ changes. The  most salient
 result is that for $\nu$ between $0.19$ and $0.24$, there is an
@@
 \end{tabular}
-\caption{Ratio of cooperators as a function of carrying capacity and time during First Experiment. Topologies are: A. Random, Erd\"{o}s-R\'enyi. B. Watts-Strogatz. C. Barab\'asi-Albert. D. FOSISS.
+\caption{Ratio of cooperators as a function of the parameter of confidence and time during First Experiment.
+Topologies are: A.
+Random, Erd\"{o}s-R\'enyi.
+B.
+Watts-Strogatz.
+C.
+Barab\'asi-Albert.
+D.
+FOSISS.
 }\label{CD}
@@
 \end{tabular}
-\caption{First Experiment's utility $U$ dynamics as a function of carrying capacity $\nu$ and time.
-Topologies are: A.
-Random, Erd\"{o}s-R\'enyi.
-B.
-Watts-Strogatz.
-C.
-Barab\'asi-Albert.
-D.
-FOSISS.}\label{fitness}
+\caption{First Experiment's utility $U$ dynamics as a function of the parameter
+  of confidence $\nu$ and time. Topologies are: A. Random, Erd\"{o}s-R\'enyi. B. Watts-Strogatz. C. Barab\'asi-Albert. D. FOSISS.}\label{fitness}
 \end{figure}
@@
 \end{tabular}
-\caption{Strength of interactions $w$ dynamics as a function of carrying capacity $\nu$ and time during First Experiment.
-Topologies are: A.
-Random, Erd\"{o}s-R\'enyi.
-B.
-Watts-Strogatz.
-C.
-Barab\'asi-Albert.
-D.
-FOSISS.}\label{trust}
+\caption{Strength of interactions $w$ dynamics as a function of the parameter
+  of confidence $\nu$ and time during First Experiment. Topologies are:
+  A. Random, Erd\"{o}s-R\'enyi. B. Watts-Strogatz. C. Barab\'asi-Albert. D. FOSISS.}\label{trust}  
 \end{figure}
@@
 \caption{Shifting population between cooperators and defectors as a function of
-carrying capacity $\nu$ and time during First Experiment. Topologies are: A. Random, Erd\"{o}s-R\'enyi. B. Watts-Strogatz. C. Barab\'asi-Albert. D. FOSISS.}\label{state} 
+the parameter
+  of confidence $\nu$ and time during First Experiment. Topologies are:
+  A. Random,
+  Erd\"{o}s-R\'enyi. B. Watts-Strogatz. C. Barab\'asi-Albert. D. FOSISS.}\label{state}  
 \end{figure}
@@
 
- To close this article, we would like to comment on three
-  issues we consider important. The first one is about confronting our
-  results with data available to us from the biomedical research
-  community. Second, some remarks we believe are important about the
-  role of computational simulations in the social sciences. Finally we
-  would like to comment on our future work.\\
-
-  The two main results of our model are the smoothness in
-  the phase transition-like behavior for different parameters and the
-  distribution of utility and strength of interactions in the FOSISS
-  network compared to other networks and their topologies. We are
-  certain that the particular structure of FOSISS network is playing a
-  central role in the results and because of that we would like to
-  discuss it a little bit further.\\
-
-  FOSISS network is highly hierarchical according to its
-  heterogeneity of $0.873$. Because of it, one would expect to find
-  the presence of important hubs \cite{Wu:2008}, that is, a few
-  researchers control the whole network, as has been reported in some
-  other places \cite{Yousefi-etal:2008}. Surprisingly, FOSISS network
-  centralization is very low $0.023$, i.e. there are no researchers
-  that centralize the majority of connections. Our guess is that the
-  network is composed of many small communities or groups with a
-  central researcher or Principal Investigator (PI). If this is the
-  case in the FOSISS network, it means that those groups have a very
-  hierarchical structure as well.\\
+  There are two issues we consider important. The first one is about
+  confronting our results with data available to us from the biomedical research
+  community. Second, we would like to comment on our future work.\\
+
+  The two main results of our model are the smoothness in the phase
+  transition-like behavior for different parameters and the distribution of
+  utility and strength of interactions in the FOSISS network compared to other
+  networks and their topologies. We are certain that the particular structure of
+  FOSISS network is playing a central role in the results and because of that we
+  would like to discuss it a little bit further. FOSISS network is highly
+  hierarchical according to its heterogeneity of $0.873$. Because of it, one
+  would expect to find the presence of important hubs \cite{Wu:2008}, that is, a
+  few researchers control the whole network, as has been reported in some other
+  places \cite{Yousefi-etal:2008}. Surprisingly, FOSISS network centralization
+  is very low $0.023$, i.e. there are no researchers that centralize the
+  majority of connections. Our guess is that the network is composed of many
+  small communities or groups with a central researcher or Principal
+  Investigator (PI). If this is the case in the FOSISS network, it means that
+  those groups have a very hierarchical structure as well.\\
 
@@
   constrain them as it seems to happen with individual researchers
-  inside their communities. Nevertheless, if values of the carrying
-  capacity $\nu$ keep increasing and it becomes more difficult to
+  inside their communities. Nevertheless, if values of the parameter
+  of cooperation $\nu$ keep increasing and it becomes more difficult to
   strengthen interactions, then strength of interactions begins to

### 2017-04-04 casm.tex
these instead of this
Included new references and also the discussion of results considering the references at the itroduction.

@@
 \usepackage{color}
+\usepackage{cite}
 % \usepackage[applemac]{inputenc} %applemac support if unicode package fails
@@
 {\color{red}In a similar vein to the work of Li and Cao,} we explore the network
-effect on the distribution of players having access to certain amount
-of resources shared by other players in the network and the
-distribution of the strength of interactions among them. Particularly,
-we implemented two games played simultaneously: one for maximizing
-individual utility based on the iterated Prisoner's Dilemma; the
-other, a coordination game for maximizing the connection strength
-between players. We are interested in how they affect each other in
-the context of a network of scientific collaboration under the idea
-that while researchers are interested in maximizing their utilities,
-they also know that it is important to invest in building
-collaborative relationships. These two behaviors are explored in a
-biomedical research community in M\'exico.\\
+effect on the distribution of players having access to certain amount of
+resources shared by other players in the network and the distribution of the
+strength of interactions among them. Particularly, we implemented two games
+played simultaneously: one for maximizing individual utility based on the
+iterated Prisoner's Dilemma (PD); the other, a coordination game for maximizing the
+connection strength between players. We are interested in how they affect each
+other in the context of a network of scientific collaboration under the idea
+that while researchers are interested in maximizing their utilities, they also
+know that it is important to invest in building collaborative
+relationships. \\ %This is important because what we have seen
 
@@
 the agent to decide whether to cooperate or defect. \\
+
+{\color {red}From our anthropological fieldwork among biomedical research communities, their
+networks appear to be quite paradoxical: while they seem very
+hierarchical and only few researchers get the most of the profit of collective
+work, a great deal of collaboration is maintained. In other words, we are
+intrigued by the fact that for all the power and profit gain asymmetries,
+people are still willing to collaborate, build trust and remain loyal to their
+PI's and mentors.These two behaviors are explored in a biomedical research
+community in M\'exico. We believe that by implementing PD game and coordination
+game in a real world network is a way of capturing the essence of this
+problem. From our point of view this is an important contribution as we not only
+use data extracted from bibliometric source as most collaboration networks are
+studied, but that the founding question on which the model has been developed is
+empirically based in the sociology of the case.}\\
 
@@
 
-In this work we have analyzed the influence of parameters
-  given by the underlying social structure of a science collaborative
-  network on collective strength of interactions and utility dynamical
-  behavior, based on a class of iterated PD and coordination
-  games. Such parameters include mainly local and global connectivity
-  like the degree centrality and average clustering coefficient, as
+In this work we have analyzed the influence of parameters given by the
+underlying social structure of a science collaborative network on collective
+strength of interactions and utility dynamical behavior, based on a class of
+iterated PD and coordination games. Such parameters include mainly local and
+global connectivity like the degree centrality and average clustering
+coefficient, as
 well as communication patterns.\\
 
-  Under the assumptions given by the model, we were able to
-  notice that, in general, communication within the social
-  collaborative networks has a positive correlation with average
-  strength of interactions between the individuals partaking in the
-  games and also with the global collective utility (given by the sum
-  of the individual payoffs). The better the communication among
-  players, the higher the strength of interactions and the utility
-  leading to an optimized functioning of the whole \emph{scientific
-    collaboration system}. This is an important result that may be
-  useful for scientific policy planning and may set a foundation for
-  the optimal use of social networks in scientific collaboration as a
-  means to improve the relationships among collaborating peers and
-  ultimately the performance of research systems.  We obviously need
-  more qualitative work in order to validate these results from a
+Under the assumptions given by the model, we were able to notice that, in
+general, communication within the social collaborative networks has a positive
+correlation with average strength of interactions between the individuals
+partaking in the games and also with the global collective utility (given by the
+sum of the individual payoffs). The better the communication among players, the
+higher the strength of interactions and the utility leading to an optimized
+functioning of the whole \emph{scientific collaboration system}. This is an
+important result that may be useful for scientific policy planning and may set a
+foundation for the optimal use of social networks in scientific collaboration as
+a means to improve the relationships among collaborating peers and ultimately
+the performance of research systems.  We obviously need more qualitative work in
+order to validate these results from a
 sociological and anthropological perspective.\\
@@
 
-  There are two issues we consider important. The first one is about
-  confronting our results with data available to us from the biomedical research
-  community. Second, we would like to comment on our future work.\\
-
-  The two main results of our model are the smoothness in the phase
+% There are several issues we consider important to discuss. The first one is about confronting
+% our results with data available to us from the biomedical research
+% community. Second, we would like to comment on our future work.\\
+
+{\color {red}In the area of complex networks and game theory, it has being affirmed for a
+long time that scale-free networks promote the evolution of cooperation. Part of
+this property has been attributed to the presence of hubs
+\cite{Santos-etal:2005,Szolnoki-etal:2008,Du-etal:2008,Li-etal:2009,Yang-etal:2009,Lei-etal:2009,Liu-etal:2010,Cheng-etal:2010B,Li-etal:2014,Li-etal:2015,Ichinose:2017}. Perhaps
+less attention has been place on the persistence of cooperation and the the role
+played by the clustering coefficiente in scale-free and small-world networks
+\cite{Kim-etal:2002,Masuda-etal:2003,Wu-etal:2005,Wu-etal:2006,Guan-etal:2006,Fu:2007,Zhang-etal:2007,Thibert-Plante-etal:2007,Chen-etal:2008}. This is where our result comes in.} \\
+
+The two main outcomes of our model are the smoothness in the phase
 transition-like behavior for different parameters and the distribution of
@@
 would like to discuss it a little bit further. FOSISS network is highly
-  hierarchical according to its heterogeneity of $0.873$. Because of it, one
-  would expect to find the presence of important hubs \cite{Wu:2008}, that is, a
-  few researchers control the whole network, as has been reported in some other
-  places \cite{Yousefi-etal:2008}. Surprisingly, FOSISS network centralization
-  is very low $0.023$, i.e. there are no researchers that centralize the
-  majority of connections. Our guess is that the network is composed of many
-  small communities or groups with a central researcher or Principal
-  Investigator (PI). If this is the case in the FOSISS network, it means that
-  those groups have a very hierarchical structure as well.\\
-
-  Under such structure, when the clustering coefficient is
-  considered, it can be said that groups are also well connected but
-  that inter-group connections are sparse. In other words, individual
-  groups are strongly connected within but the network as a whole is
-  supported by a small number of links. We came by this idea partially
-  from another study about scientific collaborations based on
-  co-authorships in one of the research centers that is part of the
-  FOSISS network \cite{HernandezLemus:2013}. In the cited reference, an
-  apparently well integrated community was found (high clustering
-  coefficient and a very short characteristic path length). Such
-  integration was mostly superficial, since it depended on the
-  presence of external collaborators from other research institutions
-  (most of them from overseas).  Removing these external collaborators
-  brakes down the network into small subgraphs that worked
-  independently. Remarkably, those subgraphs corresponded to the real
-  groups of that research center.  What is more, several groups had a
-  hierarchical structure as the one we suspect is common in FOSISS
-  subgraphs. The results showed that collaboration was poor between
-  groups but strong among the members of each group, and that
-  collaboration among groups doesn't emerge bottom-up, instead it
+hierarchical according to its heterogeneity of $0.873$. Because of it, one would
+expect to find the presence of important hubs \cite{Wu:2008}, that is, a few
+researchers control the whole network, as has been reported in some elsewhere
+\cite{Yousefi-etal:2008}. Surprisingly, FOSISS network centralization is very
+low $0.023$, i.e. there are no researchers that centralize the majority of
+connections. Our guess is that the network is composed of many small communities
+or groups with a central researcher or Principal Investigator (PI). If this is
+the case, it means that those groups have a very hierarchical structure as
+well. This is similar to what has been reported by others about the
+heterogeneity in small-world networks, in which the combination of certain
+amount of hierarchy and small-worldness makes cooperation to peak over compared
+to the evolution of cooperation in homogeneous and the most heterogeneous
+networks \cite{Fu:2007}. For the FOSISS netwok, this property would enhanced
+cooperation among players, eventhough the distribution of utilities are skewed
+towards a handful of researchers. \\
+
+% The two main results of our model are the smoothness in the phase
+% transition-like behavior for different parameters and the distribution of
+% utility and strength of interactions in the FOSISS network compared to other
+% networks and their topologies. We are certain that the particular structure of
+% FOSISS network is playing a central role in the results and because of that we
+% would like to discuss it a little bit further. FOSISS network is highly
+% hierarchical according to its heterogeneity of $0.873$. Because of it, one would
+% expect to find the presence of important hubs \cite{Wu:2008}, that is, a few
+% researchers control the whole network, as has been reported in some other places
+% \cite{Yousefi-etal:2008}. Surprisingly, FOSISS network centralization is very
+% low $0.023$, i.e. there are no researchers that centralize the majority of
+% connections. Our guess is that the network is composed of many small communities
+% or groups with a central researcher or Principal Investigator (PI). If this is
+% the case in the FOSISS network, it means that
+% those groups have a very hierarchical structure as well.\\
+
+Under such structure, when the clustering coefficient is considered, it can be
+said that groups are also well connected but that inter-group connections are
+sparse. In other words, individual groups are strongly connected within but the
+network as a whole is supported by a small number of links. {\color{red}This is
+  not an uncommon pattern in social networks. It has been claimed that this form
+  of structure has been evolutionarily advantageous
+  \cite{Turchin:2015}. Moreover, research groups internal cohesion may be
+related to Wardil and Hauert idea that collaboration among scientists --at least
+in the case of multi-authored articles-, is more similar to a ``snow-drift
+game'' than to a PD game, since in the former everybody wins or everybody pays a
+cost but the cost are not evenly distributed among the players.}\\
+
+We came by the idea that intra-networks are stronger than inter-networks, from
+another study about scientific collaborations based on co-authorships 
+\cite{HernandezLemus:2013}. In the cited reference, an apparently well
+integrated community was found (high clustering coefficient and a very short
+characteristic path length). Such integration was mostly superficial, since it
+depended on the presence of external collaborators from other research
+institutions (most of them from overseas).  Removing these external
+collaborators brakes down the network into small subgraphs that worked
+independently. Remarkably, those subgraphs corresponded to the real groups of
+that research center.  What is more, several groups had a hierarchical structure
+as the one we suspect is common in FOSISS subgraphs. The results showed that
+collaboration was poor between groups but strong among the members of each
+group, and that collaboration among groups doesn't emerge bottom-up, instead it
 seems to be promoted from the top, from the administrative
@@
 
-  We believe that the situation just referred is also
-  true for the whole biomedical research community in M\'exico. The
-  amount of PIs who have also been collaborators in other projects is
-  about one fifth of the total number of participants.  This is a
-  number big enough to connect the whole network in one giant
-  component. Yet, due to the topological characteristics of the FOSISS
-  network, it appears to be the case that researchers can be the
-  leaders in one project and collaborators in a different project of
-  \emph{its own research group}. CONACyT's funding policies makes it
-  impossible for a researcher to get a grant from a fund if that
-  researcher has an ongoing project with a grant from that same
-  fund. That is, a researcher can ask for a grant from FOSISS if and
-  only if at the moment he doesn't already have one.
-  This policy has lead researchers from the same group to ask
-  for grants from the same fund in order to rise their budgets. A
-  consequence of this behavior is that group interactions get
-  reinforced, but inter-group connections not necessarily so.\\
-
- As is common among scientific communities in biomedical
-  research, PIs play a central role in the network. Strong PIs and
-  well connected groups seem to be somehow responsible for the high
-  levels of strength of interactions and the centralization of utility
-  in our simulation. As for what seems to be phase transitions, in the
-  case of FOSISS networks, these are smoother than those in the other
-  networks with different topologies, even for those with a
-  small-world topology. We think that this behavior is also the result
-  of the hierarchical structure already mentioned. If this is true,
-  strength of interactions is first lost in the edges that link
-  different groups and then in the edges that connect members of the
-  groups. Connections between groups would not be as dense as those
-  inside the groups, which means that there would not be enough
-  information on the behavior of one group regarding its neighbors to
-  constrain them as it seems to happen with individual researchers
-  inside their communities. Nevertheless, if values of the parameter
-  of cooperation $\nu$ keep increasing and it becomes more difficult to
-  strengthen interactions, then strength of interactions begins to
-  diminish inside groups.\\
-
-  Another issue that we would like to mention about FOSISS network
-  topology is that it is not a robust collaboration network.  At the
-  level of groups, nodes might be well connected and consolidated but
-  at the level of the network, they could be no more than an aggregate
-  of individual groups. A robust network would be resistant to changes
-  in the connections between groups but in the case of FOSISS, it
-  seems that the network would brake down into small research groups
-  by cutting some edges, as it happened in our co-authorship
-  collaboration network \cite{HernandezLemus:2013}. The lack of
-  robustness might be indicative of the fact that resources stay
-  inside the groups, that is, they do not circulate through or
-  articulate different communities. For example, one may think of
-  certain expensive technologies for genomic research that could be
-  bought once and shared among research groups, however, this doesn't
-  seem to happen very often. There are some other consequences, such
-  as low communication among groups, atomization of practices and
-  know-hows, redundancy in equipment tenancy, difficulties in
-  implementing community-wide infrastructures such as biobanks,
+We believe that the situation just referred is also true for the whole
+biomedical research community in M\'exico. The amount of PIs who have also been
+collaborators in other projects is about one fifth of the total number of
+participants.  This is a number big enough to connect the whole network in one
+giant component. Yet, due to the topological characteristics of the FOSISS
+network, it appears to be the case that researchers can be the leaders in one
+project and collaborators in a different project of \emph{its own research
+  group}. CONACyT's funding policies makes it impossible for a researcher to get
+a grant from a fund if that researcher has an ongoing project with a grant from
+that same fund. That is, a researcher can ask for a grant from FOSISS if and
+only if at the moment he doesn't already have one.  This policy has lead
+researchers from the same group to ask for grants from the same fund in order to
+rise their budgets. A consequence of this behavior is that group interactions
+get reinforced, but inter-group connections not necessarily so.\\
+
+As is common among scientific communities in biomedical research, PIs play a
+central role in the network. Strong PIs and well connected groups seem to be
+somehow responsible for the high levels of strength of interactions and the
+centralization of utility in our simulation. As for what seems to be phase
+transitions, in the case of FOSISS networks, these are smoother than those in
+the other networks with different topologies, even for those with a small-world
+topology. We think that this behavior is also the result of the hierarchical
+structure already mentioned. If this is true, strength of interactions is first
+lost in the edges that link different groups and then in the edges that connect
+members of the groups.\\
+
+Connections between groups would not be as dense as those
+inside the groups, which means that there would not be enough information on the
+behavior of one group regarding its neighbors to constrain them as it seems to
+happen with individual researchers inside their communities. Nevertheless, if
+values of the parameter of cooperation $\nu$ keep increasing and it becomes more
+difficult to strengthen interactions, then strength of interactions begins to
+diminish inside groups. {\color {red}And yet, the smoothness observerd in the small-world
+network and FOSISS network may be attributed to the power of the clustering
+coefficient. As has been referred by Li and Cao \cite{Li-etal:2009}, and
+Thibert-Plante and Parrott \cite{Thibert-Plante-etal:2007} for scientific
+collaboration networks, high clustering coefficient allows the system to resist
+the invasion of non-cooperators.}\\
+
+Another issue that we would like to mention about FOSISS network topology is
+that it is not a robust collaboration network.  At the level of groups, nodes
+might be well connected and consolidated but at the level of the network, they
+could be no more than an aggregate of individual groups. A robust network would
+be resistant to changes in the connections between groups but in the case of
+FOSISS, it seems that the network would brake down into small research groups by
+cutting some edges, as it happened in our co-authorship collaboration network
+\cite{HernandezLemus:2013}. The lack of robustness might be indicative of the
+fact that resources stay inside the groups, that is, they do not circulate
+through or articulate different communities. For example, one may think of
+certain expensive technologies for genomic research that could be bought once
+and shared among research groups, however, this doesn't seem to happen very
+often. There are some other consequences, such as low communication among
+groups, atomization of practices and know-hows, redundancy in equipment tenancy,
+difficulties in implementing community-wide infrastructures such as biobanks,
 etc. \\

### 2017-04-04 research_areas_fosiss.tex
Table with the 37 research areas of FOSISS

\documentclass[9.5pt]{article}

\usepackage   [spanish]{babel}
\usepackage[utf8]{inputenc}

\begin{document}

\center{\Large{\bf FOSISS Research areas\\ \large{(Supplementary material)}}}
\begin{table}
\small
  \centering
\begin{tabular}{| l |}
\hline
\bf{Research areas (Spanish)} \\ \hline

ACCIDENTES Y LESIONES	\\ \hline
ACCIDENTES Y VIOLENCIA	\\ \hline
APOYO A LA INVESTIGACIÓN DE PROBLEMAS ESPECIFICOS\\ DE SALUD EN LAS REGIONES DEL PAÍS \\ \hline
DESARROLLO DE NUEVOS TRATAMIENTOS DE LA DIABETES Y\\ OBESIDAD Y SUS COMPLICACIONES.			\\ \hline
DESARROLLO DE TECNOLOGÍAS PARA LA SALUD			\\ \hline
DESARROLLO Y EVALUACIÓN DE TECNOLOGÍAS PARA LA SALUD			\\ \hline
EDUCACIÓN PARA LA SALUD			\\ \hline
ENFERMEDADES CRÓNICAS			\\ \hline
ENFERMEDADES CRÓNICAS O DEGENERATIVAS			\\ \hline
ENFERMEDADES DEL REZAGO Y EMERGENTES			\\ \hline
ENFERMEDADES INFECCIOSAS Y PARASITARIAS			\\ \hline
ENTORNO SOCIAL Y TRANSICIÓN DEMOGRÁFICA			\\ \hline
ESTRATEGIAS DE INVESTIGACIÓN DIRIGIDAS A PREVENIR\\ LA DIABETES Y OBESIDAD Y SUS COMPLICACIONES.			\\ \hline
ESTUDIO DE LA INTERACCIÓN ENTRE LOS GENES Y\\ EL AMBIENTE EN EL DESARROLLO DE LA DIABETES Y OBESIDAD.			\\ \hline
ÉTICA Y SALUD			\\ \hline
EVALUACIÓN DEL DESEMPEÑO E IMPACTO DE LOS SERVICIOS DE SALUD			\\ \hline
FACTORES GENÉTICOS Y AMBIENTALES QUE MODIFICAN EL RIESGO\\ DE DESARROLLAR DIABETES Y OBESIDAD EN POBLACIONES.			\\ \hline
GRUPOS VULNERABLES			\\ \hline
INFLUENZA			\\ \hline
INVESTIGACIÓN SOCIAL EN GRUPOS ESPECIALES			\\ \hline
MEDIO AMBIENTE Y SALUD			\\ \hline
NEOPLASIAS MALIGNAS			\\ \hline
NEOPLASIAS MALIGNAS EN NIÑOS Y ADULTOS			\\ \hline
PADECIMIENTOS CONGÉNITOS O DE ORIGEN GENÉTICO			\\ \hline
PADECIMIENTOS ESTOMATOLÓGICOS			\\ \hline
SALUD AMBIENTAL Y RIESGOS DERIVADOS POR LOS CAMBIOS CLIMÁTICOS			\\ \hline
SALUD MENTAL Y ADICCIONES			\\ \hline
SALUD OCUPACIONAL			\\ \hline
SALUD REPRODUCTIVA Y MEDICINA PERINATAL			\\ \hline
SALUD REPRODUCTIVA Y PERINATAL			\\ \hline
SISTEMAS DE SALUD, ECONOMÍA DE LA SALUD Y SEGURIDAD SOCIAL			\\ \hline
TOXICOLOGÍA			\\ \hline
TRASPLANTES Y PRESERVACIÓN DE ÓRGANOS, CÉLULAS,\\ CÉLULAS TRONCALES Y TEJIDOS			\\ \hline
TRASTORNOS DE LA NUTRICIÓN			\\ \hline
TRASTORNOS LIGADOS AL ESTILO DE VIDA			\\ \hline
TRASTORNOS PSIQUIÁTRICOS, NEUROLÓGICOS Y SALUD MENTAL			\\ \hline
TRASTORNOS PSIQUIÁTRICOS O NEUROLÓGICOS			\\ \hline

\end{tabular}
\end{table}
\end{document}

### 2017-04-05 casm.tex
Finished conclusions and added Conte et al reference

@@
 Another interesting behavior explored by game-theoretical modeling and
-complex networks has been done by Li and Cao \cite{Li-etal:2009}. This
+complex networks has been done by Li and Cao \cite{Li-etal:2009}. These
 authors analyze the role of punishment in a science collaboration
@@
 
-{\color{red}In a similar vein to the work of Li and Cao,} we explore the network
-effect on the distribution of players having access to certain amount of
-resources shared by other players in the network and the distribution of the
-strength of interactions among them. Particularly, we implemented two games
-played simultaneously: one for maximizing individual utility based on the
-iterated Prisoner's Dilemma (PD); the other, a coordination game for maximizing the
-connection strength between players. We are interested in how they affect each
-other in the context of a network of scientific collaboration under the idea
-that while researchers are interested in maximizing their utilities, they also
-know that it is important to invest in building collaborative
-relationships. \\ %This is important because what we have seen
+{\color{red} In our model we explore the network effect on two issues: a) the distribution of the amount of
+resources players can access from other players and, b) the distribution of the strength of
+interactions among players as they interact. Also, in a similar
+vein to the work of Li and Cao, we explore how resistant are the different
+topologies to defection as it becames harder for the population to cooperate.}
+Particularly, we implemented two games played simultaneously: one for maximizing
+individual utility based on the iterated Prisoner's Dilemma (PD); the other, a
+coordination game for maximizing the connection strength between players. We are
+interested in how they affect each other in the context of a network of
+scientific collaboration under the idea that while researchers are interested in
+maximizing their utilities, they also know that it is important to invest in
+building collaborative relationships.
+\\ %This is important because what we have seen
 
@@
 
-  On these grounds, part of our future work is based on the results
-  presented here. We would like to identify researchers in our
-  simulations and corroborate their situation in the model and in the
-  real world. We are also interested in going back to the field and
-  interviewing those groups with an interesting behavior found in our
-  simulations, we would probably follow a similar strategy as the one
-  developed in \cite{Hara:2003}. Finding communities beyond the level
-  of the groups is an important task. We think that there are many
-  possibilities that emerge from the integration of different
-  methodologies. Moreover, studying social processes in science is
-  particularly attractive due to the amounts of data already available
-  that can be easily collected. This is a privilege because
-  simulations can be designed on real world data, something that only
-  very recently has become possible \cite{Barabasi:2012}.\\
-
 \section*{Conclusions}
 
-No doubt social sciences are becoming more ``computational''. This can
-be seen everywhere, but curiously enough, disciplines like physics
-and computer science are moving towards the social
-sciences and not so much the other way around. It might be the case
-that the pioneering disciplines in the computational social sciences
-will set the agenda, an agenda that will apparently be mostly based on
-taking advantage of big data and on hypothesis-free approaches. We
-believe that the social sciences have important questions that should
-be added to that agenda and those questions may not be answered only
-by big data techniques but they may require creating models and
-simulations in the style of the best hypothesis-driven research.
+Our future work is based on the results presented here. We would like to
+identify researchers in our simulations and corroborate their situation in the
+model and in the real world. We are also interested in going back to the field
+and interviewing those groups with an interesting behavior found in our
+simulations, we would probably follow a similar strategy as the one developed in
+\cite{Hara:2003}. Another idea we would like to follow is related to the
+parameter $\nu$. As it is now implemented in the model, $\nu$ is an external
+parameter to the system but in future work we would like to explore the
+possibility of $\nu$ being controlled by the dynamics of the system. The
+assumption behind this idea is that society self-imposes norms and it
+dynamically regulates how difficult is for its members to comply. In our model
+we used this parameter to control how hard or easy is for a player to
+cooperate. Finding communities beyond the level of the groups is an important
+task. We think that there are many possibilities that emerge from the
+integration of different methodologies. Moreover, studying social processes in
+science is particularly attractive due to the amounts of data already available
+that can be easily collected. This is a privilege because simulations can be
+designed on real world data, something that only very recently has become
+possible \cite{Barabasi:2012}.\\
+
+No doubt social sciences are becoming more ``computational''
+\cite{Conte-etal:2012}. This can be seen everywhere, but curiously enough,
+disciplines like physics and computer science are moving towards the social
+sciences and not so much the other way around. It might be the case that the
+pioneering disciplines in the computational social sciences will set the agenda,
+an agenda that will apparently be mostly based on taking advantage of big data
+and on hypothesis-free approaches. We believe that the social sciences have
+important questions that should be added to that agenda and those questions may
+not be answered only by big data techniques but they may require creating models
+and simulations in the style of the best hypothesis-driven research.
 
@@
 for their work curating databases of researchers. We are grateful to
-Be Luecke for copy editing the manuscript.
+Be Luecke for copy editing the manuscript. We would also like to thank to the
+reviewers for their comments and suggestions.
 

### 2017-04-05 casm.tex
Added reference to supplementary material --research areas table-.OF

@@
 
-Even though curation and analysis work of this database is still going
-on, some relevant facts about the biomedical research can be
-said. Over the period of 12 years, 37 general research areas have been
-defined, the three most funded research areas are \emph{chronic and
-  degenerative diseases}, \emph{malignant neoplasms}, and
-\emph{infectious and parasitic diseases}. The least funded area is
-\emph{Ethics and medicine}. The area with the most researchers is
+Even though curation and analysis work of this database is still going on, some
+relevant facts about the biomedical research can be said. Over the period of 12
+years, 37 general research areas have been defined, the three most funded
+research areas are \emph{chronic and degenerative diseases}, \emph{malignant
+  neoplasms}, and \emph{infectious and parasitic diseases}. The least funded
+area is \emph{Ethics and medicine}. The area with the most researchers is
 \emph{malignant neoplasms}. Other areas of relevance for M\'exico are
 \emph{diseases related to poverty} and \emph{Health and vulnerable
-  groups}. \\
+  groups} {\color{red}(See Supplementary material)}.\\
 
